### 2019-05-10 main.tex
Initial Overleaf Import

\documentclass[a4paper,12pt]{article}
\usepackage{titling}
\usepackage{lscape}
\usepackage{amssymb, amsmath, amssymb}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage[stable]{footmisc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scale=.8]{FiraMono}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage{float}
\usepackage[top=2.1cm, bottom=2.1cm, left=2.1cm, right=2.1cm]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{dcolumn}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{mathtools}
\usepackage{caption}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[authoryear]{natbib}
\usepackage{babelbib}
\cleanlookdateon
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=10000
\clubpenalty=10000
\setcitestyle{aysep={}} 
\usepackage{etoolbox}
\makeatletter
\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
	\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
		   {\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
	  {}{}
\makeatother
\usepackage{hyperref}

\hypersetup{
	pdftitle={Do Elites Support Polycentric Climate Governance?},
	pdfauthor={Danilo Freire, Umberto Mignozzetti, and David Skarbek},
	pdfsubject={Climate change governance},
    pdfkeywords={climate change, conjoint experiment, elites, Latin America, polycentrism},
	pdfborder={0 0 0},
	breaklinks=true,
	linkcolor=Mahogany,
	citecolor=Mahogany,
	urlcolor=darkblue,
	colorlinks=true} %

\doublespacing

\title{Do Elites Support Polycentric Climate Governance? Evidence from Ten Latin American Countries\thanks{We thank Nigel Ashford, F\'{a}bio Barros, Daniel D'Amico, Malte Hendricks, Christian H\"{u}bner, Karina Marzano, Emily Skarbek, and Matias Spektor for helpful and engaging feedback. This research received financial support from the Konrad Adenauer Stiftung Latin American Regional Programme for Energy Security and Climate (EKLA-KAS). The authors declare there are no conflicts of interest. The data, code, and any additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.}}

\author{Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, \href{mailto:danilo_freire@brown.edu}{\texttt{danilo\_freire@brown.edu}}, \href{http://danilofreire.github.io}{\texttt{http://danilofreire.github.io}}, \href{http://twitter.com/danilofreire}{\texttt{http://twitter.com/danilofreire}}, Voice: +1 (401) 584-2494. Corresponding author.} 
\and Umberto Mignozzetti\thanks{School of International Relations, Funda\c{c}\~{a}o Getulio Vargas, S\~{a}o Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, \href{mailto:umberto.mig@nyu.edu}{\texttt{umberto.mig@nyu.edu}}, \href{http://umbertomig.com}{\texttt{http://umbertomig.com}}, \href{http://twitter.com/umbertomig}{\texttt{http://twitter.com/umbertomig}}.} \and David Skarbek\thanks{The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \href{http://davidskarbek.com}{\texttt{http://davidskarbek.com}}, \href{http://twitter.com/davidskarbek}{\texttt{http://twitter.com/davidskarbek}}.}
}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\onehalfspacing
\noindent
Policy-makers generally assume that climate change mitigation requires global scale governance. Conversely, recent studies suggest that decentralised approaches can better cope with climate problems. But despite the large social impact each solution implies, it is unclear which political arrangement potential veto players support. Here we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate 6,000 possible climate change agreements that vary across six dimensions. We find that institutional features have a substantial effect on support for climate treaties. Overall, Latin American elites prefer state-based solutions to global warming, but there is considerable heterogeneity across countries and elite types. Our results suggest novel ways to craft accountable, democratic climate change mitigation agreements, and also offer new insights on how to integrate interventions at the local and international levels.

\vspace{.5cm}

\noindent 
\textbf{Keywords:} climate change, conjoint experiment, elites, Latin America, polycentrism

\vspace{.5cm}

\noindent 
\textbf{Word count:} 3,000
\end{abstract}

\newpage

\doublespacing

\section{Introduction}%
\label{sec:introduction}

Over the last years, we have seen an emerging consensus about the causes and consequences of anthropogenic climate change. Despite some variation in climate risk beliefs, mostly due to cultural worldviews and political orientation \citep{hornsey2016meta}, recent surveys show that the public is increasingly aware of the dangers of greenhouse gas emissions. For example, 59\% of Americans are sure the Earth's temperature is increasing \citep{stanfordearth2018}; 74\% of European Union citizens consider global warming a `very serious problem' \citep{europe2018survey}; and 90\% of Brazilians believe climate change is already harming people around the world \citep{pew2018climate}.

Yet this consensus does not translate itself into effective political action. Global climate negotiations have progressed slowly under the guidelines of the United Nations Framework Convention on Climate Change (UNFCCC), and there is wide scepticism that multilateral talks will move faster in the next years \citep{cole2015advantages, hjerpe2015views}. As carbon dioxide emissions continue to increase, current efforts are likely to be insufficient to meet the Paris Agreement target of $2^{\circ}$C temperature rise above pre-industrial levels \citep{jordan2015emergence}. Existing research affirms that this unsatisfactory performance is partially due to institutional design \citep{ostrom2014polycentric, cole2015advantages}. For instance, multilateral forums downplay the domestic constraints political leaders experience when implementing strategies to reduce greenhouse gas emissions \citep{rayner2010eat}. Universal binding agreements also offer limited scope for experimentation, which hinders the ability for individuals to solve complex collective action problems \citep{de2014global}.

More recently, scholars have argued that polycentric governance approaches provide a better `institutional fit' for natural resource systems \citep{turnheim2018innovating,berkhout2003negotiating, carlisle2017polycentric, ostrom1990governing}. Polycentrism is defined as a political arrangement in which formally independent units operating at different levels engage in a continuous process of cooperation and competition \citep{cole2015advantages,aligica2013co}. Experiences such as inshore fisheries in Turkey or timber management in Switzerland show that polycentrism induces individual cooperation and allows communities to avoid the `tragedy of the commons', that is, the overexploitation of shared resources \citep{hardin1968tragedy, ostrom1990governing}. Authors also point out that polycentrism promotes quick adaptation to bad use of public resources because of continuous experimentation at smaller scales \citep{turnheim2018innovating,ostrom2012nested,ostrom2014polycentric,sovacool2013adaptation}.

% Rewrite last sentence

Despite their potential advantages, two challenges may undermine the support for multilevel arrangements. On the one hand, pluralistic systems demand high levels of participation. Since climate change has diffuse benefits but concentrated costs, individuals have a strong incentive not to join collective efforts \citep{barrett2003increasing, heitzig2011self, nordhaus2015climate}. On the other hand, individuals tend to heavily discount climate change investments \citep{dasgupta2008discounting, nordhaus1997discounting}. Reducing carbon emissions requires significant expenditures today, yet the benefits of climate mitigation will arise only in a distant future. In that regard, citizens might prefer state-based initiatives to prevent climate change if private costs are too high or expected results too uncertain to encourage voluntary action.

% Maybe write a paragraph about elites and veto players?

We design a conjoint experiment to assess which type of climate change governance system Latin American elites are willing to support. Conjoint experiments allow respondents to evaluate two competing profiles that vary across multiple dimensions of interest, and under sensible assumptions, they can estimate the causal impact of each factor on the respondent's decision \citep{bansak2016economic, hainmueller2014causal}. In our survey, we asked 651 `elites' -- academics, members of the executive power, legislators, businesspeople, and members of non-governmental organisations -- to select their preferred agreement in 7 randomised binary choices. We recruited respondents from Argentina, Brazil, Bolivia, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.

In what follows, we describe our experimental methods and results. We then turn to two additional analyses, in which we disaggregate the responses according to country and elite type, and proceed to the concluding remarks.

\section{Research Design}%
\label{sec:research_design}

We chose to survey Latin American elites for several reasons. First, Latin America is the most bio-diverse region in the world. The Amazon river basin is the largest preserved forest on Earth, and it contains about half of the world's carbon stock \citep{yang2018post}. Second, the region remains largely dependent on agriculture, so global warming will severely disrupt Latin American economies \citep{jones2003potential}. Lastly, Latin American elites have vast disagreements about societal issues. For instance, the rapid shifts between leftist and rightist governments, along with growing ideological polarisation in the region, indicate that local elites are not a cohesive social group  \citep{ellner2019pinktide}. Latin American elites are capable of influencing if climate change solutions are pursued, but they might disagree more on which particular solutions to pursue.

We formulate our experiment according to Elinor Ostrom's `design principles' of successful common pool resource management and selected our category values according to them \citep{ostrom1990governing, bechtel2013mass}. The hypothetical climate change agreements includes six dimensions: 1) which organisation defines the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated. Table~\ref{tab:categories} describes the values we included in each design principle. \\

\begin{table}[ht]
  \begin{center}
      \caption{\textbf{Design principles for climate change mitigation conjoint experiments.}}
      \label{tab:categories}
    \begin{tabular}{l|l}
      \toprule
      \textbf{Design principle} & \textbf{Values} \\
      \midrule
      Who makes the rules? & International organisations \\ 
	  & Federal government \\ 
	  & Local government \\ 
	  & Local community members \\
	  & Non-Governmental organisations \\
	  & \\
      Conflict resolution mechanism & United Nations \\
	  & Government bureaucracy \\
	  & Local courts \\
	  & Private arbitration \\
	  & Informal norms \\
	  & \\
      Punishment & Imprisonment \\
	  & Fines \\
	  & Blacklist \\
	  & None \\
	  & \\
	  Punishment for repeated violations & More penalty \\
	  & Same \\
	  & Less penalty \\
	  & \\
	  Agreement costs & Rich countries pay more than poor countries \\
      & Proportional to history of emissions \\ 
      & Proportional to current emissions \\
	  & Only rich countries pay\\
	  & \\
	  Renegotiation & Never \\
	  & Fifty years \\
	  & Twenty years \\
	  & Five years \\
	  & One year \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

Our six principles correspond to a standard set of resolutions international treaties are expected to cover. However, the categories open the possibility for respondents to combine multiple levels of governance into a single climate change agreement as they see fit. We give no prior indication of whether a certain value is more prevalent in actual agreements, and we randomise the values to ensure that they all have the same probability of being selected. In total, there are 6,000 possible value combinations. Figure~\ref{fig:conjoint} illustrates our experimental design.\\

\begin{figure}[H]
	\centering
	\includegraphics[width=12cm,angle=270,origin=c]{conjoint.pdf}
	\caption{\textbf{Example of conjoint experiment design.} We presented respondents with 7 binary choices similar to this one. The values for the six design principles were randomly sampled from our list of attributes. More information is available in the Supplementary Appendix.}
	\label{fig:conjoint}
\end{figure}

Figure~\ref{fig:pooled} shows our main results. The findings indicate that Latin American elites have a strong preference for a polycentric approach to mitigate climate change. We see that the respondents have a positive view about two sources of climate governance, namely those located at the international and the local levels. Importantly, Latin American elites support both levels \textit{simultaneously}; this provides evidence that they favour agreements which incorporate action separate political spheres at the same time in the same regime.

\begin{figure}[H]
	\centering
	\includegraphics[width=.9\linewidth]{pooled.pdf}
	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement in 10 Latin American countries (pooled data).} The horizontal bars correspond to the 95\% confidence interval of the estimated effect. Standard errors are clustered by respondent (respondents = 651; comparisons = 7,968). Full numerical estimates are available in the Supplementary Information Appendix.}
	\label{fig:pooled}
\end{figure}

Climate change agreements designed by international organisations are viewed more favourably than the alternatives. Global institutions receive 54\% (SE = 1.25) of acceptance in our sample. At the same time, respondents clearly indicate their preference for bottom-up rule-making. Agreements formulated by local community members and local governments are the second and third-preferred choices with 51.6\% (SE = 1.25) and 49.8\% (SE = 1.24) approval. In contrast, Latin American elites see non-governmental organisations are their least preferred option for climate change rule-making with 45.5\% (SE = 1.26).

We see a similar pattern with respect to conflict resolution. Respondents suggest disputes should be addressed mainly by the United Nations and local courts. These two choices have 57.3\% (SE = 1.22) and 54.6\% (SE = 1.23) approval, respectively. Private arbitration comes next with 50\% (SE = 1.26), followed by government bureaucracy with 46.4\% (SE = 1.25). Informal norms is the least preferred mechanism to deal with conflicts between agreement parties (41\%, SE = 1.25).

In line with Ostrom's predictions, Latin American elites agree with graduated sanctions to repeated offenders (53.2\%, SE = 0.94) and they believe agreement costs should be allocated according to the country's history of emissions (53.6\%, SE = 1.14). Moreover, related to the same idea of proportionality, respondents indicate that lawbreakers should be punished with fines (55.3\%, SE = 1.06), which can be easily increased if necessary.

We find no evidence that rich countries alone should bear the burden of climate change mitigation costs. Latin American elites believe developing countries should also contribute to the provision of global public goods. This suggests that elites view it was legitimate to contribute to climate change solutions, so this may not be a major source of free riding to climate change solutions in the region.

In terms of agreement duration, respondents are interested in a balance between stability and flexibility. This also lends support to Elinor Ostrom's theory of polycentric climate change governance. Agreements that either cannot be modified or that last for 50 years are rejected by the interviewees. Their preference lies in agreements that can be renegotiated every five years (59\%, SE = 1.2), as they are durable enough to provide long-term incentives to the parties, yet still adaptable to unforeseen demands.

We also examine if our results vary across countries and types of elites. Figure~\ref{fig:countries} displays the preferred climate change agreement characteristics for each of the 10 countries in our sample. Despite Latin America's wide social heterogeneity, we observe that the results are notably similar. Most respondents affirm that the United Nations should be responsible for resolving conflicts, and six of them place local courts as the second-preferred choice. Peruvian elites are the only to prefer private arbitration to mediate disputes (60.7\%, SE = 4.5). We see that respondents in eight out of ten countries are willing to apply fines as punishment for agreement violators, with Chileans and Ecuadorians stating they would rather blacklist defectors. The majority also prefers to employ more penalties to repeated offenders.

Another interesting cross-country similarity is that our sample largely supports agreements that can be renegotiated every five or twenty years. The difference is particularly wide in Costa Rica, where five-year agreements receive 29.4\% more approval than treaties that will never be revised. Chileans, in contrast, have the largest gap between one-year and five-year agreements: 22.7\%. Two possible explanations is that Chilean elites are either sensitive to transaction costs of negotiating repeated agreements, or they worry that one-year treaties may not provide enough stability for collective action.

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{countries.pdf}
	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by country.} Bars represent 95\% confidence intervals.}
	\label{fig:countries}
\end{figure}

There are some interesting differences about which institutions should make the agreement rules. Argentinians are particularly sceptical about local community members (44.9\%, SE = 4.4) and favourable towards international organisations (61.9\%, SE = 4.1), whereas Bolivians believe local communities (57.5\%, SE = 5.3) and governments (55.9\%, SE = 5.4) are the best source for climate change rules. Respondents in most countries place NGOs as their least-preferred option, but elites from Brazil and Costa Rica have a more positive view of these organisations. Federal governments receive the lowest support in Chile, but respondents have the highest preference for local communities with 63\% (SE = 3.9).

Figure~\ref{fig:types} shows the results disaggregated by elite type. We find that several positions are comparable across all subgroups. Academics, members of the civil society, and representatives in the executive and legislative branches hold similar views about how conflicts should be resolved, what punishment to apply to lawbreakers (fines and blacklisting), and the duration of the agreements.

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{types.pdf}
	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by elite type.} Bars represent 95\% confidence intervals.}
	\label{fig:types}
\end{figure}

Differences emerge in two of the six dimensions of interest. First, whereas academics and members of the civil society are less favourable to allowing the federal government to formulate the rules, members of the executive and the legislative -- part of federal government themselves -- are more likely to see themselves as the preferred rule-makers. Second, members of the legislative have a stronger opinion that rich countries should bear the larger part of the agreement costs (58.4\%, SE = 3.5).

\section*{Discussion}
\label{sec:discussion}

In this article, we analyse whether Latin American elites support a polycentric climate change mitigation regime. We find that respondents prefer climate agreements that incorporate multiple government institutions, mainly international and local-level organisations. The results remain stable after disaggregating the data by country and elite composition. Our experiment also validates the importance of Elinor Ostrom's `design principles' as respondents largely act as her theory predicts. But despite the many similarities in the responses, we observe that national and occupational characteristics still influence how elites perceive the costs and benefits of carbon emission agreements.

Our results have meaningful theoretical and practical implications. The findings we present here suggest there is considerable scope for new studies on polycentrism. For example, our analysis can be extended to examine if the Latin American public has the same opinion on multilevel arrangements as do the elites; and if not, it would be important to ask what explains the mismatch between groups. Moreover, future work may address whether other areas of scholarship which assume international-level coordination could benefit from Ostromian polycentricity.

We also provide experimental evidence that individuals have preferences that are not fully represented in current climate change agreements. We identify that Latin American elites are interested not only in incorporating local demands into the current framework, but also in strengthening the role international organisations play in climate governance. In our view, these are reasons for optimism. They indicate willingness to engage under-represented sectors of the civil society while at the same time promoting broad, consensus-based carbon emission agreements. Polycentricity, in that regard, may provide the trust and accountability this complex system requires.

\section*{Supplementary Material}
\label{sec:supplementary}

To view supplementary material for this article, please visit \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.

\newpage

\bibliographystyle{apalike}
\bibliography{references.bib}

\end{document}

### 2019-05-10 main.tex
Add longtable

@@
 \usepackage{makecell}
+\usepackage{float}
+\floatplacement{figure}{H}
+\usepackage{longtable}
 \usepackage[stable]{footmisc}
@@
 \usepackage{float}
-\usepackage[top=2.1cm, bottom=2.1cm, left=2.1cm, right=2.1cm]{geometry}
+\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
 \usepackage{graphicx}
@@
 \usepackage{dcolumn}
-\usepackage{float}
-\floatplacement{figure}{H}
 \usepackage{mathtools}
@@
 
-More recently, scholars have argued that polycentric governance approaches provide a better `institutional fit' for natural resource systems \citep{turnheim2018innovating,berkhout2003negotiating, carlisle2017polycentric, ostrom1990governing}.
+More recently, scholars have argued that polycentric approaches provide a better `institutional fit' for natural resource systems \citep{turnheim2018innovating,berkhout2003negotiating, carlisle2017polycentric, ostrom1990governing}.
 Polycentrism is defined as a political arrangement in which formally independent units operating at different levels engage in a continuous process of cooperation and competition \citep{cole2015advantages,aligica2013co}.
-Experiences such as inshore fisheries in Turkey or timber management in Switzerland show that polycentrism induces individual cooperation and allows communities to avoid the `tragedy of the commons', that is, the overexploitation of shared resources \citep{hardin1968tragedy, ostrom1990governing}.
-Authors also point out that polycentrism promotes quick adaptation to bad use of public resources because of continuous experimentation at smaller scales \citep{turnheim2018innovating,ostrom2012nested,ostrom2014polycentric,sovacool2013adaptation}.
-
-% Rewrite last sentence
+Experiences such as inshore fisheries in Turkey and timber management in Switzerland show that polycentrism induces individual cooperation and allows communities to avoid the `tragedy of the commons', that is, the overexploitation of shared resources \citep{hardin1968tragedy, ostrom1990governing}.
+Authors also point out that polycentric systems improve accountability as decentralisation reduces rent-seeking opportunities for interest groups \citep{turnheim2018innovating,ostrom2012nested,ostrom2014polycentric,sovacool2013adaptation}.
 
@@
 
-% Maybe write a paragraph about elites and veto players?
+Self-enforcing environmental governance faces further difficulties in new democracies.
+In Latin America, authoritarian regimes discouraged civil participation and reduced social capital, two requirements for effective polycentric arrangements \citep{aligica2014institutional,ostrom1990governing}.
+Top-down climate policies also create incentives for organised groups to collude with state officials and pursue private interests.
+In that scenario, elites and state representatives have \textit{de facto} veto power over environmental legislation and can override local decisions to their own benefit.
 
@@
 
-We chose to survey Latin American elites for several reasons.
-First, Latin America is the most bio-diverse region in the world.
-The Amazon river basin is the largest preserved forest on Earth, and it contains about half of the world's carbon stock \citep{yang2018post}.
-Second, the region remains largely dependent on agriculture, so global warming will severely disrupt Latin American economies \citep{jones2003potential}.
-Lastly, Latin American elites have vast disagreements about societal issues.
-For instance, the rapid shifts between leftist and rightist governments, along with growing ideological polarisation in the region, indicate that local elites are not a cohesive social group  \citep{ellner2019pinktide}.
-Latin American elites are capable of influencing if climate change solutions are pursued, but they might disagree more on which particular solutions to pursue.
+We conducted our experiment in 10 Latin American countries.
+Latin America is the most biodiverse region in the world and it remains largely dependent on agriculture, thus global warming can severely disrupt the regional environment and economy \citep{jones2003potential, yang2018post}.
+Moreover, survey experiments on climate policies have focused on a small set of developed countries, so truly comparative experimental work is still scarce.
+We fill this gap by including countries in South, Central, and North America where local elites have different stakes at climate change negotiations.
 
-We formulate our experiment according to Elinor Ostrom's `design principles' of successful common pool resource management and selected our category values according to them \citep{ostrom1990governing, bechtel2013mass}.
 The hypothetical climate change agreements includes six dimensions: 1) which organisation defines the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated.
+The categories map conceptual differences between polycentric and state-led climate mitigation policies \citep{bechtel2013mass, ostrom1990governing}.
 Table~\ref{tab:categories} describes the values we included in each design principle.
@@
 
-\begin{table}[ht]
-  \begin{center}
-      \caption{\textbf{Design principles for climate change mitigation conjoint experiments.}}
-      \label{tab:categories}
-    \begin{tabular}{l|l}
-      \toprule
-      \textbf{Design principle} & \textbf{Values} \\
-      \midrule
+\begin{longtable}{l|l}
+\caption{Design principles for climate change mitigation conjoint experiments} \label{tab:categories} \\
+
+\hline \multicolumn{1}{c|}{\textbf{Attribute}} & \multicolumn{1}{c}{\textbf{Values}}\\ \hline 
+\endfirsthead
+
+\multicolumn{2}{c}%
+{{\tablename \thetable{} Design principles for climate change mitigation conjoint experiments (\textit{cont.})}} \\
+\hline \multicolumn{1}{c|}{\textbf{Attribute}} & \multicolumn{1}{c}{\textbf{Values}} \\ \hline 
+\endhead
+
+\hline \multicolumn{2}{r}{{\textit{Continued on next page}}} 
+\endfoot
+
+\hline
+\endlastfoot
+
 Who makes the rules? & International organisations \\ 
@@
 & None \\
-	  & \\
 Punishment for repeated violations & More penalty \\
@@
 & Five years \\
-	  & One year \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
+& One year\\
+\end{longtable}
 

### 2019-05-12 main.tex
intro and methods

@@
 \noindent
-Policy-makers generally assume that climate change mitigation requires global scale governance.
-Conversely, recent studies suggest that decentralised approaches can better cope with climate problems.
-But despite the large social impact each solution implies, it is unclear which political arrangement potential veto players support.
-Here we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate 6,000 possible climate change agreements that vary across six dimensions.
+Policy makers generally assume that climate change mitigation requires global scale governance.
+In contrast, recent studies suggest that polycentrism provides an effective alternative to top-down environmental policies.
+But despite the high social costs each solution implies, it is unclear which institutional arrangement potential veto players support.
+Here we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate 6,000 possible climate change agreements.
 We find that institutional features have a substantial effect on support for climate treaties.
-Overall, Latin American elites prefer state-based solutions to global warming, but there is considerable heterogeneity across countries and elite types.
-Our results suggest novel ways to craft accountable, democratic climate change mitigation agreements, and also offer new insights on how to integrate interventions at the local and international levels.
+Latin American elites prefer state-based solutions to global warming, but there is considerable heterogeneity across countries and elite types.
+Our results suggest novel ways to craft accountable, democratic climate change mitigation agreements, and they offer new insights on how to integrate interventions at the local and international levels.
 
@@
 
-More recently, scholars have argued that polycentric approaches provide a better `institutional fit' for natural resource systems \citep{turnheim2018innovating,berkhout2003negotiating, carlisle2017polycentric, ostrom1990governing}.
+Recently, scholars have argued that polycentric approaches provide a better `institutional fit' for natural resource systems \citep{turnheim2018innovating,berkhout2003negotiating, carlisle2017polycentric, ostrom1990governing}.
 Polycentrism is defined as a political arrangement in which formally independent units operating at different levels engage in a continuous process of cooperation and competition \citep{cole2015advantages,aligica2013co}.
@@
 
-Despite their potential advantages, two challenges may undermine the support for multilevel arrangements.
-On the one hand, pluralistic systems demand high levels of participation.
-Since climate change has diffuse benefits but concentrated costs, individuals have a strong incentive not to join collective efforts \citep{barrett2003increasing, heitzig2011self, nordhaus2015climate}.
-On the other hand, individuals tend to heavily discount climate change investments \citep{dasgupta2008discounting, nordhaus1997discounting}.
+Despite the potential advantages of polycentric arrangements, two challenges may undermine their popular support.
+First, polycentric systems demand constant civic participation at multiple government levels.
+But as climate change has diffuse benefits but concentrated costs, individuals have few incentives to join collective efforts \citep{barrett2003increasing, heitzig2011self, nordhaus2015climate}.
+Second, individuals tend to heavily discount climate change investments \citep{dasgupta2008discounting, nordhaus1997discounting}.
 Reducing carbon emissions requires significant expenditures today, yet the benefits of climate mitigation will arise only in a distant future.
-In that regard, citizens might prefer state-based initiatives to prevent climate change if private costs are too high or expected results too uncertain to encourage voluntary action.
+In that regard, citizens might prefer state-based initiatives to prevent climate change if private costs are too high or expected results too uncertain.
 
-Self-enforcing environmental governance faces further difficulties in new democracies.
+Voluntary environmental governance faces further difficulties in new democracies.
 In Latin America, authoritarian regimes discouraged civil participation and reduced social capital, two requirements for effective polycentric arrangements \citep{aligica2014institutional,ostrom1990governing}.
@@
 
-We design a conjoint experiment to assess which type of climate change governance system Latin American elites are willing to support.
-Conjoint experiments allow respondents to evaluate two competing profiles that vary across multiple dimensions of interest, and under sensible assumptions, they can estimate the causal impact of each factor on the respondent's decision \citep{bansak2016economic, hainmueller2014causal}.
-In our survey, we asked 651 `elites' -- academics, members of the executive power, legislators, businesspeople, and members of non-governmental organisations -- to select their preferred agreement in 7 randomised binary choices.
+We design a conjoint experiment to assess which climate change governance system Latin American elites are willing to support.
+In our survey, we asked 654 `elites' -- academics, members of the executive power, legislators, businesspeople, and members of non-governmental organisations -- to select their preferred agreement in 7 randomised binary choices.
 We recruited respondents from Argentina, Brazil, Bolivia, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
@@
 
-We conducted our experiment in 10 Latin American countries.
-Latin America is the most biodiverse region in the world and it remains largely dependent on agriculture, thus global warming can severely disrupt the regional environment and economy \citep{jones2003potential, yang2018post}.
-Moreover, survey experiments on climate policies have focused on a small set of developed countries, so truly comparative experimental work is still scarce.
-We fill this gap by including countries in South, Central, and North America where local elites have different stakes at climate change negotiations.
+We use a conjoint experiment to analyse how institutional characteristics shape support for climate change agreements in Latin America.
+First, Latin America is the most biodiverse region in the world and it plays a major role in global climate mitigation projects.
+For instance, the Amazon basin contains about half of the world's carbon stock, so local elites are crucial actors in emissions trading markets \citep{yang2018post}.
+Second, Latin American elites have wide disagreements over preservations policies, and the recent shift towards populist governments has highlighted the need for a robust framework to protect environmental resources \citep{ellner2019pinktide}.
+In that regard, veto players can counterbalance governmental time discounting and secure the long-term provision of public goods.
+Lastly, survey experiments on climate policies have focused on a small set of developed countries, so truly comparative experimental work is still scarce.
+We fill this gap by analysing 10 countries where elites have different stakes at climate change negotiations.
 
-The hypothetical climate change agreements includes six dimensions: 1) which organisation defines the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated.
-The categories map conceptual differences between polycentric and state-led climate mitigation policies \citep{bechtel2013mass, ostrom1990governing}.
-Table~\ref{tab:categories} describes the values we included in each design principle.
+We use an original dataset compiled specifically for this study.
+The sampling process was as follows.
+From 1st of October to 5th of December 2018, we ran an elite survey in ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
+The survey proceeded in two steps.
+We started by collecting information on Latin American elites.
+Our target was to interview 10 members of the Executive, 10 members of the Legislative, 15 academics, and 15 members of the civil society per country.
+To do so, we built a dataset of prospective respondents ten times our country target.
+Then, we ran an online and telephone survey where we collected information regarding the climate change agreements and other related questions.
+
+After finishing this dataset, we started the surveying stage.
+From 12th of November to 5th of December, we ran the survey by contacting elite members by phone or by email.
+We had two teams of enumerators, one based in S\~{a}o Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers.
+Although the overall aim of the survey was 500 responses, the teams collected 654 interviews.
+Please refer to the Supplementary Material for more information about the sampling process and descriptive statistics.
+
+The hypothetical climate change agreements includes six attributes: 1) which organisation defines the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated.
+Table~\ref{tab:categories} describes the values we included in each treaty attribute.
 \\
 
+\newpage
+
+\begin{footnotesize}
 \begin{longtable}{l|l}
-\caption{Design principles for climate change mitigation conjoint experiments} \label{tab:categories} \\
+\caption{\textbf{Design principles for climate change mitigation conjoint experiments}} \label{tab:categories} \\
 
@@
 \multicolumn{2}{c}%
-{{\tablename \thetable{} Design principles for climate change mitigation conjoint experiments (\textit{cont.})}} \\
+{{\tablename \: \thetable{}: \textbf{Design principles for climate change mitigation conjoint experiments} (\textit{cont.})}} \\
 \hline \multicolumn{1}{c|}{\textbf{Attribute}} & \multicolumn{1}{c}{\textbf{Values}} \\ \hline 
@@
 & None \\
+& \\
 Punishment for repeated violations & More penalty \\
@@
 \end{longtable}
+\end{footnotesize}
 
-Our six principles correspond to a standard set of resolutions international treaties are expected to cover.
-However, the categories open the possibility for respondents to combine multiple levels of governance into a single climate change agreement as they see fit.
+The categories map the main conceptual differences between polycentric and state-led climate mitigation policies \citep{bechtel2013mass, ostrom1990governing}.
+The conjoint experiment design open the possibility for respondents to combine multiple levels of governance into a single climate change agreement as they see fit.
 We give no prior indication of whether a certain value is more prevalent in actual agreements, and we randomise the values to ensure that they all have the same probability of being selected.
@@
 	\centering
-	\includegraphics[width=12cm,angle=270,origin=c]{conjoint.pdf}
-	\caption{\textbf{Example of conjoint experiment design.} We presented respondents with 7 binary choices similar to this one.
-The values for the six design principles were randomly sampled from our list of attributes.
-More information is available in the Supplementary Appendix.}
+	\includegraphics[width=16cm]{conjoint-cropped.pdf}
+	\caption{\textbf{Example of conjoint experiment design}}
 	\label{fig:conjoint}
 \end{figure}
+
+% Add paragraph about marginal means -- cite Leeper (2019).
+
+\section{Results}%
+\label{sec:results}
 

### 2019-05-12 main.tex
fix table 1

@@
 \floatplacement{figure}{H}
-\usepackage{longtable}
 \usepackage[stable]{footmisc}
@@
 \cleanlookdateon
-\exhyphenpenalty=1000
-\hyphenpenalty=1000
+\exhyphenpenalty=10000
+\hyphenpenalty=10000
 \widowpenalty=10000
@@
 Experiences such as inshore fisheries in Turkey and timber management in Switzerland show that polycentrism induces individual cooperation and allows communities to avoid the `tragedy of the commons', that is, the overexploitation of shared resources \citep{hardin1968tragedy, ostrom1990governing}.
-Authors also point out that polycentric systems improve accountability as decentralisation reduces rent-seeking opportunities for interest groups \citep{turnheim2018innovating,ostrom2012nested,ostrom2014polycentric,sovacool2013adaptation}.
+Authors also point out that polycentric systems improve accountability as decentralisation reduces rent-seeking opportunities for politicians and interest groups \citep{turnheim2018innovating,ostrom2012nested,ostrom2014polycentric,sovacool2013adaptation}.
 
@@
 The sampling process was as follows.
-From 1st of October to 5th of December 2018, we ran an elite survey in ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
-The survey proceeded in two steps.
+From 1\textsuperscript{st} of October to 5\textsuperscript{th} of December 2018, we ran an elite survey in ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
 We started by collecting information on Latin American elites.
@@
 After finishing this dataset, we started the surveying stage.
-From 12th of November to 5th of December, we ran the survey by contacting elite members by phone or by email.
+From 12\textsuperscript{th} of November to 5\textsuperscript{th} of December, we ran the survey by contacting elite members by phone or by email.
 We had two teams of enumerators, one based in S\~{a}o Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers.
@@
 
-\begin{footnotesize}
-\begin{longtable}{l|l}
-\caption{\textbf{Design principles for climate change mitigation conjoint experiments}} \label{tab:categories} \\
-
-\hline \multicolumn{1}{c|}{\textbf{Attribute}} & \multicolumn{1}{c}{\textbf{Values}}\\ \hline 
-\endfirsthead
-
-\multicolumn{2}{c}%
-{{\tablename \: \thetable{}: \textbf{Design principles for climate change mitigation conjoint experiments} (\textit{cont.})}} \\
-\hline \multicolumn{1}{c|}{\textbf{Attribute}} & \multicolumn{1}{c}{\textbf{Values}} \\ \hline 
-\endhead
-
-\hline \multicolumn{2}{r}{{\textit{Continued on next page}}} 
-\endfoot
-
-\hline
-\endlastfoot
-
-Who makes the rules? & International organisations \\ 
-& Federal government \\ 
-& Local government \\ 
-& Local community members \\
-& Non-Governmental organisations \\
+\begin{table}[ht]
+\begin{center}
+\caption{\textbf{Design principles for climate change mitigation conjoint experiments}}
+\label{tab:categories} 
+\begin{tabular}{l !{\vrule width 1}p{9cm}}
+\Xhline{2\arrayrulewidth}
+\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Values}} \\
+\Xhline{2\arrayrulewidth} \\
+Who makes the rules? & International organisations; federal government; local government; local community members; non-governmental organisations \\
 & \\
-Conflict resolution mechanism & United Nations \\
-& Government bureaucracy \\
-& Local courts \\
-& Private arbitration \\
-& Informal norms \\
+Conflict resolution mechanism & United Nations; government bureaucracy; local courts; private arbitration; informal norms \\
 & \\
-Punishment & Imprisonment \\
-& Fines \\
-& Blacklist \\
-& None \\
+Punishment & Imprisonment; fines; blacklist; none \\
 & \\
-Punishment for repeated violations & More penalty \\
-& Same \\
-& Less penalty \\
+Punishment for repeated violations & More penalty; same; less penalty \\
 & \\
-Agreement costs & Rich countries pay more than poor countries \\
-& Proportional to history of emissions \\ 
-& Proportional to current emissions \\
-& Only rich countries pay\\
+Agreement costs & Rich countries pay more than poor countries; proportional to history of emissions; proportional to current emissions; only rich countries pay \\
 & \\
-Renegotiation & Never \\
-& Fifty years \\
-& Twenty years \\
-& Five years \\
-& One year\\
-\end{longtable}
-\end{footnotesize}
+Renegotiation & Never; fifty years; twenty years; five years; one year \\
+\Xhline{2\arrayrulewidth} 
+\end{tabular}
+\end{center}
+\end{table}
 

### 2019-05-13 appendix/appendix.Rmd
reorder files

---
title: "Appendix: Latin American Elites Favour Polycentric Governance in Climate Change Agreements"
output: pdf_document
toc: true
number_sections: true
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{libertine}
    - \usepackage[libertine]{newtxmath}
    - \usepackage[scaled=.9]{inconsolata}
    - \usepackage[UKenglish]{babel}
    - \usepackage[UKenglish]{isodate}
    - \usepackage{hyperref}
    - \hypersetup{linkcolor=Mahogany, citecolor=Mahogany, urlcolor=darkblue, breaklinks=true}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plm); library(tidyverse)
library(haven); library(clusterSEs)
library(stargazer); library(cjoint)
library(sp); library(cregg)
library(kableExtra)
setwd("~/Downloads/1_data/")
load('conj.RData')

plot_mm <- function(
  x,
  group = attr(x, "by"),
  feature_headers = TRUE,
  header_fmt = "%s",
  size = 2,
  xlab = "Marginal Mean",
  ylab = "",
  legend_title = if (is.null(group)) "Feature" else group,
  legend_pos = "bottom",
  xlim = NULL,
  vline = 0,
  vline_color = "gray",
  theme = ggplot2::theme_bw(),
  ...
) {

  # function used in cj and ammplot to produce "fancy" feature labels
  clean_feature_labels <- function(data, RHS, feature_labels) {
    if (inherits(data, "cj_df") | inherits(data, "data.frame")) {
      fancy_labels <- stats::setNames(lapply(data[RHS], attr, "label"), RHS)
    } else if (inherits(data, "survey.design")) {
      fancy_labels <- stats::setNames(lapply(data[["variables"]][RHS], attr, "label"), RHS)
    } else {
      stop("'data' is not a 'data.frame' or 'survey.design' object")
    }
    ## check `feature_labels`, if present
    missing_labels <- RHS[!RHS %in% names(feature_labels)]
    feature_labels <- c(feature_labels, stats::setNames(rep(list(NULL), length(missing_labels)), missing_labels))
    ## clean fancy labels (use variable name if variable has no "label" attribute)
    for (i in seq_along(feature_labels)) {
      if (is.null(feature_labels[[i]]) || feature_labels[[i]] == "") {
        if (is.null(fancy_labels[[RHS[i]]])) {
          feature_labels[[i]] <- RHS[i]
        } else {
          feature_labels[[i]] <- fancy_labels[[RHS[i]]]
        }
      }
    }
    return(feature_labels)
  }

  # function to cleanup term labels (due to factor variable blah blah)
  clean_term_names <- function(x, RHS) {
    out <- data.frame(feature = character(length(x)), 
                      level = character(length(x)), 
                      stringsAsFactors = FALSE)
    for (i in seq_along(RHS)) {
      w <- grepl(RHS[i], x)
      out$feature[w] <- RHS[i]
      out$level[w] <- sub(paste0("^`?", RHS[i], "`?"), "", x[w])
    }

    # check whether levels are all unique
    if (any(duplicated(out$level))) {
      warning("Some level labels are duplicated across features. This may cause problems!")
    }

    return(out)
  }

  # function used to produce a data frame of features and levels
  make_term_labels_df <- function(data, feature_names, level_order = c("ascending", "descending")) {
    # setup data
    if (inherits(data, "data.frame")) {
      term_levels_list <- lapply(data[feature_names], levels)
    } else if (inherits(data, "survey.design")) {
      term_levels_list <- lapply(data[["variables"]][feature_names], levels)
    } else {
      stop("'data' is not a 'data.frame' or 'survey.design' object")
    }

    # figure out level order
    level_order <- match.arg(level_order)
    if (level_order == "descending") {
      term_levels_list[] <- lapply(term_levels_list, rev)
    }

    # construct data frame
    term_levels <- rev(unlist(term_levels_list))
    term_labels <- stats::setNames(rep(feature_names, lengths(term_levels_list)), rev(term_levels))
    data.frame(feature = unlist(term_labels), level = unlist(names(term_labels)), stringsAsFactors = FALSE)
  }

  # function used in plot() methods to make pretty feature headers
  make_feature_headers <- function(x, fmt = "(%s)") {
    feature_levels <- rev(split(x$level, x$feature))
    for (i in seq_along(feature_levels)) {
      feature_levels[[i]] <- levels(x$level)[match(feature_levels[[i]], levels(x$level))]
      feature_levels[[i]] <- c(feature_levels[[i]], sprintf(fmt, names(feature_levels)[i]))
    }
    factor(as.character(x$level), levels = unique(unname(unlist(feature_levels))))
  }

  # function used to check whether, if specified, the 'feature_order' argument is valid
  check_feature_order <- function(feature_order, RHS) {
    if (!is.null(feature_order)) {
      if (length(RHS) > length(feature_order)) {
        stop("'feature_order' appears to be missing values")
      } else if (length(RHS) < length(feature_order)) {
        stop("'feature_order' appears to have excess values")
      } else if (any(!names(feature_order) %in% RHS)) {
        stop("'feature_order' appears to contain erroneous values")
      }
    } else {
      feature_order <- RHS
    }
    return(feature_order)
  }

  # optionally, add gaps between features
  if (isTRUE(feature_headers)) {
    x$level <- make_feature_headers(x, fmt = header_fmt)
    to_merge <- data.frame(feature = unique(x$feature), level = sprintf(header_fmt, unique(x$feature)))
    if ("BY" %in% names(x)) {
      to_merge <- do.call("rbind", lapply(unique(x[["BY"]]), function(lev) {
        to_merge[["BY"]] <- lev
        to_merge
      }))
    } else if (!is.null(group)) {
      to_merge <- do.call("rbind", lapply(unique(x[[group]]), function(lev) {
        to_merge[[group]] <- lev
        to_merge
      }))
    }
    x <- merge(x, to_merge, all = TRUE)
  }

  if (is.null(group)) {
    p <- ggplot2::ggplot(data = x, ggplot2::aes_string(x = "estimate", y = "level", colour = "feature"))
  } else {
    p <- ggplot2::ggplot(data = x, ggplot2::aes_string(x = "estimate", y = "level", colour = group, group = group))
  }

  if (is.null(xlim)) {
    xmin <- min(x$lower, na.rm = TRUE)
    xmin <- if (xmin < 0) 1.04*xmin else .96*xmin
    xmax <- max(x$upper, na.rm = TRUE)
    xmax <- if (xmax > 0) 1.04*xmax else .96*xmax
    xlim <- c(xmin, xmax)
  }

  if (!is.null(vline)) {
    p <- p + ggplot2::geom_vline(xintercept = vline, colour = vline_color)
  }

  ggplotColours <- function(n = 6, h = c(0, 360) + 15){
    if ((diff(h) %% 360) < 1) h[2] <- h[2] - 360/n
    hcl(h = (seq(h[1], h[2], length = n)), c = 100, l = 65)
  }
  myColors <- ggplotColours(length(unique(x$feature)))
  myColors <- c(rep(myColors[1], 6), rep(myColors[2], 5),
                rep(myColors[3], 4), rep(myColors[4], 5),
                rep(myColors[5], 6), rep(myColors[6], 6))
  myFaces <- c(rep('plain', 5), "bold",
               rep('plain', 4), "bold",
               rep('plain', 3), "bold",
               rep('plain', 4), "bold",
               rep('plain', 5), "bold",
               rep('plain', 5), "bold")
  mySizes <-  c(rep(10, 5), 11,
               rep(10, 4), 11,
               rep(10, 3), 11,
               rep(10, 4), 11,
               rep(10, 5), 11,
               rep(10, 5), 11)
  myColors <- rep(myColors, ifelse(length(unique(x[,group])), length(unique(x[,group])), 1))

  p <- p + ggplot2::geom_point(position = ggstance::position_dodgev(height = 0.75), 
                               size = size, na.rm = TRUE, color = myColors) +
    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower", xmax = "upper"),  
                            size = 0.7, height = 0, na.rm = TRUE, color = myColors,
                            position = ggstance::position_dodgev(height = 0.75))
  if (is.null(group)) {
    p <- p + ggplot2::scale_colour_discrete(guide = ggplot2::guide_legend(title = legend_title))
  } else {
    p <- p + ggplot2::scale_colour_discrete(breaks = levels(x[[group]]),
                                            labels = levels(x[[group]]),
                                            guide = ggplot2::guide_legend(title = legend_title))
  }
  p <- p + theme_bw() +
    ggplot2::scale_x_continuous(limits = xlim, oob = scales::rescale_none) +
    ggplot2::xlab(xlab) + 
    ggplot2::ylab(ylab) + 
    theme + ggplot2::theme(
      legend.position = legend_pos,
      panel.grid.major = ggplot2::element_blank(),
      panel.grid.minor = ggplot2::element_blank(),
      axis.text.y = element_text(face=myFaces, size = mySizes)
    ) + 
    ggplot2::guides(colour = ggplot2::guide_legend(title = legend_title))
  return(p)
}

plotAMCE <- 
  function (x, main = "", xlab = "Change in E[Y]", 
            ci = 0.95, colors = NULL, 
            xlim = NULL, breaks = NULL, 
            labels = NULL, attribute.names = NULL, 
            level.names = NULL, label.baseline = TRUE, 
            text.size = 11, 
            text.color = "black", 
            point.size = 0.5, dodge.size = 0.9, 
            plot.theme = NULL, plot.display = "all", 
            facet.names = NULL, 
            facet.levels = NULL, 
            group.order = NULL, font.family = NULL, 
            tblfy = F, ...) {
    amce_obj <- x
    ylim <- xlim
    pe <- NULL
    se <- NULL
    group <- NULL
    lower <- NULL
    upper <- NULL
    var <- NULL
    printvar <- NULL
    facet <- NULL
    raw_attributes <- names(amce_obj$estimates)
    raw_levels <- lapply(amce_obj$estimates, colnames)
    for (effect in names(raw_levels)) {
        effect_elements <- strsplit(effect, ":")[[1]]
        baseline_interactions <- c()
        for (elem in effect_elements) {
            base_coef <- paste(c(elem, amce_obj$baselines[[elem]]), 
                collapse = "")
            baseline_interactions <- c(baseline_interactions, 
                base_coef)
        }
        interaction_str <- paste(baseline_interactions, sep = "", 
            collapse = ":")
        raw_levels[[effect]] <- c(interaction_str, raw_levels[[effect]])
    }
    if (ci < 1 & ci > 0) {
        zscr <- qnorm(1 - ((1 - ci)/2))
    }
    else {
        cat("Invalid confidence interval -- Defaulting to 95%")
        zscr <- qnorm(1 - ((1 - 0.95)/2))
    }
    if (!is.null(attribute.names)) {
        attribute.names <- unique(attribute.names)
        if (length(attribute.names) != length(raw_attributes)) {
            cat(paste("Error: The number of unique elements in attribute.names ", 
                length(attribute.names), " does not match the attributes in amce object for which estimates were obtained: ", 
                paste(raw_attributes, collapse = ", "), "\n", 
                sep = ""))
            cat("Defaulting attribute.names to attribute names in AMCE object\n")
            attribute.names <- NULL
        }
    }
    if (!is.null(level.names)) {
        names(level.names) <- clean.names(names(level.names))
        for (name in names(level.names)) {
            if (name %in% names(raw_levels)) {
                if (length(level.names[[name]]) != length(raw_levels[[name]])) {
                  cat(paste("Error: level.names lengths do not match levels for attribute ", 
                    name, "\n", sep = ""))
                  cat(paste("Defaulting level.names for attribute ", 
                    name, " to level names in AMCE object", "\n", 
                    sep = ""))
                  level.names[[name]] <- NULL
                }
            }
            else {
                cat(paste("Error: level.names entry ", name, 
                  " not in AMCE object. Removing level.names for attribute.", 
                  "\n", sep = ""))
                level.names[[name]] <- NULL
            }
        }
    }
    if (is.null(attribute.names)) {
        attribute.names <- c()
        for (attr in names(amce_obj$estimates)) {
            attr_split <- strsplit(attr, ":")[[1]]
            attr_lookup <- paste(unlist(sapply(attr_split, function(x) amce_obj$user.names[x])), 
                collapse = ":")
            attribute.names <- c(attribute.names, attr_lookup)
        }
    }
    if (is.null(level.names)) 
        level.names <- list()
    if (any(!names(raw_levels) %in% names(level.names))) {
        for (attr in names(raw_levels)[!names(raw_levels) %in% 
            names(level.names)]) {
            attr_split <- strsplit(raw_levels[[attr]], ":")
            level.names[[attr]] <- unlist(lapply(attr_split, 
                function(x) paste(sapply(x, function(y) amce_obj$user.levels[y]), 
                  collapse = ":")))
        }
    }
    plot.display.opts <- c("all", "unconditional", "interaction")
    if (!is.element(plot.display, plot.display.opts)) {
        stop(paste(c("Error-- plot.display must be once of: ", 
            paste(plot.display.opts, collapse = ", ")), collapse = " "))
    }
    if (!is.null(facet.names)) {
        facet.names <- clean.names(facet.names)
    }
    else if (!is.null(facet.levels)) {
        facet.names <- clean.names(names(facet.levels))
    }
    if (!is.null(facet.names)) {
        facet.names.check <- c()
        for (facet.name in facet.names) {
            if (grepl(":", facet.name)) 
                stop("Error-- cannot facet by interaction in current version.")
            if (!facet.name %in% names(amce_obj$estimates) & 
                !facet.name %in% names(amce_obj$cond.estimates)) {
                stop(paste(c("Error-- cannot find facet name", 
                  facet.name, "in AMCE object output."), collapse = " "))
            }
            else {
                facet.names.check <- c(facet.names.check, facet.name)
            }
        }
        facet.names <- facet.names.check
    }
    if ((is.null(facet.names)) & (length(amce_obj$respondent.varying) > 
        0) & (plot.display != "unconditional")) {
        facet.names <- amce_obj$respondent.varying
    }
    if (is.null(facet.names) & plot.display == "interaction") {
        warning("Warning: no facet name or respondent varying characteristic provided to calculate conditional estimates. Will display unconditional only")
        plot.display <- "unconditional"
    }
    if (plot.display == "unconditional" & !is.null(facet.names)) {
        warning("Warning-- plot display is set to unconditional, facet names will be ignored")
        facet.names <- NULL
        facet.levels <- NULL
    }
    if (!is.null(facet.levels)) {
        names(facet.levels) <- clean.names(names(facet.levels))
        for (facet.name in names(facet.levels)) {
            if (facet.name %in% names(amce_obj$baselines)) {
                facet.levels[[facet.name]] <- clean.names(facet.levels[[facet.name]])
                if (facet.name %in% names(amce_obj$estimates) && 
                  is.element(amce_obj$baselines[[facet.name]], 
                    facet.levels[[facet.name]])) {
                  stop(paste(c("Error: Facet level \"", as.character(amce_obj$baselines[[facet.name]]), 
                    "\" is the baseline level of a profile varying attribute. Please provide alternative facet level or use defaults."), 
                    collapse = ""))
                }
                if (is.null(names(facet.levels[[facet.name]]))) {
                  fac.levs <- sapply(facet.levels[[facet.name]], 
                    function(x) paste(facet.name, x, sep = ""))
                  names(facet.levels[[facet.name]]) <- sapply(fac.levs, 
                    USE.NAMES = F, function(x) amce_obj$user.levels[[x]])
                }
            }
            else if (is.null(names(facet.levels[[facet.name]]))) {
                names(facet.levels[[facet.name]]) <- as.character(facet.levels[[facet.name]])
            }
        }
    }
    if (is.null(facet.levels)) 
        facet.levels <- list()
    if (any(!facet.names %in% names(facet.levels))) {
        for (facet.name in facet.names[!facet.names %in% names(facet.levels)]) {
            if (facet.name %in% names(amce_obj$baselines)) {
                if (facet.name %in% names(amce_obj$estimates)) {
                  fac.levs <- colnames(amce_obj$estimates[[facet.name]])
                }
                else {
                  fac.levs <- colnames(amce_obj$cond.estimates[[facet.name]])
                }
                facet.levels[[facet.name]] <- sub(facet.name, 
                  "", fac.levs)
                facet.levels[[facet.name]] <- c(amce_obj$baselines[[facet.name]], 
                  facet.levels[[facet.name]])
                fac.levs <- c(paste(facet.name, amce_obj$baselines[[facet.name]], 
                  sep = ""), fac.levs)
                names(facet.levels[[facet.name]]) <- sapply(fac.levs, 
                  USE.NAMES = F, function(x) amce_obj$user.levels[[x]])
            }
            else if (facet.name %in% names(amce_obj$continuous)) {
                facet.levels[[facet.name]] <- amce_obj$continuous[[facet.name]]
            }
        }
    }
    covariate.values <- list()
    for (var in names(facet.levels)) {
        if (var %in% amce_obj$respondent.varying) {
            covariate.values[[var]] <- facet.levels[[var]]
        }
    }
    d <- data.frame(pe = c(), se = c(), upper = c(), lower = c(), 
        var = c(), printvar = c(), group = c(), facet = c())
    if (plot.display != "interaction") {
        if (plot.display == "all") {
            uncond.facet.name <- "Unconditional"
        }
        else {
            uncond.facet.name <- NA
        }
        if (plot.display == "all" && !is.null(facet.names)) {
            attr_remove <- c()
            for (facet.name in facet.names[!is.element(facet.names, 
                amce_obj$respondent.varying)]) {
                attr_remove1 <- raw_attributes[grepl(":", raw_attributes)]
                attr_remove1 <- attr_remove1[grepl(facet.name, 
                  attr_remove1)]
                attr_remove <- c(attr_remove, attr_remove1)
            }
            raw_attributes <- raw_attributes[!is.element(raw_attributes, 
                attr_remove)]
        }
        for (i in 1:length(raw_attributes)) {
            attr_name <- raw_attributes[i]
            print_attr_name <- attribute.names[which(names(amce_obj$estimates) == 
                raw_attributes[i])]
            d_head <- data.frame(pe = NA, se = NA, upper = NA, 
                lower = NA, var = attr_name, printvar = paste(print_attr_name, 
                  ":", sep = ""), group = "<NA>", facet = uncond.facet.name)
            d <- rbind(d, d_head)
            for (j in 1:length(raw_levels[[attr_name]])) {
                level_name <- raw_levels[[attr_name]][j]
                print_level_name <- level.names[[attr_name]][j]
                if (j == 1) {
                  if (label.baseline) {
                    print_level_name <- paste("(Baseline = ", 
                      print_level_name, ")", sep = "")
                  }
                  d_lev <- data.frame(pe = NA, se = NA, upper = NA, 
                    lower = NA, var = level_name, printvar = paste("   ", 
                      print_level_name, sep = ""), group = print_attr_name, 
                    facet = uncond.facet.name)
                }
                else {
                  val_pe <- amce_obj$estimates[[attr_name]][1, 
                    level_name]
                  val_se <- amce_obj$estimates[[attr_name]][2, 
                    level_name]
                  upper_bnd <- val_pe + zscr * val_se
                  lower_bnd <- val_pe - zscr * val_se
                  d_lev <- data.frame(pe = val_pe, se = val_se, 
                    upper = upper_bnd, lower = lower_bnd, var = level_name, 
                    printvar = paste("   ", print_level_name, 
                      sep = ""), group = print_attr_name, facet = uncond.facet.name)
                }
                d <- rbind(d, d_lev)
            }
        }
    }
    if (plot.display != "unconditional" & !is.null(facet.names)) {
        for (facet.name in facet.names) {
            print_facet_name <- amce_obj$user.names[[facet.name]]
            all_req_vars <- attr(terms(amce_obj$formula), "term.labels")
            all_mod <- unlist(sapply(all_req_vars, function(x) {
                y <- strsplit(x, ":")[[1]]
                if (any(y == facet.name)) 
                  x
            }))
            all_mod <- unlist(sapply(all_mod, function(x) {
                subs <- strsplit(x, ":")[[1]]
                subs <- subs[is.element(subs, names(amce_obj$estimates))]
                subs <- subs[subs != facet.name]
                if (length(subs) > 0) 
                  paste(subs, collapse = ":")
            }))
            if (length(all_mod) == 0) {
                stop(paste(c("Error: Facet variable", facet.name, 
                  "not interacted with profile attributes"), 
                  collapse = " "))
            }
            all_mod <- unique(all_mod)
            if (is.element(facet.name, names(amce_obj$estimates))) {
                facet.start <- 2
            }
            else {
                facet.start <- 1
            }
            for (k in facet.start:length(facet.levels[[facet.name]])) {
                facet_lev <- facet.levels[[facet.name]][k]
                if (is.element(facet.name, names(amce_obj$estimates))) {
                  print_facet_level <- paste(c("ACIE", paste(c(print_facet_name, 
                    names(facet.levels[[facet.name]])[k]), collapse = " = ")), 
                    collapse = "\n")
                }
                else {
                  print_facet_level <- paste(c("Conditional on", 
                    paste(c(print_facet_name, names(facet.levels[[facet.name]])[k]), 
                      collapse = " = ")), collapse = "\n")
                }
                for (mod_var in all_mod) {
                  print_attr_name <- attribute.names[which(names(amce_obj$estimates) == 
                    mod_var)]
                  d_head <- data.frame(pe = NA, se = NA, upper = NA, 
                    lower = NA, var = mod_var, printvar = paste(print_attr_name, 
                      ":", sep = ""), group = "<NA>", facet = print_facet_level)
                  d <- rbind(d, d_head)
                  if (facet.name %in% names(amce_obj$estimates)) {
                    inter_coef <- paste(sort(c(mod_var, facet.name)), 
                      collapse = ":")
                    estimate.source <- amce_obj$estimates[[inter_coef]]
                    estimate.source <- estimate.source[, grep(paste0(facet.name, 
                      facet_lev), colnames(estimate.source))]
                  }
                  else {
                    estimate.source <- get.conditional.effects(amce_obj, 
                      covariate.values, facet.name, facet_lev, 
                      mod_var)
                  }
                  mod_vars <- strsplit(mod_var, ":")[[1]]
                  for (p in 1:length(raw_levels[[mod_var]])) {
                    mod_coef <- raw_levels[[mod_var]][p]
                    mod_coefs <- strsplit(mod_coef, ":")[[1]]
                    for (lev in 1:length(mod_coefs)) {
                      mod_lev <- sub(mod_vars[lev], "", mod_coefs[lev])
                    }
                    print_level_name <- level.names[[mod_var]][p]
                    if (p == 1) {
                      if (label.baseline) {
                        print_level_name <- paste("(Baseline = ", 
                          print_level_name, ")", sep = "")
                      }
                      d_lev <- data.frame(pe = NA, se = NA, upper = NA, 
                        lower = NA, var = mod_coef, printvar = paste("   ", 
                          print_level_name, sep = ""), group = print_attr_name, 
                        facet = print_facet_level)
                    }
                    else {
                      val_pe <- estimate.source[1, p - 1]
                      if (!is.na(val_pe)) {
                        val_se <- estimate.source[2, p - 1]
                        upper_bnd <- val_pe + zscr * val_se
                        lower_bnd <- val_pe - zscr * val_se
                      }
                      else {
                        val_se <- upper_bnd <- lower_bnd <- NA
                      }
                      d_lev <- data.frame(pe = val_pe, se = val_se, 
                        upper = upper_bnd, lower = lower_bnd, 
                        var = mod_coef, printvar = paste("   ", 
                          print_level_name, sep = ""), group = print_attr_name, 
                        facet = print_facet_level)
                    }
                    d <- rbind(d, d_lev)
                  }
                }
            }
        }
    }
    else {
        d <- d[, -which(colnames(d) == "facet")]
    }
    if (is.null(ylim)) {
        max_upper <- max(d$upper, na.rm = T) + 0.05
        min_lower <- min(d$lower, na.rm = T) - 0.05
        ylim <- c(min_lower, max_upper)
        d[is.na(d)] <- max_upper + 100
    }
    else {
        d[is.na(d)] <- max(ylim) + 100
    }
    d$group[d$group == "<NA>"] <- NA
    if (!is.null(facet.names)) 
        d$facet[d$facet == "<NA>"] <- NA
    d$var <- factor(d$var, levels = unique(d$var)[length(d$var):1])
    if (!is.null(facet.names)) {
        d$facet <- factor(d$facet, levels = unique(d$facet))
    }
    if (!is.null(group.order)) {
        n.row <- length(unique(as.character(d$var)))
        order.var <- vector("character", length = n.row)
        i <- 1
        while (i < n.row) {
            for (j in group.order) {
                order.var[i] <- unique(as.character(d$var[d$var == 
                  gsub(" ", "", j)]))
                i <- i + 1
                temp.d <- d
                temp.d$group <- gsub(" ", "", temp.d$group)
                temp.d <- subset(temp.d, group == gsub(" ", "", 
                  j))
                temp.var <- unique((as.character(temp.d$var)))
                order.var[i:(i + length(temp.var) - 1)] <- temp.var
                i <- i + length(temp.var)
            }
        }
        order.var <- rev(order.var)
        order.df <- data.frame(order.var, 1:length(order.var))
        colnames(order.df) <- c("var", "order")
        d$var <- factor(d$var, levels = order.var)
        d <- merge(d, order.df, by.x = "var", by.y = "var", suffixes = c("", 
            ""))
    }
    levs <- as.character(d$printvar)
    levs <- gsub('organizations', 'organisations', levs)
    d$printvar <- factor(levs, levels = levs)
    if(tblfy) {
      return(d)
    }
    p = ggplot(d, aes(y = pe, x = var, colour = group))
    p = p + coord_flip(ylim = ylim)
    p = p + geom_hline(yintercept = 0, size = 0.5, colour = "black", 
        linetype = "dotted")
    p = p + geom_pointrange(aes(ymin = lower, ymax = upper), 
        position = position_dodge(width = dodge.size), size = point.size)
    if (!is.null(facet.names)) {
        p = p + facet_wrap(~facet)
    }
    if (is.null(breaks) & is.null(labels)) {
        p = p + scale_y_continuous(name = xlab)
    }
    else if (is.null(breaks) & !is.null(labels)) {
        p = p + scale_y_continuous(name = xlab, labels = labels)
    }
    else if (!is.null(breaks) & is.null(labels)) {
        p = p + scale_y_continuous(name = xlab, breaks = breaks)
    }
    else if (!is.null(breaks) & !is.null(labels)) {
        p = p + scale_y_continuous(name = xlab, breaks = breaks, 
            labels = labels)
    }
    if (!is.null(group.order)) {
        fix.xlabs.df <- d[!duplicated(d$var), ]
        fix.xlabs <- fix.xlabs.df[order(-fix.xlabs.df$order), 
            ]$printvar
    }
    else {
        fix.xlabs <- as.character(d$printvar)[!duplicated(d$var)]
    }
    p = p + scale_x_discrete(name = "", labels = fix.xlabs[length(fix.xlabs):1])
    if (!is.null(main)) {
        if (main != "") {
            p = p + ggtitle(main)
        }
    }
    if (is.null(colors)) {
        p = p + scale_colour_discrete(" ")
    }
    else if (is.vector(colors)) {
        cPal <- rep(colors, ceiling(length(unique(d$group))/length(colors)))
        p = p + scale_colour_manual(values = cPal)
    }
    else {
        cat("Error: 'colors' must be a vector. Using default colors\n")
        p = p + scale_colour_discrete(" ")
    }
    if (is.null(plot.theme)) {
        theme_bw1 <- function(base_size = text.size, base_family = "") {
            theme_grey(base_size = base_size, base_family = base_family) %+replace% 
                theme(axis.text.x = element_text(size = base_size * 
                  0.9, colour = text.color, hjust = 0.5, vjust = 1), 
                  axis.text.y = element_text(size = base_size, 
                    colour = text.color, hjust = 0, vjust = 0.5, 
                    family = font.family), axis.ticks = element_line(colour = "grey50"), 
                  axis.title.y = element_text(size = base_size, 
                    angle = 90, vjust = 0.01, hjust = 0.1, family = font.family), 
                  plot.title = element_text(face = "bold", family = font.family), 
                  legend.position = "none")
        }
        p = p + theme_bw1()
        print(p)
    }
    else if (is.null(class(plot.theme))) {
        cat("Error: 'plot.theme' is not a valid ggplot theme object. Using default theme\n")
        theme_bw1 <- function(base_size = text.size, base_family = "") {
            theme_grey(base_size = base_size, base_family = base_family) %+replace% 
                theme(axis.text.x = element_text(size = base_size * 
                  0.9, colour = text.color, hjust = 0.5, vjust = 1), 
                  axis.text.y = element_text(size = base_size, 
                    colour = text.color, hjust = 0, vjust = 0.5, 
                    family = font.family), axis.ticks = element_line(colour = "grey50"), 
                  axis.title.y = element_text(size = base_size, 
                    angle = 90, vjust = 0.01, hjust = 0.1, family = font.family), 
                  plot.title = element_text(face = "bold", family = font.family), 
                  legend.position = "none")
        }
        p = p + theme_bw1()
        print(p)
    }
    else if (class(plot.theme)[1] != "theme") {
        cat("Error: 'plot.theme' is not a valid ggplot theme object. Using default theme\n")
        theme_bw1 <- function(base_size = text.size, base_family = "") {
            theme_grey(base_size = base_size, base_family = base_family) %+replace% 
                theme(axis.text.x = element_text(size = base_size * 
                  0.9, colour = text.color, hjust = 0.5, vjust = 1), 
                  axis.text.y = element_text(size = base_size, 
                    colour = text.color, hjust = 0, vjust = 0.5, 
                    family = font.family), axis.ticks = element_line(colour = "grey50"), 
                  axis.title.y = element_text(size = base_size, 
                    angle = 90, vjust = 0.01, hjust = 0.1, family = font.family), 
                  plot.title = element_text(face = "bold", family = font.family), 
                  legend.position = "none")
        }
        p = p + theme_bw1()
        print(p)
    }
    else {
        p = p + plot.theme
        print(p)
    }
    if (length(covariate.values) > 1) {
        resp.message <- c("Note:")
        for (this.var in names(covariate.values)) {
            resp.message <- paste(c(resp.message, " For AMCE and ACIE conditional on ", 
                this.var, ", "), collapse = "")
            other.vars <- names(covariate.values)[names(covariate.values) != 
                this.var]
            other.levels <- c()
            for (var in other.vars) {
                other.levels <- c(other.levels, paste(c(var, 
                  " will be held at level \"", names(covariate.values[[var]])[1], 
                  "\""), collapse = ""))
            }
            other.levels <- paste(other.levels, collapse = ", and ")
            resp.message <- c(resp.message, other.levels, ".")
            resp.message <- paste(resp.message, collapse = "")
        }
        cat(resp.message, "\n")
    }
}

# Function
table_mm <- function(mms, capt) {
  dfr <- data.frame(feature = mms[,c(4)], 
             round(mms[,c(5,6,8,9,10)], digits=3))
  names(dfr) <- c('Feature', 'Estimate', 'Std.Error',
                'P-Value', 'Lower', 'Upper')
  return(kable(dfr, "latex", caption = capt, booktabs = T) %>%
    kable_styling(font_size = 10) %>%
    group_rows('Who makes the rules?', 1, 5) %>%
    group_rows('How are conflicts resolved?', 6, 10) %>%
    group_rows('What punishments do they use?', 11, 14) %>%
    group_rows('How are repeated violations punished?', 15, 17) %>%
    group_rows('How are costs distributed?', 18, 21) %>%
    group_rows('How often will the agreement be renegotiated?', 22, 26))
}

tableAMCE <- function(results, capt = 'Main Model') {
  aux <- plotAMCE(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Full Model',
     attribute.names = attrs, tblfy = T)
  aux <- aux %>%
    filter(!is.na(group))%>%
    select(printvar, pe, se, lower, upper)
  indx <- grep('Baseline =', aux$printvar)
  aux$pe <- round(aux$pe, digits = 3)
  aux$se <- round(aux$se, digits = 3)
  aux$lower <- round(aux$lower, digits = 3)
  aux$upper <- round(aux$upper, digits = 3)
  aux$pe[indx] = ''
  aux$se[indx] = ''
  aux$lower[indx] = ''
  aux$upper[indx] = ''
  names(aux) <- c('Feature', 'Estimate', 'Std.Error', 
                  'Lower', 'Upper')
  return(kable(aux, "latex", caption = capt, booktabs = T, align = c('l', rep('c', 4))) %>%
    kable_styling(font_size = 10) %>%
    group_rows('How are conflicts resolved?', 1, 5) %>%
    group_rows('How are costs distributed?', 6, 9) %>%
    group_rows('How are repeated violations punished?', 10, 12) %>%
    group_rows('How often will the agreement be renegotiated?', 13, 17) %>%
    group_rows('What punishments do they use?', 18, 21) %>%
    group_rows('Who makes the rules?', 22, 26))
}

# Britishfy
cj$`Who makes the rules?` <- as.character(cj$`Who makes the rules?`)
cj$`Who makes the rules?`[cj$`Who makes the rules?`=='International organizations'] = 'International organisations'
cj$`Who makes the rules?` <- 
  factor(cj$`Who makes the rules?`, 
         levels = c("NGOs", "Local community members", 
                    "Local government", "Federal government",
                    "International organisations"))
```

\newpage

# Latin American Elite Survey

From 1st of October to 5th of December 2018, we run an elite survey in ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru. The survey proceeded in two steps.

We collected information on Latin American elites. The target was:

1. Executive members
2. Legislative members
3. Civil society
4. Academics

For each profile, in each country, we aimed at surveying:

1. 10 Executive members
2. 10 Legislative members
3. 15 Civil society
4. 15 Academics

To do so, we build a prospective respondents dataset with ten times these members for each country. Then, we run an online and telephone survey where we collected information regarding the climate change agreements and other climate change related problems.

After finishing this dataset, we started the surveying stage. From 12th of November to 5th of December, we ran the survey by contacting elite members by phone or by email. We had two teams of enumerators, one based in Sao Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers. Although the overall aim of the survey was 500 responses, the teams managed to collect 654 interviews.

# Conjoint Experiment Analysis: Identification and Estimation

A conjoint experiment is a statistical technique that allows individuals to express their preferences on multiple attributes of a single topic [@hainmueller2014causal; @bansak2016economic]. Individuals are presented with two hypothetical scenarios, A and B, each containing a series of characteristics a researcher wants to evaluate. The individual chooses one of them. As the attributes are randomised and individuals choose between different pairs of hypothetical scenarios, we can estimate how individuals value each of the conjoined elements.

In our research, we ask what features elite members would like to see implemented in a climate change agreement. We ask their opinion on 6 questions: 1) who makes the rules; 2) who enforces the laws; 3) what punishment should be used against lawbreakers; 4) how are repeated violations punished; 5) how are costs distributed, and 6) how often the agreement will be renegotiated. Each of the questions has four to five different attributes. For the first two questions, we ask individuals if they would rather have the community, local governments, federal governments, or international organisations to create or enforce rules. As for punishments, we have options ranging from do nothing to fines and incarceration. We ask whether the costs of climate change agreements should be paid mostly or exclusively by developed countries, by polluter countries regardless of their wealth, or if costs should be allocated according to the history of emissions of a given nation. Individuals also state their preferences for short-term agreements, a proxy we use for flexibility, or for long-term ones, what we see as a proxy for the stability of rules. Lastly, we ask which of the two conjoined choices individuals perceive as more legitimate and more efficient.

Conjoint experiments have many advantages. First, as each individual chooses between many pairs of possible climate agreements -- seven in our case -- we can drastically increase our sample size without incurring in further financial costs. The design thus maximises our research budget. Second, individuals rarely decide considering one attribute at a time, as presented in other types of survey experiments. In that regard, our conjoint analysis mirrors how people naturally make their choices, that is, by simultaneously taking several characteristics into consideration. Finally, as the experiments consist of a simple choice between A and B, conjoint analyses are easy to understand and to implement. This research design reduces the cognitive load interviewees have while answering surveys and as a result, we can expect more accurate responses from our sample.

# Descriptive Statistics

The main demographic statistics collected were the country and elite types, and the geolocation of the respondents. They follow in the graphs below.

```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5}
aux <- cj %>%
  select(Response.ID, countryOrigin, groupOrigin, LocationLongitude, LocationLatitude) %>%
  unique()

# Country
tab <- data.frame(table(aux$countryOrigin))
names(tab) <- c('Country', 'Frequency')
p<-ggplot(data=tab, aes(x = Country, y=Frequency)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=50, linetype="dashed", color = "black") + 
  theme_bw() + annotate(geom = "text", label = tab$Frequency,
                        x = tab$Country, y = tab$Frequency + 2)
p

# Elite type
tab <- data.frame(table(aux$groupOrigin))
names(tab) <- c('Group Origin', 'Frequency')
p<-ggplot(data=tab, aes(x = `Group Origin`, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + annotate(geom = "text", label = tab$Frequency,
                        x = tab$`Group Origin`, y = tab$Frequency + 5)
p
```

As we can see, we managed to contact more than fifty elite members for all countries but Bolivia and Peru. To compensate for the low collection rates in these two countries, note that we exceeded the sample size in all the remaining states.

Considering the elite type, note that we have, as expected, more people from academia and the civil society, followed by Executive and Legislative. The legislative collection was below the original target, but above the minimum mark of 5 for each country. This is expected, given the difficulty of accessing these elite members.

In the map, we can see that the answers concentrate on the country's capitals, with some variation within the state, but with sample concentrated in the largest municipalities. This is expected, as elite members are assumed to gravitate around the capitals and the influence centers.

# Frequency of features selected by each attribute

The figures below display the freature frequency for each attribute, by each task.

```{r attributes, echo=FALSE, fig.align='center', fig.height=4}
aux <- cj %>%
  select(Response.ID, `Who makes the rules?`, `How are conflicts resolved?`, `What punishments do they use?`,`How are repeated violations punished?`, `How are costs distributed?`,`How often will the agreement be renegotiated?`) %>%
  unique()

# Who makes the rules
tab <- data.frame(table(aux$`Who makes the rules?`))
names(tab) <- c('Levels', 'Frequency')
p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('Who makes the rules?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 35) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are conflicts resolved?
tab <- data.frame(table(aux$`How are conflicts resolved?`))
names(tab) <- c('Levels', 'Frequency')
p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are conflicts resolved?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 35) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# What punishments do they use?
tab <- data.frame(table(aux$`What punishments do they use?`))
names(tab) <- c('Levels', 'Frequency')
p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('What punishments do they use?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 40) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are repeated violations punished?
tab <- data.frame(table(aux$`How are repeated violations punished?`))
names(tab) <- c('Levels', 'Frequency')
p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are repeated violations punished?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are costs distributed?
tab <- data.frame(table(aux$`How are costs distributed?`))
names(tab) <- c('Levels', 'Frequency')
p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are costs distributed?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How often will the agreement be renegotiated?
tab <- data.frame(table(aux$`How often will the agreement be renegotiated?`))
names(tab) <- c('Levels', 'Frequency')
p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How often will the agreement be renegotiated?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```

The two remarkable issues are the low frequency of *Less penalty* in the attribute *How are repeated violations punished?* and the low frequency of *None* for the attribute *What punishments do they use?*. This because when we draw the level none for the attribute *What punishments do they use?* or the level less penalty for *How are repeated violations punished?*, then it makes no sense to have less penalty than the minimum possible.

# Code for the Main Paper

The code for Figure 2 of the paper follows below, with also the point estimates in a companion table.

```{r codefig2}
## Main plot

# Main estimation equation
fm <- selected ~ `Who makes the rules?` +
  `How are conflicts resolved?` +
  `What punishments do they use?` + 
  `How are repeated violations punished?` +
  `How are costs distributed?` +
  `How often will the agreement be renegotiated?`

# Plot
mms <- mm(cj, fm, id = ~Response.ID, alpha = .1, h0=0.5)
p <- plot_mm(mms, vline = 0.5)
ggsave(filename = 'MM_all.pdf', plot = p, width = 6, height = 5)
p

# Table
table_mm(mms, capt = 'Marginal Means -- Full Dataset')
```

The code for Figure 3 of the paper follows below, with also the point estimates in a companion table.

\newpage

```{r codefig3}
## Marginal means by Country

# Argentina
arg <- mm(subset(cj, countryOrigin=='Argentina'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(arg, capt = 'Marginal Means -- Argentina Only')
```

\newpage

```{r}
# Bolivia
bol <- mm(subset(cj, countryOrigin=='Bolivia'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(bol, capt = 'Marginal Means -- Bolivia Only')
```

\newpage

```{r}
# Brazil
bra <- mm(subset(cj, countryOrigin=='Brazil'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(bra, capt = 'Marginal Means -- Brazil Only')
```

\newpage

```{r}
# Chile
chi <- mm(subset(cj, countryOrigin=='Chile'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(chi, capt = 'Marginal Means -- Chile Only')
```

\newpage

```{r}
# Colombia
col <- mm(subset(cj, countryOrigin=='Colombia'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(col, capt = 'Marginal Means -- Colombia Only')
```

\newpage

```{r}
# Costa Rica
cri <- mm(subset(cj, countryOrigin=='Costa Rica'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(cri, capt = 'Marginal Means -- Costa Rica Only')
```

\newpage

```{r}
# Ecuador
ecu <- mm(subset(cj, countryOrigin=='Ecuador'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(ecu, capt = 'Marginal Means -- Ecuador Only')
```

\newpage

```{r}
# Mexico
mex <- mm(subset(cj, countryOrigin=='Mexico'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(mex, capt = 'Marginal Means -- Mexico Only')
```

\newpage

```{r}
# Panama
pan <- mm(subset(cj, countryOrigin=='Panama'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(pan, capt = 'Marginal Means -- Panama Only')
```

\newpage

```{r}
# Peru
per <- mm(subset(cj, countryOrigin=='Peru'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(per, capt = 'Marginal Means -- Peru Only')
```

\newpage

```{r, fig.width = 10, fig.height = 10}
# Changing country labels
arg$country <- 'Argentina'
bol$country <- 'Bolivia'
bra$country <- 'Brazil'
chi$country <- 'Chile'
col$country <- 'Colombia'
cri$country <- 'Costa Rica'
ecu$country <- 'Ecuador'
mex$country <- 'Mexico'
pan$country <- 'Panama'
per$country <- 'Peru'
# Plot by country
p <- plot_mm(rbind(arg, bol, bra, chi, col, 
              cri, ecu, mex, pan, per), 
        group = 'country', vline = 0.5, nr=10) +
  facet_wrap( ~ country, ncol=5)
ggsave(filename = 'MM_country.pdf', 
       plot = p, width = 12, height = 12)
p
```

The code for Figure 4 of the paper follows below, with also the point estimates in a companion table.

```{r}
## Elite type graphs and estimates

# Table for the Executive
res1 <- mm(subset(cj, groupOrigin=='Executive'), 
           fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(res1, capt = 'Marginal Means -- Executive Only')
```

\newpage

```{r}
# Legislative
res2 <- mm(subset(cj, groupOrigin=='Legislative'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(res2, capt = 'Marginal Means -- Legislative Only')
```

\newpage

```{r}
# Civil Society
res3 <- mm(subset(cj, groupOrigin=='Civil Society'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(res3, capt = 'Marginal Means -- Civil Society Only')
```

\newpage

```{r}
# Academia
res4 <- mm(subset(cj, groupOrigin=='Academia'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(res4, capt = 'Marginal Means -- Academia Only')

```

\newpage

```{r, fig.width = 7, fig.height = 8}
# Changing labels
res1$MemberType <- 'Executive'
res2$MemberType <- 'Legislative'
res3$MemberType <- 'Civil Society'
res4$MemberType <- 'Academia'

# Plot by Elite Type
p <- plot_mm(rbind(res1, res2, res3, res4), 
     group = 'MemberType', vline = 0.5, nr=4) + 
  facet_wrap( ~ MemberType, ncol=4)
p
ggsave(filename = 'MM_membertype.pdf', plot = p, 
       width = 8, height = 5)
```

# AMCE (Average Marginal Component Effect) Estimator

This estimator fixes one category and look at changes from this baseline category. Below follows the plots for the main model and the country and elite type subsamples.

```{r}
## Main model
rm(cj)
load('conj.RData')
# Set conjoint baselines
baselines <- list()
baselines$`How often will the agreement be renegotiated?` <- "One year"
baselines$`What punishments do they use?` <- 'None'
baselines$`How are conflicts resolved?` <- 'Government bureaucracy'
baselines$`How are costs distributed?` <- 'Rich countries pay more than poor countries'
attrs <- 
  c("How are conflicts resolved?",
    "How are costs distributed?",
    "How are repeated violations punished?",
    "How often will the agreement be renegotiated?",
    "What punishments do they use?",
    "Who makes the rules?"
    )

results <- 
  cjoint::amce(fm, data=cj, cluster=T, 
               respondent.id="Response.ID", 
               design=conjDesign, 
               baselines = baselines, na.ignore = T)
```

\newpage

```{r}
# Table AMCE -- Full Model 
tableAMCE(results, capt = 'AMCE -- Full Model')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Full Model',
     attribute.names = attrs)
```

\newpage

```{r}
## Country subsample

## Argentina
results <- cjoint::amce(fm, data=cj, cluster=TRUE,
                        respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Argentina')
# AMCE -- Argentina Only
tableAMCE(results, capt = 'AMCE -- Argentina Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Argentina Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Bolivia
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Bolivia')
# Table AMCE -- Full Model 
tableAMCE(results, capt = 'AMCE -- Bolivia Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Bolivia Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Brazil
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Brazil')
# Table AMCE -- Brazil Only
tableAMCE(results, capt = 'AMCE -- Brazil Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Brazil Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Chile
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Chile')
# Table AMCE -- Chile Only
tableAMCE(results, capt = 'AMCE -- Chile Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Chile Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Colombia
results <- cjoint::amce(fm, data=cj, cluster=TRUE, 
                        respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Colombia')
# Table AMCE -- Colombia Only
tableAMCE(results, capt = 'AMCE -- Colombia Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Colombia Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Costa Rica
results <- cjoint::amce(fm, data=cj, cluster=TRUE,
                        respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Costa Rica')
# Table AMCE -- Costa Rica Only
tableAMCE(results, capt = 'AMCE -- Costa Rica Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Costa Rica Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Ecuador
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Ecuador')
# Table AMCE -- Ecuador Only
tableAMCE(results, capt = 'AMCE -- Ecuador Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Ecuador Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Mexico
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Mexico')
# Table AMCE -- Full Model 
tableAMCE(results, capt = 'AMCE -- Mexico Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Mexico Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Panama
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Panama')
# Table AMCE -- Panama Only
tableAMCE(results, capt = 'AMCE -- Panama Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Panama Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Peru
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$countryOrigin=='Peru')
# Table AMCE -- Peru Only
tableAMCE(results, capt = 'AMCE -- Peru Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Peru Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Elite Subsample

# Executive
results <- cjoint::amce(fm, data=cj, cluster=TRUE,
                        respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$groupOrigin=='Executive')
# Table AMCE -- Executive Only
tableAMCE(results, capt = 'AMCE -- Executive Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Executive Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Legislative
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$groupOrigin=='Legislative')
# Table AMCE -- Legislative Only
tableAMCE(results, capt = 'AMCE -- Legislative Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Legislative Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Civil society
results <- cjoint::amce(fm, data=cj, cluster=TRUE, 
                        respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = (cj$groupOrigin=='Civil Society'))
# Table AMCE -- Civil Society Only 
tableAMCE(results, capt = 'AMCE -- Civil Society Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Civil Society Only',
     attribute.names = attrs)
```

\newpage

```{r}
## Academia Only
results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
                        design=conjDesign, baselines = baselines,
                        subset = cj$groupOrigin=='Academia')
# Table AMCE -- Full Model 
tableAMCE(results, capt = 'AMCE -- Academia Only')
```

\newpage

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Academia Only',
     attribute.names = attrs)
```

\newpage

# Bibliography

### 2019-05-13 manuscript/main.tex
reorder files
fix bibliography

--- 2019-05-12 main.tex
@@
 \makeatother
-\usepackage{hyperref}
+\usepackage[hyphens]{url}
+\usepackage[hidelinks]{hyperref}
+\usepackage[hyphenbreaks]{breakurl}
 
@@
 We find that institutional features have a substantial effect on support for climate treaties.
-Latin American elites prefer state-based solutions to global warming, but there is considerable heterogeneity across countries and elite types.
+Latin American elites prefer multilevel state-based solutions to global warming, but there is considerable heterogeneity across countries and elite types.
 Our results suggest novel ways to craft accountable, democratic climate change mitigation agreements, and they offer new insights on how to integrate interventions at the local and international levels.
@@
 Voluntary environmental governance faces further difficulties in new democracies.
-In Latin America, authoritarian regimes discouraged civil participation and reduced social capital, two requirements for effective polycentric arrangements \citep{aligica2014institutional,ostrom1990governing}.
+In Latin America, authoritarian regimes discouraged civil participation and reduced social capital, two necessary conditions for effective polycentric arrangements \citep{aligica2014institutional,ostrom1990governing}.
 Top-down climate policies also create incentives for organised groups to collude with state officials and pursue private interests.
-In that scenario, elites and state representatives have \textit{de facto} veto power over environmental legislation and can override local decisions to their own benefit.
+As a result, elites and state representatives have \textit{de facto} veto power over environmental legislation and can override local decisions to their own benefit.
 
@@
 
-\section{Research Design}%
-\label{sec:research_design}
+\section{Data and Methods}%
+\label{sec:data_and_methods}
 
@@
 First, Latin America is the most biodiverse region in the world and it plays a major role in global climate mitigation projects.
-For instance, the Amazon basin contains about half of the world's carbon stock, so local elites are crucial actors in emissions trading markets \citep{yang2018post}.
+For instance, the Amazon basin contains about half of the world's carbon stock, so local elites are essential for the success of emissions trading markets \citep{yang2018post}.
 Second, Latin American elites have wide disagreements over preservations policies, and the recent shift towards populist governments has highlighted the need for a robust framework to protect environmental resources \citep{ellner2019pinktide}.
 In that regard, veto players can counterbalance governmental time discounting and secure the long-term provision of public goods.
-Lastly, survey experiments on climate policies have focused on a small set of developed countries, so truly comparative experimental work is still scarce.
+Lastly, survey experiments on climate policies have focused on a small set of developed countries, so truly comparative experimental work remains scarce.
 We fill this gap by analysing 10 countries where elites have different stakes at climate change negotiations.
 
-We use an original dataset compiled specifically for this study.
+We use a dataset compiled specifically for this study.
 The sampling process was as follows.
@@
 \label{tab:categories} 
-\begin{tabular}{l !{\vrule width 1}p{9cm}}
+\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
 \Xhline{2\arrayrulewidth}
@@
 In total, there are 6,000 possible value combinations.
-Figure~\ref{fig:conjoint} illustrates our experimental design.\\
+Figure~\ref{fig:conjoint} illustrates our experimental design.
 
@@
 	\centering
-	\includegraphics[width=16cm]{conjoint-cropped.pdf}
+	\includegraphics[width=13cm]{conjoint-cropped.pdf}
 	\caption{\textbf{Example of conjoint experiment design}}
@@
 
-% Add paragraph about marginal means -- cite Leeper (2019).
+We estimate our models with the \texttt{cregg} package \citep{leeper2018cregg} for the \texttt{R} statistical language \citep{rstats2019}.
+We report marginal means instead of average marginal conditional effects (AMCE).
+\citet{leeper2019subgroup} show that AMCEs can be misleading when applied to subgroup analysis as results are sensitive to the choice of reference categories in interactions.
+Marginal means provide a clear description of quantities of interest -- preference towards a given attribute -- and allows for easy comparisons between different groups of respondents.
+AMCE estimates are available in the Supplementary Materials.
 

### 2019-05-13 manuscript/main.tex
working on discussion

@@
 \usepackage[hidelinks]{hyperref}
-\usepackage[hyphenbreaks]{breakurl}
 
@@
 We report marginal means instead of average marginal conditional effects (AMCE).
-\citet{leeper2019subgroup} show that AMCEs can be misleading when applied to subgroup analysis as results are sensitive to the choice of reference categories in interactions.
+\citet{leeper2018subgroup} show that AMCEs can be misleading when applied to subgroup analysis as results are sensitive to the choice of reference categories in interactions.
 Marginal means provide a clear description of quantities of interest -- preference towards a given attribute -- and allows for easy comparisons between different groups of respondents.
@@
 In this article, we analyse whether Latin American elites support a polycentric climate change mitigation regime.
-We find that respondents prefer climate agreements that incorporate multiple government institutions, mainly international and local-level organisations.
-The results remain stable after disaggregating the data by country and elite composition.
-Our experiment also validates the importance of Elinor Ostrom's `design principles' as respondents largely act as her theory predicts.
-But despite the many similarities in the responses, we observe that national and occupational characteristics still influence how elites perceive the costs and benefits of carbon emission agreements.
+We find that respondents prefer international organisations to create rules and resolve conflicts, to impose increasing fines on violators and to renew agreements every five years.
+The results also suggest that respondents are sceptical about non-governmental organisations and consistently reject informal norms as an instrument to solve disputes.
+Taken together, our experiment is very consistent with the Latin American tradition of heavier reliance on the state than on voluntary solutions.
+After disaggregating the data by country and elite type, we find large heterogeneity in the responses.
+Nevertheless, elites remain sceptical about civil society organisations and informal norms.
 
-Our results have meaningful theoretical and practical implications.
-The findings we present here suggest there is considerable scope for new studies on polycentrism.
-For example, our analysis can be extended to examine if the Latin American public has the same opinion on multilevel arrangements as do the elites; and if not, it would be important to ask what explains the mismatch between groups.
-Moreover, future work may address whether other areas of scholarship which assume international-level coordination could benefit from Ostromian polycentricity.
+Our results have important theoretical and practical implications.
+The findings we present here suggest there is considerable scope for new studies on global governance, specially in underrepresented regions.
+Our analysis can be extended to examine if the Latin American public has the same opinion on multilevel arrangements as do the elites; and if not, it would be important to know what explains the mismatch between groups.
+Moreover, future work may address whether other areas of scholarship which assume international-level coordination could benefit from multilevel arrangements, either state-based or not.
 
-We also provide experimental evidence that individuals have preferences that are not fully represented in current climate change agreements.
-We identify that Latin American elites are interested not only in incorporating local demands into the current framework, but also in strengthening the role international organisations play in climate governance.
-In our view, these are reasons for optimism.
-They indicate willingness to engage under-represented sectors of the civil society while at the same time promoting broad, consensus-based carbon emission agreements.
-Polycentricity, in that regard, may provide the trust and accountability this complex system requires.
+The findings also highlight the importance of comparative work in experimental studies.
+As a region, Latin America favours results that are in line with polycentric arrangements, but we find that those preferences derive from the aggregation of heterogeneous effects.
+Our study indicates researchers should be cautious about the external validity of experimental findings.
+% Add a couple more sentences here
+
+With regards to environmental policies, we provide experimental evidence that individuals have preferences that are not fully represented in current climate mitigation agreements.
+We identify that Latin American elites are interested in incorporating different political actors and in strengthening the role international organisations play in climate governance.
+Future climate negotiations can achieve better results if they take those preferences into account.
 
@@
 
-To view supplementary material for this article, please visit \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.
+Please visit \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}} for supplementary materials for this article.
 

### 2019-05-14 manuscript/main.tex
fix section number "discussion"
delete sentence
second draft v0.1

@@
 We find that institutional features have a substantial effect on support for climate treaties.
-Latin American elites prefer multilevel state-based solutions to global warming, but there is considerable heterogeneity across countries and elite types.
-Our results suggest novel ways to craft accountable, democratic climate change mitigation agreements, and they offer new insights on how to integrate interventions at the local and international levels.
+Latin American elites prefer multilevel solutions to global warming, but there is considerable heterogeneity across countries and elite types.
+Our results highlights the possible difficulties in crafting broad climate mitigation agreements, and they offer new insights on how to integrate interventions at the local and international levels.
 
@@
 \noindent 
-\textbf{Word count:} 3,000
+\textbf{Word count:} 3,510
 \end{abstract}
@@
 We use a dataset compiled specifically for this study.
-The sampling process was as follows.
 From 1\textsuperscript{st} of October to 5\textsuperscript{th} of December 2018, we ran an elite survey in ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
@@
 We report marginal means instead of average marginal conditional effects (AMCE).
-\citet{leeper2018subgroup} show that AMCEs can be misleading when applied to subgroup analysis as results are sensitive to the choice of reference categories in interactions.
-Marginal means provide a clear description of quantities of interest -- preference towards a given attribute -- and allows for easy comparisons between different groups of respondents.
-AMCE estimates are available in the Supplementary Materials.
+\citet{leeper2018subgroup} show that AMCEs can be misleading in subgroup analysis as model results are sensitive to the choice of reference categories in interactions.
+In contrast, marginal means provide a clear description of quantities of interest, in our case preferences towards agreement attributes, while allowing for easy comparisons between groups of respondents.
+For these reason, we opt for a visual presentation of our results using marginal means, but readers can refer to the Supplementary Material for ACME estimates.
 
@@
 Figure~\ref{fig:pooled} shows our main results.
-The findings indicate that Latin American elites have a strong preference for a polycentric approach to mitigate climate change.
-We see that the respondents have a positive view about two sources of climate governance, namely those located at the international and the local levels.
-Importantly, Latin American elites support both levels \textit{simultaneously}; this provides evidence that they favour agreements which incorporate action separate political spheres at the same time in the same regime.
+The graph illustrates the preference associate with each attribute of hypothetical climate mitigation agreements.
+Dots with horizontal bars represent point estimates and 95\% confidence intervals from linear regressions with cluster-robust standard errors.
+\\
 
@@
 	\centering
-	\includegraphics[width=.9\linewidth]{pooled.pdf}
-	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement in 10 Latin American countries (pooled data).} The horizontal bars correspond to the 95\% confidence interval of the estimated effect.
-Standard errors are clustered by respondent (respondents = 651; comparisons = 7,968).
-Full numerical estimates are available in the Supplementary Information Appendix.}
+	\includegraphics[width=.9\linewidth,height=11.5cm]{pooled.pdf}
+	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement in 10 Latin American countries (pooled data)}}
 	\label{fig:pooled}
@@
 
-Climate change agreements designed by international organisations are viewed more favourably than the alternatives.
-Global institutions receive 54\% (SE = 1.25) of acceptance in our sample.
-At the same time, respondents clearly indicate their preference for bottom-up rule-making.
-Agreements formulated by local community members and local governments are the second and third-preferred choices with 51.6\% (SE = 1.25) and 49.8\% (SE = 1.24) approval.
-In contrast, Latin American elites see non-governmental organisations are their least preferred option for climate change rule-making with 45.5\% (SE = 1.26).
+Respondents prefer that international organisations create climate mitigation rules (54\%, SE = 1.2), but they also hold favourable views of local communities (51.6\%, SE = 1.25), local governments (49.8\%, SE = 1.2), and state governments (48.6\%, SE = 1.3) as rule-makers.
+Although local communities receive slightly more support than the other alternatives, the differences among the three groups are not statistically significant.
+Interestingly, Latin American elites support multiple levels simultaneously, what suggests they are willing to incorporate separate political spheres into the climate change regime.
+We also observe that non-governmental organisations are the least preferred option for climate change rule-making with 45.5\% (SE = 1.26).
 
@@
 Respondents suggest disputes should be addressed mainly by the United Nations and local courts.
-These two choices have 57.3\% (SE = 1.22) and 54.6\% (SE = 1.23) approval, respectively.
-Private arbitration comes next with 50\% (SE = 1.26), followed by government bureaucracy with 46.4\% (SE = 1.25).
-Informal norms is the least preferred mechanism to deal with conflicts between agreement parties (41\%, SE = 1.25).
+These two choices have 57.3\% (SE = 1.2) and 54.6\% (SE = 1.2) approval, respectively.
+Private arbitration comes next with 50\% (SE = 1.3), followed by government bureaucracy with 46.4\% (SE = 1.3).
+Informal norms receive only 41\% support (SE = 1.3).
 
-In line with Ostrom's predictions, Latin American elites agree with graduated sanctions to repeated offenders (53.2\%, SE = 0.94) and they believe agreement costs should be allocated according to the country's history of emissions (53.6\%, SE = 1.14).
-Moreover, related to the same idea of proportionality, respondents indicate that lawbreakers should be punished with fines (55.3\%, SE = 1.06), which can be easily increased if necessary.
+Latin American elites agree with graduated sanctions to repeated offenders (53.2\%, SE = 0.9) and they believe agreement costs should be allocated according to the country's history of emissions (53.6\%, SE = 1.1).
+Moreover, related to the same idea of proportionality, respondents indicate that lawbreakers should be punished with fines (55.3\%, SE = 1.1), which can be easily increased if necessary.
 
@@
 In terms of agreement duration, respondents are interested in a balance between stability and flexibility.
-This also lends support to Elinor Ostrom's theory of polycentric climate change governance.
 Agreements that either cannot be modified or that last for 50 years are rejected by the interviewees.
@@
 
-We also examine if our results vary across countries and types of elites.
-Figure~\ref{fig:countries} displays the preferred climate change agreement characteristics for each of the 10 countries in our sample.
-Despite Latin America's wide social heterogeneity, we observe that the results are notably similar.
-Most respondents affirm that the United Nations should be responsible for resolving conflicts, and six of them place local courts as the second-preferred choice.
-Peruvian elites are the only to prefer private arbitration to mediate disputes (60.7\%, SE = 4.5).
-We see that respondents in eight out of ten countries are willing to apply fines as punishment for agreement violators, with Chileans and Ecuadorians stating they would rather blacklist defectors.
-The majority also prefers to employ more penalties to repeated offenders.
-
-Another interesting cross-country similarity is that our sample largely supports agreements that can be renegotiated every five or twenty years.
-The difference is particularly wide in Costa Rica, where five-year agreements receive 29.4\% more approval than treaties that will never be revised.
-Chileans, in contrast, have the largest gap between one-year and five-year agreements: 22.7\%.
-Two possible explanations is that Chilean elites are either sensitive to transaction costs of negotiating repeated agreements, or they worry that one-year treaties may not provide enough stability for collective action.
+Overall, the results do not conform to strictly top-down or bottom-down approaches.
+While we do see evidence for coordination at the macro level, respondents are open to input from other government actors and local groups.
+But we find that elites also do not fully agree with polycentric arrangements.
+As we noted above, the data do not show major difference in preferences between federal and local governments and between these and community-based solutions.
+Further, the rejection on non-governmental organisations points to a discredit of self-governing arrangements to deal with global warming.
+This last result is consistent with the Latin American tradition of heavier reliance on the state than on voluntary organisations.
 
@@
 
-There are some interesting differences about which institutions should make the agreement rules.
-Argentinians are particularly sceptical about local community members (44.9\%, SE = 4.4) and favourable towards international organisations (61.9\%, SE = 4.1), whereas Bolivians believe local communities (57.5\%, SE = 5.3) and governments (55.9\%, SE = 5.4) are the best source for climate change rules.
-Respondents in most countries place NGOs as their least-preferred option, but elites from Brazil and Costa Rica have a more positive view of these organisations.
-Federal governments receive the lowest support in Chile, but respondents have the highest preference for local communities with 63\% (SE = 3.9).
+We also examine how our results vary across countries and types of elites.
+Figure~\ref{fig:countries} displays the preferred climate change agreement characteristics for each of the 10 countries in our sample.
+The disaggregated data confirm that elites have a generalised preference for a heavy role by international agencies in terms of solving conflicts, and a generalised dislike for informal norms.
+In addition, the cross-country results also show a preference for a positive role by federal to local government, or local community members being involved in the deliberation process.
+
+However, some of the regional patterns are a by-product of sample aggregation.
+Latin American countries do not agree on which organisations should provide the rules Costa Rica prefers local to global rule-making; Mexico prefers global and dislikes local, similar to Peru, Argentina, and Brazil; Colombia prefers global and local rule-making simultaneously; and Bolivia prefers local organisations to design climate treaties.
+This has important consequences for climate policies in the region.
+The lack of coordination about which governance body should create the treaty may configure a case of Arrow's impossibility theorem \citep{arrow1950difficulty}.
+Should a polycentric system be put for vote at international arenas, it is unclear what would be the outcome as regional consensus seems unlikely.
 
 Figure~\ref{fig:types} shows the results disaggregated by elite type.
-We find that several positions are comparable across all subgroups.
 Academics, members of the civil society, and representatives in the executive and legislative branches hold similar views about how conflicts should be resolved, what punishment to apply to lawbreakers (fines and blacklisting), and the duration of the agreements.
+These are in line with our previous results.
 
@@
 	\includegraphics[width=\linewidth]{types.pdf}
-	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by elite type.} Bars represent 95\% confidence intervals.}
+	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by elite type.}}
 	\label{fig:types}
@@
 
-Differences emerge in two of the six dimensions of interest.
+Differences emerge in two of the six attributes of interest.
 First, whereas academics and members of the civil society are less favourable to allowing the federal government to formulate the rules, members of the executive and the legislative -- part of federal government themselves -- are more likely to see themselves as the preferred rule-makers.
@@
 
-\section*{Discussion}
+\section{Discussion}
 \label{sec:discussion}
 
-In this article, we analyse whether Latin American elites support a polycentric climate change mitigation regime.
-We find that respondents prefer international organisations to create rules and resolve conflicts, to impose increasing fines on violators and to renew agreements every five years.
-The results also suggest that respondents are sceptical about non-governmental organisations and consistently reject informal norms as an instrument to solve disputes.
-Taken together, our experiment is very consistent with the Latin American tradition of heavier reliance on the state than on voluntary solutions.
-After disaggregating the data by country and elite type, we find large heterogeneity in the responses.
-Nevertheless, elites remain sceptical about civil society organisations and informal norms.
+In this article, we examine which attributes of climate change mitigation treaties Latin American elites support.
+We find that respondents prefer international organisations to resolve conflicts, are favourable to imposing increasing fines on violators and renewing agreements every five years.
+Survey participants are sceptical about non-governmental organisations and consistently reject informal norms as an instrument to solve disputes.
+Taken together, our experiment suggests that Latin American elites oppose non-governmental organisations as rule-makers and want legal punishment to agreement violators.
+
+While our results confirm that Latin Americans prefer the state to conduce public policy, they do not match the typical cases of centralised or polycentric climate change regimes suggested in the literature.
+After disaggregating the data by country and elite type, we confirm that elites prefer international organisations to resolve disputes and that federal and local sources of governance should have a say in climate agreements.
+However, we find large heterogeneity in the responses, with groups holding different opinions on how competences should be divided.
 
@@
 As a region, Latin America favours results that are in line with polycentric arrangements, but we find that those preferences derive from the aggregation of heterogeneous effects.
-Our study indicates researchers should be cautious about the external validity of experimental findings.
-% Add a couple more sentences here
+Our study indicates researchers should be cautious about the external validity of experimental studies.
 
@@
 
-Please visit \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}} for supplementary materials for this article.
-
-\newpage
+The data, code, and any additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.
 

### 2019-05-14 manuscript/main.tex

@@
 Latin American elites prefer multilevel solutions to global warming, but there is considerable heterogeneity across countries and elite types.
-Our results highlights the possible difficulties in crafting broad climate mitigation agreements, and they offer new insights on how to integrate interventions at the local and international levels.
+Our results identify possible challenges in crafting regional climate mitigation agreements, and offer new insights on how to integrate interventions at the local and international levels.
 

### 2019-05-14 manuscript/main.tex
edit figures 3 and 4

@@
 	\includegraphics[width=\linewidth]{countries.pdf}
-	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by country.} Bars represent 95\% confidence intervals.}
+	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by country}}
 	\label{fig:countries}
@@
 	\includegraphics[width=\linewidth]{types.pdf}
-	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by elite type.}}
+	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by elite type}}
 	\label{fig:types}

### 2019-05-14 manuscript/main.tex
round number SE
add one word to abstract

@@
 We find that institutional features have a substantial effect on support for climate treaties.
-Latin American elites prefer multilevel solutions to global warming, but there is considerable heterogeneity across countries and elite types.
+Latin American elites prefer multilevel solutions to tackle global warming, but there is considerable heterogeneity across countries and elite types.
 Our results identify possible challenges in crafting regional climate mitigation agreements, and offer new insights on how to integrate interventions at the local and international levels.
@@
 Interestingly, Latin American elites support multiple levels simultaneously, what suggests they are willing to incorporate separate political spheres into the climate change regime.
-We also observe that non-governmental organisations are the least preferred option for climate change rule-making with 45.5\% (SE = 1.26).
+We also observe that non-governmental organisations are the least preferred option for climate change rule-making with 45.5\% (SE = 1.3).
 

### 2019-05-14 manuscript/main.tex
draft v0.2.1

@@
 Latin American elites prefer multilevel solutions to tackle global warming, but there is considerable heterogeneity across countries and elite types.
-Our results identify possible challenges in crafting regional climate mitigation agreements, and offer new insights on how to integrate interventions at the local and international levels.
+Our results identify possible challenges in crafting regional climate mitigation policies and offer new insights on how to integrate interventions at the local and international levels.
 
@@
 \noindent 
-\textbf{Word count:} 3,510
+\textbf{Word count:} 3,527
 \end{abstract}
@@
 
-Despite the potential advantages of polycentric arrangements, two challenges may undermine their popular support.
+Despite the potential advantages of polycentric arrangements, two challenges may undermine their efficiency and popular support.
 First, polycentric systems demand constant civic participation at multiple government levels.
-But as climate change has diffuse benefits but concentrated costs, individuals have few incentives to join collective efforts \citep{barrett2003increasing, heitzig2011self, nordhaus2015climate}.
+Because climate change has diffuse benefits but concentrated costs, individuals have few incentives to join collective efforts \citep{barrett2003increasing, heitzig2011self, nordhaus2015climate}.
 Second, individuals tend to heavily discount climate change investments \citep{dasgupta2008discounting, nordhaus1997discounting}.
@@
 
-We design a conjoint experiment to assess which climate change governance system Latin American elites are willing to support.
-In our survey, we asked 654 `elites' -- academics, members of the executive power, legislators, businesspeople, and members of non-governmental organisations -- to select their preferred agreement in 7 randomised binary choices.
-We recruited respondents from Argentina, Brazil, Bolivia, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
+We design an experiment to assess which climate change governance system Latin American elites are willing to support.
+In our survey, we asked 654 respondents -- academics, members of the executive power, legislators, businesspeople, and members of non-governmental organisations -- to select their preferred agreement in 7 randomised binary choices.
 
@@
 
-We use a conjoint experiment to analyse how institutional characteristics shape support for climate change agreements in Latin America.
-First, Latin America is the most biodiverse region in the world and it plays a major role in global climate mitigation projects.
-For instance, the Amazon basin contains about half of the world's carbon stock, so local elites are essential for the success of emissions trading markets \citep{yang2018post}.
-Second, Latin American elites have wide disagreements over preservations policies, and the recent shift towards populist governments has highlighted the need for a robust framework to protect environmental resources \citep{ellner2019pinktide}.
+We use conjoint experiments to estimate the effect of institutional features on climate mitigation agreements.
+Our sample consists of Latin American elites.
+Latin America is the most biodiverse region in the world and plays a major role in global climate mitigation projects.
+For instance, the Amazon basin contains about half of the world's carbon stock, so local elites are essential for the success of emissions trading markets \citep{benitez2006site,yang2018post}.
+Second, Latin American elites have wide disagreements over preservation policies, and the recent shift towards populist governments has highlighted the need for a robust framework to protect environmental resources \citep{ellner2019pinktide,lyall2019speculative,sagarzazu2019foreign}.
 In that regard, veto players can counterbalance governmental time discounting and secure the long-term provision of public goods.
@@
 We use a dataset compiled specifically for this study.
-From 1\textsuperscript{st} of October to 5\textsuperscript{th} of December 2018, we ran an elite survey in ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
+From 1\textsuperscript{st} of October to 5\textsuperscript{th} of December 2018, we ran an elite survey in Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
 We started by collecting information on Latin American elites.
@@
 
-The categories map the main conceptual differences between polycentric and state-led climate mitigation policies \citep{bechtel2013mass, ostrom1990governing}.
+The categories map main conceptual differences between polycentric and state-led climate mitigation policies \citep[e.g.][]{bechtel2013mass, ostrom1990governing}.
 The conjoint experiment design open the possibility for respondents to combine multiple levels of governance into a single climate change agreement as they see fit.
@@
 We estimate our models with the \texttt{cregg} package \citep{leeper2018cregg} for the \texttt{R} statistical language \citep{rstats2019}.
-We report marginal means instead of average marginal conditional effects (AMCE).
+Here we report marginal means instead of average marginal conditional effects (AMCE) of climate agreement attributes.
 \citet{leeper2018subgroup} show that AMCEs can be misleading in subgroup analysis as model results are sensitive to the choice of reference categories in interactions.
 In contrast, marginal means provide a clear description of quantities of interest, in our case preferences towards agreement attributes, while allowing for easy comparisons between groups of respondents.
-For these reason, we opt for a visual presentation of our results using marginal means, but readers can refer to the Supplementary Material for ACME estimates.
+For these reasons, we include marginal means in the visual presentation of our results, but readers can refer to the Supplementary Material for AMCE estimates.
 
@@
 Figure~\ref{fig:pooled} shows our main results.
-The graph illustrates the preference associate with each attribute of hypothetical climate mitigation agreements.
+The graph illustrates the preference associated with each attribute of hypothetical climate mitigation agreements.
 Dots with horizontal bars represent point estimates and 95\% confidence intervals from linear regressions with cluster-robust standard errors.
@@
 
-Respondents prefer that international organisations create climate mitigation rules (54\%, SE = 1.2), but they also hold favourable views of local communities (51.6\%, SE = 1.25), local governments (49.8\%, SE = 1.2), and state governments (48.6\%, SE = 1.3) as rule-makers.
+Respondents prefer international organisations to establish climate mitigation rules (54\%, SE = 1.2), but they also hold favourable views of local communities (51.6\%, SE = 1.25), local governments (49.8\%, SE = 1.2), and state governments (48.6\%, SE = 1.3) as rule-makers.
 Although local communities receive slightly more support than the other alternatives, the differences among the three groups are not statistically significant.
@@
 
-Latin American elites agree with graduated sanctions to repeated offenders (53.2\%, SE = 0.9) and they believe agreement costs should be allocated according to the country's history of emissions (53.6\%, SE = 1.1).
+Participants agree with graduated sanctions to repeated offenders (53.2\%, SE = 0.9) and they believe agreement costs should be allocated according to the country's history of emissions (53.6\%, SE = 1.1).
 Moreover, related to the same idea of proportionality, respondents indicate that lawbreakers should be punished with fines (55.3\%, SE = 1.1), which can be easily increased if necessary.
@@
 Overall, the results do not conform to strictly top-down or bottom-down approaches.
-While we do see evidence for coordination at the macro level, respondents are open to input from other government actors and local groups.
-But we find that elites also do not fully agree with polycentric arrangements.
+While elites favour solutions provided at the macro level, they are also open to input from other government actors and local groups.
+But we find that respondents do not fully agree with polycentric arrangements.
 As we noted above, the data do not show major difference in preferences between federal and local governments and between these and community-based solutions.
-Further, the rejection on non-governmental organisations points to a discredit of self-governing arrangements to deal with global warming.
+Further, the rejection on non-governmental organisations points to a discredit of self-governing arrangements as a means to deal with global warming.
 This last result is consistent with the Latin American tradition of heavier reliance on the state than on voluntary organisations.
@@
 The disaggregated data confirm that elites have a generalised preference for a heavy role by international agencies in terms of solving conflicts, and a generalised dislike for informal norms.
-In addition, the cross-country results also show a preference for a positive role by federal to local government, or local community members being involved in the deliberation process.
+In addition, the cross-country results show a preference for a positive role by federal and local governments, and that local community members should also participate in the deliberation process.
 
-However, some of the regional patterns are a by-product of sample aggregation.
-Latin American countries do not agree on which organisations should provide the rules Costa Rica prefers local to global rule-making; Mexico prefers global and dislikes local, similar to Peru, Argentina, and Brazil; Colombia prefers global and local rule-making simultaneously; and Bolivia prefers local organisations to design climate treaties.
-This has important consequences for climate policies in the region.
-The lack of coordination about which governance body should create the treaty may configure a case of Arrow's impossibility theorem \citep{arrow1950difficulty}.
-Should a polycentric system be put for vote at international arenas, it is unclear what would be the outcome as regional consensus seems unlikely.
+However, some of the regional preferences are a by-product of sample aggregation.
+Latin American countries do not have a consensus on which organisations should provide the rules.
+For example, Costa Rica prefers local to global rule-making; Mexico prefers global and dislikes local, similar to Peru, Argentina, and Brazil; Colombia prefers global and local rule-making simultaneously; and Bolivia prefers local organisations to design climate treaties.
+This is an important point and has far-reaching consequences for policy design in the region.
+The lack of coordination on rule-making responsibilities may configure a case of Arrow's impossibility theorem \citep{arrow1950difficulty}.
+Should a polycentric system be put for vote at international arenas such as the United Nations or the Organisation of American States, it is not clear how elites would reach a consensus decision.
+Based on our data, we cannot affirm which outcome would prevail.
 
@@
 
-Differences emerge in two of the six attributes of interest.
+Significant differences emerge in two of the six attributes of interest.
 First, whereas academics and members of the civil society are less favourable to allowing the federal government to formulate the rules, members of the executive and the legislative -- part of federal government themselves -- are more likely to see themselves as the preferred rule-makers.

### 2019-05-14 manuscript/main.tex
change figure labels

@@
 \begin{center}
-\caption{\textbf{Design principles for climate change mitigation conjoint experiments}}
+\caption{\textbf{Attributes and values for climate change mitigation conjoint experiments}}
 \label{tab:categories} 
@@
 	\includegraphics[width=13cm]{conjoint-cropped.pdf}
-	\caption{\textbf{Example of conjoint experiment design}}
+	\caption{\textbf{Example of conjoint table presented to respondents}}
 	\label{fig:conjoint}
@@
 	\includegraphics[width=.9\linewidth,height=11.5cm]{pooled.pdf}
-	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement in 10 Latin American countries (pooled data)}}
+	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreements in 10 Latin American countries (pooled data)}}
 	\label{fig:pooled}
@@
 	\includegraphics[width=\linewidth]{countries.pdf}
-	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by country}}
+	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreement by country}}
 	\label{fig:countries}
@@
 	\includegraphics[width=\linewidth]{types.pdf}
-	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by elite type}}
+	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreement by elite type}}
 	\label{fig:types}

### 2019-05-15 manuscript/main.tex
small edits

@@
 The categories map main conceptual differences between polycentric and state-led climate mitigation policies \citep[e.g.][]{bechtel2013mass, ostrom1990governing}.
-The conjoint experiment design open the possibility for respondents to combine multiple levels of governance into a single climate change agreement as they see fit.
+The conjoint experiment design opens the possibility for respondents to combine multiple levels of governance into a single climate change agreement as they see fit.
 We give no prior indication of whether a certain value is more prevalent in actual agreements, and we randomise the values to ensure that they all have the same probability of being selected.
@@
 In contrast, marginal means provide a clear description of quantities of interest, in our case preferences towards agreement attributes, while allowing for easy comparisons between groups of respondents.
-For these reasons, we include marginal means in the visual presentation of our results, but readers can refer to the Supplementary Material for AMCE estimates.
+For these reasons, we include marginal means in the visual presentation of our results.
+Readers can refer to the Supplementary Material for AMCE estimates.
 
@@
 Although local communities receive slightly more support than the other alternatives, the differences among the three groups are not statistically significant.
-Interestingly, Latin American elites support multiple levels simultaneously, what suggests they are willing to incorporate separate political spheres into the climate change regime.
+We note that Latin American elites support multiple governance levels simultaneously, what suggests they are willing to include separate political spheres into a single climate regime.
 We also observe that non-governmental organisations are the least preferred option for climate change rule-making with 45.5\% (SE = 1.3).
@@
 We see a similar pattern with respect to conflict resolution.
-Respondents suggest disputes should be addressed mainly by the United Nations and local courts.
+Respondents affirm disputes should be addressed mainly by the United Nations and local courts.
 These two choices have 57.3\% (SE = 1.2) and 54.6\% (SE = 1.2) approval, respectively.
@@
 Latin American elites believe developing countries should also contribute to the provision of global public goods.
-This suggests that elites view it was legitimate to contribute to climate change solutions, so this may not be a major source of free riding to climate change solutions in the region.
+Our sample views it was legitimate to contribute to climate change solutions, so this may not be a major source of free riding to climate change solutions in the region.
 
@@
 While elites favour solutions provided at the macro level, they are also open to input from other government actors and local groups.
-But we find that respondents do not fully agree with polycentric arrangements.
+But we find that respondents do not fully agree with polycentric arrangements either.
 As we noted above, the data do not show major difference in preferences between federal and local governments and between these and community-based solutions.

### 2019-05-15 appendix/freire-mignozzetti-skarbek-appendix.Rmd
add appendix files

--- 2019-05-13 appendix/appendix.Rmd
@@
 ---
-title: "Appendix: Latin American Elites Favour Polycentric Governance in Climate Change Agreements"
-output: pdf_document
+title: "Supplementary Materials for: Do Elites Support Polycentric Climate Governance? Evidence from Ten Latin American Countries"
+author: 
+- "Danilo Freire[^freire]"
+- "Umberto Mignozzetti[^mignozzetti]"
+- "David Skarbek[^skarbek]"
+date: "15 May 2019"
+fontfamily: libertine
+fontawesome: yes
+fontsize: 12pt
+monospace-url: yes
+spacing: double
+papersize: a4paper
+bibliography: references.bib
+biblio-style: apalike
+output:
+  pdf_document:
+    citation_package: natbib
+    fig_caption: yes
+    number_sections: yes
     toc: true
-number_sections: true
+    keep_tex: no
+    template: template.latex
 header-includes:
-    - \usepackage{setspace}\doublespacing
     - \usepackage{booktabs}
@@
     - \usepackage{array}
-    - \usepackage{libertine}
-    - \usepackage[libertine]{newtxmath}
-    - \usepackage[scaled=.9]{inconsolata}
-    - \usepackage[UKenglish]{babel}
-    - \usepackage[UKenglish]{isodate}
-    - \usepackage{hyperref}
-    - \hypersetup{linkcolor=Mahogany, citecolor=Mahogany, urlcolor=darkblue, breaklinks=true}
     - \usepackage{multirow}
     - \usepackage{wrapfig}
-    - \usepackage{float}
     - \usepackage{colortbl}
@@
     - \usepackage{makecell}
-    - \usepackage{xcolor}
-bibliography: references.bib
 ---
+
+[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, [danilofreire@brown.edu](mailto:danilo_freire@brown.edu), <http://danilofreire.github.io>.
+Corresponding author.
+
+[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, [umberto.mig@nyu.edu](mailto:umberto.mig@nyu.edu), <http://umbertomig.com>.
+
+[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, [davidskarbek@brown.edu](mailto:david_skarbek@brown.edu), <http://davidskarbek.com>.
 
@@
 library(kableExtra)
-setwd("~/Downloads/1_data/")
-load('conj.RData')
+setwd("~/Documents/github/polycentrism/appendix/")
+load('freire-mignozzetti-skarbek.RData')
 
@@
 Lastly, we ask which of the two conjoined choices individuals perceive as more legitimate and more efficient.
-
 Conjoint experiments have many advantages.
@@
 rm(cj)
-load('conj.RData')
+setwd("~/Documents/github/polycentrism/appendix/")
+load('freire-mignozzetti-skarbek.RData')
 # Set conjoint baselines

### 2019-05-16 manuscript/main.tex
small text revisions

@@
 \title{Do Elites Support Polycentric Climate Governance?
-Evidence from Ten Latin American Countries\thanks{We thank Nigel Ashford, F\'{a}bio Barros, Daniel D'Amico, Malte Hendricks, Christian H\"{u}bner, Karina Marzano, Emily Skarbek, and Matias Spektor for helpful and engaging feedback.
+Evidence from Latin American Countries\thanks{We thank Nigel Ashford, F\'{a}bio Barros, Daniel D'Amico, Malte Hendricks, Christian H\"{u}bner, Karina Marzano, Emily Skarbek, and Matias Spektor for helpful and engaging feedback.
 This research received financial support from the Konrad Adenauer Stiftung Latin American Regional Programme for Energy Security and Climate (EKLA-KAS).
@@
 \noindent 
-\textbf{Word count:} 3,527
+\textbf{Word count:} 3,524
 \end{abstract}
@@
 
-Recently, scholars have argued that polycentric approaches provide a better `institutional fit' for natural resource systems \citep{turnheim2018innovating,berkhout2003negotiating, carlisle2017polycentric, ostrom1990governing}.
-Polycentrism is defined as a political arrangement in which formally independent units operating at different levels engage in a continuous process of cooperation and competition \citep{cole2015advantages,aligica2013co}.
-Experiences such as inshore fisheries in Turkey and timber management in Switzerland show that polycentrism induces individual cooperation and allows communities to avoid the `tragedy of the commons', that is, the overexploitation of shared resources \citep{hardin1968tragedy, ostrom1990governing}.
-Authors also point out that polycentric systems improve accountability as decentralisation reduces rent-seeking opportunities for politicians and interest groups \citep{turnheim2018innovating,ostrom2012nested,ostrom2014polycentric,sovacool2013adaptation}.
+Recently, scholars have argued that polycentric approaches provide a better \textit{institutional fit} for natural resource systems \citep{turnheim2018innovating, berkhout2003negotiating, carlisle2017polycentric, ostrom1990governing}.
+Polycentrism is defined as a political arrangement in which formally independent units operating at different levels engage in a continuous process of cooperation and competition \citep{cole2015advantages, aligica2013co}.
+Experiences such as inshore fisheries in Turkey and timber management in Switzerland show that polycentrism induces individual cooperation and allows communities to avoid the \textit{tragedy of the commons}, that is, the overexploitation of shared resources \citep{hardin1968tragedy, ostrom1990governing}.
+Authors also point out that polycentric systems improve accountability as decentralisation reduces rent-seeking opportunities for politicians and interest groups \citep{turnheim2018innovating, ostrom2012nested, ostrom2014polycentric, sovacool2013adaptation}.
 
@@
 Latin America is the most biodiverse region in the world and plays a major role in global climate mitigation projects.
-For instance, the Amazon basin contains about half of the world's carbon stock, so local elites are essential for the success of emissions trading markets \citep{benitez2006site,yang2018post}.
-Second, Latin American elites have wide disagreements over preservation policies, and the recent shift towards populist governments has highlighted the need for a robust framework to protect environmental resources \citep{ellner2019pinktide,lyall2019speculative,sagarzazu2019foreign}.
+For instance, the Amazon basin contains about half of the world's carbon stock, so local elites are essential for the success of emissions trading markets \citep{benitez2006site, yang2018post}.
+Second, Latin American elites have wide disagreements over preservation policies, and the recent shift towards populist governments has highlighted the need for a robust framework to protect environmental resources \citep{ellner2019pinktide, lyall2019speculative, sagarzazu2019foreign}.
 In that regard, veto players can counterbalance governmental time discounting and secure the long-term provision of public goods.
@@
 From 1\textsuperscript{st} of October to 5\textsuperscript{th} of December 2018, we ran an elite survey in Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
-We started by collecting information on Latin American elites.
-Our target was to interview 10 members of the Executive, 10 members of the Legislative, 15 academics, and 15 members of the civil society per country.
-To do so, we built a dataset of prospective respondents ten times our country target.
-Then, we ran an online and telephone survey where we collected information regarding the climate change agreements and other related questions.
+We started by gathering information on Latin American elites.
+For each country, we collected the profiles of 100 members of the Executive, 100 members of the Legislative, 150 academics in the energy sector, and 150 members of the civil society.
+We then sampled these profiles until we achieved a minimum of 10\% of responses within each group.
+We ran our survey both online and by telephone, collecting information on the climate change agreements and other related questions.
 
@@
 We had two teams of enumerators, one based in S\~{a}o Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers.
-Although the overall aim of the survey was 500 responses, the teams collected 654 interviews.
 Please refer to the Supplementary Material for more information about the sampling process and descriptive statistics.
@@
 The categories map main conceptual differences between polycentric and state-led climate mitigation policies \citep[e.g.][]{bechtel2013mass, ostrom1990governing}.
-The conjoint experiment design opens the possibility for respondents to combine multiple levels of governance into a single climate change agreement as they see fit.
+The conjoint experiment design opens the possibility for interviewees to combine multiple levels of governance into a single climate change agreement as they see fit.
 We give no prior indication of whether a certain value is more prevalent in actual agreements, and we randomise the values to ensure that they all have the same probability of being selected.
@@
 In terms of agreement duration, respondents are interested in a balance between stability and flexibility.
-Agreements that either cannot be modified or that last for 50 years are rejected by the interviewees.
+Interviewees reject agreements that either cannot be modified or that last for 50 years.
 Their preference lies in agreements that can be renegotiated every five years (59\%, SE = 1.2), as they are durable enough to provide long-term incentives to the parties, yet still adaptable to unforeseen demands.
@@
 While elites favour solutions provided at the macro level, they are also open to input from other government actors and local groups.
-But we find that respondents do not fully agree with polycentric arrangements either.
+But we find little support for fully polycentric arrangements either.
 As we noted above, the data do not show major difference in preferences between federal and local governments and between these and community-based solutions.
@@
 However, some of the regional preferences are a by-product of sample aggregation.
-Latin American countries do not have a consensus on which organisations should provide the rules.
-For example, Costa Rica prefers local to global rule-making; Mexico prefers global and dislikes local, similar to Peru, Argentina, and Brazil; Colombia prefers global and local rule-making simultaneously; and Bolivia prefers local organisations to design climate treaties.
+Latin American elites do not have a consensus on which organisations should provide the rules.
+For example, elites in Costa Rica prefer local to global rule-making; in Mexico, they prefer global and dislike local, similar to Peru, Argentina, and Brazil; in Colombia, elites favour global and local rule-making simultaneously; and in Bolivia, respondents prefer local organisations to design climate treaties.
 This is an important point and has far-reaching consequences for policy design in the region.
@@
 In this article, we examine which attributes of climate change mitigation treaties Latin American elites support.
-We find that respondents prefer international organisations to resolve conflicts, are favourable to imposing increasing fines on violators and renewing agreements every five years.
+We find that interviewees prefer international organisations to resolve conflicts, are favourable to imposing increasing fines on violators and renewing agreements every five years.
 Survey participants are sceptical about non-governmental organisations and consistently reject informal norms as an instrument to solve disputes.

### 2019-05-16 appendix/freire-mignozzetti-skarbek-appendix.Rmd
add appendix files

@@
 ---
-title: "Supplementary Materials for: Do Elites Support Polycentric Climate Governance? Evidence from Ten Latin American Countries"
+title: |
+       | Supplementary Materials for "Do Elites Support Polycentric Climate Governance? Evidence from Latin American Countries"
 author: 
@@
 - "David Skarbek[^skarbek]"
-date: "15 May 2019"
+date: "16 May 2019"
 fontfamily: libertine
@@
 library(kableExtra)
-setwd("~/Documents/github/polycentrism/appendix/")
 load('freire-mignozzetti-skarbek.RData')
@@
 rm(cj)
-setwd("~/Documents/github/polycentrism/appendix/")
 load('freire-mignozzetti-skarbek.RData')

### 2019-05-16 manuscript/main.tex
Updates from Overleaf

@@
 In Latin America, authoritarian regimes discouraged civil participation and reduced social capital, two necessary conditions for effective polycentric arrangements \citep{aligica2014institutional,ostrom1990governing}.
-Top-down climate policies also create incentives for organised groups to collude with state officials and pursue private interests.
+Top-down climate policies also create incentives for organised groups to collude with state officials and pursue private interests \citep{aklin2013understanding,aklin2014blames}.
 As a result, elites and state representatives have \textit{de facto} veto power over environmental legislation and can override local decisions to their own benefit.

### 2019-07-15 appendix/appendix-institutional-design-climate-policy.Rmd
revisions v1.0

--- 2019-05-16 appendix/freire-mignozzetti-skarbek-appendix.Rmd
@@
 title: |
-       | Supplementary Materials for "Do Elites Support Polycentric Climate Governance? Evidence from Latin American Countries"
+       | Supplementary Materials for "Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries"
 author: 
@@
 - "David Skarbek[^skarbek]"
-date: "16 May 2019"
+date: \today
 fontfamily: libertine
@@
 
-[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, [davidskarbek@brown.edu](mailto:david_skarbek@brown.edu), <http://davidskarbek.com>.
+[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, <davidskarbek@brown.edu>, <http://davidskarbek.com>.
 
@@
 library(kableExtra)
-load('freire-mignozzetti-skarbek.RData')
+load('/Users/politicaltheory/Documents/github/climate/appendix/freire-mignozzetti-skarbek.RData')
 
@@
 
-From 1st of October to 5th of December 2018, we run an elite survey in ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
+\setlength{\parindent}{1cm}
+\setlength{\parskip}{0pt}
+
+From 1st of October to 5th of December 2018, we run an elite survey with respondents from ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
 The survey proceeded in two steps.
@@
 Lastly, we ask which of the two conjoined choices individuals perceive as more legitimate and more efficient.
+
 Conjoint experiments have many advantages.
@@
 
-```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5}
+```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
 aux <- cj %>%
@@
 
-# Frequency of features selected by each attribute
+# Frequency of Features Selected by Each Attribute
 
@@
 ## Main plot
-
 # Main estimation equation
@@
 mms <- mm(cj, fm, id = ~Response.ID, alpha = .1, h0=0.5)
-p <- plot_mm(mms, vline = 0.5)
+p <- plot(mms, vline = 0.5)
+p
 ggsave(filename = 'MM_all.pdf', plot = p, width = 6, height = 5)
-p
 
@@
 arg <- mm(subset(cj, countryOrigin=='Argentina'),  
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(arg, capt = 'Marginal Means -- Argentina Only')
@@
 bol <- mm(subset(cj, countryOrigin=='Bolivia'),  
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(bol, capt = 'Marginal Means -- Bolivia Only')
@@
 bra <- mm(subset(cj, countryOrigin=='Brazil'),  
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(bra, capt = 'Marginal Means -- Brazil Only')
@@
 chi <- mm(subset(cj, countryOrigin=='Chile'),  
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(chi, capt = 'Marginal Means -- Chile Only')
@@
 col <- mm(subset(cj, countryOrigin=='Colombia'),  
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(col, capt = 'Marginal Means -- Colombia Only')
@@
 cri <- mm(subset(cj, countryOrigin=='Costa Rica'),  
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(cri, capt = 'Marginal Means -- Costa Rica Only')
@@
 ecu <- mm(subset(cj, countryOrigin=='Ecuador'),  
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(ecu, capt = 'Marginal Means -- Ecuador Only')
@@
 mex <- mm(subset(cj, countryOrigin=='Mexico'),  
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(mex, capt = 'Marginal Means -- Mexico Only')
@@
 pan <- mm(subset(cj, countryOrigin=='Panama'),  
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(pan, capt = 'Marginal Means -- Panama Only')
@@
 per <- mm(subset(cj, countryOrigin=='Peru'),  
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(per, capt = 'Marginal Means -- Peru Only')
@@
 # Plot by country
-p <- plot_mm(rbind(arg, bol, bra, chi, col, 
+p <- plot(rbind(arg, bol, bra, chi, col, 
               cri, ecu, mex, pan, per), 
-        group = 'country', vline = 0.5, nr=10) +
-  facet_wrap( ~ country, ncol=5)
+        group = 'country', vline = 0.5, nr = 10) +
+  facet_wrap( ~ country, ncol = 5)
+
+p
+
 ggsave(filename = 'MM_country.pdf', 
        plot = p, width = 12, height = 12)
-p
 ```
@@
 res1 <- mm(subset(cj, groupOrigin=='Executive'), 
-           fm, id = ~Response.ID, alpha = .1, h0=0.5)
+           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(res1, capt = 'Marginal Means -- Executive Only')
@@
 res2 <- mm(subset(cj, groupOrigin=='Legislative'), 
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(res2, capt = 'Marginal Means -- Legislative Only')
@@
 res3 <- mm(subset(cj, groupOrigin=='Civil Society'), 
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(res3, capt = 'Marginal Means -- Civil Society Only')
@@
 res4 <- mm(subset(cj, groupOrigin=='Academia'), 
-        fm, id = ~Response.ID, alpha = .1, h0=0.5)
+           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
 table_mm(res4, capt = 'Marginal Means -- Academia Only')
@@
 # Plot by Elite Type
-p <- plot_mm(rbind(res1, res2, res3, res4), 
+p <- plot(rbind(res1, res2, res3, res4), 
      group = 'MemberType', vline = 0.5, nr=4) + 
@@
 p
+
 ggsave(filename = 'MM_membertype.pdf', plot = p, 
@@
 
-```{r}
+```{r, fig.width = 7, fig.height = 8}
 ## Main model
@@
 load('freire-mignozzetti-skarbek.RData')
+
 # Set conjoint baselines
@@
 baselines$`How are costs distributed?` <- 'Rich countries pay more than poor countries'
+baselines$`Who makes the rules?` <- 'Federal government'
+
 attrs <- 
-  c("How are conflicts resolved?",
+  c("Who makes the rules?",
+    "How are conflicts resolved?",
+    "What punishments do they use?",
+    "How are repeated violations punished?",
     "How are costs distributed?",
-    "How are repeated violations punished?",
-    "How often will the agreement be renegotiated?",
-    "What punishments do they use?",
-    "Who makes the rules?"
-    )
+    "How often will the agreement be renegotiated?")
 
@@
                baselines = baselines, na.ignore = T)
-```
-
-\newpage
-
-```{r}
+
 # Table AMCE -- Full Model 
@@
 ```{r, fig.width = 7, fig.height = 8}
+# Plot AMCE -- Full Model
 plot(results, ci=0.9, point.size = .8, dodge.size = 1,

### 2019-07-15 manuscript/institutional-design-climate-policy.tex
revisions v1.0

\documentclass[a4paper,12pt]{article}
\usepackage{titling}
\usepackage{lscape}
\usepackage{amssymb, amsmath, amssymb}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage[stable]{footmisc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scale=.8]{FiraMono}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage{float}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{dcolumn}
\usepackage{mathtools}
\usepackage{caption}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[authoryear]{natbib}
\usepackage{babelbib}
\usepackage{bibentry}
\cleanlookdateon
\exhyphenpenalty=10000
\hyphenpenalty=10000
\widowpenalty=10000
\clubpenalty=10000
\setcitestyle{aysep={}} 
\usepackage{etoolbox}
\makeatletter
\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
	\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
		   {\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
	  {}{}
\makeatother
\usepackage[hyphens]{url}
\usepackage[hidelinks]{hyperref}

\hypersetup{
	pdftitle={Institutional Design and Elite Support for Climate Policies},
	pdfauthor={Danilo Freire, Umberto Mignozzetti and David Skarbek},
	pdfsubject={Climate change governance},
    pdfkeywords={climate change, institutional design, elites, Latin America, regime complex},
	pdfborder={0 0 0},
	breaklinks=true,
	linkcolor=Mahogany,
	citecolor=Mahogany,
	urlcolor=darkblue,
	colorlinks=true} %

\doublespacing

\title{Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries\thanks{We thank Nigel Ashford, F\'{a}bio Barros, Daniel D'Amico, Guilherme Fasolin, Malte Hendricks, Christian H\"{u}bner, Karina Marzano, Emily Skarbek, Matias Spektor and the participants at the FGV IR Seminar for their valuable comments. Special thanks to Natalia Liberato, Lucas Mingardi, Ingrid Oliveira, Catarina Roman, Leticia Santana and Larissa Santos for their excellent research assistance. This research received IRB approval from Brown University (Protocol 2195/2018) and Funda\c{c}\~{a}o Get\'{u}lio Vargas (Protocol 83/2018). We acknowledge financial support from the Konrad Adenauer Stiftung Latin American Regional Programme for Energy Security and Climate (EKLA-KAS) and declare there are no conflicts of interest. The data, code and additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.}
}

\author{Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, \href{mailto:danilo_freire@brown.edu}{\texttt{danilo\_freire@brown.edu}}, \href{http://danilofreire.github.io}{\texttt{http://danilofreire.github.io}}, \href{http://twitter.com/danilofreire}{\texttt{http://twitter.com/danilofreire}}, Voice: +1 (401) 584-2494. Corresponding author.}
\and Umberto Mignozzetti\thanks{School of International Relations, Funda\c{c}\~{a}o Getulio Vargas, S\~{a}o Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, \href{mailto:umberto.mignozzetti@fgv.br}{\texttt{umberto.mignozzetti@fgv.br}}, \href{http://umbertomig.com}{\texttt{http://umbertomig.com}}, \href{http://twitter.com/umbertomig}{\texttt{http://twitter.com/umbertomig}}.} 
\and David Skarbek\thanks{The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \href{http://davidskarbek.com}{\texttt{http://davidskarbek.com}}, \href{http://twitter.com/davidskarbek}{\texttt{http://twitter.com/davidskarbek}}.}
}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\onehalfspacing
\noindent
Climate change mitigation requires global scale governance, but it remains unclear which institutional arrangements maximise the support for collective environmental policies. In this paper, we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate institutional designs randomly drawn from a pool of 6,000 possible climate change agreements. We find that institutional features have a substantial effect on support for climate change mitigation treaties. In general, Latin American elites prefer multilevel solutions with flexible punishment schemes to tackle global warming, but there is considerable heterogeneity across countries and elite types. Our results identify possible challenges in crafting regional climate mitigation policies and offer new insights about how to integrate interventions at the local and international levels.

\vspace{.5cm}

\noindent 
\textbf{Keywords:} climate change, institutional design, elites, Latin America, regime complex

\vspace{.5cm}

\noindent 
\textbf{Word count:} 3884
\end{abstract}

\newpage

\doublespacing

\section{Introduction}%
\label{sec:introduction}

Over the last years, we have seen an emerging consensus about the causes and consequences of anthropogenic climate change. Despite some variation in climate risk beliefs, mostly due to cultural worldviews and political orientation \citep{hornsey2016meta}, recent surveys show that the public is increasingly aware of the dangers of greenhouse gas emissions. For example, 59\% of Americans are sure the Earth's temperature is increasing \citep{stanfordearth2018}; 74\% of European Union citizens consider global warming a `very serious problem' \citep{europe2018survey}; and 90\% of Brazilians believe climate change is already harming people around the world \citep{pew2018climate}.

Yet this consensus does not automatically translate itself into effective political action. Global climate negotiations have progressed slowly under the guidelines of the United Nations Framework Convention on Climate Change (UNFCCC), and there is wide scepticism that multilateral talks will move faster in the next years \citep{cole2015advantages, hjerpe2015views}. As carbon dioxide emissions continue to increase, current efforts may not be sufficient to meet the target of $2^{\circ}$C temperature rise above pre-industrial levels \citep{jordan2015emergence}.

In this scenario, there has been a growing discussion about the desirable features for successful climate change agreements \citep{bechtel2013mass, bechtel2017interests, keohane2011regime}. Climate treaties are incomplete contracts, in which members purposefully design flexible provisions that take domestic circumstances into account \citep[607]{brauninger2000making}. For instance, the Paris Agreement relies on Nationally Determined Contributions (NDCs), a set of greenhouse gas reduction targets each member state voluntarily pledges to achieve. This decentralisation of competences increases the weight of national stakeholders in climate negotiations, and studies have shown that local advocacy coalitions largely explain countries' climate policy performance \citep{jahn2016politics,karapin2012explaining}. Although there is extensive research on the public opinion on global warming in developed economies \citep{bechtel2013mass, bechtel2017interests, beiser2019commitment, buntaine2018preferences, mildenberger2017beliefs}, less is known about the preferences of other key players in climate policy-making: elites in developing countries.

Here we remedy this gap by assessing which climate change governance systems Latin American elites are willing to support. In our survey experiment, we asked 654 respondents -- academics, members of the executive power, legislators, businesspeople and members of non-governmental organisations -- to select their preferred agreement among 7 repetitions of binary choices. We vary the agreements across six dimensions commonly debated in the climate change and institutional design literatures: rule-making capabilities \citep{dubash2013developments, massey2014climate}; conflict resolution mechanisms \citep{huntjens2012institutional, ostrom2014polycentric}; enforcement methods \citep{barrett2008climate}; punishment for repeated violators \citep{ostrom1990governing}; cost sharing \citep{bechtel2013mass}; and agreement duration \citep{copelovitch2014design, marcoux2009institutional}. Variations in any of those features can substantially change the potential outcomes of climate institutions \citep{bodin2017collaborative, ostrom2014polycentric}.

We find that interviewees prefer international organisations to design climate policies and that they are favourable to imposing increasing fines on violators and renewing agreements every five years. Survey participants also want both international institutions and local courts to mediate conflicts, but they are sceptical about non-governmental organisations and consistently reject informal norms as an instrument to solve disputes. The results lend support to theories that define climate governance as a loose `regime complex' instead of a cohesive, integrated institution \citep{abbott2012transnational, colgan2012punctuated, de2014global, keohane2011regime}. A regime complex is one characterised by `an array of partially overlapping and non-hierarchical institutions governing a particular issue area' \citep[279]{raustiala2004regime}. Our findings suggest that Latin American elites embrace the complexity of climate policy and believe that regime should incorporate several layers of governance simultaneously.

This article contributes to three strands of the literature. First, we add experimental evidence to the literature on institutional design. Our results confirm previous studies that stress the importance of institutional features on support for climate change policies \citep{bechtel2013mass, bechtel2017interests}. We show that institutional support varies markedly according to elite type and country of origin, and that this heterogeneity has an important impact on collective choice and preference aggregation.

Second, we contribute to classical theories on international regimes. \citet{abbott2000hard} introduce the idea of hard versus soft international law to explain why actors pursue a variety of legal agreements to foster their interests in the international realm. \citet{mildenberger2017beliefs} and \citet{rosendorff2001optimal} add to this view by positing that the superiority of soft, incomplete contracts is due to observability issues: when compliance is hard to observe, incompleteness is superior than rigid contracts as it avoids unnecessary punishments and improves long-run cooperation stability. \citet{keohane2011regime}, in turn, argue that non-hierarchical international rulings help states to avoid gridlocks by reducing contracting costs and embracing `problem diversity', in which each particular climate problem requires a specific solution. Our results confirm that institutional features should be adapted to the issue at hand, and that flexible regime designs are decisive to foster international cooperation.

Finally, we also present novel information on Latin American elite behaviour regarding climate institutions. Our findings indicate that elites in Latin America favour institutions that do not fit into the broad categories of `centralised' or `polycentric' arrangements, but they rather opt for a balance between the two. The results are consistent with the Latin American tradition of heavier reliance on the state than on self-governed solutions, but we identify that local elites also believe that both international and local-level institutions should engage in climate policy design. The data provide new insights on how Latin American policy-makers can form domestic coalitions and which climate mitigation agreement faces lower resistance from potential veto players \citep{beiser2019commitment, hovi2019club}.

\section{Data and Methods}%
\label{sec:data_and_methods}

We use conjoint experiments to estimate the effect of institutional features on climate mitigation agreements. A conjoint experiment is a statistical technique that allows individuals to express their preferences on multiple attributes of a single topic \citep{bansak2016economic, hainmueller2014causal}. Individuals are presented with hypothetical scenarios, each containing a randomly assigned series of characteristics a researcher wants to evaluate. The individual selects one of them. As the attributes are randomised and individuals choose between different pairs of hypothetical scenarios, we can estimate how individuals value each of the conjoined elements.

We focus on Latin American elites for three reasons. First, elites have a decisive impact on public decisions, as they are closer to the policy-making process. Second, Latin American countries are in a region where extreme weather events are likely to produce substantial damages. According to \citet{eckstein2017global}, Central America alone has four countries in the top ten most affected by extreme weather events. Lastly, Latin America is the most biodiverse region in the world and plays a major role in global climate mitigation projects. For instance, the Amazon basin contains about half of the world's carbon stock, so local elites are essential for the success of emissions trading markets \citep{benitez2006site, yang2018post}.

We use a dataset compiled specifically for this study. From 1\textsuperscript{st} of October to 5\textsuperscript{th} of December 2018, we ran an elite survey with respondents from Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama and Peru. We started by gathering information on Latin American elites. For each country, we collected the profiles of 100 members of the Executive, 100 members of the Legislative, 150 academics in the energy sector and 150 members of the civil society. We then sampled these profiles until we achieved a minimum of 10\% of responses within each group. We ran our survey both online and by telephone, collecting information on the climate change agreements and other related questions in a non-intrusive manner \citep{loewen2010help}. We had two teams of enumerators, one based in S\~{a}o Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers. Please refer to the Supplementary Material for more information about the sampling process and descriptive statistics.

The hypothetical climate change agreements include six attributes: 1) which organisation defines the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated. Table~\ref{tab:categories} describes the values we included in each treaty attribute. \\

\begin{table}[ht]
\begin{center}
\caption{\textbf{Attributes and values for climate change mitigation conjoint experiments}}
\label{tab:categories} 
\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
\Xhline{2\arrayrulewidth}
\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Values}} \\
\Xhline{2\arrayrulewidth} \\
Who makes the rules? & International organisations; federal government; local government; local community members; non-governmental organisations \\
& \\
Conflict resolution mechanism & United Nations; government bureaucracy; local courts; private arbitration; informal norms \\
& \\
Punishment & Imprisonment; fines; blacklist; none \\
& \\
Punishment for repeated violations & More penalty; same; less penalty \\
& \\
Agreement costs & Rich countries pay more than poor countries; proportional to history of emissions; proportional to current emissions; only rich countries pay \\
& \\
Renegotiation & Never; fifty years; twenty years; five years; one year \\
\Xhline{2\arrayrulewidth} 
\end{tabular}
\end{center}
\end{table}

We give no prior indication of whether a certain value is more prevalent in actual agreements to elicit truthful responses from the interviewees. We also randomise the values to ensure that they all have the same probability of being selected. In total, there are 6,000 possible value combinations. Figure~\ref{fig:conjoint} illustrates how a typical conjoint element appeared in the respondents' screen.

\begin{figure}[H]
	\centering
	\includegraphics[width=13cm]{conjoint-cropped.pdf}
	\caption{\textbf{Example of conjoint table presented to respondents}}
	\label{fig:conjoint}
\end{figure}

We estimate our models with the \texttt{cregg} package \citep{leeper2018cregg} for the \texttt{R} statistical language \citep{rstats2019}. Here we report marginal means instead of average marginal conditional effects (AMCE) of climate agreement attributes. \citet{leeper2018subgroup} show that AMCEs can be misleading in subgroup analysis as model results are sensitive to the choice of reference categories in interactions. In contrast, marginal means provide a clear description of quantities of interest, in our case preferences towards agreement attributes, while allowing for easy comparisons between groups of respondents. Their interpretation is also straightforward: a 50\% marginal means estimate represents that respondents are indifferent when this attribute appear vis-\`{a}-vis other attributes. When the coefficient is lower than 50\%, respondents dislike packages with this attribute. Conversely, when the point estimate is higher than 50\%, respondents prefer packages containing a given attribute. Readers can refer to the Supplementary Material for AMCE estimates.

\section{Results}%
\label{sec:results}

Figure~\ref{fig:pooled} shows our main results. The graph illustrates the preference associated with each attribute of hypothetical climate mitigation agreements. Dots with horizontal bars represent point estimates and 95\% confidence intervals from linear regressions with robust standard errors clustered at the respondent level. \\

\begin{figure}[H]
	\centering
	\includegraphics[width=.9\linewidth,height=11.5cm]{pooled.pdf}
	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreements in 10 Latin American countries (pooled data)}}
	\label{fig:pooled}
\end{figure}

Respondents prefer international organisations to establish climate mitigation rules (54\%, SE = 1.2), but they also hold favourable views of local communities (51.6\%, SE = 1.25). We note that Latin American elites support multiple governance levels simultaneously, which suggests that they are willing to include separate political spheres into a single climate policy design.  Local governments (49.8\%, SE = 1.2) and state governments (48.6\%, SE = 1.3) receive slightly more support than the other alternatives, yet the difference between them is not statistically significant. Non-governmental organisations are the least preferred option for climate change rule-making with 45.5\% (SE = 1.3).

We see a similar pattern with respect to conflict resolution. Respondents affirm disputes should be addressed mainly by the United Nations and local courts. These two choices have 57.3\% (SE = 1.2) and 54.6\% (SE = 1.2) approval, respectively. Private arbitration comes next with 50\% (SE = 1.3). Government bureaucracy and informal norms lower the chance of selecting a climate agreement, with 46.4\% (SE = 1.3) and 41\% (SE = 1.3) of support, respectively.

Participants agree with graduated sanctions to repeated offenders (53.2\%, SE = 0.9) and they believe agreement costs should be allocated according to the country's history of emissions (53.6\%, SE = 1.1). Moreover, related to the same idea of proportionality, respondents indicate that lawbreakers should be punished with fines (55.3\%, SE = 1.1), which can be easily increased if necessary. This is in line with the literature arguing that climate change agreements present a middle ground between rigidity and flexibility to accommodate domestic demands and increase national compliance \citep{von2008international}.

Elites believe that Latin American countries should contribute to the provision of global public goods. We find no evidence that respondents intend to free ride on climate agreements, as they position themselves against the idea that rich nations should bear the costs of climate protection. This is conductive to long-term cooperation as placing the burden exclusively on rich countries is off the equilibrium path and would, presumably, not lead to a stable arrangement.

Regarding agreement duration, respondents are interested in a balance between stability and flexibility. Interviewees reject agreements that either cannot be modified or that last for 50 years. Their preference lies in agreements that can be renegotiated every five years (59\%, SE = 1.2). This is consistent with a concern that agreements should be durable enough to provide long-term incentives to the parties, yet remain adaptable to unforeseen demands.

Overall, the results do not conform to strictly top-down or bottom-up approaches, but to a combination of these attributes. While elites favour solutions provided at the macro level, they are also open to input from other government actors and local groups. Further, the rejection on non-governmental organisations points to a discredit of self-governing arrangements as a means to deal with global warming. This result is in line with Latin America's long reliance on the state to design and implement policies.

We also examine how our results vary across countries and types of elites. Figure~\ref{fig:countries} displays the preferred climate change agreement characteristics for each of the 10 countries in our sample. The disaggregated data confirm that elites have a generalised preference for international agencies to solve conflicts, and they dislike informal norms. In addition, the cross-country results show a preference for a positive role by federal and local governments, and that local community members should also participate in the deliberation process.

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{countries.pdf}
	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreement by country}}
	\label{fig:countries}
\end{figure}

However, some of the regional preferences are a by-product of sample aggregation. Latin American elites do not have a consensus on which organisations should provide the rules. For example, elites in Costa Rica prefer local to global rule-making; in Mexico, they prefer global and dislike local, similar to Peru, Argentina and Brazil; in Colombia, elites favour global and local rule-making simultaneously; and in Bolivia, respondents prefer local organisations to design climate treaties. This is an important point and has far-reaching consequences for policy design in the region. The lack of coordination on rule-making responsibilities can make decisions to cycle, lowering the chance of a Condorcet winner. Nevertheless, these dissensions can be resolved by decentralisation, boosting the idea that flexible regime complexes, such as polycentric governance schemes, may provide a solution to potential gridlocks.

Figure~\ref{fig:types} shows the results disaggregated by elite type. Academics, members of the civil society and representatives in the executive and legislative branches hold similar views about how conflicts should be resolved, what punishment to apply to lawbreakers (fines and blacklisting) and the duration of the agreements.

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{types.pdf}
	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreement by elite type}}
	\label{fig:types}
\end{figure}

Differences emerge in two of the six attributes. Academics and members of the civil society are sceptical about the role of federal government in climate policy-making, while members of the executive and legislative -- part of the government themselves -- have a more positive view of national institutions. The differences, however, are not large. Second, members of the legislative prefer rich countries to bear the larger part of agreement costs (58.4\%, SE = 3.5). This provides evidence for the idea of historical responsibility for climate protection, an argument which developing countries have recently brought to climate negotiations \citep{muller2009differentiating,friman2015agreement}.

\section{Discussion}%
\label{sec:discussion}

In this article, we examine which attributes of climate change mitigation treaties Latin American elites support. We find that interviewees prefer international organisations to resolve conflicts, are favourable to imposing increasing fines on violators and renewing agreements every five years. Survey participants are sceptical about non-governmental organisations and consistently reject informal norms as an instrument to solve disputes. Taken together, our evidence suggests that Latin American elites oppose non-governmental organisations as rule-makers and want legal punishment to agreement violators.

While our results confirm that Latin Americans prefer the state to conduct public policy, they do not match the typical dichotomy of hierarchical versus decentralised climate change regimes. After disaggregating the data by country and elite type, we confirm that elites prefer international organisations to resolve disputes and that federal and local sources of governance should have a say in climate agreements. However, we find large heterogeneity in the responses, with groups holding different opinions on how competences should be divided.

Our results have important theoretical and practical implications. The findings we present here suggest there is considerable scope for new studies on global governance, specially in underrepresented regions. Our analysis can be extended to examine if the Latin American public has the same opinion on multilevel arrangements as do the elites; and if not, it would be important to know what explains the mismatch between groups \citep{luna2005political}. Moreover, future work may address whether elites in other regions also understand climate policy as a regime complex, in which different actors play a constructive yet decentralised role in policy-making.

With regards to environmental policies, we identify that Latin American elites are interested in incorporating different political actors and in strengthening the role of international organisations in climate governance. Building on these insights, our study provides novel information to policy-makers, as it evaluates which climate agreements are politically acceptable to Latin American elites. Future climate negotiations can achieve better results if they take those preferences into account.

\section*{Supplementary Material}
\label{sec:supplementary}

The data, code and any additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.

\bibliographystyle{apalike}
\bibliography{references.bib}

\end{document}

### 2019-07-15 appendix/appendix-institutional-design-climate-policy.Rmd
small edits to the appendix

@@
 
-[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, [danilofreire@brown.edu](mailto:danilo_freire@brown.edu), <http://danilofreire.github.io>.
-Corresponding author.
+[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@brown.edu>, <http://danilofreire.github.io>. Corresponding author.
 
@@
 
-# AMCE (Average Marginal Component Effect) Estimator
+# Average Marginal Component Effect (AMCE) Estimator
 

### 2019-07-22 appendix/appendix-institutional-design-climate-policy.Rmd
add info to appendix

@@
 - "David Skarbek[^skarbek]"
-date: \today
+date: July 22, 2019
 fontfamily: libertine
@@
 library(kableExtra)
-load('/Users/politicaltheory/Documents/github/climate/appendix/freire-mignozzetti-skarbek.RData')
+load('freire-mignozzetti-skarbek.RData')
 
@@
 }
-
-# Britishfy
-cj$`Who makes the rules?` <- as.character(cj$`Who makes the rules?`)
-cj$`Who makes the rules?`[cj$`Who makes the rules?`=='International organizations'] = 'International organisations'
-cj$`Who makes the rules?` <- 
-  factor(cj$`Who makes the rules?`, 
-         levels = c("NGOs", "Local community members", 
-                    "Local government", "Federal government",
-                    "International organisations"))
-```
-
-\newpage
-
-# Latin American Elite Survey
+```
+
+# Latin American Elite Survey \label{sec:latam}
 
@@
 
-From 1st of October to 5th of December 2018, we run an elite survey with respondents from ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
+From October 1 to December 5, 2018, we run an elite survey with respondents from ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
 The survey proceeded in two steps.
@@
 After finishing this dataset, we started the surveying stage.
-From 12th of November to 5th of December, we ran the survey by contacting elite members by phone or by email.
-We had two teams of enumerators, one based in Sao Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers.
+From November 12 to December 5, we ran the survey by contacting elite members by phone or by email.
+We had two teams of enumerators, one based in São Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers.
 Although the overall aim of the survey was 500 responses, the teams managed to collect 654 interviews.
 
-# Conjoint Experiment Analysis: Identification and Estimation
+# Conjoint Experiment Analysis: Identification and Estimation \label{sec:conjoint}
 
@@
 First, as each individual chooses between many pairs of possible climate agreements -- seven in our case -- we can drastically increase our sample size without incurring in further financial costs.
-The design thus maximises our research budget.
+The design thus maximizes our research budget.
 Second, individuals rarely decide considering one attribute at a time, as presented in other types of survey experiments.
@@
 
-# Descriptive Statistics
+# Descriptive Statistics \label{sec:descstats}
 
@@
 In the map, we can see that the answers concentrate on the country's capitals, with some variation within the state, but with sample concentrated in the largest municipalities.
-This is expected, as elite members are assumed to gravitate around the capitals and the influence centers.
-
-# Frequency of Features Selected by Each Attribute
+This is also in line with our expectations, as elite members are assumed to gravitate around the capitals and the influence centers.
+
+# Frequency of Features Selected by Each Attribute \label{sec:features}
 
@@
 
-# Average Marginal Component Effect (AMCE) Estimator
+# Average Marginal Component Effect (AMCE) Estimator \label{sec:amce}
 
@@
 
+# APSA Experimental Section Standard Report for Experiments
+
+## Hypothesis
+
+The experiment was designed to study the characteristics of the climate change mitigation treaties favored by Latin American elites.
+
+## Subjects and Context
+
+The eligibility criteria for the research was to belong to one of the four elite profiles listed below.
+
+1. **Executive members**: members of regulatory agencies, politicians (mayors, governors, presidents), members of ministries and secretaries at the federal and state levels.
+2. **Legislative members**: legislators and staff officers from the federal and state level in the researched countries.
+3. **Civil society**: environmental and energy-related NGO members; oil, renewables, and environmental solutions firm owners in the researched countries.
+4. **Academics**: professors from energy and engineering departments of the most prestigious universities in the countries researched.
+
+We decided to include these profiles based on the stakes and influence that such elites have on climate change policies.
+According to the IR constructivist theories, academics have notable influence on our topic of interest as they form the epistemic community around climate change policies.
+Civil society members that have stakes on climate policies are also influential, such as oil-extracting companies, lobby groups, and environmental NGOs.
+Executive and Legislative elites handle the decisions themselves, so their importance.
+
+We selected ten countries to our sample: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
+Our selection criteria were the impact of climate change on each nation, their size and regional importance, and natural resources availability.
+For each country, we built a dataset of potential respondents with at least:
+
+* 150 potential legislative respondents
+* 150 potential executive respondents
+* 200 potential civil society respondents
+* 200 potential academic respondents
+
+These numbers represent ten times the number of respondents we were aiming to interview by the end of the survey.
+The dataset was build from October 5th to November 12th, 2018.
+We hired a team of enumerators that searched the internet for people in the countries that fulfilled our pre-determined elite profiles.
+
+We ranked the possible respondents in two tiers.
+In the first tier we placed people that we had complete information about their profiles: office telephone numbers, emails, social media contacts, and so on.
+In the second tier we included participants that had incomplete profiles, such as those with only online information available.
+The dataset including the first-tier respondents was randomly divided between enumerators in Rio de Janeiro and São Paulo to avoid any eventual biases from the collecting stage.
+Both groups conducted the interviews by phone from November 12th to December 5th, 2018.
+The second tier dataset was used for an online only version of the survey.
+
+The response rate in each of the enumeration sites and in the online only survey follows in the table below.
+
+\vspace{.5cm}
+
+| Country    | Enumeration Place | Type             | Total | Phone  | Online |
+|:-----------|:------------------|:-----------------|------:|-------:|-------:|
+| Argentina  | Rio de Janeiro    | Online and Phone | 300   | 33     | 17     |
+| Bolivia    | Rio de Janeiro    | Online and Phone | 372   | 31     | 11     |
+| Brazil     | Rio de Janeiro    | Online and Phone | 346   | 34     | 12     |
+| Chile      | Rio de Janeiro    | Online and Phone | 417   | 35     | 12     |
+| Colombia   | Rio de Janeiro    | Online and Phone | 445   | 35     | 21     |
+| Costa Rica | Rio de Janeiro    | Online and Phone | 409   | 32     | 11     |
+| Ecuador    | Rio de Janeiro    | Online and Phone | 512   | 30     | 12     |
+| Mexico     | Rio de Janeiro    | Online and Phone | 468   | 41     | 17     |
+| Panama     | Rio de Janeiro    | Online and Phone | 291   | 30     | 14     |
+| Peru       | Rio de Janeiro    | Online and Phone | 243   | 32     | 11     |
+| *TOTAL*    |                   | Online and Phone | 3803  | 333    | 138    |
+|            |                   |                  |       |        |        |
+| Argentina  | Sao Paulo         | Online and Phone | 292   | 48     | 16     |
+| Bolivia    | Sao Paulo         | Online and Phone | 373   | 50     | 13     |
+| Brazil     | Sao Paulo         | Online and Phone | 344   | 43     | 15     |
+| Chile      | Sao Paulo         | Online and Phone | 416   | 41     | 15     |
+| Colombia   | Sao Paulo         | Online and Phone | 448   | 42     | 19     |
+| Costa Rica | Sao Paulo         | Online and Phone | 412   | 44     | 20     |
+| Ecuador    | Sao Paulo         | Online and Phone | 507   | 43     | 18     |
+| Mexico     | Sao Paulo         | Online and Phone | 464   | 41     | 17     |
+| Panama     | Sao Paulo         | Online and Phone | 291   | 50     | 19     |
+| Peru       | Sao Paulo         | Online and Phone | 248   | 44     | 9      |
+| *TOTAL*    |                   | Online and Phone | 3803  | 446    | 161    |
+|            |                   |                  |       |        |        |
+| Argentina  |                   | Online Only      | 517   |        | 19     |
+| Bolivia    |                   | Online Only      | 132   |        | 12     |
+| Brazil     |                   | Online Only      | 1183  |        | 52     |
+| Chile      |                   | Online Only      | 470   |        | 31     |
+| Colombia   |                   | Online Only      | 522   |        | 29     |
+| Costa Rica |                   | Online Only      | 325   |        | 20     |
+| Ecuador    |                   | Online Only      | 460   |        | 37     |
+| Mexico     |                   | Online Only      | 955   |        | 29     |
+| Panama     |                   | Online Only      | 319   |        | 26     |
+| Peru       |                   | Online Only      | 540   |        | 25     |
+| *TOTAL*    |                   | Online Only      | 5569  |        | 293    |
+Table: Survey response rates.
+
+The response rate was 10.24 percent of the original population in the telephone survey (779 of 7606 possible respondents).
+We had an attrition of 61.62 percent from the telephone (779) to the online survey (299).
+The response rate for the online only survey was 5.26 percent (293 of 5569 invited by email).
+
+The conjoint experiment analyzed in this paper was in the online and online-only dataset. Therefore, the relevant column for our data is the last one.
+
+## Allocation Methods
+
+**Random Assignment:** We programmed the experiment using a Python application provided by @strezhnev2013conjoint.
+We translated the original survey questions (as shown in the text) into Portuguese and Spanish, and then embedded the PHP file with the randomization parameters in a Qualtrics survey.
+The PHP code we used to randomize the values of the attributes is available at the project's GitHub repository: <http://github.com/danilofreire/climate-governance>.
+
+For each attribute, the probability of selecting a given component follows a uniform distribution function. The table below describes the results.
+
+\vspace{.5cm}
+
+| **Attribute**                          | **Values**                                   | **Probabilities** |
+|:---------------------------------------|:---------------------------------------------|------------------:|
+| **Who makes the rules?**               | International organizations                  | 1/5               | 
+|                                        | Federal government                           | 1/5               |
+|                                        | Local government                             | 1/5               |
+|                                        | Local community members                      | 1/5               |
+|                                        | Non-governmental organizations               | 1/5               |
+|                                        |                                              |                   |
+| **Conflict resolution mechanism**      | United Nations                               | 1/5               |
+|                                        | Government bureaucracy                       | 1/5               |
+|                                        | Local courts                                 | 1/5               |
+|                                        | Private arbitration                          | 1/5               |
+|                                        | Informal norms                               | 1/5               |
+|                                        |                                              |                   |
+| **Punishment**                         | Imprisonment                                 | 1/4               |
+|                                        | Fines                                        | 1/4               |
+|                                        | Blacklist                                    | 1/4               |
+|                                        | None                                         | 1/4               |
+|                                        |                                              |                   |
+| **Punishment for repeated violations** | More penalty                                 | 1/3               |
+|                                        | Same                                         | 1/3               |
+|                                        | Less penalty                                 | 1/3               |
+|                                        |                                              |                   |
+| **Agreement costs**                    | Rich countries pay more than poor countries  | 1/4               |
+|                                        | Proportional to history of emissions         | 1/4               |
+|                                        | Proportional to current emissions            | 1/4               |
+|                                        | Only rich countries pay                      | 1/4               |
+|                                        |                                              |                   |
+| **Renegotiation**                      | Never                                        | 1/5               |
+|                                        | Fifty years                                  | 1/5               |
+|                                        | Twenty years                                 | 1/5               |
+|                                        | Five years                                   | 1/5               |
+|                                        | One year                                     | 1/5               |
+Table: Conjoint experiment attributes and their respective probabilities.
+
+We added one logical restriction to the set climate change treaties: **Punishment = None** can never appear together with **Punishment for repeated violations = Less penalty**.
+The number of possible treaties are the product of the attributes ($5\times 5 \times 4 \times 3 \times 4 \times 5 = 6,000$) minus the number of removed possibilities ($5\times 5  \times 4 \times 5 = 500$).
+The total number of possible treaties is $5,500$.
+
+## Treatments
+
+**Descriptions of the intervention:** Our treatment was the randomization of components in the conjoined climate mitigation treaties.
+We provided the following description before the conjoint experiment starts, in Spanish and Portuguese:
+
+\vspace{.5cm}
+
+```
+For the following questions, read carefully the instructions below.
+
+Imagine that your country would sign an international treaty to mitigate climate change. 
+A climate mitigation treaty has, in general, the following attributes:
+
+1. Who defines the rules? Which group will define the parameters for the treaty?
+2. How are the conflicts that might happen when the treaty begin be resolved?
+3. What punishments should be applied to ensure compliance?
+4. How will repeated violations be punished?
+5. How are costs for implementing the treaty be distributed?
+6. How often the treaty has to be renegotiated?
+
+In the following questions, you will see variations in treaties on these six attributes.
+Please select the treaty that has the characteristics that you believe are best for your country.
+```
+
+\vspace{.5cm}
+
+The conjoint experiment consisted in comparing two treaties that vary in these six attributes, repeating the application for seven times for each respondent.
+
+\noindent \textbf{Software:} To program the PHP randomization device we used the Python application provided by @strezhnev2013conjoint. We used Qualtrics to administer the survey.
+
+\noindent \textbf{Delivery:} We repeated the conjoint experiment seven times, to improve test power.
+
+\noindent \textbf{Dataset description:} Each line in the dataset represents a given treaty, varying for the selection status (selected versus non-selected) for a given respondent.
+When a respondent finished an entire response set, this adds 14 rows to the dataset.
+Seven rows with the selected treaties and other seven rows with the non-selected treaties.
+
+\noindent \textbf{Deception:} We used no deception in this survey experiment.
+
+## Results
+
+\noindent \textbf{Outcome measures and covariates:} The main outcome is a binary indicator for the selection of a given conjoined package.
+We added two covariates to measure heterogeneous effects: *Country* and *Elite type*.
+
+\noindent \textbf{Questionnaire:} For the English translation of the entire survey instrument, with both the telephone and the online components, see the attachment below.
+
+\noindent \textbf{Statistical analysis:} We fit a marginal means estimator and an AMCE estimator.
+The estimation conditions the results within subjects and the presented conjoined packages.
+The results are available in sections \ref{sec:features} and \ref{sec:amce}.
+
+\noindent \textbf{Missing data and attrition:} Conditional on having started the conjoint experiment, for each task we had the following completion rates:
+
+```{r, fig.width = 7, fig.height = 8}
+barplot(100*table(cj$task)/max(table(cj$task)), xlab = 'Conjoint task', ylab = 'Percentage completed')
+```
+
+## Other information
+
+\noindent \textbf{IRB:} This research received IRB approval from Brown University (Protocol 2195/2018) and Funda\c{c}\~{a}o Get\'{u}lio Vargas (Protocol 83/2018).
+
+\noindent \textbf{Pre-registration:} The result was not pre-registered.
+
+\noindent \textbf{Funding:} The research was funded by Konrad Adenauer Stiftung (KAS).
+KAS provided EUR$ 55,000.00 for this research.
+They have not interfered in the research design and in the question choices.
+
+\noindent \textbf{Replication materials:} The replication materials are <http://github.com/danilofreire/climate-governance>.
+
 # Bibliography

### 2019-07-22 manuscript/institutional-design-climate-policy.tex
add info to appendix

@@
 
-\title{Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries\thanks{We thank Nigel Ashford, F\'{a}bio Barros, Daniel D'Amico, Guilherme Fasolin, Malte Hendricks, Christian H\"{u}bner, Karina Marzano, Emily Skarbek, Matias Spektor and the participants at the FGV IR Seminar for their valuable comments.
+\title{Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries\thanks{We thank Nigel Ashford, F\'{a}bio Barros, Frans Berkhout, Daniel D'Amico, Guilherme Fasolin, Manoel Galdino, Malte Hendricks, Stephen Herzog, Christian H\"{u}bner, Karina Marzano, Davi Moreira, Emily Skarbek and the participants at the FGV IR Seminar for their valuable comments.
 Special thanks to Natalia Liberato, Lucas Mingardi, Ingrid Oliveira, Catarina Roman, Leticia Santana and Larissa Santos for their excellent research assistance.
@@
 
-\date{\today}
+\date{20 July 2019}
 
@@
 \noindent 
-Climate change mitigation requires global scale governance, but it remains unclear which institutional arrangements maximise the support for collective environmental policies.
-In this paper, we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate institutional designs randomly drawn from a pool of 6,000 possible climate change agreements.
-We find that institutional features have a substantial effect on support for climate change mitigation treaties.
-In general, Latin American elites prefer multilevel solutions with flexible punishment schemes to tackle global warming, but there is considerable heterogeneity across countries and elite types.
+Which institutional features do Latin American elites favor for climate change policies?
+Climate change mitigation requires global scale governance, but it remains unclear which institutional arrangements maximize the support for environmental agreements.
+In this paper, we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate institutional designs drawn from a pool of 5,500 possible climate change treaties.
+We find that Latin American elites prefer international organizations to formulate climate policies, support imposing increasing fines on violators and favor renewing agreements every five years.
+We also find that elites support both international institutions and local courts to mediate conflicts, but they distrust non-governmental organizations and reject informal norms as an means of conflict resolution.
 Our results identify possible challenges in crafting regional climate mitigation policies and offer new insights about how to integrate interventions at the local and international levels.
+% reescrever essa última frase
 
@@
 
-Over the last years, we have seen an emerging consensus about the causes and consequences of anthropogenic climate change.
+There is an emerging consensus in public opinion about the causes and consequences of anthropogenic climate change.
 Despite some variation in climate risk beliefs, mostly due to cultural worldviews and political orientation \citep{hornsey2016meta}, recent surveys show that the public is increasingly aware of the dangers of greenhouse gas emissions.
@@
 Yet this consensus does not automatically translate itself into effective political action.
-Global climate negotiations have progressed slowly under the guidelines of the United Nations Framework Convention on Climate Change (UNFCCC), and there is wide scepticism that multilateral talks will move faster in the next years \citep{cole2015advantages, hjerpe2015views}.
+Global climate negotiations have progressed slowly under the guidelines of the United Nations Framework Convention on Climate Change (UNFCCC), and there is widespread skepticism that multilateral talks will advance more quickly in the coming years \citep{cole2015advantages, hjerpe2015views}.
 As carbon dioxide emissions continue to increase, current efforts may not be sufficient to meet the target of $2^{\circ}$C temperature rise above pre-industrial levels \citep{jordan2015emergence}.
@@
 For instance, the Paris Agreement relies on Nationally Determined Contributions (NDCs), a set of greenhouse gas reduction targets each member state voluntarily pledges to achieve.
-This decentralisation of competences increases the weight of national stakeholders in climate negotiations, and studies have shown that local advocacy coalitions largely explain countries' climate policy performance \citep{jahn2016politics,karapin2012explaining}.
+This decentralization of competences increases the importance of national stakeholders in climate negotiations, and studies have shown that local advocacy coalitions largely explain countries' climate policy performance \citep{jahn2016politics,karapin2012explaining}.
 Although there is extensive research on the public opinion on global warming in developed economies \citep{bechtel2013mass, bechtel2017interests, beiser2019commitment, buntaine2018preferences, mildenberger2017beliefs}, less is known about the preferences of other key players in climate policy-making: elites in developing countries.
+% reescrever esse também
 
-Here we remedy this gap by assessing which climate change governance systems Latin American elites are willing to support.
-In our survey experiment, we asked 654 respondents -- academics, members of the executive power, legislators, businesspeople and members of non-governmental organisations -- to select their preferred agreement among 7 repetitions of binary choices.
+We help remedy this gap by assessing which climate change governance systems Latin American elites are willing to support.
+In our survey experiment, we asked 654 respondents -- academics, members of the executive power, legislators, businesspeople and members of non-governmental organizations -- to select their preferred agreement among 7 repetitions of binary choices.
 We vary the agreements across six dimensions commonly debated in the climate change and institutional design literatures: rule-making capabilities \citep{dubash2013developments, massey2014climate}; conflict resolution mechanisms \citep{huntjens2012institutional, ostrom2014polycentric}; enforcement methods \citep{barrett2008climate}; punishment for repeated violators \citep{ostrom1990governing}; cost sharing \citep{bechtel2013mass}; and agreement duration \citep{copelovitch2014design, marcoux2009institutional}.
@@
 
-We find that interviewees prefer international organisations to design climate policies and that they are favourable to imposing increasing fines on violators and renewing agreements every five years.
-Survey participants also want both international institutions and local courts to mediate conflicts, but they are sceptical about non-governmental organisations and consistently reject informal norms as an instrument to solve disputes.
+We find that interviewees prefer international organizations to design climate policies and are favorable to imposing increasing fines on violators and renewing agreements every five years.
+Survey participants also want both international institutions and local courts to mediate conflicts, but they are skeptical about non-governmental organizations and consistently reject informal norms as an instrument to solve disputes.
 The results lend support to theories that define climate governance as a loose `regime complex' instead of a cohesive, integrated institution \citep{abbott2012transnational, colgan2012punctuated, de2014global, keohane2011regime}.
 A regime complex is one characterised by `an array of partially overlapping and non-hierarchical institutions governing a particular issue area' \citep[279]{raustiala2004regime}.
-Our findings suggest that Latin American elites embrace the complexity of climate policy and believe that regime should incorporate several layers of governance simultaneously.
+Our findings suggest that Latin American elites embrace the complexity of climate policy and believe that policies should incorporate several layers of governance simultaneously.
 
@@
 
-Finally, we also present novel information on Latin American elite behaviour regarding climate institutions.
-Our findings indicate that elites in Latin America favour institutions that do not fit into the broad categories of `centralised' or `polycentric' arrangements, but they rather opt for a balance between the two.
-The results are consistent with the Latin American tradition of heavier reliance on the state than on self-governed solutions, but we identify that local elites also believe that both international and local-level institutions should engage in climate policy design.
+Finally, we also present novel information on Latin American elite behavior regarding climate institutions.
+Our findings indicate that elites in Latin America favor institutions that do not fit into the broad categories of `centralized' or `polycentric' arrangements, but they rather opt for a balance between the two.
+The results are consistent with the Latin American tradition of heavier reliance on the state than on self-governed solutions, but we find that local elites also believe that both international and local-level institutions should engage in climate policy design.
 The data provide new insights on how Latin American policy-makers can form domestic coalitions and which climate mitigation agreement faces lower resistance from potential veto players \citep{beiser2019commitment, hovi2019club}.
@@
 A conjoint experiment is a statistical technique that allows individuals to express their preferences on multiple attributes of a single topic \citep{bansak2016economic, hainmueller2014causal}.
-Individuals are presented with hypothetical scenarios, each containing a randomly assigned series of characteristics a researcher wants to evaluate.
+Individuals are presented with two hypothetical scenarios, each containing a randomly assigned series of characteristics a researcher wants to evaluate.
 The individual selects one of them.
-As the attributes are randomised and individuals choose between different pairs of hypothetical scenarios, we can estimate how individuals value each of the conjoined elements.
+As the attributes are randomized, we can estimate how individuals value each of the conjoined elements.
 
 We focus on Latin American elites for three reasons.
-First, elites have a decisive impact on public decisions, as they are closer to the policy-making process.
+First, elites have an important impact on public decisions, as they are often closer to the policy-making process.
 Second, Latin American countries are in a region where extreme weather events are likely to produce substantial damages.
@@
 For instance, the Amazon basin contains about half of the world's carbon stock, so local elites are essential for the success of emissions trading markets \citep{benitez2006site, yang2018post}.
+% aqui tem que entrar mais um resumo do argumento das elites
 
 We use a dataset compiled specifically for this study.
-From 1\textsuperscript{st} of October to 5\textsuperscript{th} of December 2018, we ran an elite survey with respondents from Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama and Peru.
-We started by gathering information on Latin American elites.
+From October 1 to December 5, 2018, we ran an elite survey with respondents from Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama and Peru.
+We started by gathering information on potential interviewees.
 For each country, we collected the profiles of 100 members of the Executive, 100 members of the Legislative, 150 academics in the energy sector and 150 members of the civil society.
@@
 
-The hypothetical climate change agreements include six attributes: 1) which organisation defines the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated.
+The hypothetical climate change agreements include six attributes: 1) which organizations defines the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated.
 Table~\ref{tab:categories} describes the values we included in each treaty attribute.
@@
 \Xhline{2\arrayrulewidth} \\
-Who makes the rules? & International organisations; federal government; local government; local community members; non-governmental organisations \\
+Who makes the rules? & International organizations; federal government; local government; local community members; non-governmental organizations \\
 & \\
@@
 We give no prior indication of whether a certain value is more prevalent in actual agreements to elicit truthful responses from the interviewees.
-We also randomise the values to ensure that they all have the same probability of being selected.
-In total, there are 6,000 possible value combinations.
+We also randomize the values to ensure that they all have the same probability of being selected.
+In total, there are 5,500 possible value combinations.
 Figure~\ref{fig:conjoint} illustrates how a typical conjoint element appeared in the respondents' screen.
@@
 In contrast, marginal means provide a clear description of quantities of interest, in our case preferences towards agreement attributes, while allowing for easy comparisons between groups of respondents.
-Their interpretation is also straightforward: a 50\% marginal means estimate represents that respondents are indifferent when this attribute appear vis-\`{a}-vis other attributes.
+Their interpretation is also straightforward: a 50\% marginal means estimate represents that respondents are indifferent when this attribute appears vis-\`{a}-vis other attributes.
 When the coefficient is lower than 50\%, respondents dislike packages with this attribute.
@@
 
-Respondents prefer international organisations to establish climate mitigation rules (54\%, SE = 1.2), but they also hold favourable views of local communities (51.6\%, SE = 1.25).
+Respondents prefer international organizations to establish climate mitigation rules (54\%, SE = 1.2), but they also hold favorable views of local communities (51.6\%, SE = 1.25).
 We note that Latin American elites support multiple governance levels simultaneously, which suggests that they are willing to include separate political spheres into a single climate policy design.
-Local governments (49.8\%, SE = 1.2) and state governments (48.6\%, SE = 1.3) receive slightly more support than the other alternatives, yet the difference between them is not statistically significant.
-Non-governmental organisations are the least preferred option for climate change rule-making with 45.5\% (SE = 1.3).
+Local governments (49.8\%, SE = 1.2) and federal governments (48.6\%, SE = 1.3) receive slightly more support than the other alternatives, yet the difference between them is not statistically significant.
+Non-governmental organizations are the least preferred option for climate change rule-making with 45.5\% (SE = 1.3).
 
@@
 Private arbitration comes next with 50\% (SE = 1.3).
-Government bureaucracy and informal norms lower the chance of selecting a climate agreement, with 46.4\% (SE = 1.3) and 41\% (SE = 1.3) of support, respectively.
+Government bureaucracy and informal norms lower the chance of selecting a climate agreement, with 46.4\% (SE = 1.3) and 41\% (SE = 1.3) of support.
 
 Participants agree with graduated sanctions to repeated offenders (53.2\%, SE = 0.9) and they believe agreement costs should be allocated according to the country's history of emissions (53.6\%, SE = 1.1).
-Moreover, related to the same idea of proportionality, respondents indicate that lawbreakers should be punished with fines (55.3\%, SE = 1.1), which can be easily increased if necessary.
+Moreover, related to the same idea of proportionality, respondents indicate that lawbreakers should be punished with fines (55.3\%, SE = 1.1), which can be increased if necessary.
 This is in line with the literature arguing that climate change agreements present a middle ground between rigidity and flexibility to accommodate domestic demands and increase national compliance \citep{von2008international}.
@@
 We find no evidence that respondents intend to free ride on climate agreements, as they position themselves against the idea that rich nations should bear the costs of climate protection.
-This is conductive to long-term cooperation as placing the burden exclusively on rich countries is off the equilibrium path and would, presumably, not lead to a stable arrangement.
+This is conductive to long-term cooperation as placing the burden exclusively on rich countries is likely to be off the equilibrium path and would, presumably, not lead to a stable arrangement.
 
@@
 Overall, the results do not conform to strictly top-down or bottom-up approaches, but to a combination of these attributes.
-While elites favour solutions provided at the macro level, they are also open to input from other government actors and local groups.
-Further, the rejection on non-governmental organisations points to a discredit of self-governing arrangements as a means to deal with global warming.
+While elites favor solutions provided at the macro level, they are also open to input from other government actors and local groups.
+Further, the rejection on non-governmental organizations points to a discredit of self-governing arrangements as a means to deal with global warming.
 This result is in line with Latin America's long reliance on the state to design and implement policies.
@@
 Figure~\ref{fig:countries} displays the preferred climate change agreement characteristics for each of the 10 countries in our sample.
-The disaggregated data confirm that elites have a generalised preference for international agencies to solve conflicts, and they dislike informal norms.
+The disaggregated data confirm that elites have a generalized preference for international agencies to solve conflicts, and they dislike informal norms.
 In addition, the cross-country results show a preference for a positive role by federal and local governments, and that local community members should also participate in the deliberation process.
@@
 	\centering
-	\includegraphics[width=\linewidth]{countries.pdf}
+	\includegraphics[width=\linewidth, height=20cm]{countries.pdf}
 	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreement by country}}
@@
 However, some of the regional preferences are a by-product of sample aggregation.
-Latin American elites do not have a consensus on which organisations should provide the rules.
-For example, elites in Costa Rica prefer local to global rule-making; in Mexico, they prefer global and dislike local, similar to Peru, Argentina and Brazil; in Colombia, elites favour global and local rule-making simultaneously; and in Bolivia, respondents prefer local organisations to design climate treaties.
-This is an important point and has far-reaching consequences for policy design in the region.
-The lack of coordination on rule-making responsibilities can make decisions to cycle, lowering the chance of a Condorcet winner.
-Nevertheless, these dissensions can be resolved by decentralisation, boosting the idea that flexible regime complexes, such as polycentric governance schemes, may provide a solution to potential gridlocks.
+Latin American elites do not have a consensus on which organizations should provide the rules.
+For example, elites in Costa Rica prefer local to global rule-making; in Mexico, they prefer global and dislike local, similar to Peru, Argentina and Brazil; in Colombia, elites favor global and local rule-making simultaneously; and in Bolivia, respondents prefer local organizations to design climate treaties.
+This is an important point and might have far-reaching consequences for environmental policy design.
+The lack of coordination on rule-making responsibilities can give rise to decision cycles, lowering the chance of a Condorcet winner.
+Nevertheless, these dissensions might be resolved by decentralization, boosting the idea that flexible regime complexes, such as polycentric governance schemes, might provide a solution to gridlocks.
 
@@
 Differences emerge in two of the six attributes.
-Academics and members of the civil society are sceptical about the role of federal government in climate policy-making, while members of the executive and legislative -- part of the government themselves -- have a more positive view of national institutions.
+Academics and members of the civil society are skeptical about the role of federal government in climate policy-making, while members of the executive and legislative --- part of the government themselves --- have a more positive view of national institutions.
 The differences, however, are not large.
@@
 In this article, we examine which attributes of climate change mitigation treaties Latin American elites support.
-We find that interviewees prefer international organisations to resolve conflicts, are favourable to imposing increasing fines on violators and renewing agreements every five years.
-Survey participants are sceptical about non-governmental organisations and consistently reject informal norms as an instrument to solve disputes.
-Taken together, our evidence suggests that Latin American elites oppose non-governmental organisations as rule-makers and want legal punishment to agreement violators.
+We find that interviewees prefer international organizations to resolve conflicts, are favorable to imposing increasing fines on violators and renewing agreements every five years.
+Survey participants also signal their distrust of non-governmental organizations and informal norms.
+Taken together, our evidence suggests that Latin American elites oppose non-governmental organizations as rule-makers and want legal punishment to agreement violators.
 
-While our results confirm that Latin Americans prefer the state to conduct public policy, they do not match the typical dichotomy of hierarchical versus decentralised climate change regimes.
-After disaggregating the data by country and elite type, we confirm that elites prefer international organisations to resolve disputes and that federal and local sources of governance should have a say in climate agreements.
+While our results confirm that Latin Americans prefer the state to conduct public policy, they do not match the typical dichotomy of hierarchical versus decentralized climate change regimes.
+After disaggregating the data by country and elite type, we confirm that elites prefer international organizations to resolve disputes and that federal and local sources of governance should have a say in climate agreements.
 However, we find large heterogeneity in the responses, with groups holding different opinions on how competences should be divided.
 
-Our results have important theoretical and practical implications.
+Our results have several theoretical and practical implications.
 The findings we present here suggest there is considerable scope for new studies on global governance, specially in underrepresented regions.
@@
 
-With regards to environmental policies, we identify that Latin American elites are interested in incorporating different political actors and in strengthening the role of international organisations in climate governance.
+With regards to environmental policies, we identify that Latin American elites are interested in incorporating different political actors and in strengthening the role of international organizations in climate governance.
 Building on these insights, our study provides novel information to policy-makers, as it evaluates which climate agreements are politically acceptable to Latin American elites.

### 2019-07-22 appendix/appendix-institutional-design-climate-policy.Rmd
update appendix

@@
     template: template.latex
-header-includes:
-    - \usepackage{booktabs}
-    - \usepackage{longtable}
-    - \usepackage{array}
-    - \usepackage{multirow}
-    - \usepackage{wrapfig}
-    - \usepackage{colortbl}
-    - \usepackage{pdflscape}
-    - \usepackage{tabu}
-    - \usepackage{threeparttable}
-    - \usepackage{threeparttablex}
-    - \usepackage[normalem]{ulem}
-    - \usepackage{makecell}
 ---
@@
 
-\noindent \textbf{Replication materials:} The replication materials are <http://github.com/danilofreire/climate-governance>.
+\noindent \textbf{Replication materials:} Available at <http://github.com/danilofreire/climate-governance>.
 

### 2019-07-26 appendix/appendix-institutional-design-climate-policy.Rmd
revised version

@@
 - "David Skarbek[^skarbek]"
-date: July 22, 2019
+date: July 25, 2019
 fontfamily: libertine
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-library(plm); library(tidyverse)
-library(haven); library(clusterSEs)
-library(stargazer); library(cjoint)
-library(sp); library(cregg)
-library(kableExtra)
-load('freire-mignozzetti-skarbek.RData')
-
-plot_mm <- function(
-  x,
-  group = attr(x, "by"),
-  feature_headers = TRUE,
-  header_fmt = "%s",
-  size = 2,
-  xlab = "Marginal Mean",
-  ylab = "",
-  legend_title = if (is.null(group)) "Feature" else group,
-  legend_pos = "bottom",
-  xlim = NULL,
-  vline = 0,
-  vline_color = "gray",
-  theme = ggplot2::theme_bw(),
-  ...
-) {
-
-  # function used in cj and ammplot to produce "fancy" feature labels
-  clean_feature_labels <- function(data, RHS, feature_labels) {
-    if (inherits(data, "cj_df") | inherits(data, "data.frame")) {
-      fancy_labels <- stats::setNames(lapply(data[RHS], attr, "label"), RHS)
-    } else if (inherits(data, "survey.design")) {
-      fancy_labels <- stats::setNames(lapply(data[["variables"]][RHS], attr, "label"), RHS)
-    } else {
-      stop("'data' is not a 'data.frame' or 'survey.design' object")
-    }
-    ## check `feature_labels`, if present
-    missing_labels <- RHS[!RHS %in% names(feature_labels)]
-    feature_labels <- c(feature_labels, stats::setNames(rep(list(NULL), length(missing_labels)), missing_labels))
-    ## clean fancy labels (use variable name if variable has no "label" attribute)
-    for (i in seq_along(feature_labels)) {
-      if (is.null(feature_labels[[i]]) || feature_labels[[i]] == "") {
-        if (is.null(fancy_labels[[RHS[i]]])) {
-          feature_labels[[i]] <- RHS[i]
-        } else {
-          feature_labels[[i]] <- fancy_labels[[RHS[i]]]
-        }
-      }
-    }
-    return(feature_labels)
-  }
-
-  # function to cleanup term labels (due to factor variable blah blah)
-  clean_term_names <- function(x, RHS) {
-    out <- data.frame(feature = character(length(x)), 
-                      level = character(length(x)), 
-                      stringsAsFactors = FALSE)
-    for (i in seq_along(RHS)) {
-      w <- grepl(RHS[i], x)
-      out$feature[w] <- RHS[i]
-      out$level[w] <- sub(paste0("^`?", RHS[i], "`?"), "", x[w])
-    }
-
-    # check whether levels are all unique
-    if (any(duplicated(out$level))) {
-      warning("Some level labels are duplicated across features. This may cause problems!")
-    }
-
-    return(out)
-  }
-
-  # function used to produce a data frame of features and levels
-  make_term_labels_df <- function(data, feature_names, level_order = c("ascending", "descending")) {
-    # setup data
-    if (inherits(data, "data.frame")) {
-      term_levels_list <- lapply(data[feature_names], levels)
-    } else if (inherits(data, "survey.design")) {
-      term_levels_list <- lapply(data[["variables"]][feature_names], levels)
-    } else {
-      stop("'data' is not a 'data.frame' or 'survey.design' object")
-    }
-
-    # figure out level order
-    level_order <- match.arg(level_order)
-    if (level_order == "descending") {
-      term_levels_list[] <- lapply(term_levels_list, rev)
-    }
-
-    # construct data frame
-    term_levels <- rev(unlist(term_levels_list))
-    term_labels <- stats::setNames(rep(feature_names, lengths(term_levels_list)), rev(term_levels))
-    data.frame(feature = unlist(term_labels), level = unlist(names(term_labels)), stringsAsFactors = FALSE)
-  }
-
-  # function used in plot() methods to make pretty feature headers
-  make_feature_headers <- function(x, fmt = "(%s)") {
-    feature_levels <- rev(split(x$level, x$feature))
-    for (i in seq_along(feature_levels)) {
-      feature_levels[[i]] <- levels(x$level)[match(feature_levels[[i]], levels(x$level))]
-      feature_levels[[i]] <- c(feature_levels[[i]], sprintf(fmt, names(feature_levels)[i]))
-    }
-    factor(as.character(x$level), levels = unique(unname(unlist(feature_levels))))
-  }
-
-  # function used to check whether, if specified, the 'feature_order' argument is valid
-  check_feature_order <- function(feature_order, RHS) {
-    if (!is.null(feature_order)) {
-      if (length(RHS) > length(feature_order)) {
-        stop("'feature_order' appears to be missing values")
-      } else if (length(RHS) < length(feature_order)) {
-        stop("'feature_order' appears to have excess values")
-      } else if (any(!names(feature_order) %in% RHS)) {
-        stop("'feature_order' appears to contain erroneous values")
-      }
-    } else {
-      feature_order <- RHS
-    }
-    return(feature_order)
-  }
-
-  # optionally, add gaps between features
-  if (isTRUE(feature_headers)) {
-    x$level <- make_feature_headers(x, fmt = header_fmt)
-    to_merge <- data.frame(feature = unique(x$feature), level = sprintf(header_fmt, unique(x$feature)))
-    if ("BY" %in% names(x)) {
-      to_merge <- do.call("rbind", lapply(unique(x[["BY"]]), function(lev) {
-        to_merge[["BY"]] <- lev
-        to_merge
-      }))
-    } else if (!is.null(group)) {
-      to_merge <- do.call("rbind", lapply(unique(x[[group]]), function(lev) {
-        to_merge[[group]] <- lev
-        to_merge
-      }))
-    }
-    x <- merge(x, to_merge, all = TRUE)
-  }
-
-  if (is.null(group)) {
-    p <- ggplot2::ggplot(data = x, ggplot2::aes_string(x = "estimate", y = "level", colour = "feature"))
-  } else {
-    p <- ggplot2::ggplot(data = x, ggplot2::aes_string(x = "estimate", y = "level", colour = group, group = group))
-  }
-
-  if (is.null(xlim)) {
-    xmin <- min(x$lower, na.rm = TRUE)
-    xmin <- if (xmin < 0) 1.04*xmin else .96*xmin
-    xmax <- max(x$upper, na.rm = TRUE)
-    xmax <- if (xmax > 0) 1.04*xmax else .96*xmax
-    xlim <- c(xmin, xmax)
-  }
-
-  if (!is.null(vline)) {
-    p <- p + ggplot2::geom_vline(xintercept = vline, colour = vline_color)
-  }
-
-  ggplotColours <- function(n = 6, h = c(0, 360) + 15){
-    if ((diff(h) %% 360) < 1) h[2] <- h[2] - 360/n
-    hcl(h = (seq(h[1], h[2], length = n)), c = 100, l = 65)
-  }
-  myColors <- ggplotColours(length(unique(x$feature)))
-  myColors <- c(rep(myColors[1], 6), rep(myColors[2], 5),
-                rep(myColors[3], 4), rep(myColors[4], 5),
-                rep(myColors[5], 6), rep(myColors[6], 6))
-  myFaces <- c(rep('plain', 5), "bold",
-               rep('plain', 4), "bold",
-               rep('plain', 3), "bold",
-               rep('plain', 4), "bold",
-               rep('plain', 5), "bold",
-               rep('plain', 5), "bold")
-  mySizes <-  c(rep(10, 5), 11,
-               rep(10, 4), 11,
-               rep(10, 3), 11,
-               rep(10, 4), 11,
-               rep(10, 5), 11,
-               rep(10, 5), 11)
-  myColors <- rep(myColors, ifelse(length(unique(x[,group])), length(unique(x[,group])), 1))
-
-  p <- p + ggplot2::geom_point(position = ggstance::position_dodgev(height = 0.75), 
-                               size = size, na.rm = TRUE, color = myColors) +
-    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower", xmax = "upper"),  
-                            size = 0.7, height = 0, na.rm = TRUE, color = myColors,
-                            position = ggstance::position_dodgev(height = 0.75))
-  if (is.null(group)) {
-    p <- p + ggplot2::scale_colour_discrete(guide = ggplot2::guide_legend(title = legend_title))
-  } else {
-    p <- p + ggplot2::scale_colour_discrete(breaks = levels(x[[group]]),
-                                            labels = levels(x[[group]]),
-                                            guide = ggplot2::guide_legend(title = legend_title))
-  }
-  p <- p + theme_bw() +
-    ggplot2::scale_x_continuous(limits = xlim, oob = scales::rescale_none) +
-    ggplot2::xlab(xlab) + 
-    ggplot2::ylab(ylab) + 
-    theme + ggplot2::theme(
-      legend.position = legend_pos,
-      panel.grid.major = ggplot2::element_blank(),
-      panel.grid.minor = ggplot2::element_blank(),
-      axis.text.y = element_text(face=myFaces, size = mySizes)
-    ) + 
-    ggplot2::guides(colour = ggplot2::guide_legend(title = legend_title))
-  return(p)
-}
-
+```{r setup, echo=FALSE}
 plotAMCE <- 
@@
 
-# Function
+```
+
+# Latin American Elite Survey \label{sec:latam}
+
+\setlength{\parindent}{1cm}
+\setlength{\parskip}{0pt}
+
+From October 1 to December 5, 2018, we run an elite survey with respondents from ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
+The survey proceeded in two steps.
+
+We collected information on Latin American elites. The target was:
+
+1. Executive members
+2. Legislative members
+3. Civil society
+4. Academics
+
+For each profile, in each country, we aimed at surveying:
+
+1. 10 Executive members
+2. 10 Legislative members
+3. 15 Civil society
+4. 15 Academics
+
+To do so, we build a prospective respondents dataset with ten times these members for each country.
+Then, we run an online and telephone survey where we collected information regarding the climate change agreements and other climate change related problems.
+
+After finishing this dataset, we started the surveying stage.
+From November 12 to December 5, we ran the survey by contacting elite members by phone or by email.
+We had two teams of enumerators, one based in São Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers.
+Although the overall aim of the survey was 500 responses, the teams managed to collect 654 interviews.
+
+# Conjoint Experiment Analysis: Identification and Estimation \label{sec:conjoint}
+
+A conjoint experiment is a statistical technique that allows individuals to express their preferences on multiple attributes of a single topic [@hainmueller2014causal; @bansak2016economic].
+Individuals are presented with two hypothetical scenarios, A and B, each containing a series of characteristics a researcher wants to evaluate.
+The individual chooses one of them.
+As the attributes are randomised and individuals choose between different pairs of hypothetical scenarios, we can estimate how individuals value each of the conjoined elements.
+
+In our research, we ask what features elite members would like to see implemented in a climate change agreement.
+We ask their opinion on 6 questions: 1) who makes the rules; 2) who enforces the laws; 3) what punishment should be used against lawbreakers; 4) how are repeated violations punished; 5) how are costs distributed, and 6) how often the agreement will be renegotiated.
+Each of the questions has four to five different attributes.
+For the first two questions, we ask individuals if they would rather have the community, local governments, federal governments, or international organisations to create or enforce rules.
+As for punishments, we have options ranging from do nothing to fines and incarceration.
+We ask whether the costs of climate change agreements should be paid mostly or exclusively by developed countries, by polluter countries regardless of their wealth, or if costs should be allocated according to the history of emissions of a given nation.
+Individuals also state their preferences for short-term agreements, a proxy we use for flexibility, or for long-term ones, what we see as a proxy for the stability of rules.
+Lastly, we ask which of the two conjoined choices individuals perceive as more legitimate and more efficient.
+
+Conjoint experiments have many advantages.
+First, as each individual chooses between many pairs of possible climate agreements -- seven in our case -- we can drastically increase our sample size without incurring in further financial costs.
+The design thus maximizes our research budget.
+Second, individuals rarely decide considering one attribute at a time, as presented in other types of survey experiments.
+In that regard, our conjoint analysis mirrors how people naturally make their choices, that is, by simultaneously taking several characteristics into consideration.
+Finally, as the experiments consist of a simple choice between A and B, conjoint analyses are easy to understand and to implement.
+This research design reduces the cognitive load interviewees have while answering surveys and as a result, we can expect more accurate responses from our sample.
+
+# Descriptive Statistics \label{sec:descstats}
+
+The main demographic statistics collected were the country and elite types, and the geolocation of the respondents. They follow in the graphs below.
+
+```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
+library(plm); library(tidyverse)
+library(haven); library(clusterSEs)
+library(stargazer); library(cjoint)
+library(sp); library(cregg)
+library(kableExtra)
+load('freire-mignozzetti-skarbek.RData')
+
+aux <- cj %>%
+  select(Response.ID, countryOrigin, groupOrigin, LocationLongitude, LocationLatitude) %>%
+  unique()
+
+# Country
+tab <- data.frame(table(aux$countryOrigin))
+names(tab) <- c('Country', 'Frequency')
+p<- ggplot(data = tab, aes(x = Country, y = Frequency)) +
+  geom_bar(stat = "identity") +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "black") + 
+  theme_bw() + annotate(geom = "text", label = tab$Frequency,
+                        x = tab$Country, y = tab$Frequency + 2)
+p
+
+# Elite type
+tab <- data.frame(table(aux$groupOrigin))
+names(tab) <- c('Group Origin', 'Frequency')
+p<- ggplot(data = tab, aes(x = `Group Origin`, y = Frequency)) +
+  geom_bar(stat = "identity") +
+  theme_bw() + annotate(geom = "text", label = tab$Frequency,
+                        x = tab$`Group Origin`, y = tab$Frequency + 5)
+p
+```
+
+As we can see, we managed to contact more than fifty elite members for all countries but Bolivia and Peru.
+To compensate for the low collection rates in these two countries, note that we exceeded the sample size in all the remaining states.
+
+Considering the elite type, note that we have, as expected, more people from academia and the civil society, followed by Executive and Legislative.
+The legislative collection was below the original target, but above the minimum mark of 5 for each country.
+This is expected, given the difficulty of accessing these elite members.
+
+In the map, we can see that the answers concentrate on the country's capitals, with some variation within the state, but with sample concentrated in the largest municipalities.
+This is also in line with our expectations, as elite members are assumed to gravitate around the capitals and the influence centers.
+
+# Frequency of Features Selected by Each Attribute \label{sec:features}
+
+The figures below display the freature frequency for each attribute, by each task.
+
+```{r attributes, echo=FALSE, fig.align='center', fig.height=4}
+aux <- cj %>%
+  select(Response.ID, `Who makes the rules?`, `How are conflicts resolved?`, `What punishments do they use?`,`How are repeated violations punished?`, `How are costs distributed?`,`How often will the agreement be renegotiated?`) %>%
+  unique()
+
+# Who makes the rules
+tab <- data.frame(table(aux$`Who makes the rules?`))
+names(tab) <- c('Levels', 'Frequency')
+p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
+  geom_bar(stat="identity") +
+  theme_bw() + xlab('Who makes the rules?') +
+  annotate(geom = "text", label = tab$Frequency,
+           x = tab$Levels, y = tab$Frequency + 35) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+p
+
+# How are conflicts resolved?
+tab <- data.frame(table(aux$`How are conflicts resolved?`))
+names(tab) <- c('Levels', 'Frequency')
+p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
+  geom_bar(stat="identity") +
+  theme_bw() + xlab('How are conflicts resolved?') +
+  annotate(geom = "text", label = tab$Frequency,
+           x = tab$Levels, y = tab$Frequency + 35) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+p
+
+# What punishments do they use?
+tab <- data.frame(table(aux$`What punishments do they use?`))
+names(tab) <- c('Levels', 'Frequency')
+p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
+  geom_bar(stat="identity") +
+  theme_bw() + xlab('What punishments do they use?') +
+  annotate(geom = "text", label = tab$Frequency,
+           x = tab$Levels, y = tab$Frequency + 40) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+p
+
+# How are repeated violations punished?
+tab <- data.frame(table(aux$`How are repeated violations punished?`))
+names(tab) <- c('Levels', 'Frequency')
+p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
+  geom_bar(stat="identity") +
+  theme_bw() + xlab('How are repeated violations punished?') +
+  annotate(geom = "text", label = tab$Frequency,
+           x = tab$Levels, y = tab$Frequency + 50) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+p
+
+# How are costs distributed?
+tab <- data.frame(table(aux$`How are costs distributed?`))
+names(tab) <- c('Levels', 'Frequency')
+p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
+  geom_bar(stat="identity") +
+  theme_bw() + xlab('How are costs distributed?') +
+  annotate(geom = "text", label = tab$Frequency,
+           x = tab$Levels, y = tab$Frequency + 50) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+p
+
+# How often will the agreement be renegotiated?
+tab <- data.frame(table(aux$`How often will the agreement be renegotiated?`))
+names(tab) <- c('Levels', 'Frequency')
+p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
+  geom_bar(stat="identity") +
+  theme_bw() + xlab('How often will the agreement be renegotiated?') +
+  annotate(geom = "text", label = tab$Frequency,
+           x = tab$Levels, y = tab$Frequency + 50) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+p
+```
+
+The two remarkable issues are the low frequency of *Less penalty* in the attribute *How are repeated violations punished?* and the low frequency of *None* for the attribute *What punishments do they use?*.
+This because when we draw the level none for the attribute *What punishments do they use?* or the level less penalty for *How are repeated violations punished?*, then it makes no sense to have less penalty than the minimum possible.
+
+# Code for the Main Paper
+
+The code for Figure 2 of the paper follows below. We also include the point estimates in companion tables.
+
+```{r codefig2}
+## Main plot
+# Main estimation equation
+fm <- selected ~ `Who makes the rules?` +
+  `How are conflicts resolved?` +
+  `What punishments do they use?` + 
+  `How are repeated violations punished?` +
+  `How are costs distributed?` +
+  `How often will the agreement be renegotiated?`
+
+# Plot
+mms <- mm(cj, fm, id = ~Response.ID, alpha = .1, h0 = 0.5)
+
+myFaces <- c(rep('plain', 5), "bold",
+             rep('plain', 4), "bold",
+             rep('plain', 3), "bold",
+             rep('plain', 4), "bold",
+             rep('plain', 5), "bold",
+             rep('plain', 5), "bold")
+
+p <- plot(mms, vline = 0.5, header_fmt = "%s", size = 2) +
+  ggplot2::theme(
+    legend.position = "none",
+    panel.grid.major = ggplot2::element_blank(),
+    panel.grid.minor = ggplot2::element_blank(),
+    axis.text.y = element_text(face=myFaces, size = 11)) + 
+    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
+                                                xmax = "upper"),
+                            size = 0.5, height = 0, na.rm = TRUE)
+p
+
+ggsave(filename = 'MM_all.pdf', plot = p, width = 6, height = 5)
+
+# Table
 table_mm <- function(mms, capt) {
@@
 
+table_mm(mms, capt = 'Marginal Means -- Full Dataset')
+```
+
+The code for Figure 3 of the paper follows below, with also the point estimates in a companion table.
+
+\newpage
+
+```{r codefig3}
+## Marginal means by Country
+
+# Argentina
+arg <- mm(subset(cj, countryOrigin=='Argentina'),  
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(arg, capt = 'Marginal Means -- Argentina Only')
+```
+
+\newpage
+
+```{r}
+# Bolivia
+bol <- mm(subset(cj, countryOrigin=='Bolivia'),  
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(bol, capt = 'Marginal Means -- Bolivia Only')
+```
+
+\newpage
+
+```{r}
+# Brazil
+bra <- mm(subset(cj, countryOrigin=='Brazil'),  
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(bra, capt = 'Marginal Means -- Brazil Only')
+```
+
+\newpage
+
+```{r}
+# Chile
+chi <- mm(subset(cj, countryOrigin=='Chile'),  
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(chi, capt = 'Marginal Means -- Chile Only')
+```
+
+\newpage
+
+```{r}
+# Colombia
+col <- mm(subset(cj, countryOrigin=='Colombia'),  
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(col, capt = 'Marginal Means -- Colombia Only')
+```
+
+\newpage
+
+```{r}
+# Costa Rica
+cri <- mm(subset(cj, countryOrigin=='Costa Rica'),  
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(cri, capt = 'Marginal Means -- Costa Rica Only')
+```
+
+\newpage
+
+```{r}
+# Ecuador
+ecu <- mm(subset(cj, countryOrigin=='Ecuador'),  
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(ecu, capt = 'Marginal Means -- Ecuador Only')
+```
+
+\newpage
+
+```{r}
+# Mexico
+mex <- mm(subset(cj, countryOrigin=='Mexico'),  
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(mex, capt = 'Marginal Means -- Mexico Only')
+```
+
+\newpage
+
+```{r}
+# Panama
+pan <- mm(subset(cj, countryOrigin=='Panama'),  
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(pan, capt = 'Marginal Means -- Panama Only')
+```
+
+\newpage
+
+```{r}
+# Peru
+per <- mm(subset(cj, countryOrigin=='Peru'),  
+        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(per, capt = 'Marginal Means -- Peru Only')
+```
+
+\newpage
+
+```{r, fig.width = 13, fig.height = 13}
+# Changing country labels
+arg$country <- 'Argentina'
+bol$country <- 'Bolivia'
+bra$country <- 'Brazil'
+chi$country <- 'Chile'
+col$country <- 'Colombia'
+cri$country <- 'Costa Rica'
+ecu$country <- 'Ecuador'
+mex$country <- 'Mexico'
+pan$country <- 'Panama'
+per$country <- 'Peru'
+# Plot by country
+p <- plot(rbind(arg, bol, bra, chi, col, 
+              cri, ecu, mex, pan, per), 
+        group = 'country', vline = 0.5, nr = 10,
+        header_fmt = "%s", size = 2) +
+  facet_wrap( ~ country, ncol = 5) +
+  ggplot2::theme(
+    axis.text.y = element_text(face=myFaces, size = 13)) + 
+    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
+                                                xmax = "upper"),
+                            size = 0.75, height = 0, na.rm = TRUE)
+
+p
+
+ggsave(filename = 'MM_country.pdf', 
+       plot = p, width = 10, height = 12)
+```
+
+The code for Figure 4 of the paper is available below. Tables displaying the point estimates are also included.
+
+```{r}
+## Elite type graphs and estimates
+
+# Table for the Executive
+res1 <- mm(subset(cj, groupOrigin=='Executive'), 
+           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(res1, capt = 'Marginal Means -- Executive Only')
+```
+
+\newpage
+
+```{r}
+# Legislative
+res2 <- mm(subset(cj, groupOrigin=='Legislative'), 
+           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(res2, capt = 'Marginal Means -- Legislative Only')
+```
+
+\newpage
+
+```{r}
+# Civil Society
+res3 <- mm(subset(cj, groupOrigin=='Civil Society'), 
+           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(res3, capt = 'Marginal Means -- Civil Society Only')
+```
+
+\newpage
+
+```{r}
+# Academia
+res4 <- mm(subset(cj, groupOrigin=='Academia'), 
+           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
+table_mm(res4, capt = 'Marginal Means -- Academia Only')
+
+```
+
+\newpage
+
+```{r, fig.width = 10, fig.height = 8}
+# Changing labels
+res1$MemberType <- 'Executive'
+res2$MemberType <- 'Legislative'
+res3$MemberType <- 'Civil Society'
+res4$MemberType <- 'Academia'
+
+# Plot by Elite Type
+p <- plot(rbind(res1, res2, res3, res4), 
+     group = 'MemberType', vline = 0.5, nr = 4,
+        header_fmt = "%s", size = 2) + 
+  facet_wrap( ~ MemberType, ncol = 4) +
+  ggplot2::theme(
+    axis.text.y = element_text(face=myFaces, size = 11)) + 
+    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
+                                                xmax = "upper"),
+                            size = 0.5, height = 0, na.rm = TRUE,
+                            position = ggstance::position_dodgev(height = 1))
+p
+
+ggsave(filename = 'MM_membertype.pdf', plot = p,
+       width = 8, height = 6)
+```
+
+# Average Marginal Component Effect (AMCE) Estimator \label{sec:amce}
+
+This estimator fixes one category and look at changes from this baseline category. Below follows the plots for the main model and the country and elite type subsamples.
+
+```{r, fig.width = 7, fig.height = 8}
+## Main model
+rm(cj)
+load('freire-mignozzetti-skarbek.RData')
+
+# Set conjoint baselines
+baselines <- list()
+baselines$`How often will the agreement be renegotiated?` <- "One year"
+baselines$`What punishments do they use?` <- 'None'
+baselines$`How are conflicts resolved?` <- 'Government bureaucracy'
+baselines$`How are costs distributed?` <- 'Rich countries pay more than poor countries'
+baselines$`Who makes the rules?` <- 'Federal government'
+
+attrs <- c("Who makes the rules?",
+           "How are conflicts resolved?",
+           "What punishments do they use?",
+           "How are repeated violations punished?",
+           "How are costs distributed?",
+           "How often will the agreement be renegotiated?")
+
+results <- cjoint::amce(fm, data = cj, cluster = TRUE, 
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, 
+                        baselines = baselines, na.ignore = T)
+
+# Table AMCE -- Full Model 
 tableAMCE <- function(results, capt = 'Main Model') {
-  aux <- plotAMCE(results, ci=0.9, point.size = .8, dodge.size = 1,
+  aux <- plotAMCE(results, ci = 0.9, point.size = .8, dodge.size = 1,
      text.size = 10, main = 'AMCE -- Full Model',
@@
   aux <- aux %>%
-    filter(!is.na(group))%>%
+    filter(!is.na(group)) %>%
     select(printvar, pe, se, lower, upper)
@@
 }
-```
-
-# Latin American Elite Survey \label{sec:latam}
-
-\setlength{\parindent}{1cm}
-\setlength{\parskip}{0pt}
-
-From October 1 to December 5, 2018, we run an elite survey with respondents from ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
-The survey proceeded in two steps.
-
-We collected information on Latin American elites. The target was:
-
-1. Executive members
-2. Legislative members
-3. Civil society
-4. Academics
-
-For each profile, in each country, we aimed at surveying:
-
-1. 10 Executive members
-2. 10 Legislative members
-3. 15 Civil society
-4. 15 Academics
-
-To do so, we build a prospective respondents dataset with ten times these members for each country.
-Then, we run an online and telephone survey where we collected information regarding the climate change agreements and other climate change related problems.
-
-After finishing this dataset, we started the surveying stage.
-From November 12 to December 5, we ran the survey by contacting elite members by phone or by email.
-We had two teams of enumerators, one based in São Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers.
-Although the overall aim of the survey was 500 responses, the teams managed to collect 654 interviews.
-
-# Conjoint Experiment Analysis: Identification and Estimation \label{sec:conjoint}
-
-A conjoint experiment is a statistical technique that allows individuals to express their preferences on multiple attributes of a single topic [@hainmueller2014causal; @bansak2016economic].
-Individuals are presented with two hypothetical scenarios, A and B, each containing a series of characteristics a researcher wants to evaluate.
-The individual chooses one of them.
-As the attributes are randomised and individuals choose between different pairs of hypothetical scenarios, we can estimate how individuals value each of the conjoined elements.
-
-In our research, we ask what features elite members would like to see implemented in a climate change agreement.
-We ask their opinion on 6 questions: 1) who makes the rules; 2) who enforces the laws; 3) what punishment should be used against lawbreakers; 4) how are repeated violations punished; 5) how are costs distributed, and 6) how often the agreement will be renegotiated.
-Each of the questions has four to five different attributes.
-For the first two questions, we ask individuals if they would rather have the community, local governments, federal governments, or international organisations to create or enforce rules.
-As for punishments, we have options ranging from do nothing to fines and incarceration.
-We ask whether the costs of climate change agreements should be paid mostly or exclusively by developed countries, by polluter countries regardless of their wealth, or if costs should be allocated according to the history of emissions of a given nation.
-Individuals also state their preferences for short-term agreements, a proxy we use for flexibility, or for long-term ones, what we see as a proxy for the stability of rules.
-Lastly, we ask which of the two conjoined choices individuals perceive as more legitimate and more efficient.
-
-Conjoint experiments have many advantages.
-First, as each individual chooses between many pairs of possible climate agreements -- seven in our case -- we can drastically increase our sample size without incurring in further financial costs.
-The design thus maximizes our research budget.
-Second, individuals rarely decide considering one attribute at a time, as presented in other types of survey experiments.
-In that regard, our conjoint analysis mirrors how people naturally make their choices, that is, by simultaneously taking several characteristics into consideration.
-Finally, as the experiments consist of a simple choice between A and B, conjoint analyses are easy to understand and to implement.
-This research design reduces the cognitive load interviewees have while answering surveys and as a result, we can expect more accurate responses from our sample.
-
-# Descriptive Statistics \label{sec:descstats}
-
-The main demographic statistics collected were the country and elite types, and the geolocation of the respondents. They follow in the graphs below.
-
-```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
-aux <- cj %>%
-  select(Response.ID, countryOrigin, groupOrigin, LocationLongitude, LocationLatitude) %>%
-  unique()
-
-# Country
-tab <- data.frame(table(aux$countryOrigin))
-names(tab) <- c('Country', 'Frequency')
-p<-ggplot(data=tab, aes(x = Country, y=Frequency)) +
-  geom_bar(stat="identity") +
-  geom_hline(yintercept=50, linetype="dashed", color = "black") + 
-  theme_bw() + annotate(geom = "text", label = tab$Frequency,
-                        x = tab$Country, y = tab$Frequency + 2)
-p
-
-# Elite type
-tab <- data.frame(table(aux$groupOrigin))
-names(tab) <- c('Group Origin', 'Frequency')
-p<-ggplot(data=tab, aes(x = `Group Origin`, y=Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + annotate(geom = "text", label = tab$Frequency,
-                        x = tab$`Group Origin`, y = tab$Frequency + 5)
-p
-```
-
-As we can see, we managed to contact more than fifty elite members for all countries but Bolivia and Peru.
-To compensate for the low collection rates in these two countries, note that we exceeded the sample size in all the remaining states.
-
-Considering the elite type, note that we have, as expected, more people from academia and the civil society, followed by Executive and Legislative.
-The legislative collection was below the original target, but above the minimum mark of 5 for each country.
-This is expected, given the difficulty of accessing these elite members.
-
-In the map, we can see that the answers concentrate on the country's capitals, with some variation within the state, but with sample concentrated in the largest municipalities.
-This is also in line with our expectations, as elite members are assumed to gravitate around the capitals and the influence centers.
-
-# Frequency of Features Selected by Each Attribute \label{sec:features}
-
-The figures below display the freature frequency for each attribute, by each task.
-
-```{r attributes, echo=FALSE, fig.align='center', fig.height=4}
-aux <- cj %>%
-  select(Response.ID, `Who makes the rules?`, `How are conflicts resolved?`, `What punishments do they use?`,`How are repeated violations punished?`, `How are costs distributed?`,`How often will the agreement be renegotiated?`) %>%
-  unique()
-
-# Who makes the rules
-tab <- data.frame(table(aux$`Who makes the rules?`))
-names(tab) <- c('Levels', 'Frequency')
-p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + xlab('Who makes the rules?') +
-  annotate(geom = "text", label = tab$Frequency,
-           x = tab$Levels, y = tab$Frequency + 35) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-p
-
-# How are conflicts resolved?
-tab <- data.frame(table(aux$`How are conflicts resolved?`))
-names(tab) <- c('Levels', 'Frequency')
-p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + xlab('How are conflicts resolved?') +
-  annotate(geom = "text", label = tab$Frequency,
-           x = tab$Levels, y = tab$Frequency + 35) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-p
-
-# What punishments do they use?
-tab <- data.frame(table(aux$`What punishments do they use?`))
-names(tab) <- c('Levels', 'Frequency')
-p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + xlab('What punishments do they use?') +
-  annotate(geom = "text", label = tab$Frequency,
-           x = tab$Levels, y = tab$Frequency + 40) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-p
-
-# How are repeated violations punished?
-tab <- data.frame(table(aux$`How are repeated violations punished?`))
-names(tab) <- c('Levels', 'Frequency')
-p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + xlab('How are repeated violations punished?') +
-  annotate(geom = "text", label = tab$Frequency,
-           x = tab$Levels, y = tab$Frequency + 50) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-p
-
-# How are costs distributed?
-tab <- data.frame(table(aux$`How are costs distributed?`))
-names(tab) <- c('Levels', 'Frequency')
-p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + xlab('How are costs distributed?') +
-  annotate(geom = "text", label = tab$Frequency,
-           x = tab$Levels, y = tab$Frequency + 50) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-p
-
-# How often will the agreement be renegotiated?
-tab <- data.frame(table(aux$`How often will the agreement be renegotiated?`))
-names(tab) <- c('Levels', 'Frequency')
-p<-ggplot(data=tab, aes(x = Levels, y=Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + xlab('How often will the agreement be renegotiated?') +
-  annotate(geom = "text", label = tab$Frequency,
-           x = tab$Levels, y = tab$Frequency + 50) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-p
-```
-
-The two remarkable issues are the low frequency of *Less penalty* in the attribute *How are repeated violations punished?* and the low frequency of *None* for the attribute *What punishments do they use?*.
-This because when we draw the level none for the attribute *What punishments do they use?* or the level less penalty for *How are repeated violations punished?*, then it makes no sense to have less penalty than the minimum possible.
-
-# Code for the Main Paper
-
-The code for Figure 2 of the paper follows below, with also the point estimates in a companion table.
-
-```{r codefig2}
-## Main plot
-# Main estimation equation
-fm <- selected ~ `Who makes the rules?` +
-  `How are conflicts resolved?` +
-  `What punishments do they use?` + 
-  `How are repeated violations punished?` +
-  `How are costs distributed?` +
-  `How often will the agreement be renegotiated?`
-
-# Plot
-mms <- mm(cj, fm, id = ~Response.ID, alpha = .1, h0=0.5)
-p <- plot(mms, vline = 0.5)
-p
-ggsave(filename = 'MM_all.pdf', plot = p, width = 6, height = 5)
-
-# Table
-table_mm(mms, capt = 'Marginal Means -- Full Dataset')
-```
-
-The code for Figure 3 of the paper follows below, with also the point estimates in a companion table.
-
-\newpage
-
-```{r codefig3}
-## Marginal means by Country
-
-# Argentina
-arg <- mm(subset(cj, countryOrigin=='Argentina'),  
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(arg, capt = 'Marginal Means -- Argentina Only')
-```
-
-\newpage
-
-```{r}
-# Bolivia
-bol <- mm(subset(cj, countryOrigin=='Bolivia'),  
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(bol, capt = 'Marginal Means -- Bolivia Only')
-```
-
-\newpage
-
-```{r}
-# Brazil
-bra <- mm(subset(cj, countryOrigin=='Brazil'),  
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(bra, capt = 'Marginal Means -- Brazil Only')
-```
-
-\newpage
-
-```{r}
-# Chile
-chi <- mm(subset(cj, countryOrigin=='Chile'),  
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(chi, capt = 'Marginal Means -- Chile Only')
-```
-
-\newpage
-
-```{r}
-# Colombia
-col <- mm(subset(cj, countryOrigin=='Colombia'),  
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(col, capt = 'Marginal Means -- Colombia Only')
-```
-
-\newpage
-
-```{r}
-# Costa Rica
-cri <- mm(subset(cj, countryOrigin=='Costa Rica'),  
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(cri, capt = 'Marginal Means -- Costa Rica Only')
-```
-
-\newpage
-
-```{r}
-# Ecuador
-ecu <- mm(subset(cj, countryOrigin=='Ecuador'),  
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(ecu, capt = 'Marginal Means -- Ecuador Only')
-```
-
-\newpage
-
-```{r}
-# Mexico
-mex <- mm(subset(cj, countryOrigin=='Mexico'),  
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(mex, capt = 'Marginal Means -- Mexico Only')
-```
-
-\newpage
-
-```{r}
-# Panama
-pan <- mm(subset(cj, countryOrigin=='Panama'),  
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(pan, capt = 'Marginal Means -- Panama Only')
-```
-
-\newpage
-
-```{r}
-# Peru
-per <- mm(subset(cj, countryOrigin=='Peru'),  
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(per, capt = 'Marginal Means -- Peru Only')
-```
-
-\newpage
-
-```{r, fig.width = 10, fig.height = 10}
-# Changing country labels
-arg$country <- 'Argentina'
-bol$country <- 'Bolivia'
-bra$country <- 'Brazil'
-chi$country <- 'Chile'
-col$country <- 'Colombia'
-cri$country <- 'Costa Rica'
-ecu$country <- 'Ecuador'
-mex$country <- 'Mexico'
-pan$country <- 'Panama'
-per$country <- 'Peru'
-# Plot by country
-p <- plot(rbind(arg, bol, bra, chi, col, 
-              cri, ecu, mex, pan, per), 
-        group = 'country', vline = 0.5, nr = 10) +
-  facet_wrap( ~ country, ncol = 5)
-
-p
-
-ggsave(filename = 'MM_country.pdf', 
-       plot = p, width = 12, height = 12)
-```
-
-The code for Figure 4 of the paper follows below, with also the point estimates in a companion table.
-
-```{r}
-## Elite type graphs and estimates
-
-# Table for the Executive
-res1 <- mm(subset(cj, groupOrigin=='Executive'), 
-           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(res1, capt = 'Marginal Means -- Executive Only')
-```
-
-\newpage
-
-```{r}
-# Legislative
-res2 <- mm(subset(cj, groupOrigin=='Legislative'), 
-           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(res2, capt = 'Marginal Means -- Legislative Only')
-```
-
-\newpage
-
-```{r}
-# Civil Society
-res3 <- mm(subset(cj, groupOrigin=='Civil Society'), 
-           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(res3, capt = 'Marginal Means -- Civil Society Only')
-```
-
-\newpage
-
-```{r}
-# Academia
-res4 <- mm(subset(cj, groupOrigin=='Academia'), 
-           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(res4, capt = 'Marginal Means -- Academia Only')
-
-```
-
-\newpage
-
-```{r, fig.width = 7, fig.height = 8}
-# Changing labels
-res1$MemberType <- 'Executive'
-res2$MemberType <- 'Legislative'
-res3$MemberType <- 'Civil Society'
-res4$MemberType <- 'Academia'
-
-# Plot by Elite Type
-p <- plot(rbind(res1, res2, res3, res4), 
-     group = 'MemberType', vline = 0.5, nr=4) + 
-  facet_wrap( ~ MemberType, ncol=4)
-p
-
-ggsave(filename = 'MM_membertype.pdf', plot = p, 
-       width = 8, height = 5)
-```
-
-# Average Marginal Component Effect (AMCE) Estimator \label{sec:amce}
-
-This estimator fixes one category and look at changes from this baseline category. Below follows the plots for the main model and the country and elite type subsamples.
-
-```{r, fig.width = 7, fig.height = 8}
-## Main model
-rm(cj)
-load('freire-mignozzetti-skarbek.RData')
-
-# Set conjoint baselines
-baselines <- list()
-baselines$`How often will the agreement be renegotiated?` <- "One year"
-baselines$`What punishments do they use?` <- 'None'
-baselines$`How are conflicts resolved?` <- 'Government bureaucracy'
-baselines$`How are costs distributed?` <- 'Rich countries pay more than poor countries'
-baselines$`Who makes the rules?` <- 'Federal government'
-
-attrs <- 
-  c("Who makes the rules?",
-    "How are conflicts resolved?",
-    "What punishments do they use?",
-    "How are repeated violations punished?",
-    "How are costs distributed?",
-    "How often will the agreement be renegotiated?")
-
-results <- 
-  cjoint::amce(fm, data=cj, cluster=T, 
-               respondent.id="Response.ID", 
-               design=conjDesign, 
-               baselines = baselines, na.ignore = T)
-
-# Table AMCE -- Full Model 
+
 tableAMCE(results, capt = 'AMCE -- Full Model')
@@
 # Plot AMCE -- Full Model
-plot(results, ci=0.9, point.size = .8, dodge.size = 1,
+plot(results, ci = 0.9, point.size = .8, dodge.size = 1,
      text.size = 10, main = 'AMCE -- Full Model',
@@
 ## Argentina
-results <- cjoint::amce(fm, data=cj, cluster=TRUE,
-                        respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$countryOrigin=='Argentina')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$countryOrigin == 'Argentina')
 # AMCE -- Argentina Only
@@
 ## Bolivia
-results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$countryOrigin=='Bolivia')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$countryOrigin == 'Bolivia')
 # Table AMCE -- Full Model 
@@
 ## Brazil
-results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$countryOrigin=='Brazil')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$countryOrigin == 'Brazil')
 # Table AMCE -- Brazil Only
@@
 ## Chile
-results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$countryOrigin=='Chile')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$countryOrigin == 'Chile')
 # Table AMCE -- Chile Only
@@
 ## Colombia
-results <- cjoint::amce(fm, data=cj, cluster=TRUE, 
-                        respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$countryOrigin=='Colombia')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$countryOrigin == 'Colombia')
 # Table AMCE -- Colombia Only
@@
 ## Costa Rica
-results <- cjoint::amce(fm, data=cj, cluster=TRUE,
-                        respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$countryOrigin=='Costa Rica')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$countryOrigin == 'Costa Rica')
 # Table AMCE -- Costa Rica Only
@@
 ## Ecuador
-results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$countryOrigin=='Ecuador')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$countryOrigin == 'Ecuador')
 # Table AMCE -- Ecuador Only
@@
 ## Mexico
-results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$countryOrigin=='Mexico')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$countryOrigin == 'Mexico')
 # Table AMCE -- Full Model 
@@
 ## Panama
-results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$countryOrigin=='Panama')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$countryOrigin == 'Panama')
 # Table AMCE -- Panama Only
@@
 ## Peru
-results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$countryOrigin=='Peru')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$countryOrigin == 'Peru')
 # Table AMCE -- Peru Only
@@
 # Executive
-results <- cjoint::amce(fm, data=cj, cluster=TRUE,
-                        respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$groupOrigin=='Executive')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$groupOrigin == 'Executive')
 # Table AMCE -- Executive Only
@@
 ## Legislative
-results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$groupOrigin=='Legislative')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$groupOrigin == 'Legislative')
 # Table AMCE -- Legislative Only
@@
 ## Civil society
-results <- cjoint::amce(fm, data=cj, cluster=TRUE, 
-                        respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = (cj$groupOrigin=='Civil Society'))
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$groupOrigin == 'Civil Society')
 # Table AMCE -- Civil Society Only 
@@
 ## Academia Only
-results <- cjoint::amce(fm, data=cj, cluster=TRUE, respondent.id="Response.ID", 
-                        design=conjDesign, baselines = baselines,
-                        subset = cj$groupOrigin=='Academia')
+results <- cjoint::amce(fm, data = cj, cluster = TRUE,
+                        respondent.id = "Response.ID", 
+                        design = conjDesign, baselines = baselines,
+                        subset = cj$groupOrigin == 'Academia')
 # Table AMCE -- Full Model 
@@
 
-\noindent \textbf{IRB:} This research received IRB approval from Brown University (Protocol 2195/2018) and Funda\c{c}\~{a}o Get\'{u}lio Vargas (Protocol 83/2018).
+\noindent \textbf{IRB:} This research received IRB approval from Brown University (Protocol 2195/2018) and Fundação Getulio Vargas (Protocol 83/2018).
 

### 2019-07-26 manuscript/institutional-design-climate-policy.tex
revised version

@@
 \usepackage[libertine]{newtxmath}
-\usepackage[scale=.8]{FiraMono}
+\usepackage[scale=.9]{inconsolata}
 \usepackage[usenames, dvipsnames]{xcolor}
@@
 \usepackage{caption}
-\usepackage[UKenglish]{babel}
-\usepackage[UKenglish]{isodate}
+\usepackage[english]{babel}
 \usepackage[authoryear]{natbib}
@@
 \usepackage{bibentry}
-\cleanlookdateon
 \exhyphenpenalty=10000
@@
 
-\title{Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries\thanks{We thank Nigel Ashford, F\'{a}bio Barros, Frans Berkhout, Daniel D'Amico, Guilherme Fasolin, Manoel Galdino, Malte Hendricks, Stephen Herzog, Christian H\"{u}bner, Karina Marzano, Davi Moreira, Emily Skarbek and the participants at the FGV IR Seminar for their valuable comments.
-Special thanks to Natalia Liberato, Lucas Mingardi, Ingrid Oliveira, Catarina Roman, Leticia Santana and Larissa Santos for their excellent research assistance.
-This research received IRB approval from Brown University (Protocol 2195/2018) and Funda\c{c}\~{a}o Get\'{u}lio Vargas (Protocol 83/2018).
+\title{Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries\thanks{We thank Nigel Ashford, F\'{a}bio Barros, Frans Berkhout, Daniel D'Amico, Guilherme Fasolin, Manoel Galdino, Malte Hendricks, Stephen Herzog, Christian H\"{u}bner, Karina Marzano, Davi Moreira, Emily Skarbek, Paula Vedovelli, and the participants at the FGV IR Seminar for their valuable comments.
+Special thanks to Natalia Liberato, Lucas Mingardi, Ingrid Oliveira, Catarina Roman, Leticia Santana, and Larissa Santos for their excellent research assistance.
+This research received IRB approval from Brown University (Protocol 2195/2018) and Funda\c{c}\~{a}o Getulio Vargas (Protocol 83/2018).
 We acknowledge financial support from the Konrad Adenauer Stiftung Latin American Regional Programme for Energy Security and Climate (EKLA-KAS) and declare there are no conflicts of interest.
-The data, code and additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.}
+The data, code, and additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.}
 }
@@
 
-\date{20 July 2019}
+\date{\today}
 
@@
 In this paper, we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate institutional designs drawn from a pool of 5,500 possible climate change treaties.
-We find that Latin American elites prefer international organizations to formulate climate policies, support imposing increasing fines on violators and favor renewing agreements every five years.
+We find that Latin American elites prefer international organizations to formulate climate policies, support imposing increasing fines on violators, and favor renewing agreements every five years.
 We also find that elites support both international institutions and local courts to mediate conflicts, but they distrust non-governmental organizations and reject informal norms as an means of conflict resolution.
-Our results identify possible challenges in crafting regional climate mitigation policies and offer new insights about how to integrate interventions at the local and international levels.
-% reescrever essa última frase
+Our results identify possible challenges in crafting climate mitigation policies and offer new insights about how to integrate local and international levels in environmental agreements.
 
@@
 \noindent 
-\textbf{Word count:} 3884
+\textbf{Word count:} 3908
 \end{abstract}
@@
 
-There is an emerging consensus in public opinion about the causes and consequences of anthropogenic climate change.
-Despite some variation in climate risk beliefs, mostly due to cultural worldviews and political orientation \citep{hornsey2016meta}, recent surveys show that the public is increasingly aware of the dangers of greenhouse gas emissions.
-For example, 59\% of Americans are sure the Earth's temperature is increasing \citep{stanfordearth2018}; 74\% of European Union citizens consider global warming a `very serious problem' \citep{europe2018survey}; and 90\% of Brazilians believe climate change is already harming people around the world \citep{pew2018climate}.
+Despite the emerging consensus about the causes and consequences of global warming, international climate summits have often fallen short of expectations \citep{rogelj2010copenhagen, rosen2015wrong, victor2017prove}.
+Multilateral negotiations have progressed slowly under the guidelines of the United Nations Framework Convention on Climate Change (UNFCCC), and there is widespread skepticism that international talks will advance more quickly in the coming years \citep{cole2015advantages, hjerpe2015views}.
+As carbon dioxide emissions continue to increase, scientists believe current efforts may not be sufficient to meet the target of $2^{\circ}$C temperature rise above pre-industrial levels \citep{jordan2015emergence}.
 
-Yet this consensus does not automatically translate itself into effective political action.
-Global climate negotiations have progressed slowly under the guidelines of the United Nations Framework Convention on Climate Change (UNFCCC), and there is widespread skepticism that multilateral talks will advance more quickly in the coming years \citep{cole2015advantages, hjerpe2015views}.
-As carbon dioxide emissions continue to increase, current efforts may not be sufficient to meet the target of $2^{\circ}$C temperature rise above pre-industrial levels \citep{jordan2015emergence}.
+These concerns have motivated a growing debate about which institutional characteristics lead to successful climate agreements \citep[e.g.,][]{aklin2013understanding, bechtel2013mass, bechtel2017interests, keohane2011regime, ostrom2014polycentric}.
+Climate treaties are incomplete contracts, in which members purposefully design flexible provisions that take domestic circumstances into account \citep[607]{brauninger2000making}.
+For instance, the Paris Agreement relies on Nationally Determined Contributions (NDCs), a set of greenhouse gas reduction targets each member state voluntarily pledges to achieve \citep{winning2019nationally}.
+This decentralization increases the importance of national stakeholders in climate negotiations, and studies have shown that the behavior of elite groups, like advocacy coalitions and political parties, largely explain countries' climate policy performance \citep{jahn2016politics, karapin2012explaining}.
 
-In this scenario, there has been a growing discussion about the desirable features for successful climate change agreements \citep{bechtel2013mass, bechtel2017interests, keohane2011regime}.
-Climate treaties are incomplete contracts, in which members purposefully design flexible provisions that take domestic circumstances into account \citep[607]{brauninger2000making}.
-For instance, the Paris Agreement relies on Nationally Determined Contributions (NDCs), a set of greenhouse gas reduction targets each member state voluntarily pledges to achieve.
-This decentralization of competences increases the importance of national stakeholders in climate negotiations, and studies have shown that local advocacy coalitions largely explain countries' climate policy performance \citep{jahn2016politics,karapin2012explaining}.
-Although there is extensive research on the public opinion on global warming in developed economies \citep{bechtel2013mass, bechtel2017interests, beiser2019commitment, buntaine2018preferences, mildenberger2017beliefs}, less is known about the preferences of other key players in climate policy-making: elites in developing countries.
-% reescrever esse também
+Elites engage in different forms of `societal steering' to achieve policy goals, such as information sharing or rule setting \citep{andonova2009transnational, bulkeley2014transnational}.
+For example, non-governmental organizations have played a major role in the fossil fuel divestment movement by highlighting the urgency of the topic in developed countries \citep{ayling2017non}.
+In contrast, Brazil's rural caucus, an informal coalition of landholders and mining industrialists, have successfully lobbied for legislation that undermines previous carbon emission policies \citep{rochedo2018threat, simionatto2012dominantes}.
+Therefore, understanding the preferences of elite groups provides policy-makers with key information for designing effective, politically viable climate agreements.
+
+Although research on public opinion about climate change has increased significantly in the last years \citep[e.g.,][]{aklin2013understanding, bechtel2013mass, bechtel2017interests, mildenberger2017beliefs}, elite preferences are not well documented in the literature.
+This is a significant omission considering their importance as lobbyists or veto players in domestic climate politics.
+Elites in developing countries are specially understudied, despite the fact that emerging economies account for 63\% of the world's carbon emissions \citep{busch2015developing}.
+It is unclear which climate strategies face lower internal resistance from these groups, or whether their environmental preferences are fundamentally different from those of their developed countries counterparts \citep[28]{aklin2013understanding}.
 
@@
 We vary the agreements across six dimensions commonly debated in the climate change and institutional design literatures: rule-making capabilities \citep{dubash2013developments, massey2014climate}; conflict resolution mechanisms \citep{huntjens2012institutional, ostrom2014polycentric}; enforcement methods \citep{barrett2008climate}; punishment for repeated violators \citep{ostrom1990governing}; cost sharing \citep{bechtel2013mass}; and agreement duration \citep{copelovitch2014design, marcoux2009institutional}.
-Variations in any of those features can substantially change the potential outcomes of climate institutions \citep{bodin2017collaborative, ostrom2014polycentric}.
+Variations in any of those features can substantially change the outcomes of climate institutions \citep{bodin2017collaborative, ostrom2014polycentric}.
 
@@
 Survey participants also want both international institutions and local courts to mediate conflicts, but they are skeptical about non-governmental organizations and consistently reject informal norms as an instrument to solve disputes.
-The results lend support to theories that define climate governance as a loose `regime complex' instead of a cohesive, integrated institution \citep{abbott2012transnational, colgan2012punctuated, de2014global, keohane2011regime}.
-A regime complex is one characterised by `an array of partially overlapping and non-hierarchical institutions governing a particular issue area' \citep[279]{raustiala2004regime}.
-Our findings suggest that Latin American elites embrace the complexity of climate policy and believe that policies should incorporate several layers of governance simultaneously.
+The results lend support to theories that define climate governance as a `regime complex' \citep{colgan2012punctuated,keohane2011regime}, that is, `an array of partially overlapping and non-hierarchical institutions govern a particular issue area' \citep[279]{raustiala2004regime}.
+Our findings suggest that Latin American elites embrace the complexity of climate policy and believe mitigation policies should incorporate several layers of governance simultaneously.
 
 This article contributes to three strands of the literature.
-First, we add experimental evidence to the literature on institutional design.
-Our results confirm previous studies that stress the importance of institutional features on support for climate change policies \citep{bechtel2013mass, bechtel2017interests}.
+First, we add experimental evidence to studies on institutional design.
+Our results confirm previous research that stresses the importance of institutional features on support for climate change policies \citep{aklin2013understanding, bechtel2013mass, bechtel2017interests}.
 We show that institutional support varies markedly according to elite type and country of origin, and that this heterogeneity has an important impact on collective choice and preference aggregation.
+In particular, we find that climate negotiations may not have a clear Condorcet winner.
 
@@
 \citet{abbott2000hard} introduce the idea of hard versus soft international law to explain why actors pursue a variety of legal agreements to foster their interests in the international realm.
-\citet{mildenberger2017beliefs} and \citet{rosendorff2001optimal} add to this view by positing that the superiority of soft, incomplete contracts is due to observability issues: when compliance is hard to observe, incompleteness is superior than rigid contracts as it avoids unnecessary punishments and improves long-run cooperation stability.
+\citet{mildenberger2017beliefs} and \citet{rosendorff2001optimal} posit that when compliance is hard to observe, incomplete contracts are superior as they avoid unnecessary punishments and improve long-run cooperation stability.
 \citet{keohane2011regime}, in turn, argue that non-hierarchical international rulings help states to avoid gridlocks by reducing contracting costs and embracing `problem diversity', in which each particular climate problem requires a specific solution.
-Our results confirm that institutional features should be adapted to the issue at hand, and that flexible regime designs are decisive to foster international cooperation.
+Our results confirm that flexible regime designs are decisive to foster international cooperation.
 
 Finally, we also present novel information on Latin American elite behavior regarding climate institutions.
-Our findings indicate that elites in Latin America favor institutions that do not fit into the broad categories of `centralized' or `polycentric' arrangements, but they rather opt for a balance between the two.
-The results are consistent with the Latin American tradition of heavier reliance on the state than on self-governed solutions, but we find that local elites also believe that both international and local-level institutions should engage in climate policy design.
+Our findings indicate that elites in Latin America favor agreements that do not fit into the broad categories of `centralization' or `polycentrism'; instead, they prefer a combination of the two.
+The results are consistent with the Latin American tradition of heavier reliance on the state than on self-governed solutions, but local elites also believe that both international and local-level institutions should engage in climate policy design.
 The data provide new insights on how Latin American policy-makers can form domestic coalitions and which climate mitigation agreement faces lower resistance from potential veto players \citep{beiser2019commitment, hovi2019club}.
@@
 For instance, the Amazon basin contains about half of the world's carbon stock, so local elites are essential for the success of emissions trading markets \citep{benitez2006site, yang2018post}.
-% aqui tem que entrar mais um resumo do argumento das elites
 
@@
 Table~\ref{tab:categories} describes the values we included in each treaty attribute.
-\\
 
-\begin{table}[ht]
+\begin{table}[H]
+\small
 \begin{center}
@@
 \textbf{Attribute} & \multicolumn{1}{c}{\textbf{Values}} \\
-\Xhline{2\arrayrulewidth} \\
+\Xhline{2\arrayrulewidth} 
 Who makes the rules? & International organizations; federal government; local government; local community members; non-governmental organizations \\
@@
 In total, there are 5,500 possible value combinations.
-Figure~\ref{fig:conjoint} illustrates how a typical conjoint element appeared in the respondents' screen.
+Figure~\ref{fig:conjoint} illustrates how a typical conjoint element appeared in the respondents' screen.\\
 
@@
 	\centering
-	\includegraphics[width=13cm]{conjoint-cropped.pdf}
+	\includegraphics[width=15cm]{conjoint-cropped.pdf}
 	\caption{\textbf{Example of conjoint table presented to respondents}}
@@
 	\centering
-	\includegraphics[width=.9\linewidth,height=11.5cm]{pooled.pdf}
+	\includegraphics[height=12cm]{MM_all.pdf}
 	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreements in 10 Latin American countries (pooled data)}}
@@
 	\centering
-	\includegraphics[width=\linewidth, height=20cm]{countries.pdf}
+	\includegraphics[width=\linewidth, height=20cm]{MM_country.pdf}
 	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreement by country}}
@@
 	\centering
-	\includegraphics[width=\linewidth]{types.pdf}
+	\includegraphics[height=12cm]{MM_membertype.pdf}
 	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreement by elite type}}
@@
 
-The data, code and any additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.
+For supplementary material for this article, please visit \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.
 

### 2019-07-26 appendix/appendix-institutional-design-climate-policy.Rmd
revision v2.0

@@
 - "David Skarbek[^skarbek]"
-date: July 25, 2019
+date: July 26, 2019
 fontfamily: libertine
@@
 
-```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
+```{r demogGraph, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
 library(plm); library(tidyverse)
@@
 library(kableExtra)
-load('freire-mignozzetti-skarbek.RData')
+load('data.RData')
 
@@
 
-```{r attributes, echo=FALSE, fig.align='center', fig.height=4}
+```{r attributes, fig.align='center', fig.height=4}
 aux <- cj %>%
@@
 rm(cj)
-load('freire-mignozzetti-skarbek.RData')
+load('data.RData')
 
@@
 We translated the original survey questions (as shown in the text) into Portuguese and Spanish, and then embedded the PHP file with the randomization parameters in a Qualtrics survey.
-The PHP code we used to randomize the values of the attributes is available at the project's GitHub repository: <http://github.com/danilofreire/climate-governance>.
+The PHP code we used to randomize the values of the attributes is available at the project's GitHub repository: <https://github.com/danilofreire/climate-governance>.
 
@@
 
-\noindent \textbf{Questionnaire:} For the English translation of the entire survey instrument, with both the telephone and the online components, see the attachment below.
-
 \noindent \textbf{Statistical analysis:} We fit a marginal means estimator and an AMCE estimator.
@@
 
-```{r, fig.width = 7, fig.height = 8}
-barplot(100*table(cj$task)/max(table(cj$task)), xlab = 'Conjoint task', ylab = 'Percentage completed')
+```{r, fig.width = 7, fig.height = 5, tidy=FALSE}
+barplot(100*table(cj$task)/max(table(cj$task)),
+        xlab = 'Conjoint task',
+        ylab = 'Percentage completed')
 ```

### 2019-07-26 manuscript/institutional-design-climate-policy.tex
revision v2.0

@@
 We acknowledge financial support from the Konrad Adenauer Stiftung Latin American Regional Programme for Energy Security and Climate (EKLA-KAS) and declare there are no conflicts of interest.
-The data, code, and additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.}
-}
+The data, code, and additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.}}
 
@@
 \and Umberto Mignozzetti\thanks{School of International Relations, Funda\c{c}\~{a}o Getulio Vargas, S\~{a}o Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, \href{mailto:umberto.mignozzetti@fgv.br}{\texttt{umberto.mignozzetti@fgv.br}}, \href{http://umbertomig.com}{\texttt{http://umbertomig.com}}, \href{http://twitter.com/umbertomig}{\texttt{http://twitter.com/umbertomig}}.}
-\and David Skarbek\thanks{The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \href{http://davidskarbek.com}{\texttt{http://davidskarbek.com}}, \href{http://twitter.com/davidskarbek}{\texttt{http://twitter.com/davidskarbek}}.}
-}
+\and David Skarbek\thanks{The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \href{http://davidskarbek.com}{\texttt{http://davidskarbek.com}}, \href{http://twitter.com/davidskarbek}{\texttt{http://twitter.com/davidskarbek}}.}}
 
@@
 \noindent 
-\textbf{Word count:} 3908
+\textbf{Word count:} 3839
 \end{abstract}
@@
 
-These concerns have motivated a growing debate about which institutional characteristics lead to successful climate agreements \citep[e.g.,][]{aklin2013understanding, bechtel2013mass, bechtel2017interests, keohane2011regime, ostrom2014polycentric}.
+These concerns have motivated a growing debate about which institutional characteristics lead to successful climate agreements \citep[e.g.,][]{bechtel2013mass, bechtel2017interests, keohane2011regime, mitchell2006problem, ostrom2014polycentric}.
 Climate treaties are incomplete contracts, in which members purposefully design flexible provisions that take domestic circumstances into account \citep[607]{brauninger2000making}.
 For instance, the Paris Agreement relies on Nationally Determined Contributions (NDCs), a set of greenhouse gas reduction targets each member state voluntarily pledges to achieve \citep{winning2019nationally}.
-This decentralization increases the importance of national stakeholders in climate negotiations, and studies have shown that the behavior of elite groups, like advocacy coalitions and political parties, largely explain countries' climate policy performance \citep{jahn2016politics, karapin2012explaining}.
+This decentralization increases the importance of national stakeholders in climate negotiations, and studies have shown that the behavior of elite groups -- specially that of advocacy coalitions and political networks -- largely explain countries' climate policy performance \citep{jahn2016politics, karapin2012explaining}.
+Elites can advance or constrain climate agreements using `societal steering' strategies such as capacity building and rule setting, thus acting as \textit{de facto} veto players in local environmental policies \citep{andonova2009transnational, bulkeley2014transnational}.
 
-Elites engage in different forms of `societal steering' to achieve policy goals, such as information sharing or rule setting \citep{andonova2009transnational, bulkeley2014transnational}.
-For example, non-governmental organizations have played a major role in the fossil fuel divestment movement by highlighting the urgency of the topic in developed countries \citep{ayling2017non}.
-In contrast, Brazil's rural caucus, an informal coalition of landholders and mining industrialists, have successfully lobbied for legislation that undermines previous carbon emission policies \citep{rochedo2018threat, simionatto2012dominantes}.
-Therefore, understanding the preferences of elite groups provides policy-makers with key information for designing effective, politically viable climate agreements.
-
-Although research on public opinion about climate change has increased significantly in the last years \citep[e.g.,][]{aklin2013understanding, bechtel2013mass, bechtel2017interests, mildenberger2017beliefs}, elite preferences are not well documented in the literature.
-This is a significant omission considering their importance as lobbyists or veto players in domestic climate politics.
+Although research on public opinion and climate agreements has increased significantly in the last years \citep[e.g.,][]{aklin2013understanding, bechtel2013mass, bechtel2017interests, mildenberger2017beliefs}, elite preferences are not well documented in the literature.
+This is a significant omission considering that recent work has stressed the impact of elite coalitions in areas such as global finance and international banking regulation \citep[e.g,][]{chalmers2017banks, pagliari2014leveraged}.
 Elites in developing countries are specially understudied, despite the fact that emerging economies account for 63\% of the world's carbon emissions \citep{busch2015developing}.
@@
 \begin{table}[H]
-\small
 \begin{center}

### 2019-11-16 appendix/appendix-institutional-design-climate-policy.Rmd
commit appendix adding conj dimensions expl

@@
 This research design reduces the cognitive load interviewees have while answering surveys and as a result, we can expect more accurate responses from our sample.
+
+# An Explanation for our Conjoint Dimensions \label{sec:conjdim}
+
+In Table 1 of the main paper, we present the attributes and values for climate mitigation in our conjoint experiment.
+Here, we present the theoretical underpinnings of each of the dimensions and attributes evoked.
+
+## Attribute One: *Who makes the rules*
+
+Climate change governance faces various challenges when one considers its national and local implementation.
+For example, the voluntary character of the Nationally Determined Contributions (NDCs), at the heart of the Paris Agreement, illustrates its decentralized nature and renders the local implementation crucial for the arrangement’s success and the achievement of these long-term goals.
+That said, the first natural challenge, and the first dimension of our conjoint, is *Who makes the rules?*.
+In that sense, climate governance can be observed in different levels, such as the national, international, the subnational, regional and local levels [@bruhl2001international].
+Microlevel implementation requires regulations and attribution of responsibilities for each level, for which we propose the following levels of ruling: International Organizations; federal governments; local governments; local community members; and non-governmental organizations.
+These levels reveal differences in rulemaking and top-down versus bottom-up possible schemes.
+
+Moving to the *International Organizations* dimension, there is not an international forum or International Organization that centralizes agenda-setting, rulemaking, conflict resolution or enforcement for climate-related issues.
+On the other hand, the Conference of Parties is the highest decision-making body of the UNFCCC (United Nations Framework Convention on Climate Change), and the UN Climate Convention could possibly evolve to more institutionalized models of international governance.
+The very signing of the ensemble of agreements, such as the Kyoto Protocol, the Rio Convention and the Paris Agreement, in fact, consists in a step in this direction.
+Taking as an example the WTO (World Trade Organization) historical creation from GATT (General Agreement on Tariffs and Trade), international organizations play a role as gatekeepers, issue entrepreneurs and diffusors of international norms, sometimes leading to the establishment of international organizations and regimes, as pointed by Rational functionalism IR Scholars [@simons2002handbook].
+By defining salient issues, and establishing forms of cooperation, they help determine priorities and contribute to more effective decision-making [@keohane2012power] and the development of common norms.
+This mechanism could plausibly be valued by specific country elites as a reliable and legitimate source of rulemaking.
+
+An alternative take on rulemaking schemes is the one regarding the *Federal government*.
+Once a treaty is signed and ratified, it must be internalized by at least a number of signatories in order to entry into force.
+In other words, federal governments have to comply with the engagement, which highlights the essential role played by States when implementing international treaties, mainly because despite transnational networks and the emergence on non-state actors in the globalized world, States are still the main actors of International Public Law.
+Concerning climate-related agreements, that the bare existence of international institutions doesn’t necessarily provide global governance and these engagements can be seen as a normative and discursive way to virtually meet public opinion’s demands without taking further (and perhaps more effective) initiatives [@dimitrov2005hostage].
+In that sense, elites could prefer actions taken by the federal sphere in order to advance environmental legislation.
+Indeed, there are many examples of national climate legislation for example, of the Mexican General Law for Climate Change (2012), the Bolivian Mother Earth Legal Framework (Law nº300, 2012) and the Costa Rican Biodiversity Law (1998).
+
+Local actors, such as municipal governments, have also been crucial to the implementation of policies and creation of climate mitigation norms [@barber2013if; @fraundorfer2017role].
+Significantly, cities have built a number of networks, allowing for better coordination of their actions and settlement of shared problems [@fraundorfer2017role], as shown by the ICLEI (Local Governments for Sustainability) and the C40 initiatives, which connects 94 cities in coordinated actions against climate change.
+Note that some countries commit, internalize and implement international climate rules in a more direct manner, while other countries opt to withdraw from the climate treaties altogether, leaving only local governments to voluntarily comply with the Convention.
+An example is the ruling proposed by the California Governor on a state plan to follow the mitigation schemes proposed within the Paris Agreements, even though, at national level, the USA had chosen to withdraw.
+
+Likewise, climate mitigation practices and norms are influenced, and may even be determined, by local community members and non-governmental organizations, who act as important agenda-, rule- and norm-setters in the field, contributing also to compliance monitoring [@bruhl2001international].
+Especially relevant in Latin America, some indigenous groups that are particularly vulnerable to climate changes are politically responsive to climate-related issues.
+Particularly, not only are they engaged in the local sphere but are also gradually more active in the international arena [@bellier2012peuples], for example through the United Nations Permanent Forum on Indigenous Issues.
+That is also the case for other civil society members such as non-governmental organizations (NGOs), such as the Asamblea Nacional de Afectados Ambientales (ANAA) in Mexico, the Red de los Pueblos Fumigados in Argentina and the Rede Brasileira de Justiça Ambiental (RBJA) in Brazil.
+
+## Attribute Two: *Conflict Resolution Mechanism*
+
+Reacting to non-compliance, members could take the claim to a dispute settlement mechanism or institution, and its legitimacy is key for enforcement mechanisms and cost reparation.
+We consider five dimensions that are theoretically plausible for the dispute settlement: United Nations; government bureaucracy; local courts; private arbitration; and informal norms.
+Many disputes, such as trade disagreement between two countries, are already solved by international courts, such as the WTO dispute settlement body and the International Chamber of Commerce's International Court of Arbitration.
+
+In other situations, government bureaucracies have the discretion to impose fines, punish violators and settle conflicts, playing an important role in governing climate policies [@biesbroek2018public].
+Examples of this case are the Brazilian federal agency IBAMA (Brazilian Environmental Protection Agency), that rules nationally on any violation of environmental laws in the country, and Costa Rican national environmental office (SETENA), responsible for receiving denunciations and conducting investigations on environmental crimes.
+
+Local courts can also function as conflict resolution mechanisms in case of non-compliance, as in the lawsuit filed by almost 30 thousand Ecuadorian citizens against oil companies Texaco/Chevron, in a provincial court of Ecuador [@pigrau2014texaco].
+Alternatively, private arbitration is  a low-cost and prompt approach for the problem in the case of violations.
+
+Informal norms could also be a plausible and low-cost form of solving conflicts.
+For example, non-institutionalized forms of reputational sanction within the climate international regime, such as *naming and shaming* can act as a peer-pressure mechanism pushing for compliance.
+Note that informal norms within communities usually boost compliance in many situations and allow for more flexible and context adapted solutions.
+Accordingly, @finnemore1998international point that norms enhancement process is connected with social behavior, attributing social mechanisms (persuasion, habit, socialization, etc.) to each phase.
+
+Considering all this menu of choice, therefore, it is important to understand the preferences of elites, as this could potentially legitimate a conflict resolution mechanism that may be seen as less theoretically efficient.
+
+## Attributes Three and Four: *Punishment* and *Punishment for repeated violation*
+
+The third and fourth attributes relate to punishments against non-compliance.
+Punishments are key for ensuring high levels of compliance with rules, following the type of violation and its recurrence.
+We design the first feature, *Punishment*, to capture what types of punishment are more agreeable through the elite's lenses in the case of violation of a climate agreement.
+Note that the options presented match most of the national regulations on the subject and, thus, constitute plausible answers for the interviewees.
+For instance, in Brazil, violations are punishable with a range of options, from community services and fines to imprisonment (Law 9605/98) (available in: http://www.planalto.gov.br/ccivil_03/leis/l9605.htm), that is also the case for Peru (Law 29263) (available in: http://www.minam.gob.pe/delitosambientales).
+In the same direction, Ecuador recently approved a legislation that put severe penalties on perpetrators of climate violations in the national constitution, and incarceration is one of possible punishments (Article 245, Código Orgánico Integral Penal) (available in:http://www.oas.org/juridico/PDFs/mesicic5_ecu_ane_con_judi_c%C3%B3d_org_int_pen.pdf).
+Here we want to capture which types of action are perceived by elites as more effective punishments for non-compliance.
+Following the same logic, the second feature captures the actions that should be taken upon repeated violations on the agreement or norms from the elites’ perspectives.
+
+## Attribute Five: *Agreement costs*
+
+The fifth design principle regards the distribution of the agreement’s costs.
+In this attribute we consider the normative debate according to which developed and developing countries had different pledges regarding the attribution of responsibilities on the implementation costs.
+More specifically, during the COP 21 negotiations, two main approaches have encompassed climate agreements debates: on one hand, developing nations claimed the need for an equal per capta responsibility for emissions, and, on the other hand, the developing countries' appealed to historical responsibility (Santos, 2016).
+This encompasses a bigger discussion regarding global climate discussion that was already present in the former UN Convention for Climate, which divided countries into two groups, following their level of development; under Copenhagen Accord, Cancun Agreements and the Kyoto Protocol, developed countries were the sole accountable for their emissions [@kartha2011comparison].
+Over time, developed countries contested this separation, and a new principle emerged, that of *common but differentiated responsibilities and respective capabilities*, still acknowledging that historically, developed countries have emitted more greenhouse gas than developing countries.
+
+That said, the design feature of our conjoint allows us to capture whether Latin American elites are willing to pay the costs for implementing climate change policies, or whether they are more prone to transfer the costs to developed countries; or if they consider that the cost should be allocated to those with bigger historical or current emissions.
+Understanding what the elite’s stand on this normative issue is essential for assuring compliance in the local level and for crafting national level climate governance schemes.
+
+## Attribute Six: *Renegotiation*
+
+Finally, the last dimension investigates the rigidity of the agreement.
+From the theoretical standpoint, we know from the contract theory literature that more rigid agreements may fall short when conditions changed.
+However, agreements that change constantly might be too unstable to form a path dependency and provide focal points for coordination through time.
+On the other hand, a country may require continuous and frequent changes to adapt to the new ruling, case in which it could be potentially beneficial to increase the renegotiation frequency.
+For instance, if a previous ruling has a deleterious effect in the economy while only improving slightly the environmental output, it would likely be in the elites’ interest to renegotiate frequently.
+In such a context, the timing of renegotiation becomes a crucial variable influencing the design of national and local legislation on climate mitigation, and there is no reason to assume that a renegotiation period of five years is the only plausible preference of national elites.
 

### 2019-11-20 appendix/appendix-institutional-design-climate-policy.Rmd
appendix v0.1

--- 2019-07-26 appendix/appendix-institutional-design-climate-policy.Rmd
@@
 - "David Skarbek[^skarbek]"
-date: July 26, 2019
+date: November 20, 2019
 fontfamily: libertine
@@
 
-From October 1 to December 5, 2018, we run an elite survey with respondents from ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
+From October 1 to December 5, 2018, we ran an elite survey with respondents from ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
 The survey proceeded in two steps.
 
-We collected information on Latin American elites. The target was:
+First, we collected information on Latin American elites. Our target sample included:
 
@@
 
-To do so, we build a prospective respondents dataset with ten times these members for each country.
-Then, we run an online and telephone survey where we collected information regarding the climate change agreements and other climate change related problems.
+To do so, we built a dataset of prospective respondents that was ten times larger than our sample goal of 500 elite members.
+We constructed the dataset by gathering information from government websites, local NGOs, newspapers, and university departments.
 
 After finishing this dataset, we started the surveying stage.
-From November 12 to December 5, we ran the survey by contacting elite members by phone or by email.
-We had two teams of enumerators, one based in São Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers.
-Although the overall aim of the survey was 500 responses, the teams managed to collect 654 interviews.
+From November 12 to December 5, we ran the survey by contacting the elite members by phone or by email.
+We had two teams of enumerators, one based in São Paulo and another based in Rio de Janeiro, Brazil.
+The teams were comprised of Portuguese and Spanish native speakers.
+Although our initial expectation was to collect 500 survey responses, we completed 654 interviews.
 
@@
 Each of the questions has four to five different attributes.
-For the first two questions, we ask individuals if they would rather have the community, local governments, federal governments, or international organisations to create or enforce rules.
+For the first two questions, we ask individuals if they would rather have the community, local governments, federal governments, or international organizations to create or enforce rules.
 As for punishments, we have options ranging from do nothing to fines and incarceration.
-We ask whether the costs of climate change agreements should be paid mostly or exclusively by developed countries, by polluter countries regardless of their wealth, or if costs should be allocated according to the history of emissions of a given nation.
-Individuals also state their preferences for short-term agreements, a proxy we use for flexibility, or for long-term ones, what we see as a proxy for the stability of rules.
-Lastly, we ask which of the two conjoined choices individuals perceive as more legitimate and more efficient.
+We ask whether the costs of climate change agreements should be paid mostly or exclusively by developed countries, by polluting countries regardless of their wealth, or if costs should be allocated according to the history of emissions of a given nation.
+Individuals also state their preferences for short-term agreements, a proxy we use for flexibility, or for long-term ones, our proxy for the stability of rules.
 
 Conjoint experiments have many advantages.
-First, as each individual chooses between many pairs of possible climate agreements -- seven in our case -- we can drastically increase our sample size without incurring in further financial costs.
-The design thus maximizes our research budget.
+First, as each individual chooses between many pairs of possible climate agreements---seven in our case---we can drastically increase our statistical power without incurring in further financial costs.
+Thus, the design maximizes our research budget.
 Second, individuals rarely decide considering one attribute at a time, as presented in other types of survey experiments.
 In that regard, our conjoint analysis mirrors how people naturally make their choices, that is, by simultaneously taking several characteristics into consideration.
-Finally, as the experiments consist of a simple choice between A and B, conjoint analyses are easy to understand and to implement.
-This research design reduces the cognitive load interviewees have while answering surveys and as a result, we can expect more accurate responses from our sample.
+Finally, as the experiments consist of a simple choice between two bundles, conjoint analyses are easy to understand and to implement.
+This research design reduces the cognitive load of interviewees, so we can expect more accurate responses from our sample.
+
+# Conjoint Experiment Dimensions \label{sec:conjdim}
+
+In Table 1 of the main paper, we present the attributes and values for climate mitigation in our conjoint experiment.
+Here, we discuss the theoretical underpinnings of each of the dimensions and attributes evoked.
+
+## Attribute One: *Who Makes the Rules*
+
+Climate change governance faces various challenges in terms of national and local implementations.
+For example, the voluntary character of the Nationally Determined Contributions (NDCs), which are the core mechanism of the Paris Agreement, illustrates this decentralized nature.
+Climate governance can be observed at a number of different scales, such as the international, national, subnational, regional, and local levels [@bruhl2001international].
+Microlevel implementation requires regulations and attribution of responsibilities for each level, for which we propose the first dimension of our conjoint experiment is *Who makes the rules?*.
+To mirror the choices available for climate agreement signatory countries, we included the following levels of ruling: international organizations; federal governments; local governments; local community members; and non-governmental organizations.
+These levels reveal differences in rule making and top-down versus bottom-up possible schemes.
+
+Moving to the *International Organizations* dimension, currently there is no international institution that centralizes agenda-setting, rule making, conflict resolution, and law enforcement for climate-related issues.
+On the other hand, the Conference of Parties is the highest decision-making body of the UNFCCC (United Nations Framework Convention on Climate Change), and the UN Climate Convention could possibly evolve into a more institutionalized model of international governance.
+The very signing of the many agreements that comprise the broad climate mitigation international framework---the Rio Convention, the Kyoto Protocol, and the Paris Agreement---constitute a step in this direction of further institutionalization.
+
+We can take the WTO (World Trade Organization) as an example.
+After the establishment of the GATT (General Agreement on Tariffs and Trade), trade organizations progressively increased their role as gatekeepers, issue entrepreneurs and proponents of international norms.
+In turn, this movement solidified the international trade regime and established dedicated international organizations.
+The process of continuous, and eventually formal, institutionalization of trade regimes has been discussed by the rational functionalist school of international relations [e.g., @simons2002handbook].
+This mechanism could plausibly be valued by specific country elites as a reliable and legitimate potential source of climate mitigation rules.
+
+We also include the *Federal government* as an alternative rule provider.
+Once a treaty is signed and ratified, it must be internalized by a minimum number of signatories in order to entry into force.
+In other words, federal governments have to comply with the engagement, which highlights the essential role states play in the implementation of international treaties.
+Despite the growing importance of transnational networks and non-state actors in global regimes, states remain the fundamental actors in the international realm.
+
+Concerning climate-related agreements, the bare existence of international institutions is not sufficient for global climate governance.
+In fact, scholars have posited that these engagements can be understood as a discursive strategy, one which allows states to satisfy internal public opinion demands without taking costly global warming mitigation initiatives [e.g., @dimitrov2005hostage].
+In that sense, elites may see the federal government as a more credible source of effective environmental legislation.
+Latin American countries provide examples of national-level climate legislation, such as Mexico's General Law for Climate Change (2012), Bolivia's Mother Earth Legal Framework (Law 300/2012), and Costa Rica's Biodiversity Law (1998).
+
+Local actors, such as municipal governments, have also been active players in the creation of climate mitigation norms [@barber2013if; @fraundorfer2017role].
+Significantly, cities have built a number of networks dedicated to climate issues, such as the ICLEI (Local Governments for Sustainability) and the C40.
+They include 94 cities and promote coordinated actions to fight climate change.
+While some countries opt to internalize and implement climate rules at the national level, others prefer to withdraw from the climate treaties and allow local governments to voluntarily comply with international conventions.
+The state of California is a recent example.
+Although the United States had chosen to withdraw from the Paris Agreement, the state government offered a plan to follow the mitigation schemes proposed by the treaty.
+
+Likewise, climate mitigation practices and norms are strongly influenced by local community members and non-governmental organizations.
+The civil society has long played a substantive role in setting the agenda and monitoring compliance of climate legislation [@bruhl2001international].
+This is also true for Latin America.
+Indigenous groups have been particularly active in the local sphere and the international arena, as climate change directly endangers traditional communities [@bellier2012peuples].
+At the international level, we highlight the creation of the United Nations Permanent Forum on Indigenous Issues.
+Locally, Latin American communities have founded many non-governmental organizations to fight climate change, such as the _Asamblea Nacional de Afectados Ambientales_ (ANAA) in Mexico, the _Red de los Pueblos Fumigados_ in Argentina and the _Rede Brasileira de Justiça Ambiental_ (RBJA) in Brazil.
+
+## Attribute Two: *Conflict Resolution Mechanism*
+
+International regimes require efficient institutions to deal with non-compliance and cost reparation to aggrieved parties.
+We consider five institutions that can plausibly serve as instances for conflict mediation in climate issues: the United Nations; government bureaucracies; local courts; private arbitration; and informal norms.
+
+International trade disputes, such as those concerning unfair practices, are already solved by international courts.
+The WTO Dispute Settlement Body and the International Criminal Court are two well-known examples.
+In this sense, the United Nations can also provide a similar resolution mechanism to solve climate disputes.
+
+In other situations, government bureaucracies have the discretion to settle conflicts and enforce punishment to violators [@biesbroek2018public].
+In Latin America, one example is the Brazilian Environmental Protection Agency (IBAMA), which is run by the federal government.
+The IBAMA is free to set rules nationally and punish any violation of environmental laws in Brazil.
+Another example is provided by the Costa Rican National Environmental Office (SETENA).
+It is responsible for receiving denunciations and conducting investigations on environmental crimes.
+
+Local courts can also function as conflict resolution mechanisms in case of non-compliance.
+A widely-publicized case in Latin America involves the lawsuit filed by almost 30 thousand Ecuadorian citizens against oil companies Texaco/Chevron.
+The case was brought to a provincial court in Ecuador [@pigrau2014texaco].
+Alternatively, private arbitration is a low-cost and prompt approach for the problem in the case of violations.
+Chile and Argentina resorted to private arbitration in 1972 to address a border dispute, and the Permanent Court of Arbitration frequently addresses environmental issues.
+
+Informal norms could also be a plausible and low-cost form of solving conflicts.
+For example, non-institutionalized forms of reputational sanction within the climate international regime, such as *naming and shaming*, can act as a peer-pressure mechanism pushing for compliance.
+Note that informal norms within communities usually boost compliance in many situations and allow for more flexible and context adapted solutions (@ostrom1990governing).
+
+## Attributes Three and Four: *Punishment* and *Punishment for Repeated Violations*
+
+The third and fourth attributes relate to punishments against non-compliance.
+We design the first feature, *Punishment*, to capture what types of punishment elites would like to apply to climate agreement violators.
+The options we present closely match existing Latin American regulations on the subject.
+As such, they constitute plausible answers for the interviewees.
+For instance, in Brazil, violations are punishable with a range of options, from community services and fines to imprisonment (Law 9605/98, available in: <http://www.planalto.gov.br/ccivil_03/leis/l9605.htm>.
+That is also the case for Peru (Law 29263, available in: <http://www.minam.gob.pe/delitosambientales>).
+Similarly, Ecuador has recently approved legislation that adds severe penalties on perpetrators of climate violations to the national constitution.
+Incarceration, for instance, is one of the possible punishments (Article 245, Código Orgánico Integral Penal, available in: <http://www.oas.org/juridico/PDFs/mesicic5_ecu_ane_con_judi_c%C3%B3d_org_int_pen.pdf>).
+In this respect, our selected treaty characteristics are plausible to Latin American elites.
+
+Following the same logic, the fourth experimental feature, *Punishment for repeated violations*, captures the actions that should be taken upon subsequent violations of climate change agreements.
+
+## Attribute Five: *Agreement Costs*
+
+The fifth design principle refers to the distribution of the agreement's costs.
+Here we consider the normative debates on climate equality, burden-sharing, and distributive justice in global public goods provision.
+More specifically, developing nations have stressed how wealthier countries have historically contributed more to global warming [@santos2017global].
+For instance, under Copenhagen Accord and the Kyoto Protocol, developed countries were deemed as the sole responsible for CO2 emissions [@kartha2011comparison].
+Over time, the wealthier nations successfully contested this position, arguing that emerging economies such as China and India accounted for a large share of greenhouse gas emissions as well.
+Hence, a new compensation principle emerged, that of *common but differentiated responsibilities and respective capabilities*.
+While accounting for past environmental pollution, the model also request the contribution of developing countries.
+
+Our design feature allows us to capture the position of Latin American elites in this debate.
+We add four variables derived from the discussion presented above.
+The first posits that only rich countries should pay the coses of climate agreements, reflecting the original stance of developing nations.
+The second states that rich countries should pay more than poor countries, which also test the elites' willing to contribute to public goods.
+The third alternative states that countries should pay costs according to the history of emissions, while the last one affirms that only current emissions should be taken into account.
+Understanding how Latin American elites stand on this normative issue is essential for assuring compliance in the local level and for crafting national level climate governance schemes.
+
+## Attribute Six: *Renegotiation*
+
+Finally, our last conjoint experiment dimension investigates the rigidity of the agreement.
+From a theoretical standpoint, we know from the contract theory literature that more rigid agreements may fall short when their underlying conditions change.
+However, agreements that change constantly might be too unstable to form a path dependency and provide focal points for long-run coordination.
+Thus, parties have to strike a balance between legal stability and the need for adaptation.
+For instance, if a climate agreement has deleterious effects in the economy while only marginally improving slightly the country's environmental output, decision-makers will push for treaty renegotiations.
+Conversely, longer agreements reduce coordination costs and give predictability to the system.
+We analyse temporal preferences of Latin American elites by including five different climate agreement renegotiation schedules: one year, five years, twenty years, fifty years, or never.
+
+Latin America has a history of political and economic volatility, so it is unclear whether elites will prefer long-term or short-term climate change initiatives.
+On the one hand, elites may perceive longer contracts as a means to force collective commitment to fighting global warming.
+On the other hand, elites can also anticipate future volatility discount the future more heavily in favor of immediate circumstances.
 
@@
 
-The main demographic statistics collected were the country and elite types, and the geolocation of the respondents. They follow in the graphs below.
+The main demographic statistics we collected are: country indicators, elite types, and the geolocation of the respondents. We show their distributions in the graphs below.
 
@@
 p
+
+# Elite type and group type
+tab <- data.frame(table(aux$groupOrigin, aux$countryOrigin))
+names(tab) <- c('Group Origin','Country', 'Frequency')
+p<- ggplot(data = tab, aes(x = `Group Origin`, y = Frequency)) +
+  geom_bar(stat = "identity") +
+  facet_wrap(~Country) +
+  theme_bw() + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+p
 ```
@@
 As we can see, we managed to contact more than fifty elite members for all countries but Bolivia and Peru.
-To compensate for the low collection rates in these two countries, note that we exceeded the sample size in all the remaining states.
-
-Considering the elite type, note that we have, as expected, more people from academia and the civil society, followed by Executive and Legislative.
-The legislative collection was below the original target, but above the minimum mark of 5 for each country.
-This is expected, given the difficulty of accessing these elite members.
-
-In the map, we can see that the answers concentrate on the country's capitals, with some variation within the state, but with sample concentrated in the largest municipalities.
-This is also in line with our expectations, as elite members are assumed to gravitate around the capitals and the influence centers.
+To compensate for the low response rates in these two countries, we exceeded the sample size in all the remaining states.
+
+Regarding elite type, we have more data on academics and members of civil society.
+They are followed by members the Executive and of the Legislative, respectively.
+This result is in line with our expectations given the difficulty of accessing high profile government members.
+
+In the map, we see that respondents are concentrated in the largest municipalities of their respective countries.
+As elites tend to be more urban and well-educated than the average citizen, we expected the clustering of elites in big cities.
 
@@
 
-The two remarkable issues are the low frequency of *Less penalty* in the attribute *How are repeated violations punished?* and the low frequency of *None* for the attribute *What punishments do they use?*.
+Two remarkable issues in our data are the low frequency of *Less penalty* in the attribute *How are repeated violations punished?* and the low frequency of *None* for the attribute *What punishments do they use?*.
 This because when we draw the level none for the attribute *What punishments do they use?* or the level less penalty for *How are repeated violations punished?*, then it makes no sense to have less penalty than the minimum possible.
@@
 We decided to include these profiles based on the stakes and influence that such elites have on climate change policies.
-According to the IR constructivist theories, academics have notable influence on our topic of interest as they form the epistemic community around climate change policies.
+According to constructivist international relations theories, academics have notable influence on our topic of interest as they form an epistemic community around climate change policies.
 Civil society members that have stakes on climate policies are also influential, such as oil-extracting companies, lobby groups, and environmental NGOs.
-Executive and Legislative elites handle the decisions themselves, so their importance.
+Executive and Legislative elites handle the decisions themselves, what justifies their inclusion in our sample.
 
 We selected ten countries to our sample: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
-Our selection criteria were the impact of climate change on each nation, their size and regional importance, and natural resources availability.
+Our selection criteria were: 1) the impact of climate change on each nation, 2) their size and regional importance, and 3) natural resources availability.
 For each country, we built a dataset of potential respondents with at least:
@@
 In the second tier we included participants that had incomplete profiles, such as those with only online information available.
-The dataset including the first-tier respondents was randomly divided between enumerators in Rio de Janeiro and São Paulo to avoid any eventual biases from the collecting stage.
+The dataset including the first-tier respondents was randomly divided between enumerators in Rio de Janeiro and São Paulo to avoid any eventual biases at the collecting stage.
 Both groups conducted the interviews by phone from November 12th to December 5th, 2018.
-The second tier dataset was used for an online only version of the survey.
+The second tier dataset was used for the online only version of the survey.
 
@@
 The response rate was 10.24 percent of the original population in the telephone survey (779 of 7606 possible respondents).
-We had an attrition of 61.62 percent from the telephone (779) to the online survey (299).
+We had an attrition rate of 61.62 percent from the telephone (779) to the online survey (299).
 The response rate for the online only survey was 5.26 percent (293 of 5569 invited by email).
 
-The conjoint experiment analyzed in this paper was in the online and online-only dataset. Therefore, the relevant column for our data is the last one.
+The conjoint experiment analyzed in this paper was in the online and online only dataset. Therefore, the relevant column for our data is the last one.
 
@@
 
-**Random Assignment:** We programmed the experiment using a Python application provided by @strezhnev2013conjoint.
+**Random Assignment:** We wrote the computer code for our experiment using a Python application provided by @strezhnev2013conjoint.
 We translated the original survey questions (as shown in the text) into Portuguese and Spanish, and then embedded the PHP file with the randomization parameters in a Qualtrics survey.
@@
 
-The conjoint experiment consisted in comparing two treaties that vary in these six attributes, repeating the application for seven times for each respondent.
-
-\noindent \textbf{Software:} To program the PHP randomization device we used the Python application provided by @strezhnev2013conjoint. We used Qualtrics to administer the survey.
+The conjoint experiment consisted in comparing two hypothetical climate change treaties that vary across six attributes. We presented each respondent with seven pairs of possible climate agreements.
+
+\noindent \textbf{Software:} We used the Python application provided by @strezhnev2013conjoint to program the PHP randomization device. We hosted the survey questionnaire on Qualtrics.
 
@@
 
-\noindent \textbf{Dataset description:} Each line in the dataset represents a given treaty, varying for the selection status (selected versus non-selected) for a given respondent.
-When a respondent finished an entire response set, this adds 14 rows to the dataset.
+\noindent \textbf{Dataset description:} Each line in the dataset corresponds to a given treaty, which indicates the selection status of a given treaty (selected versus non-selected) for a specific respondent.
+When a respondent finished an entire response set, this added 14 rows to the dataset.
 Seven rows with the selected treaties and other seven rows with the non-selected treaties.

### 2019-11-20 appendix/appendix-institutional-design-climate-policy.Rmd
editing

@@
 
+\newpage
+
 # Latin American Elite Survey \label{sec:latam}
@@
 
-First, we collected information on Latin American elites. Our target sample included:
+First, we collected information on Latin American elites. Our sample included:
 
@@
 The individual chooses one of them.
-As the attributes are randomised and individuals choose between different pairs of hypothetical scenarios, we can estimate how individuals value each of the conjoined elements.
+As the attributes are randomized and individuals choose between different pairs of hypothetical scenarios, we can estimate how individuals value each of the conjoined elements.
 
@@
 
-Climate change governance faces various challenges in terms of national and local implementations.
-For example, the voluntary character of the Nationally Determined Contributions (NDCs), which are the core mechanism of the Paris Agreement, illustrates this decentralized nature.
+Climate change governance faces numerous implementation challenges.
+For example, the voluntary character of the Nationally Determined Contributions (NDCs), which are the core mechanism of the Paris Agreement, illustrates how climate coordination might be difficult to achieve.
 Climate governance can be observed at a number of different scales, such as the international, national, subnational, regional, and local levels [@bruhl2001international].
-Microlevel implementation requires regulations and attribution of responsibilities for each level, for which we propose the first dimension of our conjoint experiment is *Who makes the rules?*.
-To mirror the choices available for climate agreement signatory countries, we included the following levels of ruling: international organizations; federal governments; local governments; local community members; and non-governmental organizations.
-These levels reveal differences in rule making and top-down versus bottom-up possible schemes.
-
-Moving to the *International Organizations* dimension, currently there is no international institution that centralizes agenda-setting, rule making, conflict resolution, and law enforcement for climate-related issues.
+Microlevel implementation requires regulations and attribution of responsibilities for each level, and it is unclear how competences will be distributed.
+This question motivates the first dimension of our conjoint experiment, *Who makes the rules?* Since rules might be provided by different institutions, we added the following attributes to this first category: international organizations; federal governments; local governments; local community members; and non-governmental organizations.
+These levels represent possible top-down versus bottom-up regulation schemes and reflect the choices available to treaty signatory countries.
+
+Regarding the *International organizations* dimension, currently there is no international institution that centralizes agenda-setting, rule making, conflict resolution, and law enforcement for climate-related issues.
 On the other hand, the Conference of Parties is the highest decision-making body of the UNFCCC (United Nations Framework Convention on Climate Change), and the UN Climate Convention could possibly evolve into a more institutionalized model of international governance.
-The very signing of the many agreements that comprise the broad climate mitigation international framework---the Rio Convention, the Kyoto Protocol, and the Paris Agreement---constitute a step in this direction of further institutionalization.
+The very signing of the many agreements that comprise the climate mitigation international framework---the Rio Convention, the Kyoto Protocol, and the Paris Agreement---constitutes a step in this direction of further institutionalization.
 
 We can take the WTO (World Trade Organization) as an example.
-After the establishment of the GATT (General Agreement on Tariffs and Trade), trade organizations progressively increased their role as gatekeepers, issue entrepreneurs and proponents of international norms.
+After the establishment of the GATT (General Agreement on Tariffs and Trade), trade organizations progressively increased their role as gatekeepers, issue entrepreneurs, and proponents of international norms.
 In turn, this movement solidified the international trade regime and established dedicated international organizations.
@@
 Concerning climate-related agreements, the bare existence of international institutions is not sufficient for global climate governance.
-In fact, scholars have posited that these engagements can be understood as a discursive strategy, one which allows states to satisfy internal public opinion demands without taking costly global warming mitigation initiatives [e.g., @dimitrov2005hostage].
-In that sense, elites may see the federal government as a more credible source of effective environmental legislation.
-Latin American countries provide examples of national-level climate legislation, such as Mexico's General Law for Climate Change (2012), Bolivia's Mother Earth Legal Framework (Law 300/2012), and Costa Rica's Biodiversity Law (1998).
-
-Local actors, such as municipal governments, have also been active players in the creation of climate mitigation norms [@barber2013if; @fraundorfer2017role].
-Significantly, cities have built a number of networks dedicated to climate issues, such as the ICLEI (Local Governments for Sustainability) and the C40.
-They include 94 cities and promote coordinated actions to fight climate change.
-While some countries opt to internalize and implement climate rules at the national level, others prefer to withdraw from the climate treaties and allow local governments to voluntarily comply with international conventions.
-The state of California is a recent example.
-Although the United States had chosen to withdraw from the Paris Agreement, the state government offered a plan to follow the mitigation schemes proposed by the treaty.
-
-Likewise, climate mitigation practices and norms are strongly influenced by local community members and non-governmental organizations.
+In fact, scholars have posited that these engagements can be understood as a discursive strategy, one which allows states to please the domestic public without having to take costly global warming mitigation initiatives [e.g., @dimitrov2005hostage].
+In that sense, elites may see the federal government as a more credible source of environmental legislation.
+Latin American countries provide many examples of national-level climate legislation, such as Mexico's General Law for Climate Change (2012), Bolivia's Mother Earth Legal Framework (Law 300/2012), and Costa Rica's Biodiversity Law (1998).
+
+Local actors, such as municipal governments, have also participated in the creation of climate mitigation norms [@barber2013if; @fraundorfer2017role].
+Significantly, cities have built a number of networks to tackle climate issues, such as the ICLEI (Local Governments for Sustainability) and the C40.
+Together, these networks include 94 cities and promote coordinated actions to fight climate change.
+While some countries opt to implement climate rules at the national level, others prefer to withdraw from the climate treaties while allowing local governments to voluntarily comply with international conventions.
+The state of California offers a recent example.
+Although the United States had chosen to withdraw from the Paris Agreement, the Californian government offered a plan to follow the mitigation schemes proposed by the treaty.
+
+Likewise, climate mitigation practices are strongly influenced by local community members and non-governmental organizations.
 The civil society has long played a substantive role in setting the agenda and monitoring compliance of climate legislation [@bruhl2001international].
 This is also true for Latin America.
-Indigenous groups have been particularly active in the local sphere and the international arena, as climate change directly endangers traditional communities [@bellier2012peuples].
-At the international level, we highlight the creation of the United Nations Permanent Forum on Indigenous Issues.
-Locally, Latin American communities have founded many non-governmental organizations to fight climate change, such as the _Asamblea Nacional de Afectados Ambientales_ (ANAA) in Mexico, the _Red de los Pueblos Fumigados_ in Argentina and the _Rede Brasileira de Justiça Ambiental_ (RBJA) in Brazil.
+Indigenous groups have been particularly active in the local sphere, as climate change directly endangers traditional communities [@bellier2012peuples].
+Latin American communities have founded many non-governmental organizations to fight climate change, such as the _Asamblea Nacional de Afectados Ambientales_ (ANAA) in Mexico, the _Red de los Pueblos Fumigados_ in Argentina and the _Rede Brasileira de Justiça Ambiental_ (RBJA) in Brazil.
+At the international level, we highlight the support Latin American groups have provided to the creation of the United Nations Permanent Forum on Indigenous Issues.
 
@@
 
-International regimes require efficient institutions to deal with non-compliance and cost reparation to aggrieved parties.
+International regimes require efficient institutions to deal with non-compliance and provide cost reparations to aggrieved parties.
 We consider five institutions that can plausibly serve as instances for conflict mediation in climate issues: the United Nations; government bureaucracies; local courts; private arbitration; and informal norms.
 
-International trade disputes, such as those concerning unfair practices, are already solved by international courts.
-The WTO Dispute Settlement Body and the International Criminal Court are two well-known examples.
-In this sense, the United Nations can also provide a similar resolution mechanism to solve climate disputes.
+International trade disputes, such as those concerning unfair business practices, are already solved by international courts.
+The WTO Dispute Settlement Body is the best-known example.
+Criminal offenses are also judged by the International Criminal Court.
+In this sense, it is reasonable to assume that the United Nations may also provide a similar resolution mechanism to solve climate disputes.
 
@@
 The IBAMA is free to set rules nationally and punish any violation of environmental laws in Brazil.
-Another example is provided by the Costa Rican National Environmental Office (SETENA).
-It is responsible for receiving denunciations and conducting investigations on environmental crimes.
-
-Local courts can also function as conflict resolution mechanisms in case of non-compliance.
+Another example is provided by the Costa Rican National Environmental Office (SETENA), which is responsible for receiving denunciations and conducting investigations on environmental crimes.
+
+Local courts can also function as conflict resolution mechanisms.
 A widely-publicized case in Latin America involves the lawsuit filed by almost 30 thousand Ecuadorian citizens against oil companies Texaco/Chevron.
 The case was brought to a provincial court in Ecuador [@pigrau2014texaco].
-Alternatively, private arbitration is a low-cost and prompt approach for the problem in the case of violations.
+Alternatively, private arbitration offers a low-cost approach to deal with international violations.
 Chile and Argentina resorted to private arbitration in 1972 to address a border dispute, and the Permanent Court of Arbitration frequently addresses environmental issues.
 
-Informal norms could also be a plausible and low-cost form of solving conflicts.
-For example, non-institutionalized forms of reputational sanction within the climate international regime, such as *naming and shaming*, can act as a peer-pressure mechanism pushing for compliance.
-Note that informal norms within communities usually boost compliance in many situations and allow for more flexible and context adapted solutions (@ostrom1990governing).
+Informal norms may also be a plausible and low-cost form of solving conflicts.
+Non-institutionalized forms of reputational sanctions within the climate international regime, such as *naming and shaming*, can act as a peer-pressure compliance mechanisms.
+There is comparative evidence that informal norms within communities boost local compliance and allow for flexible and context-adapted climate mitigation solutions (@ostrom1990governing).
 
@@
 As such, they constitute plausible answers for the interviewees.
-For instance, in Brazil, violations are punishable with a range of options, from community services and fines to imprisonment (Law 9605/98, available in: <http://www.planalto.gov.br/ccivil_03/leis/l9605.htm>.
+In Brazil, violations are punishable with a range of options, from community services and fines to imprisonment (Law 9605/98, available in: <http://www.planalto.gov.br/ccivil_03/leis/l9605.htm>.
 That is also the case for Peru (Law 29263, available in: <http://www.minam.gob.pe/delitosambientales>).
-Similarly, Ecuador has recently approved legislation that adds severe penalties on perpetrators of climate violations to the national constitution.
-Incarceration, for instance, is one of the possible punishments (Article 245, Código Orgánico Integral Penal, available in: <http://www.oas.org/juridico/PDFs/mesicic5_ecu_ane_con_judi_c%C3%B3d_org_int_pen.pdf>).
+Similarly, Ecuador has recently approved legislation that adds severe penalties on perpetrators of climate violations.
+Incarceration is one of the possible punishments (Article 245, Código Orgánico Integral Penal, available in: <http://www.oas.org/juridico/PDFs/mesicic5_ecu_ane_con_judi_c%C3%B3d_org_int_pen.pdf>).
 In this respect, our selected treaty characteristics are plausible to Latin American elites.
@@
 
-The fifth design principle refers to the distribution of the agreement's costs.
-Here we consider the normative debates on climate equality, burden-sharing, and distributive justice in global public goods provision.
-More specifically, developing nations have stressed how wealthier countries have historically contributed more to global warming [@santos2017global].
-For instance, under Copenhagen Accord and the Kyoto Protocol, developed countries were deemed as the sole responsible for CO2 emissions [@kartha2011comparison].
-Over time, the wealthier nations successfully contested this position, arguing that emerging economies such as China and India accounted for a large share of greenhouse gas emissions as well.
+The fifth design principle refers to the distribution of climate agreement costs.
+Here we consider the normative debates on burden-sharing and climate distributive justice.
+Developing nations have stressed how wealthier countries have historically contributed more to global warming [@santos2017global].
+More specifically, under the Copenhagen Accord and the Kyoto Protocol, developed countries were deemed as the sole responsible for CO2 emissions [@kartha2011comparison].
+Over time, the wealthier nations successfully contested this position, arguing that emerging economies such as China and India account for a large share of recent greenhouse gas emissions.
 Hence, a new compensation principle emerged, that of *common but differentiated responsibilities and respective capabilities*.
-While accounting for past environmental pollution, the model also request the contribution of developing countries.
+While accounting for past environmental pollution, the model also requires the contribution of developing countries to reduce global warming.
 
 Our design feature allows us to capture the position of Latin American elites in this debate.
-We add four variables derived from the discussion presented above.
-The first posits that only rich countries should pay the coses of climate agreements, reflecting the original stance of developing nations.
-The second states that rich countries should pay more than poor countries, which also test the elites' willing to contribute to public goods.
+We add four attributes derived from the discussion presented above.
+The first attribute posits that only rich countries should pay the costs of climate agreements, reflecting the original stance of developing nations.
+The second attribute states that rich countries should pay more than poor countries, which also tests the elites' willing to contribute to global public goods.
 The third alternative states that countries should pay costs according to the history of emissions, while the last one affirms that only current emissions should be taken into account.
-Understanding how Latin American elites stand on this normative issue is essential for assuring compliance in the local level and for crafting national level climate governance schemes.
+Understanding how Latin American elites stand on this normative issue is essential for assuring local-level compliance and crafting effective climate governance schemes.
 
@@
 
-Finally, our last conjoint experiment dimension investigates the rigidity of the agreement.
-From a theoretical standpoint, we know from the contract theory literature that more rigid agreements may fall short when their underlying conditions change.
+Finally, our last conjoint experiment dimension investigates the rigidity of climate change agreements.
+From a theoretical standpoint, the contract theory literature argues that more rigid agreements may fall short when their underlying conditions change.
 However, agreements that change constantly might be too unstable to form a path dependency and provide focal points for long-run coordination.
 Thus, parties have to strike a balance between legal stability and the need for adaptation.
-For instance, if a climate agreement has deleterious effects in the economy while only marginally improving slightly the country's environmental output, decision-makers will push for treaty renegotiations.
+If a climate agreement has deleterious effects in the economy while only marginally improving the country's environmental output, decision-makers will push for treaty renegotiations.
 Conversely, longer agreements reduce coordination costs and give predictability to the system.
@@
 Latin America has a history of political and economic volatility, so it is unclear whether elites will prefer long-term or short-term climate change initiatives.
-On the one hand, elites may perceive longer contracts as a means to force collective commitment to fighting global warming.
-On the other hand, elites can also anticipate future volatility discount the future more heavily in favor of immediate circumstances.
+On the one hand, elites may perceive longer contracts as a means to force collective commitment to fight global warming.
+On the other hand, elites can also anticipate future volatility and discount the future more heavily in favor of immediate circumstances.
 
@@
 
-As we can see, we managed to contact more than fifty elite members for all countries but Bolivia and Peru.
+As we can see, we contacted more than fifty elite members for all countries but Bolivia and Peru.
 To compensate for the low response rates in these two countries, we exceeded the sample size in all the remaining states.
 
-Regarding elite type, we have more data on academics and members of civil society.
-They are followed by members the Executive and of the Legislative, respectively.
-This result is in line with our expectations given the difficulty of accessing high profile government members.
-
-In the map, we see that respondents are concentrated in the largest municipalities of their respective countries.
-As elites tend to be more urban and well-educated than the average citizen, we expected the clustering of elites in big cities.
+Regarding elite type, we interviewed a high number of academics and members of civil society.
+They were followed by members the Executive and of the Legislative, respectively.
+This result is in line with our expectations given the difficulty of reaching high profile government members.
+
+We see that respondents are concentrated in the largest municipalities of their respective countries.
+As elites tend to be more urban and well-educated than average, we indeed expected that most of our sample would be clustered in big cities.
 

### 2019-11-21 appendix/appendix-institutional-design-climate-policy.Rmd
R&R version

@@
 Non-institutionalized forms of reputational sanctions within the climate international regime, such as *naming and shaming*, can act as a peer-pressure compliance mechanisms.
-There is comparative evidence that informal norms within communities boost local compliance and allow for flexible and context-adapted climate mitigation solutions (@ostrom1990governing).
+There is comparative evidence that informal norms within communities boost local compliance and allow for flexible and context-adapted climate mitigation solutions [@ostrom1990governing].
 
@@
 As such, they constitute plausible answers for the interviewees.
-In Brazil, violations are punishable with a range of options, from community services and fines to imprisonment (Law 9605/98, available in: <http://www.planalto.gov.br/ccivil_03/leis/l9605.htm>.
-That is also the case for Peru (Law 29263, available in: <http://www.minam.gob.pe/delitosambientales>).
+In Brazil, violations are punishable with a range of options, from community services and fines to imprisonment (Law 9605/98, available at <http://www.planalto.gov.br/ccivil_03/leis/l9605.htm>.
+That is also the case for Peru (Law 29263, available at <http://www.minam.gob.pe/delitosambientales>).
 Similarly, Ecuador has recently approved legislation that adds severe penalties on perpetrators of climate violations.
-Incarceration is one of the possible punishments (Article 245, Código Orgánico Integral Penal, available in: <http://www.oas.org/juridico/PDFs/mesicic5_ecu_ane_con_judi_c%C3%B3d_org_int_pen.pdf>).
+Incarceration is one of the possible punishments (Article 245, Código Orgánico Integral Penal, available at <http://www.oas.org/juridico/PDFs/mesicic5_ecu_ane_con_judi_c%C3%B3d_org_int_pen.pdf>).
 In this respect, our selected treaty characteristics are plausible to Latin American elites.

### 2019-11-21 manuscript/institutional-design-climate-policy.tex
change keywords
R&R version

@@
 \usepackage{bibentry}
-\exhyphenpenalty=10000
-\hyphenpenalty=10000
+\exhyphenpenalty=1000
+\hyphenpenalty=1000
 \widowpenalty=10000
@@
 	pdftitle={Institutional Design and Elite Support for Climate Policies},
-	pdfauthor={Danilo Freire, Umberto Mignozzetti and David Skarbek},
+	pdfauthor={Danilo Freire, Umberto Mignozzetti, and David Skarbek},
 	pdfsubject={Climate change governance},
@@
 
-\date{\today}
+\date{November 20, 2019}
 
@@
 \noindent 
-Which institutional features do Latin American elites favor for climate change policies?
-Climate change mitigation requires global scale governance, but it remains unclear which institutional arrangements maximize the support for environmental agreements.
-In this paper, we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate institutional designs drawn from a pool of 5,500 possible climate change treaties.
+Which institutional features do Latin American elites favor for local climate change policies?
+Climate change mitigation requires active local level implementation, but it remains unclear which institutional arrangements maximize the support for environmental rules.
+In this paper, we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate institutional designs drawn from a pool of 5,500 possible local climate governance arrangements.
 We find that Latin American elites prefer international organizations to formulate climate policies, support imposing increasing fines on violators, and favor renewing agreements every five years.
 We also find that elites support both international institutions and local courts to mediate conflicts, but they distrust non-governmental organizations and reject informal norms as an means of conflict resolution.
-Our results identify possible challenges in crafting climate mitigation policies and offer new insights about how to integrate local and international levels in environmental agreements.
+Our results identify possible challenges in crafting local level climate mitigation policies and offer new insights about how to integrate local and international levels in environmental agreements
 
@@
 \noindent 
-\textbf{Keywords:} climate change, institutional design, elites, Latin America, regime complex
+\textbf{Keywords:} climate change, elites, institutional design, Latin America, regime complex
 
@@
 \noindent 
-\textbf{Word count:} 3839
+\textbf{Word count:} 3984
 \end{abstract}
@@
 For instance, the Paris Agreement relies on Nationally Determined Contributions (NDCs), a set of greenhouse gas reduction targets each member state voluntarily pledges to achieve \citep{winning2019nationally}.
-This decentralization increases the importance of national stakeholders in climate negotiations, and studies have shown that the behavior of elite groups -- specially that of advocacy coalitions and political networks -- largely explain countries' climate policy performance \citep{jahn2016politics, karapin2012explaining}.
+This decentralization increases the importance of local stakeholders in climate negotiations, and studies have shown that the behavior of elite groups -- specially that of advocacy coalitions and political networks -- largely explain countries' climate policy performance \citep{jahn2016politics, karapin2012explaining}.
 Elites can advance or constrain climate agreements using `societal steering' strategies such as capacity building and rule setting, thus acting as \textit{de facto} veto players in local environmental policies \citep{andonova2009transnational, bulkeley2014transnational}.
@@
 Elites in developing countries are specially understudied, despite the fact that emerging economies account for 63\% of the world's carbon emissions \citep{busch2015developing}.
-It is unclear which climate strategies face lower internal resistance from these groups, or whether their environmental preferences are fundamentally different from those of their developed countries counterparts \citep[28]{aklin2013understanding}.
+It is unclear which local climate strategies face lower internal resistance from these groups, or whether their environmental preferences are fundamentally different from those of their developed countries counterparts \citep[28]{aklin2013understanding}.
 
-We help remedy this gap by assessing which climate change governance systems Latin American elites are willing to support.
-In our survey experiment, we asked 654 respondents -- academics, members of the executive power, legislators, businesspeople and members of non-governmental organizations -- to select their preferred agreement among 7 repetitions of binary choices.
-We vary the agreements across six dimensions commonly debated in the climate change and institutional design literatures: rule-making capabilities \citep{dubash2013developments, massey2014climate}; conflict resolution mechanisms \citep{huntjens2012institutional, ostrom2014polycentric}; enforcement methods \citep{barrett2008climate}; punishment for repeated violators \citep{ostrom1990governing}; cost sharing \citep{bechtel2013mass}; and agreement duration \citep{copelovitch2014design, marcoux2009institutional}.
+We help remedy this gap by assessing which local climate mitigation initiatives Latin American elites are willing to support.
+In our survey experiment, we asked 654 respondents -- academics, members of the executive power, legislators, businesspeople and members of non-governmental organizations -- to select their preferred components for local climate mitigation among 7 repetitions of binary choices.
+We vary the agreements across six dimensions commonly debated in the climate change and institutional design literatures: rule-making capabilities \citep{dubash2013developments, massey2014climate}; conflict resolution mechanisms \citep{huntjens2012institutional, ostrom2014polycentric}; enforcement methods \citep{barrett2008climate}; punishment for repeated violators \citep{ostrom1990governing}; cost sharing \citep{bansak2017europeans,bechtel2013mass}; and agreement duration \citep{copelovitch2014design, marcoux2009institutional}.
 Variations in any of those features can substantially change the outcomes of climate institutions \citep{bodin2017collaborative, ostrom2014polycentric}.
 
-We find that interviewees prefer international organizations to design climate policies and are favorable to imposing increasing fines on violators and renewing agreements every five years.
+We find that interviewees prefer international organizations to design local climate policies and are favorable to imposing increasing fines on violators and renegotiating agreements every five years.
 Survey participants also want both international institutions and local courts to mediate conflicts, but they are skeptical about non-governmental organizations and consistently reject informal norms as an instrument to solve disputes.
-The results lend support to theories that define climate governance as a `regime complex' \citep{colgan2012punctuated,keohane2011regime}, that is, `an array of partially overlapping and non-hierarchical institutions govern a particular issue area' \citep[279]{raustiala2004regime}.
+The results lend support to theories that define climate governance as a `regime complex' \citep{colgan2012punctuated, keohane2011regime}, that is, `an array of partially overlapping and non-hierarchical institutions govern a particular issue area' \citep[279]{raustiala2004regime}.
+Moreover, following the spirit of the Paris Accords, the regime complex framework stresses the role of elite perceptions on the relationship between local and global climate mitigation efforts.
 Our findings suggest that Latin American elites embrace the complexity of climate policy and believe mitigation policies should incorporate several layers of governance simultaneously.
@@
 We show that institutional support varies markedly according to elite type and country of origin, and that this heterogeneity has an important impact on collective choice and preference aggregation.
-In particular, we find that climate negotiations may not have a clear Condorcet winner.
+In particular, we find that climate negotiations may not reach a unique preferred solution.
 
@@
 \citet{keohane2011regime}, in turn, argue that non-hierarchical international rulings help states to avoid gridlocks by reducing contracting costs and embracing `problem diversity', in which each particular climate problem requires a specific solution.
-Our results confirm that flexible regime designs are decisive to foster international cooperation.
+Our results corroborate that flexible regime designs are decisive to foster international cooperation.
 
@@
 Our findings indicate that elites in Latin America favor agreements that do not fit into the broad categories of `centralization' or `polycentrism'; instead, they prefer a combination of the two.
-The results are consistent with the Latin American tradition of heavier reliance on the state than on self-governed solutions, but local elites also believe that both international and local-level institutions should engage in climate policy design.
+The results are consistent with the Latin American tradition of heavier reliance on the state than on self-governed solutions, but respondents also believe that both international and subnational institutions should play a role in local climate policy design.
 The data provide new insights on how Latin American policy-makers can form domestic coalitions and which climate mitigation agreement faces lower resistance from potential veto players \citep{beiser2019commitment, hovi2019club}.
@@
 The individual selects one of them.
-As the attributes are randomized, we can estimate how individuals value each of the conjoined elements.
+As the attributes are randomized, we can estimate how individuals value each of the conjoined elements relative to their alternatives.\footnote{We note, however, that our conjoint experiments do not allow us to infer the average level of attribute support in the sample.
+Since our design relies on forced choices, estimates should always be interpreted in comparison to the other attributes in the alternative agreement bundle.}
 
@@
 Lastly, Latin America is the most biodiverse region in the world and plays a major role in global climate mitigation projects.
-For instance, the Amazon basin contains about half of the world's carbon stock, so local elites are essential for the success of emissions trading markets \citep{benitez2006site, yang2018post}.
 
-We use a dataset compiled specifically for this study.
+We use an original dataset compiled specifically for this study.
 From October 1 to December 5, 2018, we ran an elite survey with respondents from Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama and Peru.
@@
 The hypothetical climate change agreements include six attributes: 1) which organizations defines the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated.
-Table~\ref{tab:categories} describes the values we included in each treaty attribute.
+Table~\ref{tab:categories} describes the values we included in each treaty attribute.\footnote{A discussion on the theoretical underpinnings of our choice of attributes is available in the Supplementary Material.}
 
@@
 \Xhline{2\arrayrulewidth} 
+\small
 Who makes the rules? & International organizations; federal government; local government; local community members; non-governmental organizations \\
@@
 We estimate our models with the \texttt{cregg} package \citep{leeper2018cregg} for the \texttt{R} statistical language \citep{rstats2019}.
-Here we report marginal means instead of average marginal conditional effects (AMCE) of climate agreement attributes.
+Here we report marginal means instead of average marginal conditional effects (AMCE) of local climate agreement attributes.
 \citet{leeper2018subgroup} show that AMCEs can be misleading in subgroup analysis as model results are sensitive to the choice of reference categories in interactions.
@@
 Figure~\ref{fig:pooled} shows our main results.
-The graph illustrates the preference associated with each attribute of hypothetical climate mitigation agreements.
+The graph illustrates the preference associated with each attribute of hypothetical local climate governance schemes.
 Dots with horizontal bars represent point estimates and 95\% confidence intervals from linear regressions with robust standard errors clustered at the respondent level.
-\\
 
-\begin{figure}[H]
+\begin{figure}[h]
 	\centering
 	\includegraphics[height=12cm]{MM_all.pdf}
-	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreements in 10 Latin American countries (pooled data)}}
+	\caption{\textbf{Relative preferences for institutional attributes in climate change agreements in 10 Latin American countries (pooled data, marginal means)}}
 	\label{fig:pooled}
@@
 
-Respondents prefer international organizations to establish climate mitigation rules (54\%, SE = 1.2), but they also hold favorable views of local communities (51.6\%, SE = 1.25).
+Respondents prefer international organizations to establish local climate mitigation rules (54\%, SE = 1.2), but they also hold relatively favorable views of local communities (51.6\%, SE = 1.25).
 We note that Latin American elites support multiple governance levels simultaneously, which suggests that they are willing to include separate political spheres into a single climate policy design.
-Local governments (49.8\%, SE = 1.2) and federal governments (48.6\%, SE = 1.3) receive slightly more support than the other alternatives, yet the difference between them is not statistically significant.
-Non-governmental organizations are the least preferred option for climate change rule-making with 45.5\% (SE = 1.3).
+Local governments (49.8\%, SE = 1.2) and federal governments (48.6\%, SE = 1.3) are slightly preferred over NGOs, yet the difference between them is not statistically significant.
+Non-governmental organizations are the least preferred option for local climate change rule-making with 45.5\% (SE = 1.3).
 
@@
 Respondents affirm disputes should be addressed mainly by the United Nations and local courts.
-These two choices have 57.3\% (SE = 1.2) and 54.6\% (SE = 1.2) approval, respectively.
+These two choices receive 57.3\% (SE = 1.2) and 54.6\% (SE = 1.2) relative approval, respectively.
 Private arbitration comes next with 50\% (SE = 1.3).
-Government bureaucracy and informal norms lower the chance of selecting a climate agreement, with 46.4\% (SE = 1.3) and 41\% (SE = 1.3) of support.
+Government bureaucracy and informal norms lower the chance of selecting a climate agreement, with 46.4\% (SE = 1.3) and 41\% (SE = 1.3) of support when compared to the alternatives.
 
-Participants agree with graduated sanctions to repeated offenders (53.2\%, SE = 0.9) and they believe agreement costs should be allocated according to the country's history of emissions (53.6\%, SE = 1.1).
+Participants prefer graduated sanctions to repeated offenders (53.2\%, SE = 0.9) and they prefer costs to be be allocated according to the country's history of emissions (53.6\%, SE = 1.1).
+Note, however, that the difference between history of emissions and current emissions is not statistically significant.
 Moreover, related to the same idea of proportionality, respondents indicate that lawbreakers should be punished with fines (55.3\%, SE = 1.1), which can be increased if necessary.
-This is in line with the literature arguing that climate change agreements present a middle ground between rigidity and flexibility to accommodate domestic demands and increase national compliance \citep{von2008international}.
+This is in line with the literature arguing that climate change agreements present a middle ground between rigidity and flexibility to accommodate domestic demands and increase national and local compliance \citep{von2008international}.
 
-Elites believe that Latin American countries should contribute to the provision of global public goods.
-We find no evidence that respondents intend to free ride on climate agreements, as they position themselves against the idea that rich nations should bear the costs of climate protection.
+Elites believe that Latin American countries should contribute to the global provision of public goods.
+We find no evidence that respondents intend to use local agreements to free ride on global climate change policies, as they position themselves against the idea that rich nations should bear the costs of climate protection.
 This is conductive to long-term cooperation as placing the burden exclusively on rich countries is likely to be off the equilibrium path and would, presumably, not lead to a stable arrangement.
 
-Regarding agreement duration, respondents are interested in a balance between stability and flexibility.
+Regarding local agreements' renegotiations, respondents are interested in a balance between stability and flexibility.
 Interviewees reject agreements that either cannot be modified or that last for 50 years.
@@
 
-We also examine how our results vary across countries and types of elites.
-Figure~\ref{fig:countries} displays the preferred climate change agreement characteristics for each of the 10 countries in our sample.
+We observe higher variance in the responses related to the frequency of treaty renegotiations and in those concerning the methods of conflict resolution.
+We believe that both items vary considerably because elites are concern about the region's long history of political and economic volatility.
+Elites might be divided over which strategy is best to achieve climate mitigation goals.
+On the one hand, some respondents prefer long-term agreements to induce stronger commitment to fight climate change.
+On the other hand, different groups of respondents may expect continuing instability in Latin America and therefore prefer to make agreements more flexible to cope with future chances.
+Moreover, Latin America's historically low levels of trust in public institutions may have spurred elites to have divergent opinions about which institution should be responsible for punishing non-compliers.
+
+We also examine how our results vary across countries and types of elites.\footnote{The number of respondents in each elite subgroups does not vary significantly per country, with the exception of members of the civil society.
+Brazil has a higher proportion of that particular group.
+Please refer to the Supplementary Material for additional information on our sample composition.} Figure~\ref{fig:countries} displays the preferred local climate change agreement characteristics for each of the 10 countries in our sample.
 The disaggregated data confirm that elites have a generalized preference for international agencies to solve conflicts, and they dislike informal norms.
@@
 
-\begin{figure}[H]
+\begin{figure}[hbpt]
 	\centering
 	\includegraphics[width=\linewidth, height=20cm]{MM_country.pdf}
-	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreement by country}}
+	\caption{\textbf{Relative preferences for institutional attributes in climate change agreements by country (marginal means)}}
 	\label{fig:countries}
@@
 Latin American elites do not have a consensus on which organizations should provide the rules.
-For example, elites in Costa Rica prefer local to global rule-making; in Mexico, they prefer global and dislike local, similar to Peru, Argentina and Brazil; in Colombia, elites favor global and local rule-making simultaneously; and in Bolivia, respondents prefer local organizations to design climate treaties.
+For example, elites in Costa Rica prefer local to global rule-making; in Mexico, they prefer global and dislike local, similar to Peru, Argentina and Brazil; in Colombia, elites favor global and local rule-making simultaneously; and in Bolivia, respondents prefer local organizations to design local climate rules.
 This is an important point and might have far-reaching consequences for environmental policy design.
-The lack of coordination on rule-making responsibilities can give rise to decision cycles, lowering the chance of a Condorcet winner.
+The lack of coordination on rule-making responsibilities can give rise to decision cycles, lowering the chance that a single, favourite climate change solution emerges.
 Nevertheless, these dissensions might be resolved by decentralization, boosting the idea that flexible regime complexes, such as polycentric governance schemes, might provide a solution to gridlocks.
@@
 	\includegraphics[height=12cm]{MM_membertype.pdf}
-	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreement by elite type}}
+	\caption{\textbf{Relative preferences for institutional attributes in climate change agreements by elite type (marginal means)}}
 	\label{fig:types}
@@
 Differences emerge in two of the six attributes.
-Academics and members of the civil society are skeptical about the role of federal government in climate policy-making, while members of the executive and legislative --- part of the government themselves --- have a more positive view of national institutions.
+Academics and members of the civil society are skeptical about the role of federal government in local climate policy-making, while members of the executive and legislative --- part of the government themselves --- have a more positive view of national institutions.
 The differences, however, are not large.
 Second, members of the legislative prefer rich countries to bear the larger part of agreement costs (58.4\%, SE = 3.5).
-This provides evidence for the idea of historical responsibility for climate protection, an argument which developing countries have recently brought to climate negotiations \citep{muller2009differentiating,friman2015agreement}.
+This provides evidence for the idea of historical responsibility for climate protection, an argument which developing countries have recently brought to climate negotiations \citep{muller2009differentiating, friman2015agreement}.
 
@@
 
-In this article, we examine which attributes of climate change mitigation treaties Latin American elites support.
+In this article, we examine which attributes of local climate change mitigation treaties Latin American elites support.
 We find that interviewees prefer international organizations to resolve conflicts, are favorable to imposing increasing fines on violators and renewing agreements every five years.
@@
 
-While our results confirm that Latin Americans prefer the state to conduct public policy, they do not match the typical dichotomy of hierarchical versus decentralized climate change regimes.
-After disaggregating the data by country and elite type, we confirm that elites prefer international organizations to resolve disputes and that federal and local sources of governance should have a say in climate agreements.
-However, we find large heterogeneity in the responses, with groups holding different opinions on how competences should be divided.
+While our results corroborate that Latin Americans prefer the state to conduct local public policy, they do not match the typical dichotomy of hierarchical versus decentralized climate change regimes.
+After disaggregating the data by country and elite type, we find that elites prefer international organizations to resolve disputes and that federal and local sources of governance should design local climate mitigation governance schemes.
+However, we also find large heterogeneity in the responses, with groups holding different opinions on how competences should be divided.
 
 Our results have several theoretical and practical implications.
-The findings we present here suggest there is considerable scope for new studies on global governance, specially in underrepresented regions.
+The findings we present here suggest there is considerable scope for new studies on local challenges to global governance, specially in underrepresented regions.
 Our analysis can be extended to examine if the Latin American public has the same opinion on multilevel arrangements as do the elites; and if not, it would be important to know what explains the mismatch between groups \citep{luna2005political}.
-Moreover, future work may address whether elites in other regions also understand climate policy as a regime complex, in which different actors play a constructive yet decentralised role in policy-making.
+Moreover, future work may address whether elites in other regions also understand climate policy as a regime complex, in which different actors play a constructive yet decentralized role in policy-making.
 
 With regards to environmental policies, we identify that Latin American elites are interested in incorporating different political actors and in strengthening the role of international organizations in climate governance.
-Building on these insights, our study provides novel information to policy-makers, as it evaluates which climate agreements are politically acceptable to Latin American elites.
-Future climate negotiations can achieve better results if they take those preferences into account.
+Building on these insights, our study provides novel information to policy-makers, as it evaluates which climate agreements are politically acceptable for implementation in Latin America.
+Future climate negotiations can achieve better results if they take those local preferences into account.
 

### 2019-11-21 manuscript/institutional-design-climate-policy.tex
R&R version

@@
 We also find that elites support both international institutions and local courts to mediate conflicts, but they distrust non-governmental organizations and reject informal norms as an means of conflict resolution.
-Our results identify possible challenges in crafting local level climate mitigation policies and offer new insights about how to integrate local and international levels in environmental agreements
+Our results identify possible challenges in crafting local level climate mitigation policies and offer new insights about how to integrate local and international levels in environmental agreements.
 

### 2019-11-21 manuscript/institutional-design-climate-policy.tex
R&R version

--- 2019-11-21 manuscript/institutional-design-climate-policy.tex
@@
 We find that Latin American elites prefer international organizations to formulate climate policies, support imposing increasing fines on violators, and favor renewing agreements every five years.
-We also find that elites support both international institutions and local courts to mediate conflicts, but they distrust non-governmental organizations and reject informal norms as an means of conflict resolution.
-Our results identify possible challenges in crafting local level climate mitigation policies and offer new insights about how to integrate local and international levels in environmental agreements
+We also find that elites support both international institutions and local courts to mediate conflicts, but they distrust non-governmental organizations and reject informal norms as a means of conflict resolution.
+Our results identify possible challenges in crafting local climate mitigation policies and offer new insights about how to integrate local and international levels in environmental agreements.
 

### 2020-05-27 supplementary-material/supplementary-material-climate-policy.Rmd
Accepted version

--- 2019-11-21 appendix/appendix-institutional-design-climate-policy.Rmd
@@
 - "David Skarbek[^skarbek]"
-date: November 20, 2019
+date: \today
 fontfamily: libertine
@@
     toc: true
-    keep_tex: no
+    keep_tex: yes
     template: template.latex
@@
     }
-
-```
-
-\newpage
+```
 
@@
 
-First, we collected information on Latin American elites. Our sample included:
-
-1. Executive members
-2. Legislative members
+We collected information on Latin American elites. The target was:
+
+1. Members of the Executive branch
+2. Members of the Legislative branch
 3. Civil society
@@
 
-1. 10 Executive members
-2. 10 Legislative members
+1. 10 members of the Executive branch
+2. 10 members of the Legislative branch
 3. 15 Civil society
@@
 
-To do so, we built a dataset of prospective respondents that was ten times larger than our sample goal of 500 elite members.
-We constructed the dataset by gathering information from government websites, local NGOs, newspapers, and university departments.
+To do so, we built a prospective respondents dataset with ten times these members for each country.
+Then, we ran an online and telephone survey where we collected information regarding the climate change agreements and other climate
+change-related problems.
 
 After finishing this dataset, we started the surveying stage.
-From November 12 to December 5, we ran the survey by contacting the elite members by phone or by email.
-We had two teams of enumerators, one based in São Paulo and another based in Rio de Janeiro, Brazil.
-The teams were comprised of Portuguese and Spanish native speakers.
-Although our initial expectation was to collect 500 survey responses, we completed 654 interviews.
+From November 12 to December 5, we ran the survey by contacting elite members by phone or by email.
+We had two teams of enumerators, one based in São Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers.
+Although the overall aim of the survey was 500 responses, the teams managed to collect 654 interviews.
 
@@
 As for punishments, we have options ranging from do nothing to fines and incarceration.
-We ask whether the costs of climate change agreements should be paid mostly or exclusively by developed countries, by polluting countries regardless of their wealth, or if costs should be allocated according to the history of emissions of a given nation.
-Individuals also state their preferences for short-term agreements, a proxy we use for flexibility, or for long-term ones, our proxy for the stability of rules.
-
-Conjoint experiments have many advantages.
-First, as each individual chooses between many pairs of possible climate agreements---seven in our case---we can drastically increase our statistical power without incurring in further financial costs.
-Thus, the design maximizes our research budget.
+We ask whether the costs of climate change agreements should be paid mostly or exclusively by developed countries, by polluter countries regardless of their wealth, or if costs should be allocated according to the history of emissions of a given nation.
+Individuals also state their preferences for short-term agreements, a proxy we use for flexibility, or for long-term ones, what we see as a proxy for the stability of rules.
+Lastly, we ask which of the two conjoined choices individuals perceive as more legitimate and more efficient.
+
+Conjoint experiments have many advantages [@hainmueller2014causal].
+First, as each individual chooses between many pairs of possible climate agreements -- seven in our case -- we can drastically increase our sample size without incurring in further financial costs.
+The design thus maximizes our research budget.
 Second, individuals rarely decide considering one attribute at a time, as presented in other types of survey experiments.
-In that regard, our conjoint analysis mirrors how people naturally make their choices, that is, by simultaneously taking several characteristics into consideration.
-Finally, as the experiments consist of a simple choice between two bundles, conjoint analyses are easy to understand and to implement.
-This research design reduces the cognitive load of interviewees, so we can expect more accurate responses from our sample.
-
-# Conjoint Experiment Dimensions \label{sec:conjdim}
-
-In Table 1 of the main paper, we present the attributes and values for climate mitigation in our conjoint experiment.
-Here, we discuss the theoretical underpinnings of each of the dimensions and attributes evoked.
-
-## Attribute One: *Who Makes the Rules*
-
-Climate change governance faces numerous implementation challenges.
-For example, the voluntary character of the Nationally Determined Contributions (NDCs), which are the core mechanism of the Paris Agreement, illustrates how climate coordination might be difficult to achieve.
-Climate governance can be observed at a number of different scales, such as the international, national, subnational, regional, and local levels [@bruhl2001international].
-Microlevel implementation requires regulations and attribution of responsibilities for each level, and it is unclear how competences will be distributed.
-This question motivates the first dimension of our conjoint experiment, *Who makes the rules?* Since rules might be provided by different institutions, we added the following attributes to this first category: international organizations; federal governments; local governments; local community members; and non-governmental organizations.
-These levels represent possible top-down versus bottom-up regulation schemes and reflect the choices available to treaty signatory countries.
-
-Regarding the *International organizations* dimension, currently there is no international institution that centralizes agenda-setting, rule making, conflict resolution, and law enforcement for climate-related issues.
-On the other hand, the Conference of Parties is the highest decision-making body of the UNFCCC (United Nations Framework Convention on Climate Change), and the UN Climate Convention could possibly evolve into a more institutionalized model of international governance.
-The very signing of the many agreements that comprise the climate mitigation international framework---the Rio Convention, the Kyoto Protocol, and the Paris Agreement---constitutes a step in this direction of further institutionalization.
-
-We can take the WTO (World Trade Organization) as an example.
-After the establishment of the GATT (General Agreement on Tariffs and Trade), trade organizations progressively increased their role as gatekeepers, issue entrepreneurs, and proponents of international norms.
-In turn, this movement solidified the international trade regime and established dedicated international organizations.
-The process of continuous, and eventually formal, institutionalization of trade regimes has been discussed by the rational functionalist school of international relations [e.g., @simons2002handbook].
-This mechanism could plausibly be valued by specific country elites as a reliable and legitimate potential source of climate mitigation rules.
-
-We also include the *Federal government* as an alternative rule provider.
-Once a treaty is signed and ratified, it must be internalized by a minimum number of signatories in order to entry into force.
-In other words, federal governments have to comply with the engagement, which highlights the essential role states play in the implementation of international treaties.
-Despite the growing importance of transnational networks and non-state actors in global regimes, states remain the fundamental actors in the international realm.
-
-Concerning climate-related agreements, the bare existence of international institutions is not sufficient for global climate governance.
-In fact, scholars have posited that these engagements can be understood as a discursive strategy, one which allows states to please the domestic public without having to take costly global warming mitigation initiatives [e.g., @dimitrov2005hostage].
-In that sense, elites may see the federal government as a more credible source of environmental legislation.
-Latin American countries provide many examples of national-level climate legislation, such as Mexico's General Law for Climate Change (2012), Bolivia's Mother Earth Legal Framework (Law 300/2012), and Costa Rica's Biodiversity Law (1998).
-
-Local actors, such as municipal governments, have also participated in the creation of climate mitigation norms [@barber2013if; @fraundorfer2017role].
-Significantly, cities have built a number of networks to tackle climate issues, such as the ICLEI (Local Governments for Sustainability) and the C40.
-Together, these networks include 94 cities and promote coordinated actions to fight climate change.
-While some countries opt to implement climate rules at the national level, others prefer to withdraw from the climate treaties while allowing local governments to voluntarily comply with international conventions.
-The state of California offers a recent example.
-Although the United States had chosen to withdraw from the Paris Agreement, the Californian government offered a plan to follow the mitigation schemes proposed by the treaty.
-
-Likewise, climate mitigation practices are strongly influenced by local community members and non-governmental organizations.
-The civil society has long played a substantive role in setting the agenda and monitoring compliance of climate legislation [@bruhl2001international].
-This is also true for Latin America.
-Indigenous groups have been particularly active in the local sphere, as climate change directly endangers traditional communities [@bellier2012peuples].
-Latin American communities have founded many non-governmental organizations to fight climate change, such as the _Asamblea Nacional de Afectados Ambientales_ (ANAA) in Mexico, the _Red de los Pueblos Fumigados_ in Argentina and the _Rede Brasileira de Justiça Ambiental_ (RBJA) in Brazil.
-At the international level, we highlight the support Latin American groups have provided to the creation of the United Nations Permanent Forum on Indigenous Issues.
-
-## Attribute Two: *Conflict Resolution Mechanism*
-
-International regimes require efficient institutions to deal with non-compliance and provide cost reparations to aggrieved parties.
-We consider five institutions that can plausibly serve as instances for conflict mediation in climate issues: the United Nations; government bureaucracies; local courts; private arbitration; and informal norms.
-
-International trade disputes, such as those concerning unfair business practices, are already solved by international courts.
-The WTO Dispute Settlement Body is the best-known example.
-Criminal offenses are also judged by the International Criminal Court.
-In this sense, it is reasonable to assume that the United Nations may also provide a similar resolution mechanism to solve climate disputes.
-
-In other situations, government bureaucracies have the discretion to settle conflicts and enforce punishment to violators [@biesbroek2018public].
-In Latin America, one example is the Brazilian Environmental Protection Agency (IBAMA), which is run by the federal government.
-The IBAMA is free to set rules nationally and punish any violation of environmental laws in Brazil.
-Another example is provided by the Costa Rican National Environmental Office (SETENA), which is responsible for receiving denunciations and conducting investigations on environmental crimes.
-
-Local courts can also function as conflict resolution mechanisms.
-A widely-publicized case in Latin America involves the lawsuit filed by almost 30 thousand Ecuadorian citizens against oil companies Texaco/Chevron.
-The case was brought to a provincial court in Ecuador [@pigrau2014texaco].
-Alternatively, private arbitration offers a low-cost approach to deal with international violations.
-Chile and Argentina resorted to private arbitration in 1972 to address a border dispute, and the Permanent Court of Arbitration frequently addresses environmental issues.
-
-Informal norms may also be a plausible and low-cost form of solving conflicts.
-Non-institutionalized forms of reputational sanctions within the climate international regime, such as *naming and shaming*, can act as a peer-pressure compliance mechanisms.
-There is comparative evidence that informal norms within communities boost local compliance and allow for flexible and context-adapted climate mitigation solutions [@ostrom1990governing].
-
-## Attributes Three and Four: *Punishment* and *Punishment for Repeated Violations*
-
-The third and fourth attributes relate to punishments against non-compliance.
-We design the first feature, *Punishment*, to capture what types of punishment elites would like to apply to climate agreement violators.
-The options we present closely match existing Latin American regulations on the subject.
-As such, they constitute plausible answers for the interviewees.
-In Brazil, violations are punishable with a range of options, from community services and fines to imprisonment (Law 9605/98, available at <http://www.planalto.gov.br/ccivil_03/leis/l9605.htm>.
-That is also the case for Peru (Law 29263, available at <http://www.minam.gob.pe/delitosambientales>).
-Similarly, Ecuador has recently approved legislation that adds severe penalties on perpetrators of climate violations.
-Incarceration is one of the possible punishments (Article 245, Código Orgánico Integral Penal, available at <http://www.oas.org/juridico/PDFs/mesicic5_ecu_ane_con_judi_c%C3%B3d_org_int_pen.pdf>).
-In this respect, our selected treaty characteristics are plausible to Latin American elites.
-
-Following the same logic, the fourth experimental feature, *Punishment for repeated violations*, captures the actions that should be taken upon subsequent violations of climate change agreements.
-
-## Attribute Five: *Agreement Costs*
-
-The fifth design principle refers to the distribution of climate agreement costs.
-Here we consider the normative debates on burden-sharing and climate distributive justice.
-Developing nations have stressed how wealthier countries have historically contributed more to global warming [@santos2017global].
-More specifically, under the Copenhagen Accord and the Kyoto Protocol, developed countries were deemed as the sole responsible for CO2 emissions [@kartha2011comparison].
-Over time, the wealthier nations successfully contested this position, arguing that emerging economies such as China and India account for a large share of recent greenhouse gas emissions.
-Hence, a new compensation principle emerged, that of *common but differentiated responsibilities and respective capabilities*.
-While accounting for past environmental pollution, the model also requires the contribution of developing countries to reduce global warming.
-
-Our design feature allows us to capture the position of Latin American elites in this debate.
-We add four attributes derived from the discussion presented above.
-The first attribute posits that only rich countries should pay the costs of climate agreements, reflecting the original stance of developing nations.
-The second attribute states that rich countries should pay more than poor countries, which also tests the elites' willing to contribute to global public goods.
-The third alternative states that countries should pay costs according to the history of emissions, while the last one affirms that only current emissions should be taken into account.
-Understanding how Latin American elites stand on this normative issue is essential for assuring local-level compliance and crafting effective climate governance schemes.
-
-## Attribute Six: *Renegotiation*
-
-Finally, our last conjoint experiment dimension investigates the rigidity of climate change agreements.
-From a theoretical standpoint, the contract theory literature argues that more rigid agreements may fall short when their underlying conditions change.
-However, agreements that change constantly might be too unstable to form a path dependency and provide focal points for long-run coordination.
-Thus, parties have to strike a balance between legal stability and the need for adaptation.
-If a climate agreement has deleterious effects in the economy while only marginally improving the country's environmental output, decision-makers will push for treaty renegotiations.
-Conversely, longer agreements reduce coordination costs and give predictability to the system.
-We analyse temporal preferences of Latin American elites by including five different climate agreement renegotiation schedules: one year, five years, twenty years, fifty years, or never.
-
-Latin America has a history of political and economic volatility, so it is unclear whether elites will prefer long-term or short-term climate change initiatives.
-On the one hand, elites may perceive longer contracts as a means to force collective commitment to fight global warming.
-On the other hand, elites can also anticipate future volatility and discount the future more heavily in favor of immediate circumstances.
+In that regard, the conjoint analysis mirrors how people naturally make their choices, that is, by simultaneously taking several characteristics into consideration.
+Finally, as the experiments consist of a simple choice between A and B, conjoint analyses are easy to understand and to implement.
+This research design reduces the cognitive load interviewees have while answering surveys and as a result, we can expect more accurate responses from our sample.
 
@@
 
-The main demographic statistics we collected are: country indicators, elite types, and the geolocation of the respondents. We show their distributions in the graphs below.
-
-```{r demogGraph, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
+The main demographic statistics collected were the country and elite types, and the geolocation of the respondents. They follow in the graphs below.
+
+```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
 library(plm); library(tidyverse)
@@
 library(kableExtra)
-load('data.RData')
+load('freire-mignozzetti-skarbek.RData')
 
@@
 p
-
-# Elite type and group type
-tab <- data.frame(table(aux$groupOrigin, aux$countryOrigin))
-names(tab) <- c('Group Origin','Country', 'Frequency')
-p<- ggplot(data = tab, aes(x = `Group Origin`, y = Frequency)) +
-  geom_bar(stat = "identity") +
-  facet_wrap(~Country) +
-  theme_bw() + 
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
-p
-```
-
-As we can see, we contacted more than fifty elite members for all countries but Bolivia and Peru.
-To compensate for the low response rates in these two countries, we exceeded the sample size in all the remaining states.
-
-Regarding elite type, we interviewed a high number of academics and members of civil society.
-They were followed by members the Executive and of the Legislative, respectively.
-This result is in line with our expectations given the difficulty of reaching high profile government members.
-
-We see that respondents are concentrated in the largest municipalities of their respective countries.
-As elites tend to be more urban and well-educated than average, we indeed expected that most of our sample would be clustered in big cities.
+```
+
+As we can see, we managed to contact more than fifty elite members for all countries but Bolivia and Peru.
+To compensate for the low collection rates in these two countries, note that we exceeded the sample size in all the remaining states.
+
+Considering the elite type, note that we have, as expected, more people from academia and the civil society, followed by those from the Executive and Legislative branches.
+The data collection for members of the Legislative branch was below the original target, but above the minimum mark of 5 for each country.
+This is expected, given the difficulty of accessing these elite members.
+
+In the map, we can see that the answers concentrate on the country's capitals, with some variation within the state, but with sample concentrated in the largest municipalities.
+This is also in line with our expectations, as elite members are assumed to gravitate around capital cities and large urban centers.
 
@@
 
-The figures below display the freature frequency for each attribute, by each task.
-
-```{r attributes, fig.align='center', fig.height=4}
+The figures below display the feature frequency for each attribute, by each task.
+
+```{r attributes, echo=FALSE, fig.align='center', fig.height=4}
 aux <- cj %>%
@@
 
-Two remarkable issues in our data are the low frequency of *Less penalty* in the attribute *How are repeated violations punished?* and the low frequency of *None* for the attribute *What punishments do they use?*.
+The two remarkable issues are the low frequency of *Less penalty* in the attribute *How are repeated violations punished?* and the low frequency of *None* for the attribute *What punishments do they use?*.
 This because when we draw the level none for the attribute *What punishments do they use?* or the level less penalty for *How are repeated violations punished?*, then it makes no sense to have less penalty than the minimum possible.
@@
 
-p <- plot(mms, vline = 0.5, header_fmt = "%s", size = 2) +
-  ggplot2::theme(
+p <- plot(mms, vline = 0.5, header_fmt = "%s", size = 2) + ggplot2::theme(
     legend.position = "none",
@@
                                                 xmax = "upper"),
-                            size = 0.5, height = 0, na.rm = TRUE)
+                            size = 1, height = 0, na.rm = TRUE,
+                            position = ggstance::position_dodgev(height = 1))
 p
 
-ggsave(filename = 'MM_all.pdf', plot = p, width = 6, height = 5)
+ggsave(filename = 'MM_all.pdf', plot = p, width = 8, height = 6)
 
@@
   ggplot2::theme(
-    axis.text.y = element_text(face=myFaces, size = 13)) + 
+    axis.text.y = element_text(face=myFaces, size = 11)) + 
     ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
                                                 xmax = "upper"),
-                            size = 0.75, height = 0, na.rm = TRUE)
+                            size = 1, height = 0, na.rm = TRUE,
+                            position = ggstance::position_dodgev(height = 1))
 
@@
 ggsave(filename = 'MM_country.pdf', 
-       plot = p, width = 10, height = 12)
+       plot = p, width = 12, height = 12)
 ```
@@
 
-# Table for the Executive
+# Table for the Executive branch
 res1 <- mm(subset(cj, groupOrigin=='Executive'), 
@@
 ```{r}
-# Legislative
+# Legislative branch
 res2 <- mm(subset(cj, groupOrigin=='Legislative'), 
@@
 ```{r}
-# Civil Society
+# Civil society
 res3 <- mm(subset(cj, groupOrigin=='Civil Society'), 
@@
                                                 xmax = "upper"),
-                            size = 0.5, height = 0, na.rm = TRUE,
+                            size = 1, height = 0, na.rm = TRUE,
                             position = ggstance::position_dodgev(height = 1))
@@
 rm(cj)
-load('data.RData')
+load('freire-mignozzetti-skarbek.RData')
 
@@
 
-# Executive
+# Executive branch
 results <- cjoint::amce(fm, data = cj, cluster = TRUE,
@@
                         subset = cj$groupOrigin == 'Executive')
-# Table AMCE -- Executive Only
-tableAMCE(results, capt = 'AMCE -- Executive Only')
+# Table AMCE -- Executive branch only
+tableAMCE(results, capt = 'AMCE -- Executive Branch Only')
 ```
@@
 plot(results, ci=0.9, point.size = .8, dodge.size = 1,
-     text.size = 10, main = 'AMCE -- Executive Only',
+     text.size = 10, main = 'AMCE -- Executive Branch Only',
      attribute.names = attrs)
@@
 ```{r}
-## Legislative
+## Legislative branch
 results <- cjoint::amce(fm, data = cj, cluster = TRUE,
@@
                         subset = cj$groupOrigin == 'Legislative')
-# Table AMCE -- Legislative Only
-tableAMCE(results, capt = 'AMCE -- Legislative Only')
+# Table AMCE -- Legislative branch only
+tableAMCE(results, capt = 'AMCE -- Legislative Branch Only')
 ```
@@
 plot(results, ci=0.9, point.size = .8, dodge.size = 1,
-     text.size = 10, main = 'AMCE -- Legislative Only',
+     text.size = 10, main = 'AMCE -- Legislative Branch Only',
      attribute.names = attrs)
@@
 
-# APSA Experimental Section Standard Report for Experiments
+# APSA Experimental Section Standard Report for Experiments \label{sec:apsa}
 
@@
 
-1. **Executive members**: members of regulatory agencies, politicians (mayors, governors, presidents), members of ministries and secretaries at the federal and state levels.
-2. **Legislative members**: legislators and staff officers from the federal and state level in the researched countries.
+1. **Members of the Executive branch**: members of regulatory agencies, politicians (mayors, governors, presidents), members of ministries and secretaries at the federal and state levels.
+2. **Members of the Legislative branch**: legislators and staff officers from the federal and state level in the researched countries.
 3. **Civil society**: environmental and energy-related NGO members; oil, renewables, and environmental solutions firm owners in the researched countries.
@@
 We decided to include these profiles based on the stakes and influence that such elites have on climate change policies.
-According to constructivist international relations theories, academics have notable influence on our topic of interest as they form an epistemic community around climate change policies.
+According to the IR constructivist theories, academics have notable influence on our topic of interest as they form the epistemic community around climate change policies.
 Civil society members that have stakes on climate policies are also influential, such as oil-extracting companies, lobby groups, and environmental NGOs.
-Executive and Legislative elites handle the decisions themselves, what justifies their inclusion in our sample.
+Members of the Executive and Legislative branches handle the decisions themselves, so their importance.
 
 We selected ten countries to our sample: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
-Our selection criteria were: 1) the impact of climate change on each nation, 2) their size and regional importance, and 3) natural resources availability.
+Our selection criteria were the impact of climate change on each nation, their size and regional importance, and natural resources availability.
 For each country, we built a dataset of potential respondents with at least:
@@
 In the second tier we included participants that had incomplete profiles, such as those with only online information available.
-The dataset including the first-tier respondents was randomly divided between enumerators in Rio de Janeiro and São Paulo to avoid any eventual biases at the collecting stage.
+The dataset including the first-tier respondents was randomly divided between enumerators in Rio de Janeiro and São Paulo to avoid any eventual biases from the collecting stage.
 Both groups conducted the interviews by phone from November 12th to December 5th, 2018.
-The second tier dataset was used for the online only version of the survey.
+The second tier dataset was used for an online only version of the survey.
 
@@
 The response rate was 10.24 percent of the original population in the telephone survey (779 of 7606 possible respondents).
-We had an attrition rate of 61.62 percent from the telephone (779) to the online survey (299).
+We had an attrition of 61.62 percent from the telephone (779) to the online survey (299).
 The response rate for the online only survey was 5.26 percent (293 of 5569 invited by email).
 
-The conjoint experiment analyzed in this paper was in the online and online only dataset. Therefore, the relevant column for our data is the last one.
+The conjoint experiment analyzed in this paper was in the online and online-only dataset. Therefore, the relevant column for our data is the last one.
 
@@
 
-**Random Assignment:** We wrote the computer code for our experiment using a Python application provided by @strezhnev2013conjoint.
+**Random Assignment:** We programmed the experiment using a Python application provided by @strezhnev2013conjoint.
 We translated the original survey questions (as shown in the text) into Portuguese and Spanish, and then embedded the PHP file with the randomization parameters in a Qualtrics survey.
-The PHP code we used to randomize the values of the attributes is available at the project's GitHub repository: <https://github.com/danilofreire/climate-governance>.
+The PHP code we used to randomize the values of the attributes is available at the project's GitHub repository: <http://github.com/danilofreire/climate-governance>.
 
@@
 
-The conjoint experiment consisted in comparing two hypothetical climate change treaties that vary across six attributes. We presented each respondent with seven pairs of possible climate agreements.
-
-\noindent \textbf{Software:} We used the Python application provided by @strezhnev2013conjoint to program the PHP randomization device. We hosted the survey questionnaire on Qualtrics.
+The conjoint experiment consisted in comparing two treaties that vary in these six attributes, repeating the application for seven times for each respondent.
+
+\noindent \textbf{Software:} To program the PHP randomization device we used the Python application provided by @strezhnev2013conjoint. We used Qualtrics to administer the survey.
 
@@
 
-\noindent \textbf{Dataset description:} Each line in the dataset corresponds to a given treaty, which indicates the selection status of a given treaty (selected versus non-selected) for a specific respondent.
-When a respondent finished an entire response set, this added 14 rows to the dataset.
+\noindent \textbf{Dataset description:} Each line in the dataset represents a given treaty, varying for the selection status (selected versus non-selected) for a given respondent.
+When a respondent finished an entire response set, this adds 14 rows to the dataset.
 Seven rows with the selected treaties and other seven rows with the non-selected treaties.
@@
 We added two covariates to measure heterogeneous effects: *Country* and *Elite type*.
+
+\noindent \textbf{Questionnaire:} For the English translation of the entire survey instrument, with both the telephone and the online components, see the attachment below.
 
@@
 
-```{r, fig.width = 7, fig.height = 5, tidy=FALSE}
-barplot(100*table(cj$task)/max(table(cj$task)),
-        xlab = 'Conjoint task',
-        ylab = 'Percentage completed')
+```{r, fig.width = 7, fig.height = 8}
+barplot(100*table(cj$task)/max(table(cj$task)), xlab = 'Conjoint task', ylab = 'Percentage completed')
 ```

### 2020-05-27 supplementary-material/supplementary-material-climate-policy.tex
Accepted version

% !TEX program = XeLaTeX
\documentclass[12pt,a4paper,]{article}

% Fonts
\usepackage[]{libertine}
% This is a nice mathfont, it fits well with Libertine
% Comment the line if you want to use a different one
\usepackage[libertine]{newtxmath}
% The default monofont 
% Again, comment the line below if you want to change it
\usepackage[scaled=.95]{inconsolata}

% Add the following packages to support kableExtra
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{etoolbox}
\usepackage{tocloft}

% Dots in toc
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

% Colours
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}

% Spacing
\usepackage{setspace}

% Margin
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm]{geometry}

% Packages I've been using for different reasons...
\usepackage[backref,pagebackref]{hyperref}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usepackage{mathtools}
\usepackage{caption}

% UK English
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\cleanlookdateon

% Penalties
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=1000
\clubpenalty=1000

% Back references
\renewcommand*{\backref}[1]{}
\renewcommand*{\backrefalt}[4]{%
    \ifcase #1 (Not cited.)%
    \or        Cited on page~#2.%
    \else      Cited on pages~#2.%
    \fi}
\renewcommand{\backreftwosep}{ and~} 
\renewcommand{\backreflastsep}{ and~}

% Hypersetup
\hypersetup{
  linkcolor=Mahogany,
  citecolor=Mahogany,
  urlcolor=darkblue, 
  breaklinks=true, 
  colorlinks=true,
      pdfauthor={Danilo Freire; Umberto Mignozzetti; David Skarbek},
    }

% If XeTex, LuaLaTeX, etc
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{amssymb,amsmath}
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

% Language

% Bibliography
\usepackage{natbib}
\bibliographystyle{apalike}
\makeatletter
% Remove comma after author
\setcitestyle{aysep={}}
\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
	\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
		   {\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
	  {}{}
% Patch case where name and year are separated by aysep
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
% Patch case where name and year are separated by opening bracket
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
       {\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
  {}{}
\makeatother

% Listings
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

% Verbatim

% Tables
\usepackage{longtable,booktabs}

% Graphics
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

% Make links footnotes instead of hotlinks:
%  \setlength{\emergencystretch}{3em}  % prevent overfull lines
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Numbered sections
\setcounter{secnumdepth}{5}
% % % Redefines (sub)paragraphs to behave more like sections
% \ifx\paragraph\undefined\else
% \let\oldparagraph\paragraph
% \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
% \fi
% \ifx\subparagraph\undefined\else
% \let\oldsubparagraph\subparagraph
% \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
% \fi
% 
% Spacing
\doublespacing

% Title
\title{Supplementary Materials for ``Institutional Design and Elite Support for
Climate Policies: Evidence from Latin American Countries''}

% Author
\author{Danilo Freire\footnote{Postdoctoral Research Associate, The Political
  Theory Project, Brown University, Providence, RI 02912, USA,
  \href{mailto:danilofreire@brown.edu}{\nolinkurl{danilofreire@brown.edu}},
  \url{http://danilofreire.github.io}. Corresponding author.} \and Umberto Mignozzetti\footnote{School of International Relations, Fundação
  Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of
  Politics, NYU, NY, USA,
  \href{mailto:umberto.mig@nyu.edu}{\nolinkurl{umberto.mig@nyu.edu}},
  \url{http://umbertomig.com}.} \and David Skarbek\footnote{The Department of Political Science and the
  Political Theory Project, Brown University, Providence, RI, USA,
  \href{mailto:davidskarbek@brown.edu}{\nolinkurl{davidskarbek@brown.edu}},
  \url{http://davidskarbek.com}.}}

% Date
\date{\today}

% Begin document
\begin{document}
\maketitle

% Abstract

% Table of Contents
{
\hypersetup{linkcolor=black}
\setcounter{tocdepth}{2}
\tableofcontents
}
\hypertarget{latin-american-elite-survey}{%
\section{\texorpdfstring{Latin American Elite Survey
\label{sec:latam}}{Latin American Elite Survey }}\label{latin-american-elite-survey}}

\setlength{\parindent}{1cm}
\setlength{\parskip}{0pt}

From October 1 to December 5, 2018, we ran an elite survey with
respondents from ten Latin American countries: Argentina, Bolivia,
Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
The survey proceeded in two steps.

We collected information on Latin American elites. The target was:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Members of the Executive branch
\item
  Members of the Legislative branch
\item
  Civil society
\item
  Academics
\end{enumerate}

For each profile, in each country, we aimed at surveying:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  10 members of the Executive branch
\item
  10 members of the Legislative branch
\item
  15 Civil society
\item
  15 Academics
\end{enumerate}

To do so, we built a prospective respondents dataset with ten times
these members for each country. Then, we ran an online and telephone
survey where we collected information regarding the climate change
agreements and other climate change-related problems.

After finishing this dataset, we started the surveying stage. From
November 12 to December 5, we ran the survey by contacting elite members
by phone or by email. We had two teams of enumerators, one based in São
Paulo and another based in Rio de Janeiro, Brazil, comprised of
Portuguese and Spanish native speakers. Although the overall aim of the
survey was 500 responses, the teams managed to collect 654 interviews.

\hypertarget{conjoint-experiment-analysis-identification-and-estimation}{%
\section{\texorpdfstring{Conjoint Experiment Analysis: Identification
and Estimation
\label{sec:conjoint}}{Conjoint Experiment Analysis: Identification and Estimation }}\label{conjoint-experiment-analysis-identification-and-estimation}}

A conjoint experiment is a statistical technique that allows individuals
to express their preferences on multiple attributes of a single topic
\citep{hainmueller2014causal, bansak2016economic}. Individuals are
presented with two hypothetical scenarios, A and B, each containing a
series of characteristics a researcher wants to evaluate. The individual
chooses one of them. As the attributes are randomized and individuals
choose between different pairs of hypothetical scenarios, we can
estimate how individuals value each of the conjoined elements.

In our research, we ask what features elite members would like to see
implemented in a climate change agreement. We ask their opinion on 6
questions: 1) who makes the rules; 2) who enforces the laws; 3) what
punishment should be used against lawbreakers; 4) how are repeated
violations punished; 5) how are costs distributed, and 6) how often the
agreement will be renegotiated. Each of the questions has four to five
different attributes. For the first two questions, we ask individuals if
they would rather have the community, local governments, federal
governments, or international organizations to create or enforce rules.
As for punishments, we have options ranging from do nothing to fines and
incarceration. We ask whether the costs of climate change agreements
should be paid mostly or exclusively by developed countries, by polluter
countries regardless of their wealth, or if costs should be allocated
according to the history of emissions of a given nation. Individuals
also state their preferences for short-term agreements, a proxy we use
for flexibility, or for long-term ones, what we see as a proxy for the
stability of rules. Lastly, we ask which of the two conjoined choices
individuals perceive as more legitimate and more efficient.

Conjoint experiments have many advantages \citep{hainmueller2014causal}.
First, as each individual chooses between many pairs of possible climate
agreements -- seven in our case -- we can drastically increase our
sample size without incurring in further financial costs. The design
thus maximizes our research budget. Second, individuals rarely decide
considering one attribute at a time, as presented in other types of
survey experiments. In that regard, the conjoint analysis mirrors how
people naturally make their choices, that is, by simultaneously taking
several characteristics into consideration. Finally, as the experiments
consist of a simple choice between A and B, conjoint analyses are easy
to understand and to implement. This research design reduces the
cognitive load interviewees have while answering surveys and as a
result, we can expect more accurate responses from our sample.

\hypertarget{descriptive-statistics}{%
\section{\texorpdfstring{Descriptive Statistics
\label{sec:descstats}}{Descriptive Statistics }}\label{descriptive-statistics}}

The main demographic statistics collected were the country and elite
types, and the geolocation of the respondents. They follow in the graphs
below.

\begin{center}\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/demogGraph-1} \end{center}

\begin{center}\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/demogGraph-2} \end{center}

As we can see, we managed to contact more than fifty elite members for
all countries but Bolivia and Peru. To compensate for the low collection
rates in these two countries, note that we exceeded the sample size in
all the remaining states.

Considering the elite type, note that we have, as expected, more people
from academia and the civil society, followed by those from the
Executive and Legislative branches. The data collection for members of
the Legislative branch was below the original target, but above the
minimum mark of 5 for each country. This is expected, given the
difficulty of accessing these elite members.

In the map, we can see that the answers concentrate on the country's
capitals, with some variation within the state, but with sample
concentrated in the largest municipalities. This is also in line with
our expectations, as elite members are assumed to gravitate around
capital cities and large urban centers.

\hypertarget{frequency-of-features-selected-by-each-attribute}{%
\section{\texorpdfstring{Frequency of Features Selected by Each
Attribute
\label{sec:features}}{Frequency of Features Selected by Each Attribute }}\label{frequency-of-features-selected-by-each-attribute}}

The figures below display the feature frequency for each attribute, by
each task.

\begin{center}\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/attributes-1} \end{center}

\begin{center}\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/attributes-2} \end{center}

\begin{center}\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/attributes-3} \end{center}

\begin{center}\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/attributes-4} \end{center}

\begin{center}\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/attributes-5} \end{center}

\begin{center}\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/attributes-6} \end{center}

The two remarkable issues are the low frequency of \emph{Less penalty}
in the attribute \emph{How are repeated violations punished?} and the
low frequency of \emph{None} for the attribute \emph{What punishments do
they use?}. This because when we draw the level none for the attribute
\emph{What punishments do they use?} or the level less penalty for
\emph{How are repeated violations punished?}, then it makes no sense to
have less penalty than the minimum possible.

\hypertarget{code-for-the-main-paper}{%
\section{Code for the Main Paper}\label{code-for-the-main-paper}}

The code for Figure 2 of the paper follows below. We also include the
point estimates in companion tables.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Main plot}
\CommentTok{# Main estimation equation}
\NormalTok{fm <-}\StringTok{ }\NormalTok{selected }\OperatorTok{~}\StringTok{ `}\DataTypeTok{Who makes the rules?}\StringTok{`} \OperatorTok{+}
\StringTok{  `}\DataTypeTok{How are conflicts resolved?}\StringTok{`} \OperatorTok{+}
\StringTok{  `}\DataTypeTok{What punishments do they use?}\StringTok{`} \OperatorTok{+}\StringTok{ }
\StringTok{  `}\DataTypeTok{How are repeated violations punished?}\StringTok{`} \OperatorTok{+}
\StringTok{  `}\DataTypeTok{How are costs distributed?}\StringTok{`} \OperatorTok{+}
\StringTok{  `}\DataTypeTok{How often will the agreement be renegotiated?}\StringTok{`}

\CommentTok{# Plot}
\NormalTok{mms <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(cj, fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}

\NormalTok{myFaces <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{'plain'}\NormalTok{, }\DecValTok{5}\NormalTok{), }\StringTok{"bold"}\NormalTok{,}
             \KeywordTok{rep}\NormalTok{(}\StringTok{'plain'}\NormalTok{, }\DecValTok{4}\NormalTok{), }\StringTok{"bold"}\NormalTok{,}
             \KeywordTok{rep}\NormalTok{(}\StringTok{'plain'}\NormalTok{, }\DecValTok{3}\NormalTok{), }\StringTok{"bold"}\NormalTok{,}
             \KeywordTok{rep}\NormalTok{(}\StringTok{'plain'}\NormalTok{, }\DecValTok{4}\NormalTok{), }\StringTok{"bold"}\NormalTok{,}
             \KeywordTok{rep}\NormalTok{(}\StringTok{'plain'}\NormalTok{, }\DecValTok{5}\NormalTok{), }\StringTok{"bold"}\NormalTok{,}
             \KeywordTok{rep}\NormalTok{(}\StringTok{'plain'}\NormalTok{, }\DecValTok{5}\NormalTok{), }\StringTok{"bold"}\NormalTok{)}

\NormalTok{p <-}\StringTok{ }\KeywordTok{plot}\NormalTok{(mms, }\DataTypeTok{vline =} \FloatTok{0.5}\NormalTok{, }\DataTypeTok{header_fmt =} \StringTok{"%s"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\NormalTok{ggplot2}\OperatorTok{::}\KeywordTok{theme}\NormalTok{(}
    \DataTypeTok{legend.position =} \StringTok{"none"}\NormalTok{,}
    \DataTypeTok{panel.grid.major =}\NormalTok{ ggplot2}\OperatorTok{::}\KeywordTok{element_blank}\NormalTok{(),}
    \DataTypeTok{panel.grid.minor =}\NormalTok{ ggplot2}\OperatorTok{::}\KeywordTok{element_blank}\NormalTok{(),}
    \DataTypeTok{axis.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{face=}\NormalTok{myFaces, }\DataTypeTok{size =} \DecValTok{11}\NormalTok{)) }\OperatorTok{+}\StringTok{ }
\StringTok{    }\NormalTok{ggplot2}\OperatorTok{::}\KeywordTok{geom_errorbarh}\NormalTok{(ggplot2}\OperatorTok{::}\KeywordTok{aes_string}\NormalTok{(}\DataTypeTok{xmin =} \StringTok{"lower"}\NormalTok{,}
                                                \DataTypeTok{xmax =} \StringTok{"upper"}\NormalTok{),}
                            \DataTypeTok{size =} \DecValTok{1}\NormalTok{, }\DataTypeTok{height =} \DecValTok{0}\NormalTok{, }\DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{,}
                            \DataTypeTok{position =}\NormalTok{ ggstance}\OperatorTok{::}\KeywordTok{position_dodgev}\NormalTok{(}\DataTypeTok{height =} \DecValTok{1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: Vectorized input to `element_text()` is not officially supported.
## Results may be unexpected or may change in future versions of ggplot2.
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{p}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/codefig2-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggsave}\NormalTok{(}\DataTypeTok{filename =} \StringTok{'MM_all.pdf'}\NormalTok{, }\DataTypeTok{plot =}\NormalTok{ p, }\DataTypeTok{width =} \DecValTok{8}\NormalTok{, }\DataTypeTok{height =} \DecValTok{6}\NormalTok{)}

\CommentTok{# Table}
\NormalTok{table_mm <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(mms, capt) \{}
\NormalTok{  dfr <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{feature =}\NormalTok{ mms[,}\KeywordTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{)], }
             \KeywordTok{round}\NormalTok{(mms[,}\KeywordTok{c}\NormalTok{(}\DecValTok{5}\NormalTok{,}\DecValTok{6}\NormalTok{,}\DecValTok{8}\NormalTok{,}\DecValTok{9}\NormalTok{,}\DecValTok{10}\NormalTok{)], }\DataTypeTok{digits=}\DecValTok{3}\NormalTok{))}
  \KeywordTok{names}\NormalTok{(dfr) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{'Feature'}\NormalTok{, }\StringTok{'Estimate'}\NormalTok{, }\StringTok{'Std.Error'}\NormalTok{,}
                \StringTok{'P-Value'}\NormalTok{, }\StringTok{'Lower'}\NormalTok{, }\StringTok{'Upper'}\NormalTok{)}
  \KeywordTok{return}\NormalTok{(}\KeywordTok{kable}\NormalTok{(dfr, }\StringTok{"latex"}\NormalTok{, }\DataTypeTok{caption =}\NormalTok{ capt, }\DataTypeTok{booktabs =}\NormalTok{ T) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{font_size =} \DecValTok{10}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{group_rows}\NormalTok{(}\StringTok{'Who makes the rules?'}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{5}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{group_rows}\NormalTok{(}\StringTok{'How are conflicts resolved?'}\NormalTok{, }\DecValTok{6}\NormalTok{, }\DecValTok{10}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{group_rows}\NormalTok{(}\StringTok{'What punishments do they use?'}\NormalTok{, }\DecValTok{11}\NormalTok{, }\DecValTok{14}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{group_rows}\NormalTok{(}\StringTok{'How are repeated violations punished?'}\NormalTok{, }\DecValTok{15}\NormalTok{, }\DecValTok{17}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{group_rows}\NormalTok{(}\StringTok{'How are costs distributed?'}\NormalTok{, }\DecValTok{18}\NormalTok{, }\DecValTok{21}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{group_rows}\NormalTok{(}\StringTok{'How often will the agreement be renegotiated?'}\NormalTok{, }\DecValTok{22}\NormalTok{, }\DecValTok{26}\NormalTok{))}
\NormalTok{\}}

\KeywordTok{table_mm}\NormalTok{(mms, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Full Dataset'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:codefig2}Marginal Means -- Full Dataset}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.455 & 0.013 & 0.000 & 0.434 & 0.476\\
\hspace{1em}Local community members & 0.516 & 0.013 & 0.202 & 0.495 & 0.537\\
\hspace{1em}Local government & 0.498 & 0.012 & 0.901 & 0.478 & 0.519\\
\hspace{1em}Federal government & 0.486 & 0.013 & 0.271 & 0.466 & 0.507\\
\hspace{1em}International organizations & 0.543 & 0.012 & 0.001 & 0.522 & 0.563\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.410 & 0.013 & 0.000 & 0.390 & 0.431\\
\hspace{1em}Private arbitration & 0.500 & 0.013 & 0.980 & 0.480 & 0.521\\
\hspace{1em}Local courts & 0.546 & 0.012 & 0.000 & 0.526 & 0.567\\
\hspace{1em}Government bureaucracy & 0.465 & 0.013 & 0.005 & 0.444 & 0.485\\
\hspace{1em}United Nations & 0.573 & 0.012 & 0.000 & 0.553 & 0.593\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.448 & 0.013 & 0.000 & 0.427 & 0.470\\
\hspace{1em}Blacklist & 0.523 & 0.011 & 0.035 & 0.505 & 0.540\\
\hspace{1em}Fines & 0.553 & 0.011 & 0.000 & 0.536 & 0.571\\
\hspace{1em}Imprisonment & 0.458 & 0.011 & 0.000 & 0.440 & 0.476\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.464 & 0.011 & 0.001 & 0.447 & 0.481\\
\hspace{1em}Same & 0.497 & 0.009 & 0.739 & 0.482 & 0.512\\
\hspace{1em}More penalty & 0.532 & 0.009 & 0.001 & 0.517 & 0.548\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.438 & 0.011 & 0.000 & 0.420 & 0.456\\
\hspace{1em}Proportional to current emissions & 0.524 & 0.011 & 0.030 & 0.506 & 0.542\\
\hspace{1em}Proportional to history of emissions & 0.536 & 0.011 & 0.001 & 0.518 & 0.555\\
\hspace{1em}Rich countries pay more than poor countries & 0.505 & 0.011 & 0.684 & 0.486 & 0.523\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.535 & 0.012 & 0.004 & 0.515 & 0.556\\
\hspace{1em}Five years & 0.590 & 0.012 & 0.000 & 0.570 & 0.610\\
\hspace{1em}Twenty years & 0.519 & 0.012 & 0.121 & 0.499 & 0.540\\
\hspace{1em}Fifty years & 0.442 & 0.013 & 0.000 & 0.421 & 0.463\\
\hspace{1em}Never & 0.404 & 0.013 & 0.000 & 0.383 & 0.424\\
\bottomrule
\end{tabular}
\end{table}

The code for Figure 3 of the paper follows below, with also the point
estimates in a companion table.

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Marginal means by Country}

\CommentTok{# Argentina}
\NormalTok{arg <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, countryOrigin}\OperatorTok{==}\StringTok{'Argentina'}\NormalTok{),  }
\NormalTok{        fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(arg, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Argentina Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:codefig3}Marginal Means -- Argentina Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.417 & 0.043 & 0.052 & 0.346 & 0.487\\
\hspace{1em}Local community members & 0.449 & 0.044 & 0.246 & 0.376 & 0.521\\
\hspace{1em}Local government & 0.503 & 0.042 & 0.933 & 0.435 & 0.572\\
\hspace{1em}Federal government & 0.504 & 0.045 & 0.928 & 0.429 & 0.579\\
\hspace{1em}International organizations & 0.619 & 0.041 & 0.004 & 0.551 & 0.686\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.377 & 0.043 & 0.004 & 0.307 & 0.447\\
\hspace{1em}Private arbitration & 0.522 & 0.047 & 0.638 & 0.445 & 0.599\\
\hspace{1em}Local courts & 0.574 & 0.042 & 0.074 & 0.506 & 0.643\\
\hspace{1em}Government bureaucracy & 0.446 & 0.044 & 0.217 & 0.374 & 0.518\\
\hspace{1em}United Nations & 0.568 & 0.041 & 0.097 & 0.501 & 0.635\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.361 & 0.043 & 0.001 & 0.289 & 0.432\\
\hspace{1em}Blacklist & 0.514 & 0.037 & 0.710 & 0.453 & 0.575\\
\hspace{1em}Fines & 0.587 & 0.037 & 0.019 & 0.526 & 0.647\\
\hspace{1em}Imprisonment & 0.494 & 0.037 & 0.882 & 0.433 & 0.556\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.465 & 0.035 & 0.319 & 0.406 & 0.523\\
\hspace{1em}Same & 0.516 & 0.032 & 0.608 & 0.464 & 0.569\\
\hspace{1em}More penalty & 0.514 & 0.034 & 0.686 & 0.458 & 0.569\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.408 & 0.035 & 0.009 & 0.350 & 0.466\\
\hspace{1em}Proportional to current emissions & 0.534 & 0.041 & 0.410 & 0.466 & 0.601\\
\hspace{1em}Proportional to history of emissions & 0.576 & 0.038 & 0.045 & 0.514 & 0.638\\
\hspace{1em}Rich countries pay more than poor countries & 0.500 & 0.041 & 1.000 & 0.432 & 0.568\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.604 & 0.039 & 0.008 & 0.539 & 0.669\\
\hspace{1em}Five years & 0.545 & 0.043 & 0.298 & 0.474 & 0.616\\
\hspace{1em}Twenty years & 0.438 & 0.044 & 0.157 & 0.367 & 0.510\\
\hspace{1em}Fifty years & 0.438 & 0.044 & 0.154 & 0.365 & 0.510\\
\hspace{1em}Never & 0.448 & 0.046 & 0.263 & 0.372 & 0.524\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Bolivia}
\NormalTok{bol <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, countryOrigin}\OperatorTok{==}\StringTok{'Bolivia'}\NormalTok{),  }
\NormalTok{        fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(bol, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Bolivia Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-1}Marginal Means -- Bolivia Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.421 & 0.051 & 0.119 & 0.338 & 0.504\\
\hspace{1em}Local community members & 0.575 & 0.053 & 0.159 & 0.488 & 0.662\\
\hspace{1em}Local government & 0.560 & 0.054 & 0.272 & 0.470 & 0.649\\
\hspace{1em}Federal government & 0.467 & 0.048 & 0.498 & 0.388 & 0.547\\
\hspace{1em}International organizations & 0.494 & 0.056 & 0.910 & 0.401 & 0.586\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.369 & 0.053 & 0.013 & 0.282 & 0.456\\
\hspace{1em}Private arbitration & 0.543 & 0.051 & 0.408 & 0.458 & 0.627\\
\hspace{1em}Local courts & 0.538 & 0.052 & 0.467 & 0.453 & 0.623\\
\hspace{1em}Government bureaucracy & 0.397 & 0.055 & 0.064 & 0.306 & 0.489\\
\hspace{1em}United Nations & 0.612 & 0.048 & 0.020 & 0.533 & 0.691\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.442 & 0.054 & 0.278 & 0.354 & 0.530\\
\hspace{1em}Blacklist & 0.466 & 0.044 & 0.431 & 0.394 & 0.537\\
\hspace{1em}Fines & 0.570 & 0.044 & 0.108 & 0.498 & 0.642\\
\hspace{1em}Imprisonment & 0.505 & 0.048 & 0.923 & 0.425 & 0.584\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.451 & 0.042 & 0.238 & 0.382 & 0.519\\
\hspace{1em}Same & 0.534 & 0.038 & 0.362 & 0.472 & 0.597\\
\hspace{1em}More penalty & 0.507 & 0.043 & 0.864 & 0.437 & 0.578\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.424 & 0.045 & 0.094 & 0.349 & 0.499\\
\hspace{1em}Proportional to current emissions & 0.593 & 0.047 & 0.050 & 0.515 & 0.670\\
\hspace{1em}Proportional to history of emissions & 0.427 & 0.046 & 0.112 & 0.352 & 0.503\\
\hspace{1em}Rich countries pay more than poor countries & 0.569 & 0.047 & 0.147 & 0.491 & 0.647\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.485 & 0.050 & 0.763 & 0.402 & 0.567\\
\hspace{1em}Five years & 0.624 & 0.048 & 0.010 & 0.544 & 0.703\\
\hspace{1em}Twenty years & 0.575 & 0.053 & 0.159 & 0.488 & 0.662\\
\hspace{1em}Fifty years & 0.385 & 0.055 & 0.036 & 0.294 & 0.475\\
\hspace{1em}Never & 0.402 & 0.053 & 0.063 & 0.316 & 0.489\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Brazil}
\NormalTok{bra <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, countryOrigin}\OperatorTok{==}\StringTok{'Brazil'}\NormalTok{),  }
\NormalTok{        fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(bra, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Brazil Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-2}Marginal Means -- Brazil Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.492 & 0.036 & 0.829 & 0.433 & 0.551\\
\hspace{1em}Local community members & 0.495 & 0.036 & 0.886 & 0.436 & 0.554\\
\hspace{1em}Local government & 0.456 & 0.036 & 0.219 & 0.397 & 0.515\\
\hspace{1em}Federal government & 0.481 & 0.036 & 0.610 & 0.422 & 0.541\\
\hspace{1em}International organizations & 0.563 & 0.033 & 0.053 & 0.509 & 0.617\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.434 & 0.037 & 0.079 & 0.373 & 0.496\\
\hspace{1em}Private arbitration & 0.475 & 0.035 & 0.477 & 0.416 & 0.533\\
\hspace{1em}Local courts & 0.556 & 0.035 & 0.114 & 0.498 & 0.615\\
\hspace{1em}Government bureaucracy & 0.476 & 0.035 & 0.485 & 0.418 & 0.533\\
\hspace{1em}United Nations & 0.547 & 0.033 & 0.160 & 0.492 & 0.601\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.465 & 0.038 & 0.356 & 0.402 & 0.528\\
\hspace{1em}Blacklist & 0.523 & 0.031 & 0.461 & 0.472 & 0.573\\
\hspace{1em}Fines & 0.569 & 0.030 & 0.021 & 0.520 & 0.618\\
\hspace{1em}Imprisonment & 0.434 & 0.029 & 0.024 & 0.386 & 0.482\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.416 & 0.029 & 0.004 & 0.368 & 0.464\\
\hspace{1em}Same & 0.518 & 0.027 & 0.490 & 0.475 & 0.562\\
\hspace{1em}More penalty & 0.549 & 0.026 & 0.063 & 0.506 & 0.592\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.429 & 0.033 & 0.028 & 0.375 & 0.482\\
\hspace{1em}Proportional to current emissions & 0.496 & 0.031 & 0.901 & 0.445 & 0.547\\
\hspace{1em}Proportional to history of emissions & 0.546 & 0.032 & 0.152 & 0.493 & 0.599\\
\hspace{1em}Rich countries pay more than poor countries & 0.524 & 0.030 & 0.431 & 0.474 & 0.574\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.535 & 0.034 & 0.305 & 0.479 & 0.591\\
\hspace{1em}Five years & 0.568 & 0.036 & 0.064 & 0.508 & 0.627\\
\hspace{1em}Twenty years & 0.537 & 0.034 & 0.275 & 0.481 & 0.593\\
\hspace{1em}Fifty years & 0.469 & 0.035 & 0.368 & 0.412 & 0.526\\
\hspace{1em}Never & 0.377 & 0.037 & 0.001 & 0.317 & 0.437\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Chile}
\NormalTok{chi <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, countryOrigin}\OperatorTok{==}\StringTok{'Chile'}\NormalTok{),  }
\NormalTok{        fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(chi, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Chile Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-3}Marginal Means -- Chile Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.400 & 0.043 & 0.020 & 0.329 & 0.471\\
\hspace{1em}Local community members & 0.630 & 0.039 & 0.001 & 0.566 & 0.694\\
\hspace{1em}Local government & 0.538 & 0.040 & 0.335 & 0.473 & 0.604\\
\hspace{1em}Federal government & 0.403 & 0.043 & 0.025 & 0.332 & 0.474\\
\hspace{1em}International organizations & 0.496 & 0.043 & 0.932 & 0.426 & 0.567\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.403 & 0.042 & 0.022 & 0.333 & 0.473\\
\hspace{1em}Private arbitration & 0.480 & 0.045 & 0.652 & 0.406 & 0.554\\
\hspace{1em}Local courts & 0.606 & 0.039 & 0.006 & 0.543 & 0.670\\
\hspace{1em}Government bureaucracy & 0.445 & 0.041 & 0.183 & 0.378 & 0.513\\
\hspace{1em}United Nations & 0.545 & 0.042 & 0.275 & 0.477 & 0.614\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.425 & 0.043 & 0.081 & 0.355 & 0.496\\
\hspace{1em}Blacklist & 0.607 & 0.036 & 0.003 & 0.547 & 0.666\\
\hspace{1em}Fines & 0.512 & 0.035 & 0.726 & 0.455 & 0.570\\
\hspace{1em}Imprisonment & 0.435 & 0.036 & 0.076 & 0.376 & 0.495\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.476 & 0.036 & 0.512 & 0.416 & 0.536\\
\hspace{1em}Same & 0.438 & 0.030 & 0.041 & 0.388 & 0.488\\
\hspace{1em}More penalty & 0.583 & 0.031 & 0.007 & 0.532 & 0.634\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.462 & 0.040 & 0.338 & 0.397 & 0.527\\
\hspace{1em}Proportional to current emissions & 0.524 & 0.037 & 0.508 & 0.464 & 0.585\\
\hspace{1em}Proportional to history of emissions & 0.497 & 0.037 & 0.940 & 0.436 & 0.559\\
\hspace{1em}Rich countries pay more than poor countries & 0.511 & 0.037 & 0.768 & 0.450 & 0.571\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.418 & 0.042 & 0.050 & 0.350 & 0.487\\
\hspace{1em}Five years & 0.645 & 0.038 & 0.000 & 0.582 & 0.708\\
\hspace{1em}Twenty years & 0.503 & 0.042 & 0.934 & 0.435 & 0.572\\
\hspace{1em}Fifty years & 0.489 & 0.043 & 0.795 & 0.417 & 0.560\\
\hspace{1em}Never & 0.424 & 0.043 & 0.078 & 0.353 & 0.495\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Colombia}
\NormalTok{col <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, countryOrigin}\OperatorTok{==}\StringTok{'Colombia'}\NormalTok{),  }
\NormalTok{        fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(col, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Colombia Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-4}Marginal Means -- Colombia Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.430 & 0.042 & 0.090 & 0.361 & 0.498\\
\hspace{1em}Local community members & 0.595 & 0.038 & 0.012 & 0.533 & 0.658\\
\hspace{1em}Local government & 0.465 & 0.038 & 0.359 & 0.403 & 0.528\\
\hspace{1em}Federal government & 0.463 & 0.037 & 0.327 & 0.402 & 0.525\\
\hspace{1em}International organizations & 0.544 & 0.041 & 0.285 & 0.476 & 0.611\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.410 & 0.038 & 0.018 & 0.347 & 0.472\\
\hspace{1em}Private arbitration & 0.510 & 0.040 & 0.808 & 0.443 & 0.576\\
\hspace{1em}Local courts & 0.533 & 0.039 & 0.394 & 0.469 & 0.596\\
\hspace{1em}Government bureaucracy & 0.466 & 0.039 & 0.385 & 0.401 & 0.531\\
\hspace{1em}United Nations & 0.584 & 0.039 & 0.031 & 0.520 & 0.648\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.497 & 0.038 & 0.939 & 0.434 & 0.560\\
\hspace{1em}Blacklist & 0.531 & 0.034 & 0.370 & 0.474 & 0.587\\
\hspace{1em}Fines & 0.551 & 0.033 & 0.123 & 0.497 & 0.606\\
\hspace{1em}Imprisonment & 0.414 & 0.035 & 0.013 & 0.357 & 0.471\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.479 & 0.034 & 0.537 & 0.423 & 0.535\\
\hspace{1em}Same & 0.492 & 0.029 & 0.772 & 0.444 & 0.539\\
\hspace{1em}More penalty & 0.523 & 0.029 & 0.417 & 0.476 & 0.571\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.475 & 0.034 & 0.459 & 0.420 & 0.530\\
\hspace{1em}Proportional to current emissions & 0.516 & 0.034 & 0.633 & 0.460 & 0.572\\
\hspace{1em}Proportional to history of emissions & 0.538 & 0.035 & 0.286 & 0.480 & 0.596\\
\hspace{1em}Rich countries pay more than poor countries & 0.468 & 0.038 & 0.402 & 0.406 & 0.531\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.547 & 0.038 & 0.221 & 0.484 & 0.609\\
\hspace{1em}Five years & 0.558 & 0.039 & 0.137 & 0.494 & 0.621\\
\hspace{1em}Twenty years & 0.547 & 0.039 & 0.232 & 0.482 & 0.612\\
\hspace{1em}Fifty years & 0.423 & 0.042 & 0.069 & 0.354 & 0.493\\
\hspace{1em}Never & 0.417 & 0.037 & 0.026 & 0.356 & 0.478\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Costa Rica}
\NormalTok{cri <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, countryOrigin}\OperatorTok{==}\StringTok{'Costa Rica'}\NormalTok{),  }
\NormalTok{        fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(cri, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Costa Rica Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-5}Marginal Means -- Costa Rica Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.524 & 0.044 & 0.593 & 0.451 & 0.597\\
\hspace{1em}Local community members & 0.439 & 0.042 & 0.146 & 0.370 & 0.508\\
\hspace{1em}Local government & 0.565 & 0.043 & 0.134 & 0.494 & 0.636\\
\hspace{1em}Federal government & 0.511 & 0.043 & 0.798 & 0.441 & 0.581\\
\hspace{1em}International organizations & 0.459 & 0.048 & 0.387 & 0.380 & 0.537\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.402 & 0.043 & 0.021 & 0.331 & 0.472\\
\hspace{1em}Private arbitration & 0.496 & 0.044 & 0.930 & 0.424 & 0.569\\
\hspace{1em}Local courts & 0.497 & 0.042 & 0.934 & 0.428 & 0.565\\
\hspace{1em}Government bureaucracy & 0.500 & 0.048 & 1.000 & 0.421 & 0.579\\
\hspace{1em}United Nations & 0.609 & 0.043 & 0.011 & 0.538 & 0.680\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.383 & 0.045 & 0.010 & 0.308 & 0.457\\
\hspace{1em}Blacklist & 0.477 & 0.038 & 0.541 & 0.414 & 0.539\\
\hspace{1em}Fines & 0.588 & 0.036 & 0.014 & 0.529 & 0.647\\
\hspace{1em}Imprisonment & 0.506 & 0.039 & 0.877 & 0.442 & 0.569\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.461 & 0.035 & 0.261 & 0.403 & 0.518\\
\hspace{1em}Same & 0.481 & 0.034 & 0.584 & 0.425 & 0.537\\
\hspace{1em}More penalty & 0.554 & 0.033 & 0.107 & 0.499 & 0.608\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.396 & 0.039 & 0.007 & 0.332 & 0.460\\
\hspace{1em}Proportional to current emissions & 0.582 & 0.040 & 0.041 & 0.516 & 0.647\\
\hspace{1em}Proportional to history of emissions & 0.515 & 0.039 & 0.695 & 0.451 & 0.580\\
\hspace{1em}Rich countries pay more than poor countries & 0.509 & 0.039 & 0.816 & 0.445 & 0.573\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.598 & 0.046 & 0.034 & 0.522 & 0.674\\
\hspace{1em}Five years & 0.674 & 0.040 & 0.000 & 0.608 & 0.740\\
\hspace{1em}Twenty years & 0.471 & 0.042 & 0.498 & 0.402 & 0.541\\
\hspace{1em}Fifty years & 0.381 & 0.042 & 0.004 & 0.312 & 0.450\\
\hspace{1em}Never & 0.380 & 0.044 & 0.007 & 0.308 & 0.453\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Ecuador}
\NormalTok{ecu <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, countryOrigin}\OperatorTok{==}\StringTok{'Ecuador'}\NormalTok{),  }
\NormalTok{        fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(ecu, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Ecuador Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-6}Marginal Means -- Ecuador Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.427 & 0.038 & 0.053 & 0.365 & 0.489\\
\hspace{1em}Local community members & 0.548 & 0.038 & 0.215 & 0.484 & 0.611\\
\hspace{1em}Local government & 0.518 & 0.039 & 0.643 & 0.454 & 0.581\\
\hspace{1em}Federal government & 0.475 & 0.039 & 0.529 & 0.411 & 0.540\\
\hspace{1em}International organizations & 0.531 & 0.038 & 0.405 & 0.469 & 0.593\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.420 & 0.039 & 0.039 & 0.356 & 0.484\\
\hspace{1em}Private arbitration & 0.500 & 0.036 & 1.000 & 0.440 & 0.560\\
\hspace{1em}Local courts & 0.556 & 0.037 & 0.131 & 0.495 & 0.617\\
\hspace{1em}Government bureaucracy & 0.424 & 0.039 & 0.053 & 0.359 & 0.489\\
\hspace{1em}United Nations & 0.596 & 0.039 & 0.014 & 0.532 & 0.661\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.490 & 0.040 & 0.810 & 0.424 & 0.556\\
\hspace{1em}Blacklist & 0.572 & 0.033 & 0.030 & 0.517 & 0.627\\
\hspace{1em}Fines & 0.544 & 0.033 & 0.184 & 0.490 & 0.598\\
\hspace{1em}Imprisonment & 0.397 & 0.032 & 0.001 & 0.345 & 0.450\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.468 & 0.032 & 0.329 & 0.415 & 0.522\\
\hspace{1em}Same & 0.480 & 0.029 & 0.490 & 0.433 & 0.527\\
\hspace{1em}More penalty & 0.544 & 0.029 & 0.121 & 0.497 & 0.591\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.412 & 0.033 & 0.007 & 0.359 & 0.466\\
\hspace{1em}Proportional to current emissions & 0.581 & 0.034 & 0.016 & 0.526 & 0.637\\
\hspace{1em}Proportional to history of emissions & 0.546 & 0.036 & 0.197 & 0.487 & 0.604\\
\hspace{1em}Rich countries pay more than poor countries & 0.468 & 0.035 & 0.363 & 0.411 & 0.526\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.465 & 0.040 & 0.379 & 0.399 & 0.530\\
\hspace{1em}Five years & 0.554 & 0.038 & 0.149 & 0.492 & 0.616\\
\hspace{1em}Twenty years & 0.531 & 0.038 & 0.405 & 0.469 & 0.593\\
\hspace{1em}Fifty years & 0.447 & 0.038 & 0.165 & 0.384 & 0.510\\
\hspace{1em}Never & 0.497 & 0.039 & 0.938 & 0.433 & 0.561\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Mexico}
\NormalTok{mex <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, countryOrigin}\OperatorTok{==}\StringTok{'Mexico'}\NormalTok{),  }
\NormalTok{        fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(mex, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Mexico Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-7}Marginal Means -- Mexico Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.457 & 0.042 & 0.309 & 0.388 & 0.526\\
\hspace{1em}Local community members & 0.470 & 0.043 & 0.489 & 0.399 & 0.541\\
\hspace{1em}Local government & 0.438 & 0.040 & 0.122 & 0.372 & 0.504\\
\hspace{1em}Federal government & 0.497 & 0.040 & 0.937 & 0.432 & 0.562\\
\hspace{1em}International organizations & 0.620 & 0.038 & 0.001 & 0.559 & 0.682\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.405 & 0.040 & 0.019 & 0.339 & 0.472\\
\hspace{1em}Private arbitration & 0.520 & 0.041 & 0.626 & 0.453 & 0.586\\
\hspace{1em}Local courts & 0.507 & 0.042 & 0.867 & 0.438 & 0.576\\
\hspace{1em}Government bureaucracy & 0.461 & 0.040 & 0.329 & 0.394 & 0.527\\
\hspace{1em}United Nations & 0.601 & 0.039 & 0.009 & 0.537 & 0.665\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.472 & 0.044 & 0.534 & 0.400 & 0.545\\
\hspace{1em}Blacklist & 0.478 & 0.035 & 0.531 & 0.421 & 0.535\\
\hspace{1em}Fines & 0.571 & 0.035 & 0.040 & 0.514 & 0.629\\
\hspace{1em}Imprisonment & 0.470 & 0.034 & 0.374 & 0.414 & 0.526\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.505 & 0.035 & 0.888 & 0.447 & 0.563\\
\hspace{1em}Same & 0.503 & 0.029 & 0.908 & 0.456 & 0.551\\
\hspace{1em}More penalty & 0.492 & 0.031 & 0.802 & 0.441 & 0.544\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.429 & 0.036 & 0.047 & 0.369 & 0.488\\
\hspace{1em}Proportional to current emissions & 0.500 & 0.035 & 1.000 & 0.442 & 0.558\\
\hspace{1em}Proportional to history of emissions & 0.620 & 0.038 & 0.001 & 0.559 & 0.682\\
\hspace{1em}Rich countries pay more than poor countries & 0.466 & 0.036 & 0.348 & 0.407 & 0.525\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.507 & 0.041 & 0.871 & 0.440 & 0.573\\
\hspace{1em}Five years & 0.616 & 0.038 & 0.002 & 0.553 & 0.678\\
\hspace{1em}Twenty years & 0.487 & 0.041 & 0.746 & 0.420 & 0.554\\
\hspace{1em}Fifty years & 0.493 & 0.043 & 0.864 & 0.422 & 0.563\\
\hspace{1em}Never & 0.385 & 0.040 & 0.004 & 0.319 & 0.451\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Panama}
\NormalTok{pan <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, countryOrigin}\OperatorTok{==}\StringTok{'Panama'}\NormalTok{),  }
\NormalTok{        fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(pan, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Panama Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-8}Marginal Means -- Panama Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.478 & 0.040 & 0.578 & 0.413 & 0.543\\
\hspace{1em}Local community members & 0.526 & 0.040 & 0.521 & 0.460 & 0.591\\
\hspace{1em}Local government & 0.477 & 0.041 & 0.566 & 0.409 & 0.544\\
\hspace{1em}Federal government & 0.497 & 0.040 & 0.936 & 0.431 & 0.563\\
\hspace{1em}International organizations & 0.522 & 0.040 & 0.576 & 0.457 & 0.588\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.439 & 0.040 & 0.127 & 0.374 & 0.505\\
\hspace{1em}Private arbitration & 0.488 & 0.039 & 0.756 & 0.424 & 0.552\\
\hspace{1em}Local courts & 0.549 & 0.041 & 0.241 & 0.480 & 0.617\\
\hspace{1em}Government bureaucracy & 0.477 & 0.040 & 0.571 & 0.411 & 0.544\\
\hspace{1em}United Nations & 0.551 & 0.040 & 0.198 & 0.486 & 0.617\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.455 & 0.042 & 0.275 & 0.386 & 0.523\\
\hspace{1em}Blacklist & 0.522 & 0.035 & 0.531 & 0.465 & 0.579\\
\hspace{1em}Fines & 0.531 & 0.033 & 0.349 & 0.476 & 0.586\\
\hspace{1em}Imprisonment & 0.475 & 0.035 & 0.481 & 0.417 & 0.533\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.432 & 0.033 & 0.042 & 0.378 & 0.487\\
\hspace{1em}Same & 0.466 & 0.030 & 0.253 & 0.416 & 0.515\\
\hspace{1em}More penalty & 0.588 & 0.030 & 0.003 & 0.540 & 0.637\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.473 & 0.035 & 0.442 & 0.416 & 0.531\\
\hspace{1em}Proportional to current emissions & 0.497 & 0.036 & 0.942 & 0.438 & 0.557\\
\hspace{1em}Proportional to history of emissions & 0.513 & 0.037 & 0.715 & 0.453 & 0.573\\
\hspace{1em}Rich countries pay more than poor countries & 0.518 & 0.036 & 0.614 & 0.459 & 0.577\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.605 & 0.040 & 0.008 & 0.540 & 0.670\\
\hspace{1em}Five years & 0.552 & 0.038 & 0.170 & 0.490 & 0.614\\
\hspace{1em}Twenty years & 0.573 & 0.040 & 0.069 & 0.507 & 0.640\\
\hspace{1em}Fifty years & 0.418 & 0.041 & 0.044 & 0.351 & 0.485\\
\hspace{1em}Never & 0.344 & 0.038 & 0.000 & 0.281 & 0.407\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Peru}
\NormalTok{per <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, countryOrigin}\OperatorTok{==}\StringTok{'Peru'}\NormalTok{),  }
\NormalTok{        fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(per, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Peru Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-9}Marginal Means -- Peru Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.442 & 0.049 & 0.236 & 0.362 & 0.522\\
\hspace{1em}Local community members & 0.410 & 0.048 & 0.059 & 0.331 & 0.488\\
\hspace{1em}Local government & 0.568 & 0.047 & 0.151 & 0.490 & 0.645\\
\hspace{1em}Federal government & 0.537 & 0.048 & 0.440 & 0.458 & 0.616\\
\hspace{1em}International organizations & 0.533 & 0.046 & 0.464 & 0.458 & 0.608\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.351 & 0.048 & 0.002 & 0.271 & 0.430\\
\hspace{1em}Private arbitration & 0.607 & 0.045 & 0.018 & 0.533 & 0.681\\
\hspace{1em}Local courts & 0.505 & 0.051 & 0.919 & 0.422 & 0.589\\
\hspace{1em}Government bureaucracy & 0.488 & 0.045 & 0.788 & 0.414 & 0.562\\
\hspace{1em}United Nations & 0.527 & 0.047 & 0.570 & 0.449 & 0.604\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.441 & 0.047 & 0.214 & 0.364 & 0.519\\
\hspace{1em}Blacklist & 0.500 & 0.043 & 1.000 & 0.430 & 0.570\\
\hspace{1em}Fines & 0.564 & 0.042 & 0.125 & 0.495 & 0.633\\
\hspace{1em}Imprisonment & 0.484 & 0.040 & 0.692 & 0.419 & 0.549\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.472 & 0.042 & 0.501 & 0.403 & 0.541\\
\hspace{1em}Same & 0.536 & 0.035 & 0.298 & 0.479 & 0.593\\
\hspace{1em}More penalty & 0.482 & 0.036 & 0.618 & 0.424 & 0.541\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.468 & 0.040 & 0.419 & 0.401 & 0.534\\
\hspace{1em}Proportional to current emissions & 0.497 & 0.040 & 0.936 & 0.430 & 0.563\\
\hspace{1em}Proportional to history of emissions & 0.571 & 0.047 & 0.127 & 0.495 & 0.648\\
\hspace{1em}Rich countries pay more than poor countries & 0.481 & 0.044 & 0.660 & 0.408 & 0.553\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.548 & 0.045 & 0.279 & 0.475 & 0.622\\
\hspace{1em}Five years & 0.583 & 0.047 & 0.079 & 0.505 & 0.661\\
\hspace{1em}Twenty years & 0.517 & 0.054 & 0.748 & 0.429 & 0.605\\
\hspace{1em}Fifty years & 0.420 & 0.047 & 0.085 & 0.343 & 0.496\\
\hspace{1em}Never & 0.436 & 0.046 & 0.162 & 0.360 & 0.511\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Changing country labels}
\NormalTok{arg}\OperatorTok{$}\NormalTok{country <-}\StringTok{ 'Argentina'}
\NormalTok{bol}\OperatorTok{$}\NormalTok{country <-}\StringTok{ 'Bolivia'}
\NormalTok{bra}\OperatorTok{$}\NormalTok{country <-}\StringTok{ 'Brazil'}
\NormalTok{chi}\OperatorTok{$}\NormalTok{country <-}\StringTok{ 'Chile'}
\NormalTok{col}\OperatorTok{$}\NormalTok{country <-}\StringTok{ 'Colombia'}
\NormalTok{cri}\OperatorTok{$}\NormalTok{country <-}\StringTok{ 'Costa Rica'}
\NormalTok{ecu}\OperatorTok{$}\NormalTok{country <-}\StringTok{ 'Ecuador'}
\NormalTok{mex}\OperatorTok{$}\NormalTok{country <-}\StringTok{ 'Mexico'}
\NormalTok{pan}\OperatorTok{$}\NormalTok{country <-}\StringTok{ 'Panama'}
\NormalTok{per}\OperatorTok{$}\NormalTok{country <-}\StringTok{ 'Peru'}
\CommentTok{# Plot by country}
\NormalTok{p <-}\StringTok{ }\KeywordTok{plot}\NormalTok{(}\KeywordTok{rbind}\NormalTok{(arg, bol, bra, chi, col, }
\NormalTok{              cri, ecu, mex, pan, per), }
        \DataTypeTok{group =} \StringTok{'country'}\NormalTok{, }\DataTypeTok{vline =} \FloatTok{0.5}\NormalTok{, }\DataTypeTok{nr =} \DecValTok{10}\NormalTok{,}
        \DataTypeTok{header_fmt =} \StringTok{"%s"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{2}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{facet_wrap}\NormalTok{( }\OperatorTok{~}\StringTok{ }\NormalTok{country, }\DataTypeTok{ncol =} \DecValTok{5}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\NormalTok{ggplot2}\OperatorTok{::}\KeywordTok{theme}\NormalTok{(}
    \DataTypeTok{axis.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{face=}\NormalTok{myFaces, }\DataTypeTok{size =} \DecValTok{11}\NormalTok{)) }\OperatorTok{+}\StringTok{ }
\StringTok{    }\NormalTok{ggplot2}\OperatorTok{::}\KeywordTok{geom_errorbarh}\NormalTok{(ggplot2}\OperatorTok{::}\KeywordTok{aes_string}\NormalTok{(}\DataTypeTok{xmin =} \StringTok{"lower"}\NormalTok{,}
                                                \DataTypeTok{xmax =} \StringTok{"upper"}\NormalTok{),}
                            \DataTypeTok{size =} \DecValTok{1}\NormalTok{, }\DataTypeTok{height =} \DecValTok{0}\NormalTok{, }\DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{,}
                            \DataTypeTok{position =}\NormalTok{ ggstance}\OperatorTok{::}\KeywordTok{position_dodgev}\NormalTok{(}\DataTypeTok{height =} \DecValTok{1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: Vectorized input to `element_text()` is not officially supported.
## Results may be unexpected or may change in future versions of ggplot2.
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{p}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-10-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggsave}\NormalTok{(}\DataTypeTok{filename =} \StringTok{'MM_country.pdf'}\NormalTok{, }
       \DataTypeTok{plot =}\NormalTok{ p, }\DataTypeTok{width =} \DecValTok{12}\NormalTok{, }\DataTypeTok{height =} \DecValTok{12}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

The code for Figure 4 of the paper is available below. Tables displaying
the point estimates are also included.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Elite type graphs and estimates}

\CommentTok{# Table for the Executive branch}
\NormalTok{res1 <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, groupOrigin}\OperatorTok{==}\StringTok{'Executive'}\NormalTok{), }
\NormalTok{           fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(res1, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Executive Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-11}Marginal Means -- Executive Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.392 & 0.034 & 0.001 & 0.336 & 0.447\\
\hspace{1em}Local community members & 0.516 & 0.031 & 0.618 & 0.464 & 0.567\\
\hspace{1em}Local government & 0.502 & 0.030 & 0.952 & 0.452 & 0.552\\
\hspace{1em}Federal government & 0.529 & 0.032 & 0.365 & 0.476 & 0.582\\
\hspace{1em}International organizations & 0.545 & 0.031 & 0.150 & 0.494 & 0.596\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.429 & 0.034 & 0.037 & 0.373 & 0.485\\
\hspace{1em}Private arbitration & 0.508 & 0.032 & 0.797 & 0.455 & 0.561\\
\hspace{1em}Local courts & 0.523 & 0.031 & 0.456 & 0.472 & 0.574\\
\hspace{1em}Government bureaucracy & 0.462 & 0.031 & 0.214 & 0.411 & 0.512\\
\hspace{1em}United Nations & 0.564 & 0.030 & 0.036 & 0.514 & 0.614\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.480 & 0.034 & 0.545 & 0.424 & 0.535\\
\hspace{1em}Blacklist & 0.541 & 0.028 & 0.144 & 0.495 & 0.587\\
\hspace{1em}Fines & 0.568 & 0.026 & 0.010 & 0.524 & 0.611\\
\hspace{1em}Imprisonment & 0.406 & 0.026 & 0.000 & 0.363 & 0.450\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.447 & 0.026 & 0.039 & 0.405 & 0.489\\
\hspace{1em}Same & 0.501 & 0.023 & 0.963 & 0.463 & 0.539\\
\hspace{1em}More penalty & 0.549 & 0.025 & 0.050 & 0.508 & 0.590\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.442 & 0.029 & 0.043 & 0.395 & 0.489\\
\hspace{1em}Proportional to current emissions & 0.550 & 0.028 & 0.072 & 0.504 & 0.596\\
\hspace{1em}Proportional to history of emissions & 0.524 & 0.028 & 0.396 & 0.478 & 0.570\\
\hspace{1em}Rich countries pay more than poor countries & 0.480 & 0.029 & 0.491 & 0.433 & 0.527\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.543 & 0.030 & 0.159 & 0.493 & 0.593\\
\hspace{1em}Five years & 0.586 & 0.030 & 0.005 & 0.536 & 0.636\\
\hspace{1em}Twenty years & 0.500 & 0.032 & 1.000 & 0.448 & 0.552\\
\hspace{1em}Fifty years & 0.438 & 0.032 & 0.052 & 0.386 & 0.490\\
\hspace{1em}Never & 0.414 & 0.033 & 0.009 & 0.359 & 0.468\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Legislative branch}
\NormalTok{res2 <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, groupOrigin}\OperatorTok{==}\StringTok{'Legislative'}\NormalTok{), }
\NormalTok{           fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(res2, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Legislative Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-12}Marginal Means -- Legislative Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.400 & 0.038 & 0.008 & 0.338 & 0.462\\
\hspace{1em}Local community members & 0.519 & 0.039 & 0.637 & 0.454 & 0.583\\
\hspace{1em}Local government & 0.549 & 0.039 & 0.209 & 0.485 & 0.613\\
\hspace{1em}Federal government & 0.517 & 0.041 & 0.680 & 0.449 & 0.585\\
\hspace{1em}International organizations & 0.524 & 0.042 & 0.558 & 0.456 & 0.593\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.420 & 0.037 & 0.032 & 0.358 & 0.481\\
\hspace{1em}Private arbitration & 0.506 & 0.039 & 0.876 & 0.442 & 0.570\\
\hspace{1em}Local courts & 0.547 & 0.039 & 0.235 & 0.482 & 0.611\\
\hspace{1em}Government bureaucracy & 0.500 & 0.041 & 1.000 & 0.432 & 0.568\\
\hspace{1em}United Nations & 0.539 & 0.042 & 0.353 & 0.470 & 0.608\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.438 & 0.042 & 0.143 & 0.368 & 0.508\\
\hspace{1em}Blacklist & 0.546 & 0.034 & 0.172 & 0.491 & 0.602\\
\hspace{1em}Fines & 0.581 & 0.033 & 0.013 & 0.528 & 0.635\\
\hspace{1em}Imprisonment & 0.403 & 0.034 & 0.005 & 0.347 & 0.459\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.455 & 0.033 & 0.178 & 0.400 & 0.510\\
\hspace{1em}Same & 0.521 & 0.029 & 0.481 & 0.472 & 0.569\\
\hspace{1em}More penalty & 0.515 & 0.030 & 0.629 & 0.465 & 0.564\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.411 & 0.033 & 0.007 & 0.357 & 0.465\\
\hspace{1em}Proportional to current emissions & 0.475 & 0.035 & 0.481 & 0.417 & 0.533\\
\hspace{1em}Proportional to history of emissions & 0.552 & 0.039 & 0.181 & 0.488 & 0.616\\
\hspace{1em}Rich countries pay more than poor countries & 0.584 & 0.035 & 0.017 & 0.526 & 0.642\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.533 & 0.040 & 0.416 & 0.466 & 0.599\\
\hspace{1em}Five years & 0.557 & 0.038 & 0.139 & 0.494 & 0.620\\
\hspace{1em}Twenty years & 0.526 & 0.040 & 0.519 & 0.460 & 0.592\\
\hspace{1em}Fifty years & 0.485 & 0.039 & 0.695 & 0.420 & 0.549\\
\hspace{1em}Never & 0.393 & 0.040 & 0.007 & 0.328 & 0.459\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Civil society}
\NormalTok{res3 <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, groupOrigin}\OperatorTok{==}\StringTok{'Civil Society'}\NormalTok{), }
\NormalTok{           fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(res3, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Civil Society Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-13}Marginal Means -- Civil Society Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.500 & 0.023 & 1.000 & 0.463 & 0.537\\
\hspace{1em}Local community members & 0.520 & 0.022 & 0.368 & 0.483 & 0.557\\
\hspace{1em}Local government & 0.462 & 0.023 & 0.093 & 0.425 & 0.499\\
\hspace{1em}Federal government & 0.478 & 0.022 & 0.309 & 0.441 & 0.514\\
\hspace{1em}International organizations & 0.538 & 0.022 & 0.080 & 0.502 & 0.574\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.410 & 0.022 & 0.000 & 0.373 & 0.446\\
\hspace{1em}Private arbitration & 0.503 & 0.023 & 0.892 & 0.466 & 0.540\\
\hspace{1em}Local courts & 0.551 & 0.022 & 0.021 & 0.515 & 0.587\\
\hspace{1em}Government bureaucracy & 0.430 & 0.022 & 0.002 & 0.393 & 0.467\\
\hspace{1em}United Nations & 0.594 & 0.021 & 0.000 & 0.559 & 0.629\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.453 & 0.023 & 0.036 & 0.416 & 0.490\\
\hspace{1em}Blacklist & 0.518 & 0.020 & 0.364 & 0.485 & 0.550\\
\hspace{1em}Fines & 0.548 & 0.019 & 0.011 & 0.517 & 0.579\\
\hspace{1em}Imprisonment & 0.467 & 0.019 & 0.089 & 0.436 & 0.499\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.469 & 0.019 & 0.112 & 0.437 & 0.501\\
\hspace{1em}Same & 0.479 & 0.016 & 0.203 & 0.452 & 0.506\\
\hspace{1em}More penalty & 0.545 & 0.017 & 0.007 & 0.517 & 0.572\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.449 & 0.019 & 0.008 & 0.417 & 0.481\\
\hspace{1em}Proportional to current emissions & 0.520 & 0.020 & 0.315 & 0.487 & 0.553\\
\hspace{1em}Proportional to history of emissions & 0.560 & 0.020 & 0.003 & 0.527 & 0.593\\
\hspace{1em}Rich countries pay more than poor countries & 0.476 & 0.020 & 0.230 & 0.443 & 0.509\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.548 & 0.022 & 0.026 & 0.513 & 0.584\\
\hspace{1em}Five years & 0.595 & 0.022 & 0.000 & 0.559 & 0.630\\
\hspace{1em}Twenty years & 0.493 & 0.022 & 0.757 & 0.457 & 0.530\\
\hspace{1em}Fifty years & 0.448 & 0.023 & 0.026 & 0.409 & 0.486\\
\hspace{1em}Never & 0.404 & 0.022 & 0.000 & 0.368 & 0.441\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Academia}
\NormalTok{res4 <-}\StringTok{ }\KeywordTok{mm}\NormalTok{(}\KeywordTok{subset}\NormalTok{(cj, groupOrigin}\OperatorTok{==}\StringTok{'Academia'}\NormalTok{), }
\NormalTok{           fm, }\DataTypeTok{id =} \OperatorTok{~}\NormalTok{Response.ID, }\DataTypeTok{alpha =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{h0 =} \FloatTok{0.5}\NormalTok{)}
\KeywordTok{table_mm}\NormalTok{(res4, }\DataTypeTok{capt =} \StringTok{'Marginal Means -- Academia Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-14}Marginal Means -- Academia Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
Feature & Estimate & Std.Error & P-Value & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}NGOs & 0.447 & 0.022 & 0.014 & 0.411 & 0.483\\
\hspace{1em}Local community members & 0.515 & 0.022 & 0.483 & 0.479 & 0.551\\
\hspace{1em}Local government & 0.524 & 0.022 & 0.260 & 0.489 & 0.560\\
\hspace{1em}Federal government & 0.458 & 0.021 & 0.048 & 0.423 & 0.493\\
\hspace{1em}International organizations & 0.556 & 0.021 & 0.009 & 0.521 & 0.591\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}Informal norms & 0.388 & 0.021 & 0.000 & 0.353 & 0.423\\
\hspace{1em}Private arbitration & 0.517 & 0.022 & 0.437 & 0.481 & 0.552\\
\hspace{1em}Local courts & 0.549 & 0.022 & 0.023 & 0.513 & 0.584\\
\hspace{1em}Government bureaucracy & 0.476 & 0.022 & 0.275 & 0.440 & 0.512\\
\hspace{1em}United Nations & 0.565 & 0.021 & 0.002 & 0.530 & 0.599\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}None & 0.430 & 0.022 & 0.002 & 0.393 & 0.467\\
\hspace{1em}Blacklist & 0.510 & 0.018 & 0.582 & 0.480 & 0.540\\
\hspace{1em}Fines & 0.554 & 0.019 & 0.004 & 0.523 & 0.585\\
\hspace{1em}Imprisonment & 0.483 & 0.019 & 0.371 & 0.453 & 0.514\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}Less penalty & 0.461 & 0.018 & 0.030 & 0.431 & 0.490\\
\hspace{1em}Same & 0.499 & 0.016 & 0.974 & 0.473 & 0.526\\
\hspace{1em}More penalty & 0.532 & 0.016 & 0.048 & 0.505 & 0.559\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}Only rich countries pay & 0.434 & 0.019 & 0.001 & 0.403 & 0.466\\
\hspace{1em}Proportional to current emissions & 0.540 & 0.019 & 0.036 & 0.509 & 0.571\\
\hspace{1em}Proportional to history of emissions & 0.519 & 0.020 & 0.327 & 0.487 & 0.551\\
\hspace{1em}Rich countries pay more than poor countries & 0.507 & 0.020 & 0.723 & 0.475 & 0.539\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}One year & 0.509 & 0.022 & 0.664 & 0.474 & 0.545\\
\hspace{1em}Five years & 0.595 & 0.021 & 0.000 & 0.560 & 0.629\\
\hspace{1em}Twenty years & 0.549 & 0.022 & 0.023 & 0.514 & 0.585\\
\hspace{1em}Fifty years & 0.422 & 0.021 & 0.000 & 0.386 & 0.457\\
\hspace{1em}Never & 0.421 & 0.022 & 0.000 & 0.386 & 0.456\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Changing labels}
\NormalTok{res1}\OperatorTok{$}\NormalTok{MemberType <-}\StringTok{ 'Executive'}
\NormalTok{res2}\OperatorTok{$}\NormalTok{MemberType <-}\StringTok{ 'Legislative'}
\NormalTok{res3}\OperatorTok{$}\NormalTok{MemberType <-}\StringTok{ 'Civil Society'}
\NormalTok{res4}\OperatorTok{$}\NormalTok{MemberType <-}\StringTok{ 'Academia'}

\CommentTok{# Plot by Elite Type}
\NormalTok{p <-}\StringTok{ }\KeywordTok{plot}\NormalTok{(}\KeywordTok{rbind}\NormalTok{(res1, res2, res3, res4), }
     \DataTypeTok{group =} \StringTok{'MemberType'}\NormalTok{, }\DataTypeTok{vline =} \FloatTok{0.5}\NormalTok{, }\DataTypeTok{nr =} \DecValTok{4}\NormalTok{,}
        \DataTypeTok{header_fmt =} \StringTok{"%s"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }
\StringTok{  }\KeywordTok{facet_wrap}\NormalTok{( }\OperatorTok{~}\StringTok{ }\NormalTok{MemberType, }\DataTypeTok{ncol =} \DecValTok{4}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\NormalTok{ggplot2}\OperatorTok{::}\KeywordTok{theme}\NormalTok{(}
    \DataTypeTok{axis.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{face=}\NormalTok{myFaces, }\DataTypeTok{size =} \DecValTok{11}\NormalTok{)) }\OperatorTok{+}\StringTok{ }
\StringTok{    }\NormalTok{ggplot2}\OperatorTok{::}\KeywordTok{geom_errorbarh}\NormalTok{(ggplot2}\OperatorTok{::}\KeywordTok{aes_string}\NormalTok{(}\DataTypeTok{xmin =} \StringTok{"lower"}\NormalTok{,}
                                                \DataTypeTok{xmax =} \StringTok{"upper"}\NormalTok{),}
                            \DataTypeTok{size =} \DecValTok{1}\NormalTok{, }\DataTypeTok{height =} \DecValTok{0}\NormalTok{, }\DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{,}
                            \DataTypeTok{position =}\NormalTok{ ggstance}\OperatorTok{::}\KeywordTok{position_dodgev}\NormalTok{(}\DataTypeTok{height =} \DecValTok{1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: Vectorized input to `element_text()` is not officially supported.
## Results may be unexpected or may change in future versions of ggplot2.
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{p}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-15-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggsave}\NormalTok{(}\DataTypeTok{filename =} \StringTok{'MM_membertype.pdf'}\NormalTok{, }\DataTypeTok{plot =}\NormalTok{ p, }
       \DataTypeTok{width =} \DecValTok{8}\NormalTok{, }\DataTypeTok{height =} \DecValTok{6}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{average-marginal-component-effect-amce-estimator}{%
\section{\texorpdfstring{Average Marginal Component Effect (AMCE)
Estimator
\label{sec:amce}}{Average Marginal Component Effect (AMCE) Estimator }}\label{average-marginal-component-effect-amce-estimator}}

This estimator fixes one category and look at changes from this baseline
category. Below follows the plots for the main model and the country and
elite type subsamples.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Main model}
\KeywordTok{rm}\NormalTok{(cj)}
\KeywordTok{load}\NormalTok{(}\StringTok{'freire-mignozzetti-skarbek.RData'}\NormalTok{)}

\CommentTok{# Set conjoint baselines}
\NormalTok{baselines <-}\StringTok{ }\KeywordTok{list}\NormalTok{()}
\NormalTok{baselines}\OperatorTok{$}\StringTok{`}\DataTypeTok{How often will the agreement be renegotiated?}\StringTok{`}\NormalTok{ <-}\StringTok{ "One year"}
\NormalTok{baselines}\OperatorTok{$}\StringTok{`}\DataTypeTok{What punishments do they use?}\StringTok{`}\NormalTok{ <-}\StringTok{ 'None'}
\NormalTok{baselines}\OperatorTok{$}\StringTok{`}\DataTypeTok{How are conflicts resolved?}\StringTok{`}\NormalTok{ <-}\StringTok{ 'Government bureaucracy'}
\NormalTok{baselines}\OperatorTok{$}\StringTok{`}\DataTypeTok{How are costs distributed?}\StringTok{`}\NormalTok{ <-}\StringTok{ 'Rich countries pay more than poor countries'}
\NormalTok{baselines}\OperatorTok{$}\StringTok{`}\DataTypeTok{Who makes the rules?}\StringTok{`}\NormalTok{ <-}\StringTok{ 'Federal government'}

\NormalTok{attrs <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"Who makes the rules?"}\NormalTok{,}
           \StringTok{"How are conflicts resolved?"}\NormalTok{,}
           \StringTok{"What punishments do they use?"}\NormalTok{,}
           \StringTok{"How are repeated violations punished?"}\NormalTok{,}
           \StringTok{"How are costs distributed?"}\NormalTok{,}
           \StringTok{"How often will the agreement be renegotiated?"}\NormalTok{)}

\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{, }
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }
                        \DataTypeTok{baselines =}\NormalTok{ baselines, }\DataTypeTok{na.ignore =}\NormalTok{ T)}

\CommentTok{# Table AMCE -- Full Model }
\NormalTok{tableAMCE <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'Main Model'}\NormalTok{) \{}
\NormalTok{  aux <-}\StringTok{ }\KeywordTok{plotAMCE}\NormalTok{(results, }\DataTypeTok{ci =} \FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Full Model'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs, }\DataTypeTok{tblfy =}\NormalTok{ T)}
\NormalTok{  aux <-}\StringTok{ }\NormalTok{aux }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{is.na}\NormalTok{(group)) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(printvar, pe, se, lower, upper)}
\NormalTok{  indx <-}\StringTok{ }\KeywordTok{grep}\NormalTok{(}\StringTok{'Baseline ='}\NormalTok{, aux}\OperatorTok{$}\NormalTok{printvar)}
\NormalTok{  aux}\OperatorTok{$}\NormalTok{pe <-}\StringTok{ }\KeywordTok{round}\NormalTok{(aux}\OperatorTok{$}\NormalTok{pe, }\DataTypeTok{digits =} \DecValTok{3}\NormalTok{)}
\NormalTok{  aux}\OperatorTok{$}\NormalTok{se <-}\StringTok{ }\KeywordTok{round}\NormalTok{(aux}\OperatorTok{$}\NormalTok{se, }\DataTypeTok{digits =} \DecValTok{3}\NormalTok{)}
\NormalTok{  aux}\OperatorTok{$}\NormalTok{lower <-}\StringTok{ }\KeywordTok{round}\NormalTok{(aux}\OperatorTok{$}\NormalTok{lower, }\DataTypeTok{digits =} \DecValTok{3}\NormalTok{)}
\NormalTok{  aux}\OperatorTok{$}\NormalTok{upper <-}\StringTok{ }\KeywordTok{round}\NormalTok{(aux}\OperatorTok{$}\NormalTok{upper, }\DataTypeTok{digits =} \DecValTok{3}\NormalTok{)}
\NormalTok{  aux}\OperatorTok{$}\NormalTok{pe[indx] =}\StringTok{ ''}
\NormalTok{  aux}\OperatorTok{$}\NormalTok{se[indx] =}\StringTok{ ''}
\NormalTok{  aux}\OperatorTok{$}\NormalTok{lower[indx] =}\StringTok{ ''}
\NormalTok{  aux}\OperatorTok{$}\NormalTok{upper[indx] =}\StringTok{ ''}
  \KeywordTok{names}\NormalTok{(aux) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{'Feature'}\NormalTok{, }\StringTok{'Estimate'}\NormalTok{, }\StringTok{'Std.Error'}\NormalTok{, }
                  \StringTok{'Lower'}\NormalTok{, }\StringTok{'Upper'}\NormalTok{)}
  \KeywordTok{return}\NormalTok{(}\KeywordTok{kable}\NormalTok{(aux, }\StringTok{"latex"}\NormalTok{, }\DataTypeTok{caption =}\NormalTok{ capt, }\DataTypeTok{booktabs =}\NormalTok{ T, }\DataTypeTok{align =} \KeywordTok{c}\NormalTok{(}\StringTok{'l'}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\StringTok{'c'}\NormalTok{, }\DecValTok{4}\NormalTok{))) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{font_size =} \DecValTok{10}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{group_rows}\NormalTok{(}\StringTok{'How are conflicts resolved?'}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{5}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{group_rows}\NormalTok{(}\StringTok{'How are costs distributed?'}\NormalTok{, }\DecValTok{6}\NormalTok{, }\DecValTok{9}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{group_rows}\NormalTok{(}\StringTok{'How are repeated violations punished?'}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{12}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{group_rows}\NormalTok{(}\StringTok{'How often will the agreement be renegotiated?'}\NormalTok{, }\DecValTok{13}\NormalTok{, }\DecValTok{17}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{group_rows}\NormalTok{(}\StringTok{'What punishments do they use?'}\NormalTok{, }\DecValTok{18}\NormalTok{, }\DecValTok{21}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{group_rows}\NormalTok{(}\StringTok{'Who makes the rules?'}\NormalTok{, }\DecValTok{22}\NormalTok{, }\DecValTok{26}\NormalTok{))}
\NormalTok{\}}

\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Full Model'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-16}AMCE -- Full Model}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.054 & 0.018 & -0.083 & -0.025\\
\hspace{1em}Private arbitration & 0.043 & 0.018 & 0.014 & 0.072\\
\hspace{1em}Local courts & 0.088 & 0.017 & 0.059 & 0.116\\
\hspace{1em}United Nations & 0.111 & 0.019 & 0.081 & 0.142\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.071 & 0.016 & -0.098 & -0.044\\
\hspace{1em}Proportional to current emissions & 0.018 & 0.016 & -0.008 & 0.044\\
\hspace{1em}Proportional to history of emissions & 0.029 & 0.017 & 0.002 & 0.056\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.058 & 0.015 & 0.034 & 0.082\\
\hspace{1em}More penalty & 0.096 & 0.015 & 0.072 & 0.121\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.052 & 0.018 & 0.023 & 0.082\\
\hspace{1em}Twenty years & -0.012 & 0.018 & -0.041 & 0.017\\
\hspace{1em}Fifty years & -0.093 & 0.018 & -0.124 & -0.063\\
\hspace{1em}Never & -0.132 & 0.018 & -0.162 & -0.102\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.102 & 0.017 & 0.074 & 0.13\\
\hspace{1em}Fines & 0.132 & 0.016 & 0.105 & 0.158\\
\hspace{1em}Imprisonment & 0.035 & 0.018 & 0.006 & 0.065\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & -0.031 & 0.019 & -0.062 & 0\\
\hspace{1em}Local community members & 0.024 & 0.019 & -0.008 & 0.055\\
\hspace{1em}Local government & 0.011 & 0.018 & -0.019 & 0.041\\
\hspace{1em}International organisations & 0.058 & 0.018 & 0.029 & 0.088\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Plot AMCE -- Full Model}
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci =} \FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Full Model'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-17-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Country subsample}

\CommentTok{## Argentina}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{countryOrigin }\OperatorTok{==}\StringTok{ 'Argentina'}\NormalTok{)}
\CommentTok{# AMCE -- Argentina Only}
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Argentina Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-18}AMCE -- Argentina Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.09 & 0.061 & -0.191 & 0.01\\
\hspace{1em}Private arbitration & 0.055 & 0.068 & -0.056 & 0.167\\
\hspace{1em}Local courts & 0.103 & 0.062 & 0.001 & 0.204\\
\hspace{1em}United Nations & 0.125 & 0.067 & 0.016 & 0.235\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.078 & 0.054 & -0.166 & 0.01\\
\hspace{1em}Proportional to current emissions & 0.031 & 0.056 & -0.062 & 0.124\\
\hspace{1em}Proportional to history of emissions & 0.09 & 0.048 & 0.011 & 0.169\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.095 & 0.046 & 0.018 & 0.171\\
\hspace{1em}More penalty & 0.122 & 0.055 & 0.031 & 0.213\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & -0.061 & 0.06 & -0.159 & 0.037\\
\hspace{1em}Twenty years & -0.132 & 0.068 & -0.243 & -0.021\\
\hspace{1em}Fifty years & -0.166 & 0.068 & -0.278 & -0.054\\
\hspace{1em}Never & -0.171 & 0.061 & -0.271 & -0.071\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.185 & 0.056 & 0.093 & 0.278\\
\hspace{1em}Fines & 0.262 & 0.053 & 0.174 & 0.35\\
\hspace{1em}Imprisonment & 0.154 & 0.062 & 0.052 & 0.256\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & -0.118 & 0.069 & -0.23 & -0.005\\
\hspace{1em}Local community members & -0.074 & 0.068 & -0.185 & 0.038\\
\hspace{1em}Local government & 0.003 & 0.067 & -0.108 & 0.114\\
\hspace{1em}International organisations & 0.08 & 0.06 & -0.018 & 0.178\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Argentina Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-19-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Bolivia}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{countryOrigin }\OperatorTok{==}\StringTok{ 'Bolivia'}\NormalTok{)}
\CommentTok{# Table AMCE -- Full Model }
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Bolivia Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-20}AMCE -- Bolivia Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.056 & 0.067 & -0.167 & 0.054\\
\hspace{1em}Private arbitration & 0.127 & 0.074 & 0.005 & 0.249\\
\hspace{1em}Local courts & 0.093 & 0.057 & -0.001 & 0.186\\
\hspace{1em}United Nations & 0.17 & 0.08 & 0.038 & 0.302\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.142 & 0.068 & -0.254 & -0.029\\
\hspace{1em}Proportional to current emissions & 0.012 & 0.066 & -0.097 & 0.12\\
\hspace{1em}Proportional to history of emissions & -0.149 & 0.058 & -0.245 & -0.054\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.126 & 0.052 & 0.039 & 0.212\\
\hspace{1em}More penalty & 0.117 & 0.061 & 0.016 & 0.218\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.125 & 0.072 & 0.006 & 0.244\\
\hspace{1em}Twenty years & 0.075 & 0.077 & -0.052 & 0.202\\
\hspace{1em}Fifty years & -0.116 & 0.065 & -0.223 & -0.008\\
\hspace{1em}Never & -0.114 & 0.078 & -0.243 & 0.015\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.037 & 0.075 & -0.086 & 0.16\\
\hspace{1em}Fines & 0.155 & 0.056 & 0.063 & 0.247\\
\hspace{1em}Imprisonment & 0.069 & 0.074 & -0.052 & 0.19\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & -0.033 & 0.071 & -0.15 & 0.084\\
\hspace{1em}Local community members & 0.122 & 0.08 & -0.009 & 0.253\\
\hspace{1em}Local government & 0.061 & 0.07 & -0.055 & 0.176\\
\hspace{1em}International organisations & 0.061 & 0.076 & -0.065 & 0.186\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Bolivia Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-21-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Brazil}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{countryOrigin }\OperatorTok{==}\StringTok{ 'Brazil'}\NormalTok{)}
\CommentTok{# Table AMCE -- Brazil Only}
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Brazil Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-22}AMCE -- Brazil Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.03 & 0.054 & -0.118 & 0.058\\
\hspace{1em}Private arbitration & 0.021 & 0.044 & -0.052 & 0.093\\
\hspace{1em}Local courts & 0.091 & 0.05 & 0.009 & 0.174\\
\hspace{1em}United Nations & 0.082 & 0.047 & 0.004 & 0.16\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.107 & 0.051 & -0.191 & -0.023\\
\hspace{1em}Proportional to current emissions & -0.022 & 0.05 & -0.104 & 0.06\\
\hspace{1em}Proportional to history of emissions & 0.021 & 0.049 & -0.059 & 0.101\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.134 & 0.039 & 0.069 & 0.199\\
\hspace{1em}More penalty & 0.169 & 0.044 & 0.097 & 0.241\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.025 & 0.044 & -0.048 & 0.098\\
\hspace{1em}Twenty years & -0.012 & 0.047 & -0.09 & 0.065\\
\hspace{1em}Fifty years & -0.087 & 0.057 & -0.181 & 0.007\\
\hspace{1em}Never & -0.166 & 0.054 & -0.256 & -0.077\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.13 & 0.045 & 0.055 & 0.205\\
\hspace{1em}Fines & 0.169 & 0.042 & 0.1 & 0.238\\
\hspace{1em}Imprisonment & 0.032 & 0.055 & -0.058 & 0.122\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & 0.001 & 0.051 & -0.083 & 0.086\\
\hspace{1em}Local community members & 0.003 & 0.054 & -0.086 & 0.092\\
\hspace{1em}Local government & -0.017 & 0.053 & -0.105 & 0.071\\
\hspace{1em}International organisations & 0.087 & 0.049 & 0.008 & 0.167\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Brazil Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-23-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Chile}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{countryOrigin }\OperatorTok{==}\StringTok{ 'Chile'}\NormalTok{)}
\CommentTok{# Table AMCE -- Chile Only}
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Chile Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-24}AMCE -- Chile Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.021 & 0.063 & -0.125 & 0.083\\
\hspace{1em}Private arbitration & 0.055 & 0.049 & -0.026 & 0.136\\
\hspace{1em}Local courts & 0.166 & 0.062 & 0.064 & 0.268\\
\hspace{1em}United Nations & 0.089 & 0.07 & -0.026 & 0.204\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & 0.001 & 0.052 & -0.084 & 0.086\\
\hspace{1em}Proportional to current emissions & 0.054 & 0.045 & -0.021 & 0.128\\
\hspace{1em}Proportional to history of emissions & 0.003 & 0.054 & -0.086 & 0.092\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & -0.022 & 0.045 & -0.096 & 0.052\\
\hspace{1em}More penalty & 0.106 & 0.05 & 0.024 & 0.188\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.207 & 0.053 & 0.12 & 0.294\\
\hspace{1em}Twenty years & 0.083 & 0.049 & 0.003 & 0.163\\
\hspace{1em}Fifty years & 0.057 & 0.066 & -0.052 & 0.165\\
\hspace{1em}Never & -0.029 & 0.062 & -0.13 & 0.072\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.193 & 0.049 & 0.112 & 0.274\\
\hspace{1em}Fines & 0.103 & 0.044 & 0.03 & 0.176\\
\hspace{1em}Imprisonment & 0.013 & 0.052 & -0.073 & 0.099\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & 0.001 & 0.066 & -0.107 & 0.11\\
\hspace{1em}Local community members & 0.196 & 0.063 & 0.092 & 0.301\\
\hspace{1em}Local government & 0.119 & 0.058 & 0.024 & 0.215\\
\hspace{1em}International organisations & 0.069 & 0.061 & -0.03 & 0.169\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Chile Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-25-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Colombia}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{countryOrigin }\OperatorTok{==}\StringTok{ 'Colombia'}\NormalTok{)}
\CommentTok{# Table AMCE -- Colombia Only}
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Colombia Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-26}AMCE -- Colombia Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.054 & 0.05 & -0.137 & 0.029\\
\hspace{1em}Private arbitration & 0.057 & 0.053 & -0.03 & 0.144\\
\hspace{1em}Local courts & 0.078 & 0.051 & -0.005 & 0.162\\
\hspace{1em}United Nations & 0.132 & 0.054 & 0.043 & 0.221\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.017 & 0.053 & -0.105 & 0.07\\
\hspace{1em}Proportional to current emissions & 0.046 & 0.052 & -0.04 & 0.131\\
\hspace{1em}Proportional to history of emissions & 0.059 & 0.06 & -0.039 & 0.158\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.014 & 0.046 & -0.06 & 0.089\\
\hspace{1em}More penalty & 0.051 & 0.044 & -0.021 & 0.124\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.001 & 0.046 & -0.075 & 0.077\\
\hspace{1em}Twenty years & 0.005 & 0.052 & -0.081 & 0.091\\
\hspace{1em}Fifty years & -0.126 & 0.051 & -0.21 & -0.041\\
\hspace{1em}Never & -0.122 & 0.048 & -0.201 & -0.043\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.037 & 0.059 & -0.059 & 0.133\\
\hspace{1em}Fines & 0.068 & 0.052 & -0.019 & 0.154\\
\hspace{1em}Imprisonment & -0.072 & 0.053 & -0.159 & 0.015\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & -0.023 & 0.059 & -0.12 & 0.074\\
\hspace{1em}Local community members & 0.131 & 0.06 & 0.032 & 0.229\\
\hspace{1em}Local government & -0.003 & 0.049 & -0.083 & 0.078\\
\hspace{1em}International organisations & 0.094 & 0.051 & 0.009 & 0.178\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Colombia Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-27-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Costa Rica}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{countryOrigin }\OperatorTok{==}\StringTok{ 'Costa Rica'}\NormalTok{)}
\CommentTok{# Table AMCE -- Costa Rica Only}
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Costa Rica Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-28}AMCE -- Costa Rica Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.085 & 0.066 & -0.193 & 0.023\\
\hspace{1em}Private arbitration & -0.018 & 0.064 & -0.123 & 0.087\\
\hspace{1em}Local courts & 0.013 & 0.066 & -0.095 & 0.121\\
\hspace{1em}United Nations & 0.094 & 0.071 & -0.022 & 0.21\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.106 & 0.06 & -0.205 & -0.007\\
\hspace{1em}Proportional to current emissions & 0.058 & 0.054 & -0.031 & 0.146\\
\hspace{1em}Proportional to history of emissions & 0.015 & 0.066 & -0.094 & 0.123\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.083 & 0.044 & 0.01 & 0.155\\
\hspace{1em}More penalty & 0.135 & 0.042 & 0.066 & 0.204\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.108 & 0.063 & 0.004 & 0.211\\
\hspace{1em}Twenty years & -0.115 & 0.063 & -0.219 & -0.011\\
\hspace{1em}Fifty years & -0.183 & 0.06 & -0.282 & -0.084\\
\hspace{1em}Never & -0.201 & 0.061 & -0.303 & -0.1\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.139 & 0.051 & 0.055 & 0.223\\
\hspace{1em}Fines & 0.245 & 0.051 & 0.161 & 0.328\\
\hspace{1em}Imprisonment & 0.167 & 0.057 & 0.074 & 0.261\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & 0.032 & 0.063 & -0.071 & 0.136\\
\hspace{1em}Local community members & -0.081 & 0.074 & -0.203 & 0.042\\
\hspace{1em}Local government & 0.087 & 0.059 & -0.01 & 0.184\\
\hspace{1em}International organisations & -0.042 & 0.068 & -0.154 & 0.069\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Costa Rica Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-29-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Ecuador}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{countryOrigin }\OperatorTok{==}\StringTok{ 'Ecuador'}\NormalTok{)}
\CommentTok{# Table AMCE -- Ecuador Only}
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Ecuador Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-30}AMCE -- Ecuador Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.007 & 0.055 & -0.098 & 0.084\\
\hspace{1em}Private arbitration & 0.068 & 0.052 & -0.018 & 0.154\\
\hspace{1em}Local courts & 0.122 & 0.049 & 0.042 & 0.203\\
\hspace{1em}United Nations & 0.151 & 0.058 & 0.057 & 0.246\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.044 & 0.054 & -0.134 & 0.045\\
\hspace{1em}Proportional to current emissions & 0.114 & 0.05 & 0.032 & 0.196\\
\hspace{1em}Proportional to history of emissions & 0.085 & 0.055 & -0.005 & 0.175\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.01 & 0.052 & -0.075 & 0.095\\
\hspace{1em}More penalty & 0.085 & 0.05 & 0.003 & 0.167\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.085 & 0.063 & -0.018 & 0.188\\
\hspace{1em}Twenty years & 0.076 & 0.05 & -0.006 & 0.159\\
\hspace{1em}Fifty years & -0.017 & 0.05 & -0.1 & 0.065\\
\hspace{1em}Never & 0.036 & 0.066 & -0.073 & 0.144\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.079 & 0.049 & -0.002 & 0.16\\
\hspace{1em}Fines & 0.062 & 0.055 & -0.029 & 0.153\\
\hspace{1em}Imprisonment & -0.087 & 0.055 & -0.178 & 0.003\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & -0.037 & 0.054 & -0.125 & 0.051\\
\hspace{1em}Local community members & 0.063 & 0.055 & -0.027 & 0.153\\
\hspace{1em}Local government & 0.043 & 0.061 & -0.057 & 0.142\\
\hspace{1em}International organisations & 0.051 & 0.055 & -0.04 & 0.141\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Ecuador Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-31-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Mexico}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{countryOrigin }\OperatorTok{==}\StringTok{ 'Mexico'}\NormalTok{)}
\CommentTok{# Table AMCE -- Full Model }
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Mexico Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-32}AMCE -- Mexico Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.048 & 0.057 & -0.142 & 0.047\\
\hspace{1em}Private arbitration & 0.066 & 0.054 & -0.023 & 0.154\\
\hspace{1em}Local courts & 0.036 & 0.056 & -0.056 & 0.127\\
\hspace{1em}United Nations & 0.137 & 0.063 & 0.033 & 0.242\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.059 & 0.053 & -0.146 & 0.028\\
\hspace{1em}Proportional to current emissions & 0.039 & 0.052 & -0.046 & 0.123\\
\hspace{1em}Proportional to history of emissions & 0.132 & 0.057 & 0.038 & 0.227\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.017 & 0.055 & -0.073 & 0.107\\
\hspace{1em}More penalty & 0.011 & 0.052 & -0.074 & 0.096\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.107 & 0.059 & 0.011 & 0.204\\
\hspace{1em}Twenty years & -0.023 & 0.06 & -0.122 & 0.077\\
\hspace{1em}Fifty years & -0.032 & 0.058 & -0.127 & 0.063\\
\hspace{1em}Never & -0.137 & 0.062 & -0.24 & -0.035\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.033 & 0.054 & -0.056 & 0.122\\
\hspace{1em}Fines & 0.109 & 0.056 & 0.018 & 0.201\\
\hspace{1em}Imprisonment & -0.016 & 0.053 & -0.103 & 0.071\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & -0.038 & 0.068 & -0.15 & 0.074\\
\hspace{1em}Local community members & -0.038 & 0.062 & -0.141 & 0.064\\
\hspace{1em}Local government & -0.063 & 0.065 & -0.17 & 0.043\\
\hspace{1em}International organisations & 0.136 & 0.056 & 0.044 & 0.229\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Mexico Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-33-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Panama}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{countryOrigin }\OperatorTok{==}\StringTok{ 'Panama'}\NormalTok{)}
\CommentTok{# Table AMCE -- Panama Only}
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Panama Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-34}AMCE -- Panama Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.049 & 0.062 & -0.151 & 0.054\\
\hspace{1em}Private arbitration & 0.013 & 0.065 & -0.095 & 0.12\\
\hspace{1em}Local courts & 0.079 & 0.057 & -0.014 & 0.173\\
\hspace{1em}United Nations & 0.082 & 0.065 & -0.026 & 0.189\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.085 & 0.055 & -0.175 & 0.006\\
\hspace{1em}Proportional to current emissions & -0.043 & 0.05 & -0.124 & 0.039\\
\hspace{1em}Proportional to history of emissions & -0.038 & 0.051 & -0.122 & 0.046\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.065 & 0.05 & -0.017 & 0.147\\
\hspace{1em}More penalty & 0.189 & 0.052 & 0.104 & 0.274\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & -0.067 & 0.058 & -0.162 & 0.028\\
\hspace{1em}Twenty years & -0.045 & 0.064 & -0.151 & 0.06\\
\hspace{1em}Fifty years & -0.196 & 0.064 & -0.301 & -0.092\\
\hspace{1em}Never & -0.269 & 0.057 & -0.363 & -0.175\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.112 & 0.057 & 0.018 & 0.205\\
\hspace{1em}Fines & 0.129 & 0.051 & 0.045 & 0.214\\
\hspace{1em}Imprisonment & 0.072 & 0.061 & -0.028 & 0.172\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & 0.002 & 0.057 & -0.092 & 0.096\\
\hspace{1em}Local community members & 0.039 & 0.06 & -0.06 & 0.137\\
\hspace{1em}Local government & -0.001 & 0.059 & -0.099 & 0.097\\
\hspace{1em}International organisations & 0.034 & 0.059 & -0.064 & 0.131\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Panama Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-35-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Peru}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{countryOrigin }\OperatorTok{==}\StringTok{ 'Peru'}\NormalTok{)}
\CommentTok{# Table AMCE -- Peru Only}
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Peru Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-36}AMCE -- Peru Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.121 & 0.065 & -0.228 & -0.014\\
\hspace{1em}Private arbitration & 0.123 & 0.069 & 0.01 & 0.236\\
\hspace{1em}Local courts & 0.033 & 0.065 & -0.074 & 0.14\\
\hspace{1em}United Nations & 0.05 & 0.066 & -0.058 & 0.158\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.026 & 0.047 & -0.103 & 0.052\\
\hspace{1em}Proportional to current emissions & 0.013 & 0.055 & -0.077 & 0.103\\
\hspace{1em}Proportional to history of emissions & 0.086 & 0.057 & -0.008 & 0.18\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.079 & 0.052 & -0.006 & 0.164\\
\hspace{1em}More penalty & 0.044 & 0.05 & -0.037 & 0.126\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.014 & 0.071 & -0.104 & 0.131\\
\hspace{1em}Twenty years & -0.023 & 0.077 & -0.15 & 0.104\\
\hspace{1em}Fifty years & -0.12 & 0.07 & -0.235 & -0.006\\
\hspace{1em}Never & -0.12 & 0.062 & -0.222 & -0.018\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.093 & 0.075 & -0.03 & 0.215\\
\hspace{1em}Fines & 0.128 & 0.069 & 0.014 & 0.243\\
\hspace{1em}Imprisonment & 0.075 & 0.071 & -0.042 & 0.191\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & -0.099 & 0.063 & -0.202 & 0.004\\
\hspace{1em}Local community members & -0.119 & 0.068 & -0.232 & -0.007\\
\hspace{1em}Local government & 0.029 & 0.075 & -0.095 & 0.153\\
\hspace{1em}International organisations & 0.004 & 0.067 & -0.106 & 0.114\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Peru Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-37-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Elite Subsample}

\CommentTok{# Executive branch}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{groupOrigin }\OperatorTok{==}\StringTok{ 'Executive'}\NormalTok{)}
\CommentTok{# Table AMCE -- Executive branch only}
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Executive Branch Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-38}AMCE -- Executive Branch Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.034 & 0.05 & -0.116 & 0.049\\
\hspace{1em}Private arbitration & 0.057 & 0.039 & -0.008 & 0.121\\
\hspace{1em}Local courts & 0.067 & 0.043 & -0.003 & 0.137\\
\hspace{1em}United Nations & 0.096 & 0.047 & 0.019 & 0.174\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.036 & 0.039 & -0.101 & 0.028\\
\hspace{1em}Proportional to current emissions & 0.08 & 0.04 & 0.014 & 0.146\\
\hspace{1em}Proportional to history of emissions & 0.055 & 0.044 & -0.017 & 0.127\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.081 & 0.038 & 0.018 & 0.144\\
\hspace{1em}More penalty & 0.125 & 0.039 & 0.061 & 0.188\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.06 & 0.049 & -0.02 & 0.14\\
\hspace{1em}Twenty years & -0.023 & 0.048 & -0.102 & 0.056\\
\hspace{1em}Fifty years & -0.096 & 0.045 & -0.171 & -0.022\\
\hspace{1em}Never & -0.119 & 0.045 & -0.193 & -0.045\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.103 & 0.037 & 0.043 & 0.163\\
\hspace{1em}Fines & 0.125 & 0.044 & 0.053 & 0.197\\
\hspace{1em}Imprisonment & -0.054 & 0.04 & -0.12 & 0.013\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & -0.159 & 0.051 & -0.243 & -0.076\\
\hspace{1em}Local community members & -0.027 & 0.052 & -0.113 & 0.058\\
\hspace{1em}Local government & -0.03 & 0.045 & -0.104 & 0.044\\
\hspace{1em}International organisations & 0.021 & 0.043 & -0.048 & 0.091\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Executive Branch Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-39-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Legislative branch}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{groupOrigin }\OperatorTok{==}\StringTok{ 'Legislative'}\NormalTok{)}
\CommentTok{# Table AMCE -- Legislative branch only}
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Legislative Branch Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-40}AMCE -- Legislative Branch Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.069 & 0.054 & -0.157 & 0.02\\
\hspace{1em}Private arbitration & 0.018 & 0.065 & -0.09 & 0.126\\
\hspace{1em}Local courts & 0.044 & 0.062 & -0.058 & 0.147\\
\hspace{1em}United Nations & 0.065 & 0.06 & -0.034 & 0.164\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.158 & 0.052 & -0.243 & -0.073\\
\hspace{1em}Proportional to current emissions & -0.08 & 0.052 & -0.166 & 0.005\\
\hspace{1em}Proportional to history of emissions & -0.019 & 0.049 & -0.099 & 0.062\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.074 & 0.044 & 0.002 & 0.147\\
\hspace{1em}More penalty & 0.071 & 0.044 & -0.001 & 0.143\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.003 & 0.059 & -0.095 & 0.101\\
\hspace{1em}Twenty years & 0.002 & 0.058 & -0.093 & 0.097\\
\hspace{1em}Fifty years & -0.043 & 0.061 & -0.143 & 0.057\\
\hspace{1em}Never & -0.129 & 0.066 & -0.237 & -0.02\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.113 & 0.055 & 0.022 & 0.204\\
\hspace{1em}Fines & 0.145 & 0.054 & 0.056 & 0.233\\
\hspace{1em}Imprisonment & -0.021 & 0.058 & -0.116 & 0.075\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & -0.116 & 0.064 & -0.22 & -0.011\\
\hspace{1em}Local community members & -0.003 & 0.068 & -0.115 & 0.108\\
\hspace{1em}Local government & 0.024 & 0.063 & -0.08 & 0.128\\
\hspace{1em}International organisations & -0.001 & 0.065 & -0.108 & 0.105\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Legislative Branch Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-41-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Civil society}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{groupOrigin }\OperatorTok{==}\StringTok{ 'Civil Society'}\NormalTok{)}
\CommentTok{# Table AMCE -- Civil Society Only }
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Civil Society Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-42}AMCE -- Civil Society Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.02 & 0.031 & -0.071 & 0.032\\
\hspace{1em}Private arbitration & 0.073 & 0.032 & 0.021 & 0.126\\
\hspace{1em}Local courts & 0.127 & 0.031 & 0.076 & 0.179\\
\hspace{1em}United Nations & 0.166 & 0.031 & 0.115 & 0.218\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.043 & 0.031 & -0.093 & 0.007\\
\hspace{1em}Proportional to current emissions & 0.038 & 0.03 & -0.011 & 0.087\\
\hspace{1em}Proportional to history of emissions & 0.069 & 0.029 & 0.022 & 0.117\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.035 & 0.025 & -0.006 & 0.077\\
\hspace{1em}More penalty & 0.101 & 0.026 & 0.059 & 0.143\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.044 & 0.031 & -0.007 & 0.095\\
\hspace{1em}Twenty years & -0.053 & 0.031 & -0.103 & -0.003\\
\hspace{1em}Fifty years & -0.102 & 0.034 & -0.158 & -0.047\\
\hspace{1em}Never & -0.147 & 0.034 & -0.203 & -0.09\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.097 & 0.03 & 0.047 & 0.146\\
\hspace{1em}Fines & 0.13 & 0.028 & 0.085 & 0.176\\
\hspace{1em}Imprisonment & 0.049 & 0.03 & -0.002 & 0.099\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & 0.026 & 0.031 & -0.025 & 0.077\\
\hspace{1em}Local community members & 0.037 & 0.034 & -0.019 & 0.094\\
\hspace{1em}Local government & -0.008 & 0.033 & -0.063 & 0.047\\
\hspace{1em}International organisations & 0.066 & 0.029 & 0.019 & 0.113\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Civil Society Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-43-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Academia Only}
\NormalTok{results <-}\StringTok{ }\NormalTok{cjoint}\OperatorTok{::}\KeywordTok{amce}\NormalTok{(fm, }\DataTypeTok{data =}\NormalTok{ cj, }\DataTypeTok{cluster =} \OtherTok{TRUE}\NormalTok{,}
                        \DataTypeTok{respondent.id =} \StringTok{"Response.ID"}\NormalTok{, }
                        \DataTypeTok{design =}\NormalTok{ conjDesign, }\DataTypeTok{baselines =}\NormalTok{ baselines,}
                        \DataTypeTok{subset =}\NormalTok{ cj}\OperatorTok{$}\NormalTok{groupOrigin }\OperatorTok{==}\StringTok{ 'Academia'}\NormalTok{)}
\CommentTok{# Table AMCE -- Full Model }
\KeywordTok{tableAMCE}\NormalTok{(results, }\DataTypeTok{capt =} \StringTok{'AMCE -- Academia Only'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-44}AMCE -- Academia Only}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lcccc}
\toprule
Feature & Estimate & Std.Error & Lower & Upper\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are conflicts resolved?}}\\
\hspace{1em}(Baseline = Government bureaucracy) &  &  &  & \\
\hspace{1em}Informal norms & -0.089 & 0.031 & -0.139 & -0.039\\
\hspace{1em}Private arbitration & 0.053 & 0.03 & 0.003 & 0.103\\
\hspace{1em}Local courts & 0.082 & 0.028 & 0.036 & 0.129\\
\hspace{1em}United Nations & 0.09 & 0.034 & 0.034 & 0.146\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are costs distributed?}}\\
\hspace{1em}(Baseline = Rich countries pay more than poor countries) &  &  &  & \\
\hspace{1em}Only rich countries pay & -0.07 & 0.029 & -0.117 & -0.023\\
\hspace{1em}Proportional to current emissions & 0.029 & 0.025 & -0.012 & 0.07\\
\hspace{1em}Proportional to history of emissions & 0.013 & 0.03 & -0.037 & 0.062\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How are repeated violations punished?}}\\
\hspace{1em}(Baseline = Less penalty) &  &  &  & \\
\hspace{1em}Same & 0.068 & 0.025 & 0.027 & 0.11\\
\hspace{1em}More penalty & 0.112 & 0.027 & 0.067 & 0.156\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{How often will the agreement be renegotiated?}}\\
\hspace{1em}(Baseline = One year) &  &  &  & \\
\hspace{1em}Five years & 0.075 & 0.03 & 0.026 & 0.124\\
\hspace{1em}Twenty years & 0.039 & 0.03 & -0.009 & 0.088\\
\hspace{1em}Fifty years & -0.092 & 0.032 & -0.145 & -0.039\\
\hspace{1em}Never & -0.101 & 0.03 & -0.15 & -0.052\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{What punishments do they use?}}\\
\hspace{1em}(Baseline = None) &  &  &  & \\
\hspace{1em}Blacklist & 0.121 & 0.031 & 0.07 & 0.172\\
\hspace{1em}Fines & 0.158 & 0.028 & 0.112 & 0.204\\
\hspace{1em}Imprisonment & 0.087 & 0.032 & 0.034 & 0.14\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Who makes the rules?}}\\
\hspace{1em}(Baseline = Federal government) &  &  &  & \\
\hspace{1em}NGOs & 0 & 0.031 & -0.051 & 0.051\\
\hspace{1em}Local community members & 0.055 & 0.033 & 0.001 & 0.108\\
\hspace{1em}Local government & 0.062 & 0.031 & 0.011 & 0.112\\
\hspace{1em}International organisations & 0.105 & 0.032 & 0.053 & 0.157\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{ci=}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{point.size =} \FloatTok{.8}\NormalTok{, }\DataTypeTok{dodge.size =} \DecValTok{1}\NormalTok{,}
     \DataTypeTok{text.size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{main =} \StringTok{'AMCE -- Academia Only'}\NormalTok{,}
     \DataTypeTok{attribute.names =}\NormalTok{ attrs)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-45-1.pdf}

\newpage

\hypertarget{apsa-experimental-section-standard-report-for-experiments}{%
\section{APSA Experimental Section Standard Report for
Experiments}\label{apsa-experimental-section-standard-report-for-experiments}}

\hypertarget{hypothesis}{%
\subsection{Hypothesis}\label{hypothesis}}

The experiment was designed to study the characteristics of the climate
change mitigation treaties favored by Latin American elites.

\hypertarget{subjects-and-context}{%
\subsection{Subjects and Context}\label{subjects-and-context}}

The eligibility criteria for the research was to belong to one of the
four elite profiles listed below.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Members of the Executive branch}: members of regulatory
  agencies, politicians (mayors, governors, presidents), members of
  ministries and secretaries at the federal and state levels.
\item
  \textbf{Members of the Legislative branch}: legislators and staff
  officers from the federal and state level in the researched countries.
\item
  \textbf{Civil society}: environmental and energy-related NGO members;
  oil, renewables, and environmental solutions firm owners in the
  researched countries.
\item
  \textbf{Academics}: professors from energy and engineering departments
  of the most prestigious universities in the countries researched.
\end{enumerate}

We decided to include these profiles based on the stakes and influence
that such elites have on climate change policies. According to the IR
constructivist theories, academics have notable influence on our topic
of interest as they form the epistemic community around climate change
policies. Civil society members that have stakes on climate policies are
also influential, such as oil-extracting companies, lobby groups, and
environmental NGOs. Members of the Executive and Legislative branches
handle the decisions themselves, so their importance.

We selected ten countries to our sample: Argentina, Bolivia, Brazil,
Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru. Our
selection criteria were the impact of climate change on each nation,
their size and regional importance, and natural resources availability.
For each country, we built a dataset of potential respondents with at
least:

\begin{itemize}
\tightlist
\item
  150 potential legislative respondents
\item
  150 potential executive respondents
\item
  200 potential civil society respondents
\item
  200 potential academic respondents
\end{itemize}

These numbers represent ten times the number of respondents we were
aiming to interview by the end of the survey. The dataset was build from
October 5th to November 12th, 2018. We hired a team of enumerators that
searched the internet for people in the countries that fulfilled our
pre-determined elite profiles.

We ranked the possible respondents in two tiers. In the first tier we
placed people that we had complete information about their profiles:
office telephone numbers, emails, social media contacts, and so on. In
the second tier we included participants that had incomplete profiles,
such as those with only online information available. The dataset
including the first-tier respondents was randomly divided between
enumerators in Rio de Janeiro and São Paulo to avoid any eventual biases
from the collecting stage. Both groups conducted the interviews by phone
from November 12th to December 5th, 2018. The second tier dataset was
used for an online only version of the survey.

The response rate in each of the enumeration sites and in the online
only survey follows in the table below.

\vspace{.5cm}

\begin{longtable}[]{@{}lllrrr@{}}
\caption{Survey response rates.}\tabularnewline
\toprule
Country & Enumeration Place & Type & Total & Phone &
Online\tabularnewline
\midrule
\endfirsthead
\toprule
Country & Enumeration Place & Type & Total & Phone &
Online\tabularnewline
\midrule
\endhead
Argentina & Rio de Janeiro & Online and Phone & 300 & 33 &
17\tabularnewline
Bolivia & Rio de Janeiro & Online and Phone & 372 & 31 &
11\tabularnewline
Brazil & Rio de Janeiro & Online and Phone & 346 & 34 &
12\tabularnewline
Chile & Rio de Janeiro & Online and Phone & 417 & 35 & 12\tabularnewline
Colombia & Rio de Janeiro & Online and Phone & 445 & 35 &
21\tabularnewline
Costa Rica & Rio de Janeiro & Online and Phone & 409 & 32 &
11\tabularnewline
Ecuador & Rio de Janeiro & Online and Phone & 512 & 30 &
12\tabularnewline
Mexico & Rio de Janeiro & Online and Phone & 468 & 41 &
17\tabularnewline
Panama & Rio de Janeiro & Online and Phone & 291 & 30 &
14\tabularnewline
Peru & Rio de Janeiro & Online and Phone & 243 & 32 & 11\tabularnewline
\emph{TOTAL} & & Online and Phone & 3803 & 333 & 138\tabularnewline
& & & & &\tabularnewline
Argentina & Sao Paulo & Online and Phone & 292 & 48 & 16\tabularnewline
Bolivia & Sao Paulo & Online and Phone & 373 & 50 & 13\tabularnewline
Brazil & Sao Paulo & Online and Phone & 344 & 43 & 15\tabularnewline
Chile & Sao Paulo & Online and Phone & 416 & 41 & 15\tabularnewline
Colombia & Sao Paulo & Online and Phone & 448 & 42 & 19\tabularnewline
Costa Rica & Sao Paulo & Online and Phone & 412 & 44 & 20\tabularnewline
Ecuador & Sao Paulo & Online and Phone & 507 & 43 & 18\tabularnewline
Mexico & Sao Paulo & Online and Phone & 464 & 41 & 17\tabularnewline
Panama & Sao Paulo & Online and Phone & 291 & 50 & 19\tabularnewline
Peru & Sao Paulo & Online and Phone & 248 & 44 & 9\tabularnewline
\emph{TOTAL} & & Online and Phone & 3803 & 446 & 161\tabularnewline
& & & & &\tabularnewline
Argentina & & Online Only & 517 & & 19\tabularnewline
Bolivia & & Online Only & 132 & & 12\tabularnewline
Brazil & & Online Only & 1183 & & 52\tabularnewline
Chile & & Online Only & 470 & & 31\tabularnewline
Colombia & & Online Only & 522 & & 29\tabularnewline
Costa Rica & & Online Only & 325 & & 20\tabularnewline
Ecuador & & Online Only & 460 & & 37\tabularnewline
Mexico & & Online Only & 955 & & 29\tabularnewline
Panama & & Online Only & 319 & & 26\tabularnewline
Peru & & Online Only & 540 & & 25\tabularnewline
\emph{TOTAL} & & Online Only & 5569 & & 293\tabularnewline
\bottomrule
\end{longtable}

The response rate was 10.24 percent of the original population in the
telephone survey (779 of 7606 possible respondents). We had an attrition
of 61.62 percent from the telephone (779) to the online survey (299).
The response rate for the online only survey was 5.26 percent (293 of
5569 invited by email).

The conjoint experiment analyzed in this paper was in the online and
online-only dataset. Therefore, the relevant column for our data is the
last one.

\hypertarget{allocation-methods}{%
\subsection{Allocation Methods}\label{allocation-methods}}

\textbf{Random Assignment:} We programmed the experiment using a Python
application provided by \citet{strezhnev2013conjoint}. We translated the
original survey questions (as shown in the text) into Portuguese and
Spanish, and then embedded the PHP file with the randomization
parameters in a Qualtrics survey. The PHP code we used to randomize the
values of the attributes is available at the project's GitHub
repository: \url{http://github.com/danilofreire/climate-governance}.

For each attribute, the probability of selecting a given component
follows a uniform distribution function. The table below describes the
results.

\vspace{.5cm}

\begin{longtable}[]{@{}llr@{}}
\caption{Conjoint experiment attributes and their respective
probabilities.}\tabularnewline
\toprule
\textbf{Attribute} & \textbf{Values} &
\textbf{Probabilities}\tabularnewline
\midrule
\endfirsthead
\toprule
\textbf{Attribute} & \textbf{Values} &
\textbf{Probabilities}\tabularnewline
\midrule
\endhead
\textbf{Who makes the rules?} & International organizations &
1/5\tabularnewline
& Federal government & 1/5\tabularnewline
& Local government & 1/5\tabularnewline
& Local community members & 1/5\tabularnewline
& Non-governmental organizations & 1/5\tabularnewline
& &\tabularnewline
\textbf{Conflict resolution mechanism} & United Nations &
1/5\tabularnewline
& Government bureaucracy & 1/5\tabularnewline
& Local courts & 1/5\tabularnewline
& Private arbitration & 1/5\tabularnewline
& Informal norms & 1/5\tabularnewline
& &\tabularnewline
\textbf{Punishment} & Imprisonment & 1/4\tabularnewline
& Fines & 1/4\tabularnewline
& Blacklist & 1/4\tabularnewline
& None & 1/4\tabularnewline
& &\tabularnewline
\textbf{Punishment for repeated violations} & More penalty &
1/3\tabularnewline
& Same & 1/3\tabularnewline
& Less penalty & 1/3\tabularnewline
& &\tabularnewline
\textbf{Agreement costs} & Rich countries pay more than poor countries &
1/4\tabularnewline
& Proportional to history of emissions & 1/4\tabularnewline
& Proportional to current emissions & 1/4\tabularnewline
& Only rich countries pay & 1/4\tabularnewline
& &\tabularnewline
\textbf{Renegotiation} & Never & 1/5\tabularnewline
& Fifty years & 1/5\tabularnewline
& Twenty years & 1/5\tabularnewline
& Five years & 1/5\tabularnewline
& One year & 1/5\tabularnewline
\bottomrule
\end{longtable}

We added one logical restriction to the set climate change treaties:
\textbf{Punishment = None} can never appear together with
\textbf{Punishment for repeated violations = Less penalty}. The number
of possible treaties are the product of the attributes
(\(5\times 5 \times 4 \times 3 \times 4 \times 5 = 6,000\)) minus the
number of removed possibilities (\(5\times 5 \times 4 \times 5 = 500\)).
The total number of possible treaties is \(5,500\).

\hypertarget{treatments}{%
\subsection{Treatments}\label{treatments}}

\textbf{Descriptions of the intervention:} Our treatment was the
randomization of components in the conjoined climate mitigation
treaties. We provided the following description before the conjoint
experiment starts, in Spanish and Portuguese:

\vspace{.5cm}

\begin{verbatim}
For the following questions, read carefully the instructions below.

Imagine that your country would sign an international treaty to mitigate climate change. 
A climate mitigation treaty has, in general, the following attributes:

1. Who defines the rules? Which group will define the parameters for the treaty?
2. How are the conflicts that might happen when the treaty begin be resolved?
3. What punishments should be applied to ensure compliance?
4. How will repeated violations be punished?
5. How are costs for implementing the treaty be distributed?
6. How often the treaty has to be renegotiated?

In the following questions, you will see variations in treaties on these six attributes.
Please select the treaty that has the characteristics that you believe are best for your country.
\end{verbatim}

\vspace{.5cm}

The conjoint experiment consisted in comparing two treaties that vary in
these six attributes, repeating the application for seven times for each
respondent.

\noindent \textbf{Software:} To program the PHP randomization device we
used the Python application provided by \citet{strezhnev2013conjoint}.
We used Qualtrics to administer the survey.

\noindent \textbf{Delivery:} We repeated the conjoint experiment seven
times, to improve test power.

\noindent \textbf{Dataset description:} Each line in the dataset
represents a given treaty, varying for the selection status (selected
versus non-selected) for a given respondent. When a respondent finished
an entire response set, this adds 14 rows to the dataset. Seven rows
with the selected treaties and other seven rows with the non-selected
treaties.

\noindent \textbf{Deception:} We used no deception in this survey
experiment.

\hypertarget{results}{%
\subsection{Results}\label{results}}

\noindent \textbf{Outcome measures and covariates:} The main outcome is
a binary indicator for the selection of a given conjoined package. We
added two covariates to measure heterogeneous effects: \emph{Country}
and \emph{Elite type}.

\noindent \textbf{Questionnaire:} For the English translation of the
entire survey instrument, with both the telephone and the online
components, see the attachment below.

\noindent \textbf{Statistical analysis:} We fit a marginal means
estimator and an AMCE estimator. The estimation conditions the results
within subjects and the presented conjoined packages. The results are
available in sections \ref{sec:features} and \ref{sec:amce}.

\noindent \textbf{Missing data and attrition:} Conditional on having
started the conjoint experiment, for each task we had the following
completion rates:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{barplot}\NormalTok{(}\DecValTok{100}\OperatorTok{*}\KeywordTok{table}\NormalTok{(cj}\OperatorTok{$}\NormalTok{task)}\OperatorTok{/}\KeywordTok{max}\NormalTok{(}\KeywordTok{table}\NormalTok{(cj}\OperatorTok{$}\NormalTok{task)), }\DataTypeTok{xlab =} \StringTok{'Conjoint task'}\NormalTok{, }\DataTypeTok{ylab =} \StringTok{'Percentage completed'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{appendix-institutional-design-climate-policy_files/figure-latex/unnamed-chunk-46-1.pdf}

\hypertarget{other-information}{%
\subsection{Other information}\label{other-information}}

\noindent \textbf{IRB:} This research received IRB approval from Brown
University (Protocol 2195/2018) and Fundação Getulio Vargas (Protocol
83/2018).

\noindent \textbf{Pre-registration:} The result was not pre-registered.

\noindent \textbf{Funding:} The research was funded by Konrad Adenauer
Stiftung (KAS). KAS provided EUR\$ 55,000.00 for this research. They
have not interfered in the research design and in the question choices.

\noindent \textbf{Replication materials:} Available at
\url{http://github.com/danilofreire/climate-governance}.

% More bibliography
\renewcommand\refname{Bibliography}
\bibliography{references.bib}

\end{document}

### 2020-05-27 supplementary-material/paper.R

@@ -1,0 +1,359 @@
+###################################################################
+## Replication code for:                                         ##
+## "Institutional Design and Elite Support for Climate Policies: ##
+## Evidence from Latin American Countries"                       ##
+## Danilo Freire, Umberto Mignozzetti, and David Skarbek         ##
+## Forthcoming, Journal of Experimental Political Science        ##
+## May 2020                                                      ##
+###################################################################
+
+# The R code below replicates the analyses included in the main paper.
+# The same code is also available in the Supplementary Material, which
+# contains additional estimations and the reporting standards
+# recommended by the APSA Organized Section on Experimental Research.
+
+# For any questions regarding the replication data or files, please
+# contact Danilo Freire (danilofreire@gmail.com) or Umberto Mignozzetti
+# (umberto.mig@fgv.br).
+
+
+## Load packages and data
+
+# Install and load necessary packages
+packages <- c("plm", "tidyverse", "clusterSEs",
+              "sp", "cregg", "cjoint")
+new_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
+if (length(new_packages)) install.packages(new_packages)
+
+library(plm); library(tidyverse)
+library(clusterSEs); library(sp)
+library(cregg); library(cjoint)
+
+# Load dataset - the object name is cj
+load("freire-mignozzetti-skarbek.RData")
+
+
+## Descriptive statistics
+
+# Select variables
+aux <- cj %>%
+  select(Response.ID, countryOrigin, groupOrigin,
+         LocationLongitude, LocationLatitude) %>%
+  unique()
+
+# Country
+tab <- data.frame(table(aux$countryOrigin))
+names(tab) <- c("Country", "Frequency")
+p <- ggplot(data = tab, aes(x = Country, y = Frequency)) +
+  geom_bar(stat = "identity") +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "black") +
[…]

### 2020-05-27 manuscript/manuscript-climate-policy.tex
Update README.md, add Dataverse DOI

--- 2019-11-21 manuscript/institutional-design-climate-policy.tex
@@
 \usepackage[english]{babel}
-\usepackage[authoryear]{natbib}
+\usepackage{natbib}
 \usepackage{babelbib}
@@
 Special thanks to Natalia Liberato, Lucas Mingardi, Ingrid Oliveira, Catarina Roman, Leticia Santana, and Larissa Santos for their excellent research assistance.
+We would also like to thank two anonymous reviewers for their helpful comments and suggestions.
 This research received IRB approval from Brown University (Protocol 2195/2018) and Funda\c{c}\~{a}o Getulio Vargas (Protocol 83/2018).
 We acknowledge financial support from the Konrad Adenauer Stiftung Latin American Regional Programme for Energy Security and Climate (EKLA-KAS) and declare there are no conflicts of interest.
-The data, code, and additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.}}
+The data, code, and any additional materials required to replicate all analyses in this article are available at the Journal of Experimental Political Science Dataverse within the Harvard Dataverse Network, at: \href{https://doi.org/10.7910/DVN/VTA5OA}{\texttt{doi:10.7910/DVN/VTA5OA}}.}}
 
-\author{Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, \href{mailto:danilo_freire@brown.edu}{\texttt{danilo\_freire@brown.edu}}, \href{http://danilofreire.github.io}{\texttt{http://danilofreire.github.io}}, \href{http://twitter.com/danilofreire}{\texttt{http://twitter.com/danilofreire}}, Voice: +1 (401) 584-2494.
+\author{Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, \href{mailto:danilo_freire@brown.edu}{\texttt{danilo\_freire@brown.edu}}, \href{http://danilofreire.github.io}{\texttt{http://danilofreire.github.io}}.
 Corresponding author.}
@@
 
-\date{November 20, 2019}
+\date{\today}
 
@@
 \begin{abstract}
-\onehalfspacing
+\singlespacing
 \noindent 
 Which institutional features do Latin American elites favor for local climate change policies?
-Climate change mitigation requires active local level implementation, but it remains unclear which institutional arrangements maximize the support for environmental rules.
+Climate change mitigation requires active local level implementation, but it remains unclear which institutional arrangements maximize support for environmental rules.
 In this paper, we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate institutional designs drawn from a pool of 5,500 possible local climate governance arrangements.
@@
 For instance, the Paris Agreement relies on Nationally Determined Contributions (NDCs), a set of greenhouse gas reduction targets each member state voluntarily pledges to achieve \citep{winning2019nationally}.
-This decentralization increases the importance of local stakeholders in climate negotiations, and studies have shown that the behavior of elite groups -- specially that of advocacy coalitions and political networks -- largely explain countries' climate policy performance \citep{jahn2016politics, karapin2012explaining}.
+This decentralization increases the importance of local stakeholders in climate negotiations, and studies have shown that the behavior of elite groups -- especially that of advocacy coalitions and political networks -- largely explain countries' climate policy performance \citep{jahn2016politics, karapin2012explaining}.
 Elites can advance or constrain climate agreements using `societal steering' strategies such as capacity building and rule setting, thus acting as \textit{de facto} veto players in local environmental policies \citep{andonova2009transnational, bulkeley2014transnational}.
 
-Although research on public opinion and climate agreements has increased significantly in the last years \citep[e.g.,][]{aklin2013understanding, bechtel2013mass, bechtel2017interests, mildenberger2017beliefs}, elite preferences are not well documented in the literature.
+Although research on public opinion and climate agreements has increased significantly in recent years \citep[e.g.,][]{aklin2013understanding, bechtel2013mass, bechtel2017interests, mildenberger2017beliefs}, elite preferences are not well documented in the literature.
 This is a significant omission considering that recent work has stressed the impact of elite coalitions in areas such as global finance and international banking regulation \citep[e.g,][]{chalmers2017banks, pagliari2014leveraged}.
-Elites in developing countries are specially understudied, despite the fact that emerging economies account for 63\% of the world's carbon emissions \citep{busch2015developing}.
+Elites in developing countries are especially understudied, despite the fact that emerging economies account for 63\% of the world's carbon emissions \citep{busch2015developing}.
 It is unclear which local climate strategies face lower internal resistance from these groups, or whether their environmental preferences are fundamentally different from those of their developed countries counterparts \citep[28]{aklin2013understanding}.
 
-We help remedy this gap by assessing which local climate mitigation initiatives Latin American elites are willing to support.
-In our survey experiment, we asked 654 respondents -- academics, members of the executive power, legislators, businesspeople and members of non-governmental organizations -- to select their preferred components for local climate mitigation among 7 repetitions of binary choices.
+We remedy this gap by assessing which local climate mitigation initiatives Latin American elites are willing to support.
+In our survey experiment, we asked 654 respondents -- academics, members of the executive power, legislators, businesspeople, and members of non-governmental organizations -- to select their preferred components for local climate mitigation among seven repetitions of binary choices.
 We vary the agreements across six dimensions commonly debated in the climate change and institutional design literatures: rule-making capabilities \citep{dubash2013developments, massey2014climate}; conflict resolution mechanisms \citep{huntjens2012institutional, ostrom2014polycentric}; enforcement methods \citep{barrett2008climate}; punishment for repeated violators \citep{ostrom1990governing}; cost sharing \citep{bansak2017europeans,bechtel2013mass}; and agreement duration \citep{copelovitch2014design, marcoux2009institutional}.
-Variations in any of those features can substantially change the outcomes of climate institutions \citep{bodin2017collaborative, ostrom2014polycentric}.
+Variations in any of those features can substantially change the outcomes of climate institutions \citep{bodin2017collaborative, ostrom2014polycentric}.\footnote{As we discuss below, we take a parsimonious approach in regards to the number of dimensions included in the experiment.
+In the Supplemental Material, we show that these components are commonly debated by Latin American elites.}
 
@@
 Survey participants also want both international institutions and local courts to mediate conflicts, but they are skeptical about non-governmental organizations and consistently reject informal norms as an instrument to solve disputes.
-The results lend support to theories that define climate governance as a `regime complex' \citep{colgan2012punctuated, keohane2011regime}, that is, `an array of partially overlapping and non-hierarchical institutions govern a particular issue area' \citep[279]{raustiala2004regime}.
+The results lend support to theories that define climate governance as a `regime complex' \citep{colgan2012punctuated, keohane2011regime}, that is, `an array of partially overlapping and non-hierarchical institutions [that] govern a particular issue area' \citep[279]{raustiala2004regime}.
 Moreover, following the spirit of the Paris Accords, the regime complex framework stresses the role of elite perceptions on the relationship between local and global climate mitigation efforts.
@@
 \citet{mildenberger2017beliefs} and \citet{rosendorff2001optimal} posit that when compliance is hard to observe, incomplete contracts are superior as they avoid unnecessary punishments and improve long-run cooperation stability.
-\citet{keohane2011regime}, in turn, argue that non-hierarchical international rulings help states to avoid gridlocks by reducing contracting costs and embracing `problem diversity', in which each particular climate problem requires a specific solution.
-Our results corroborate that flexible regime designs are decisive to foster international cooperation.
+\citet{keohane2011regime}, in turn, argue that non-hierarchical international rulings help states avoid gridlocks by reducing contracting costs and embracing `problem diversity', in which each particular climate problem requires a specific solution.
+Our results suggest that flexible regime designs are decisive to foster international cooperation.
 
@@
 The results are consistent with the Latin American tradition of heavier reliance on the state than on self-governed solutions, but respondents also believe that both international and subnational institutions should play a role in local climate policy design.
-The data provide new insights on how Latin American policy-makers can form domestic coalitions and which climate mitigation agreement faces lower resistance from potential veto players \citep{beiser2019commitment, hovi2019club}.
+The data offer new insights on how Latin American policy-makers can form domestic coalitions and provides a first exploration of how regional elites understand the nature of climate change mitigation efforts.
 
@@
 The individual selects one of them.
-As the attributes are randomized, we can estimate how individuals value each of the conjoined elements relative to their alternatives.\footnote{We note, however, that our conjoint experiments do not allow us to infer the average level of attribute support in the sample.
-Since our design relies on forced choices, estimates should always be interpreted in comparison to the other attributes in the alternative agreement bundle.}
+As the attributes are randomized, we can estimate how individuals value each of the conjoined elements relative to their alternatives.\footnote{We note, however, that our research design only allows us to infer the average level of attribute support within the context of the conjoint experiment.
+Since our design relies on forced choices, respondents are required to choose 50\% of the agreement bundles presented to them.
+In this respect, the findings we observe here may be different from what would see should respondents vote yes or no on a single package, without another agreement bundle for comparison.
+We elaborate on this issue in the discussion section and in the Supplementary Material.}
 
@@
 We started by gathering information on potential interviewees.
-For each country, we collected the profiles of 100 members of the Executive, 100 members of the Legislative, 150 academics in the energy sector and 150 members of the civil society.
+For each country, we collected the profiles of 100 members of the executive branch, 100 members of the legislative branch, 150 academics in the energy sector and 150 members of the civil society.
 We then sampled these profiles until we achieved a minimum of 10\% of responses within each group.
 We ran our survey both online and by telephone, collecting information on the climate change agreements and other related questions in a non-intrusive manner \citep{loewen2010help}.
-We had two teams of enumerators, one based in S\~{a}o Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers.
+We had two teams of enumerators, one based in S\~{a}o Paulo and another based in Rio de Janeiro, Brazil, composed of Portuguese and Spanish native speakers.
 Please refer to the Supplementary Material for more information about the sampling process and descriptive statistics.
-
-The hypothetical climate change agreements include six attributes: 1) which organizations defines the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated.
-Table~\ref{tab:categories} describes the values we included in each treaty attribute.\footnote{A discussion on the theoretical underpinnings of our choice of attributes is available in the Supplementary Material.}
+\\
 
@@
 
+The hypothetical climate change agreements include six attributes: 1) which organizations define the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated.
+Table~\ref{tab:categories} describes the values we included in each treaty attribute.\footnote{A discussion on the theoretical underpinnings of our choice of attributes is available in the Supplementary Material.}
+
 We give no prior indication of whether a certain value is more prevalent in actual agreements to elicit truthful responses from the interviewees.
@@
 \end{figure}
+
+In designing the experiment, we attempted to strike a balance between realism and parsimony.
+Local implementation of climate agreements may vary among a wide set of dimensions, but including too many attributes in the conjoint design would significantly increase cognitive load and induce respondent fatigue \citep{pullman1999comparison}.
+Subjects also use decision heuristics when the number of conjoint attributes is high, such as focusing on the dimensions they care the most or on the ones they see first.
+These issues lead to uninformative experimental results \citep{lines2004information}.
+In this respect, we decided to restrict the total of categories at the expense of some loss of external validity.
+However, if individuals found our choice of attributes too unrealistic, we would expect a high number of non-responses in the survey.
+Our data show that this was not the case.
+Conditional on having answered the first task, completion rates for the last task were around 90\% across countries and elite types, which suggests that respondents did engage in the experiment and that the offered options made intuitive sense to them.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 	\centering
@@
 We note that Latin American elites support multiple governance levels simultaneously, which suggests that they are willing to include separate political spheres into a single climate policy design.
-Local governments (49.8\%, SE = 1.2) and federal governments (48.6\%, SE = 1.3) are slightly preferred over NGOs, yet the difference between them is not statistically significant.
+Local governments (49.8\%, SE = 1.2) and federal governments (48.6\%, SE = 1.3) are slightly preferred over NGOs, yet the difference between the former two is not statistically significant.
 Non-governmental organizations are the least preferred option for local climate change rule-making with 45.5\% (SE = 1.3).
@@
 
-Regarding local agreements' renegotiations, respondents are interested in a balance between stability and flexibility.
+When we analyze local agreements' renegotiations, respondents are interested in a balance between stability and flexibility.
 Interviewees reject agreements that either cannot be modified or that last for 50 years.
@@
 
-We observe higher variance in the responses related to the frequency of treaty renegotiations and in those concerning the methods of conflict resolution.
-We believe that both items vary considerably because elites are concern about the region's long history of political and economic volatility.
-Elites might be divided over which strategy is best to achieve climate mitigation goals.
-On the one hand, some respondents prefer long-term agreements to induce stronger commitment to fight climate change.
-On the other hand, different groups of respondents may expect continuing instability in Latin America and therefore prefer to make agreements more flexible to cope with future chances.
-Moreover, Latin America's historically low levels of trust in public institutions may have spurred elites to have divergent opinions about which institution should be responsible for punishing non-compliers.
-
 We also examine how our results vary across countries and types of elites.\footnote{The number of respondents in each elite subgroups does not vary significantly per country, with the exception of members of the civil society.
@@
 
-\begin{figure}[hbpt]
+\begin{figure}[htbp]
 	\centering
@@
 This is an important point and might have far-reaching consequences for environmental policy design.
-The lack of coordination on rule-making responsibilities can give rise to decision cycles, lowering the chance that a single, favourite climate change solution emerges.
+The lack of coordination on rule-making responsibilities can give rise to decision cycles, lowering the chance that a single, favorite climate change solution emerges.
 Nevertheless, these dissensions might be resolved by decentralization, boosting the idea that flexible regime complexes, such as polycentric governance schemes, might provide a solution to gridlocks.
@@
 Differences emerge in two of the six attributes.
-Academics and members of the civil society are skeptical about the role of federal government in local climate policy-making, while members of the executive and legislative --- part of the government themselves --- have a more positive view of national institutions.
+Academics and members of the civil society are skeptical about the role of federal government in local climate policy-making, while members of the executive and legislative branches --- part of the government themselves --- have a more positive view of national institutions.
 The differences, however, are not large.
-Second, members of the legislative prefer rich countries to bear the larger part of agreement costs (58.4\%, SE = 3.5).
+Second, members of the legislative branch prefer rich countries to bear the larger part of agreement costs (58.4\%, SE = 3.5).
 This provides evidence for the idea of historical responsibility for climate protection, an argument which developing countries have recently brought to climate negotiations \citep{muller2009differentiating, friman2015agreement}.
@@
 
-Our results have several theoretical and practical implications.
-The findings we present here suggest there is considerable scope for new studies on local challenges to global governance, specially in underrepresented regions.
-Our analysis can be extended to examine if the Latin American public has the same opinion on multilevel arrangements as do the elites; and if not, it would be important to know what explains the mismatch between groups \citep{luna2005political}.
-Moreover, future work may address whether elites in other regions also understand climate policy as a regime complex, in which different actors play a constructive yet decentralized role in policy-making.
-
 With regards to environmental policies, we identify that Latin American elites are interested in incorporating different political actors and in strengthening the role of international organizations in climate governance.
@@
 
+We believe our findings can be extended in many ways.
+The research design we employ here provides only a first step towards understanding the behavior of local elites and their preferences regarding climate change policies.
+Our use of forced choices implies that we could not measure the overall level of attribute support in the elite population, when respondents can choose any agreement they prefer without constraints.
+Moreover, further research could better adjudicate between rules associated with the global treaty negotiations themselves and those concerning domestic politics.
+For instance, future studies may analyze how each country's specific legal framework imposes constraints we did not include in our experiment, and thus provide fine-grained information about local attitudes towards climate agreements.
+Moreover, scholars may employ other types of research designs, such as vignette experiments or qualitative interviews, to assess the robustness of our results.
+Lastly, our analysis can also be extended to examine if the Latin American public has the same opinion on multilevel arrangements as do the elites; and if not, it would be important to know what explains the mismatch between groups \citep{luna2005political}.
+
 \section*{Supplementary Material}
@@
 
-For supplementary material for this article, please visit \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.
+For supplementary material for this article, please visit \url{http://github.com/danilofreire/climate-governance}.
 
+\nocite{freire2020replication}
 \bibliographystyle{apalike}
